### 2021-03-11 Abstract/main.tex
Add some pre-written text
Build the general strucure of the paper and add some pre-written text
for some of the sections.

\begin{abstract}
    The main focus of this research is the construction of a 3-player game theoretic model between two queueing systems and a service that distributes individuals to them. The resultant model will then be used to explore dynamics between all players.

    The first aspect of this work is the development of a queueing system with two consecutive waiting spaces. The strategic managerial behaviour corresponds to how individuals use these waiting spaces. Two modelling techniques were used: discrete event simulation and Markov chains. The state probabilities of the Markov chain system have been used to extract the performance measures of the queueing model (e.g. mean time in each waiting room, mean number of individuals in each room, etc.).

    A 3-player game theoretic model is proposed between the two queueing systems and the service that distributes individuals to them. In particular this can be seen as a 2-player normal-form game where the utilities are determined by a third player with its own strategies and objectives. A backwards induction technique is used to get the utilities of the normal-form game between the two queueing systems.

    This particular system can be applied in a healthcare scenario where it captures the emergent behaviour between, for example, the Emergency Medical Service (EMS) and the Emergency Department (ED). This will be used to investigate the impact of target measures on patient welfare.
\end{abstract}

### 2021-03-11 MarkovChain/expressions_from_pi/main.tex
Add some pre-written text
Build the general strucure of the paper and add some pre-written text
for some of the sections.

\subsection{Performance Measures}
One may easily derive the average number of individuals that are at any given state 
using \( pi \). 
The average number of individuals in state \( i \) can be calculated by multiplying 
the number of individuals that are present in state \( i \) with the probability 
of being at that particular state (i.e \(\pi_i (u_i + v_i)\)). 
Using this logic it is possible to calculate any performance measures that are related 
to the mean number of individuals in the system.

Average number of people in the system: 
\begin{equation}
    L = \sum_{i=1}^{|\pi|} \pi_i (u_i + v_i)
\end{equation}

Average number of people in the service centre: 
\begin{equation}
    L_H = \sum_{i=1}^{|\pi|} \pi_i v_i
\end{equation}

Average number of people in the buffer centre:
\begin{equation}
    L_A = \sum_{i=1}^{|\pi|} \pi_i u_i
\end{equation}

Consequently getting the performance measures that are related to the duration of 
time is not as straightforward. 
Such performance measures are the mean waiting time in the system and the mean time 
blocked in the system. 
Under the scope of this study three approaches have been considered to calculate these 
performance measures; a direct approach, a recursive algorithm and consequently a
closed-form formula.

The research question that needs to be answered here is: ``When a class 1/2 
individuals enters the system, what is the expected time that they will have to 
wait?''. 
In order to formulate the answer to that question one needs to consider all possible 
scenarios of what state the system can be in when an individual arrives. 
Furthermore, different formulas arises for class 1 individuals 
and a different one for class 2 individuals.

\subsubsection{Mean waiting time} 
Upon closer inspection of the recursive formula a more compact formula can arise. 
The equivalent closed-form formula eliminates the need for recursion and thus makes 
the computation of waiting times much more efficient. 
Just like in the recursive part there are two formulas; one for \textit{class 1} 
and one for class 2 individuals. 
The formulas are given by:

\begin{equation} \label{eq:closed_form_waiting_others}
    W^{(1)} = \frac{\sum_{\substack{(u,v) \, \in S_A^{(1)} \\ v \geq C}} 
    \frac{1}{C \mu} \times (v-C+1) \times \pi(u,v)}{\sum_{(u,v) \, 
    \in S_A^{(1)}} \pi(u,v)}
\end{equation}

\begin{equation}\label{eq:closed_form_waiting_ambulance}
    W^{(2)} = \frac{\sum_{\substack{(u,v) \, \in S_A^{(2)} \\ min(v,T) \geq C}} 
    \frac{1}{C \mu} \times (\min(v+1,T)-C) \times \pi(u,v)}{\sum_{(u,v) \, 
    \in S_A^{(2)}} \pi(u,v)}
\end{equation}

Note here that the summation, in both equations \ref{eq:closed_form_waiting_others} 
and \ref{eq:closed_form_waiting_ambulance}, goes through all states in the set of 
accepting 
states of either class 1 or class 2 individuals respectively, where a wait 
incurs. 
In equation \ref{eq:closed_form_waiting_others} that includes all states \((u,v)\) 
in the set of accepting states of class 1 individuals such that \( v \geq C\); i.e. 
whenever an arrival occurs and the system is at a state where the number of individuals 
in the system is more than or equal to $C$. 
Consequently, for the states that are included in the summation the expression 
\( v-C+1 \) indicates the amount of people in service one would have to wait for 
upon arrival at the hospital.

Additionally, the minimisation function in equation 
\ref{eq:closed_form_waiting_ambulance} 
ensures that when a class 2 individual arrives at any state 
that is greater than the predetermined threshold, the wait that the individual will 
have to endure remains the same. 
In essence, the expression \(\min(v+1,T) - C\) returns the number of people in line 
in front of a particular individual upon arrival.

\subsubsection{Overall Waiting Time}

Consequently, the overall waiting time should can be estimated by a linear combination 
of the waiting times of class 1 and class 2 individuals. 
The overall waiting time can be then given by the following equation where \(c_1\) 
and \(c_2\) are the coefficients of each individual's type waiting time:

\begin{equation}\label{overall_waiting_time_coeff}
    W = c_1 W^{(1)} + c_2 W^{(2)}
\end{equation}

The two coefficients represent the proportion of individuals of each type that 
traversed through the model. 
Theoretically, getting these percentages should be as simple as looking at the arrival 
rates of each type but in practise if the service centre or the buffer centre 
is full, some individuals may be lost to the system. 
Thus, one should account for the probability that an individual is lost to the system. 
This probability can be easily calculated by using the two sets of accepting states 
\(S_A^{(2)}\) and \(S_A^{(1)}\) defined earlier in equations.
Let us define here the probability, for either class type, that an individual 
is not lost in the system by:

\begin{equation*}
    P(L'_1) = \sum_{(u,v) \, \in S_A^{(1)}} \pi(u,v) \hspace{2cm}
    P(L'_2) = \sum_{(u,v) \, \in S_A^{(2)}} \pi(u,v)
\end{equation*}

Having defined these probabilities one may combine them with the arrival rates of 
each class type in such a way to get the expected proportions of class 1 and 
class 2 individuals in the model. 
Thus, by using these values as the coefficient of equation 
\ref{overall_waiting_time_coeff} 
the resultant equation can be used to get the overall waiting time. 
Note here that the equation below gets the overall waiting time for both the recursive 
and the closed-form formula.

\begin{equation}\label{overall_waiting_time}
    W = \frac{\lambda_1 P(L'_1)}{\lambda_2 P(L'_2) + \lambda_1 P(L'_1)} W^{(1)} + 
    \frac{\lambda_2 P(L'_2)}{\lambda_2 P(L'_2) + \lambda_1 P(L'_1)} W^{(2)}
\end{equation}

\subsubsection{Mean blocking time}
Unlike the waiting time, the blocking time is only calculated for class 2 individuals.  
That is because class 1 individuals cannot be blocked. 
Thus, one only needs to consider the pathway of class 2 individuals to get the 
mean blocking time of the system. 
Blocking occurs at states \((u,v)\) where \(u > 0 \). 
Thus, the set of blocking states can be defined as:

\begin{equation*}
    S_b = \{(u,v) \in S \; | \; u > 0\}
\end{equation*}

In order to not consider individuals that will be lost to the system, the set of 
accepting states needs to be taken into account. The set of accepting states is given by:

\begin{equation*}
    S_A^{(2)}=
    \begin{cases}
        \{(u, v) \in S \; | \; u < M \} & \textbf{if } T \leq N\\
        \{(u, v) \in S \; | \; v < N \} & \textbf{otherwise}
    \end{cases}
\end{equation*}

For the waiting time formula,
the mean sojourn time for each state was considered,
ignoring any arrivals. Here, the same approach is used but ignoring only class 2
arrivals. That is because for the waiting time formula, once an individual enters 
the service centre (i.e. starts waiting) any individual arriving after them will 
not affect their
pathway. That is not the case for blocking time. When a class 2 individual is 
blocked, 
any class 1 individual that arrives will cause the blocked individual to remain 
blocked for more time. Therefore, class 1 arrivals are considered here:

\begin{equation}\label{eq:time_in_state_blocking_time}
    c(u,v) = 
    \begin{cases}
        \frac{1}{\min(v,C) \mu}, & \text{if } v = C\\
        \frac{1}{\min(v,C) \mu + \lambda_1}, & \text{otherwise}
    \end{cases}
\end{equation}

In equation \ref{eq:time_in_state_blocking_time}, both service completions and 
class 1 arrivals are considered. 
Thus, from a blocked individual's perspective whenever the system moves from one 
state \((u,v)\)
to another state it can either:

\begin{itemize}
    \item be because of a service being completed: we will denote the probability 
    of this happening by \(p_s(u,v)\). 
    \item be because of an arrival of an individual of class 1: denoting such 
    probability by \(p_o(u,v)\).
\end{itemize}
The probabilities are given by:

\begin{equation*}
    p_s(u,v) = \frac{\min(v,C)\mu}{\lambda_1 + \min(v,C)\mu}, \qquad
    p_o(u,v) = \frac{\lambda_1}{\lambda_1 + \min(v,C)\mu}
\end{equation*}

Having defined \(c(u,v)\) and \(S_b\) a formula for the blocking time that is
expected to occur at each state can be given by:

\begin{equation}\label{eq:blocking-time-at-each-state}
    b(u,v) = 
    \begin{cases} 
        0, & \textbf{if } (u,v) \notin S_b \\
        c(u,v) + b(u - 1, v), & \textbf{if } v = N = T\\
        c(u,v) + b(u, v-1), & \textbf{if } v = N \neq T \\
        c(u,v) + p_s(u,v) b(u-1, v) + p_o(u,v) b(u, v+1), & \textbf{if } u > 0 
        \textbf{ and } v = T \\
        c(u,v) + p_s(u,v) b(u, v-1) + p_o(u,v) b(u, v+1), & \textbf{otherwise} \\
    \end{cases}
\end{equation}

Equation 
(\ref{eq:blocking-time-at-each-state}) will not be solved recursively. 
A direct approach will be used to solve this equation here. 
By enumerating all equations of (\ref{eq:blocking-time-at-each-state}) for all 
states \((u,v)\) that belong in \(S_b\) 
a system of linear equations arises where the unknown variables are all the \(b(u,v)\)
terms.
For instance, let us consider a Markov model where \(C=2, T=3, N=6, M=2\). 
The Markov model is shown in Figure \ref{fig:example-algeb-blocking}
and the equivalent equations are 
(\ref{eq:first_eq_of_blocking_example})-(\ref{eq:last_eq_of_blocking_example}).
The equations considered here are only the ones that correspond to the blocking 
states.

\begin{multicols*}{2}
    \begin{figure}[H]
        \scalebox{0.50}{\input{MarkovChain/expressions_from_pi/example_model_2362/main.tex}}
        \caption{Example of Markov chain}
        \label{fig:example-algeb-blocking}
    \end{figure}
    \columnbreak
    \begin{align}
        b(1,2) &= c(1,2) + p_o b(1,3) \label{eq:first_eq_of_blocking_example} \\
        b(1,3) &= c(1,3) + p_s b(1,2) + p_o b(1,4) \\
        b(1,4) &= c(1,4) + b(1,3) \\
        b(2,2) &= c(2,2) + p_s b(1,2) + p_o b(2,3) \\
        b(2,3) &= c(2,3) + p_s b(2,2) + p_o b(1,4) \\
        b(2,4) &= c(2,4) + b(2,3)\label{eq:last_eq_of_blocking_example}
    \end{align}
\end{multicols*}

Additionally, the above equations can be transformed into a linear system of the 
form \(Zx=y\) where:

\begin{equation}\label{eq:example-algebaric-approach-blocking-time}
    Z=
    \begin{pmatrix}
        -1 & p_o & 0 & 0 & 0 & 0 \\ %(1,2)
        p_s & -1 & p_o & 0 & 0 & 0 \\ %(1,3)
        0 & 1 & -1 & 0 & 0 & 0 \\ %(1,4)
        p_s & 0 & 0 & -1 & p_o & 0\\ %(2,2)
        0 & 0 & 0 & p_s & -1 & p_o \\ %(2,3)
        0 & 0 & 0 & 0 & 1 & -1 \\ %(2,4)
    \end{pmatrix},
    x=
    \begin{pmatrix}
        b(1,2) \\
        b(1,3) \\
        b(1,4) \\
        b(2,2) \\
        b(2,3) \\
        b(2,4) \\
    \end{pmatrix}, 
    y=
    \begin{pmatrix}
        -c(1,2) \\
        -c(1,3) \\
        -c(1,4) \\
        -c(2,2) \\
        -c(2,3) \\
        -c(2,4) \\
    \end{pmatrix}
\end{equation}

A more generalised form of the equations in 
(\ref{eq:example-algebaric-approach-blocking-time})
can thus be given for any value of \(C,T,N,M\) by:

\begin{align}
    b(1,T) =& c(1, T) + p_o b(1, T + 1) \label{eq:first_eq_of_blocking_general}\\
    b(1,T + 1) =& c(1, T + 1) + p_s(1, T) + p_o b(1, T + 1) \\
    b(1,T + 2) =& c(1, T + 2) + p_s(1, T + 1) + p_o b(1, T + 3) \\
    & \vdots \nonumber \\
    b(1, N) =& c(1, N) + b(1, N - 1) \\
    b(2, T) =& c(2, T) + p_s b(1, T) + p_o b(2, T + 1) \\
    b(2, T + 1) =& c(2, T + 1) + p_s b(2, T) + p_o b(2, T + 2) \\
    & \vdots \nonumber \\
    b(M, T) =& c(M, T) + b(M, T-1) \label{eq:last_eq_of_blocking_general}
\end{align}

The equivalent matrix form of the linear system of equations 
(\ref{eq:first_eq_of_blocking_general}) - (\ref{eq:last_eq_of_blocking_general})
is given by \(Zx=y\), where:
\begin{equation}\label{eq:general-algebaric-approach-blocking-time}
    \scalebox{0.9}{
        \(
        Z = 
        \begin{pmatrix}
            -1 & p_o & 0 & \dots & 0 & 0 & 0 & 0 & 0 & \dots & 0 & 0 \\ %(1,T)
            p_s & -1 & p_o & \dots & 0 & 0 & 0 & 0 & 0 & \dots & 0 & 0 \\ %(1,T+1)
            0 & p_s & -1 & \dots & 0 & 0 & 0 & 0 & 0 & \dots & 0 & 0 \\ %(1,T+2)
            \vdots & \vdots & \vdots & \ddots & \vdots & \vdots & \vdots & \vdots & 
            \vdots & \ddots & \vdots & \vdots \\ 
            0 & 0 & 0 & \dots & 1 & -1 & 0 & 0 & 0 & \dots & 0 & 0 \\ %(1,N)
            p_s & 0 & 0 & \dots & 0 & 0 & -1 & p_o & 0 & \dots & 0 & 0 \\ %(2,T)
            0 & 0 & 0 & \dots & 0 & 0 & p_s & -1 & p_o & \dots & 0 & 0 \\ %(2,T+1)
            \vdots & \vdots & \vdots & \ddots & \vdots & \vdots & \vdots & \vdots & 
            \vdots & \ddots & \vdots & \vdots \\ 
            0 & 0 & 0 & \dots & 0 & 0 & 0 & 0 & 0 & \dots & 1 & -1 \\ %(M,T)
        \end{pmatrix},
        x = 
        \begin{pmatrix}
            b(1,T) \\
            b(1,T+1) \\
            b(1,T+2) \\
            \vdots \\
            b(1,N) \\
            b(2,T) \\
            b(2,T+1) \\
            \vdots \\
            b(M,T) \\
        \end{pmatrix}, 
        y= 
        \begin{pmatrix}
            -c(1,T) \\
            -c(1,T+1) \\
            -c(1,T+2) \\
            \vdots \\
            -c(1,N) \\
            -c(2,T) \\
            -c(2,T+1) \\
            \vdots \\
            -c(M,T) \\
        \end{pmatrix}
        \)
    }
\end{equation}

Thus, having calculated the mean blocking time for all blocking states \(b(u,v)\), 
it only remains to put them together in a formula.
The resultant blocking time formula is given by:

\begin{equation}\label{eq:algebraic-blocking-time}
    B = \frac{\sum_{(u,v) \in S_A} \pi_{(u,v)} \; b(u,v)}{\sum_{(u,v) \in S_A} 
    \pi_{(u,v)}}
\end{equation}

### 2021-03-11 MarkovChain/markov_chain_model/main.tex
Add some pre-written text
Build the general strucure of the paper and add some pre-written text
for some of the sections.

\section{A queueing model with 2 consecutive buffer centres}

\subsection{System}
The following Markov chain represents the transition between states of a service
centre 
while capturing the interactions between it and a buffer centre.
The service centre accepts two types of individuals; Class 1 and Class 2.  
Class 2 individuals are accepted until a pre-determined threshold \(T\) of 
individuals is reached.
When reached, all Class 2 individuals that arrive will remain \textit{``blocked''}
in the buffer centre until the number of people in the system is 
reduced below \(T\). 
Additionally, if the people in the service centre keep rising, they may exceed
the number 
of servers \(C\) available, which will in turn mean that every new person will 
have to wait for a server to become free. 
The states of the Markov chain are denoted by \((u,v)\) where:

\begin{itemize}
    \item \(u\) = number of Class 2 individuals blocked
    \item \(v\) = number of Class 1 individuals in the service centre
\end{itemize}

\begin{figure}
    \centering
    \begin{tikzpicture}[-, node distance = 0.9cm, auto, every node/.style={scale=0.7}]

        % Markov chain variables
        \tikzmath{
            let \initdist = 0.5cm;
            let \altdist = 1.2cm;
            let \minsz = 1.6cm;
        }

        % S_1 and S_2 rectangles
        \tikzmath{
            let \leftOne = -0.8;
            let \rightOne = 2.7;
            let \upOne = 0.8;
            let \downOne = -2.7;
            let \leftTwo = 2.8;
            let \rightTwo = 13;
            let \upTwo = -2.95;
            let \downTwo = -16.4;
        }

        % General case variables
        \tikzmath{
            let \GCsmallx = 8.3;
            let \GCsmally = -9.5;
            let \GCbigx = 4.1;
            let \GCbigy = -11.8;
        }

        % Rectangle for S1
        \draw[ultra thin, dashed] (\leftOne, \downOne) -- (\leftOne, \upOne);
        \draw[ultra thin, dashed] (\leftOne, \upOne) -- (\rightOne, \upOne);
        \draw[ultra thin, dashed] (\rightOne, \upOne) -- node 
        {\Huge{\( \quad S_1 \)}}(\rightOne, \downOne);
        \draw[ultra thin, dashed] (\rightOne, \downOne) -- (\leftOne, \downOne);

        % Rectangle for S2
        \draw[ultra thin, dashed] (\leftTwo, \downTwo) -- node 
        {\Huge{\( S_2 \quad \)}}(\leftTwo, \upTwo);
        \draw[ultra thin, dashed] (\leftTwo, \upTwo) -- (\rightTwo, \upTwo);
        \draw[ultra thin, dashed] (\rightTwo, \upTwo) -- (\rightTwo, \downTwo);
        \draw[ultra thin, dashed] (\rightTwo, \downTwo) -- (\leftTwo, \downTwo);

        % Small square of general case
        \draw [thick] (\GCsmallx, \GCsmally) -- node {} 
        (\GCsmallx + 0.4, \GCsmally);
        \draw [thick] (\GCsmallx + 0.4, \GCsmally) -- node {} 
        (\GCsmallx + 0.4, \GCsmally - 0.4);
        \draw [thick] (\GCsmallx + 0.4, \GCsmally - 0.4) -- node {} 
        (\GCsmallx, \GCsmally - 0.4);
        \draw [thick] (\GCsmallx, \GCsmally - 0.4) -- node {} 
        (\GCsmallx, \GCsmally);

        % Dashed lines to from small square to big one 
        \draw [ultra thin] (\GCsmallx, \GCsmally) -- node {} 
        (\GCbigx, \GCbigy);
        \draw [ultra thin] (\GCsmallx + 0.4, \GCsmally) -- node {} 
        (\GCbigx + 4, \GCbigy);
        \draw [ultra thin] (\GCsmallx, \GCsmally - 0.4) -- node {} (7, \GCbigy);
        \draw [ultra thin] (\GCsmallx + 0.4, \GCsmally - 0.4) -- node {} 
        (\GCbigx + 4, \GCbigy - 4);

        % Big Square of general case
        \draw [ultra thick] (\GCbigx, \GCbigy) -- node {} (\GCbigx + 4, \GCbigy);
        \draw [ultra thick] (\GCbigx + 4, \GCbigy) -- node {} 
        (\GCbigx + 4, \GCbigy - 4);
        \draw [ultra thick] (\GCbigx + 4, \GCbigy - 4) -- node {General Case} 
        (\GCbigx, \GCbigy - 4);
        \draw [ultra thick] (\GCbigx, \GCbigy - 4) -- node {} (\GCbigx, \GCbigy);

        % First Line
        \node[state, minimum size=1.5cm] (zero) {(0,0)};
        \node[state, node distance = \initdist, minimum size=\minsz, below right=of zero] 
        (one) {(0,1)};
        \node[draw=none, node distance = \initdist, minimum size=\minsz, below right=of one] 
        (two) {\textbf{\( \ddots \)}};
        \node[state, node distance = \initdist, minimum size=\minsz, below right=of two] 
        (three) {(0,T)};
        \node[state, node distance = \altdist, minimum size=\minsz, right=of three] 
        (four) {(0,T+1)};
        \node[draw=none, node distance = \altdist, minimum size=\minsz, right=of four] 
        (five) {\textbf{\dots}};
        \node[state, minimum size=\minsz, right=of five] (six) {(0,C)};
        \node[draw=none, minimum size=\minsz, right=of six] (seven) {\textbf{\dots}};

        % Second Line
        \node[state, minimum size=\minsz, below=of three] (three_one) {(1,T)};
        \node[state, minimum size=\minsz, below=of four] (four_one) {(1,T+1)};
        \node[draw=none, minimum size=\minsz, below=of five] (five_one) {\textbf{\dots}};
        \node[state, minimum size=\minsz, right=of five_one] (six_one) {(1,C)};
        \node[draw=none, minimum size=\minsz, right=of six_one] (seven_one) {\textbf{\dots}};

        % Third Line
        \node[state, minimum size=\minsz, below=of three_one] (three_two) {(2,T)};
        \node[state, minimum size=\minsz, below=of four_one] (four_two) {(2,T+1)};
        \node[draw=none, minimum size=\minsz, below=of five_one] (five_two) 
        {\textbf{\dots}};
        \node[state, minimum size=\minsz, right=of five_two] (six_two) {(2,C)};
        \node[draw=none, minimum size=\minsz, right=of six_two] (seven_two) 
        {\textbf{\dots}};

        % Fourth line
        \node[draw=none, node distance = \altdist, minimum size=\minsz, below=of three_two] 
        (three_three) {\textbf{\vdots}};
        \node[draw=none, node distance = \altdist, minimum size=\minsz, below=of four_two] 
        (four_three) {\textbf{\vdots}};
        \node[draw=none, node distance = 2cm, minimum size=\minsz, below=of five_two] 
        (five_three) {};
        \node[draw=none, node distance = \altdist, minimum size=\minsz, below=of six_two] 
        (six_three) {\textbf{\vdots}};

        % Fifth line
        % \node[state, node distance = \altdist, minimum size=\minsz, below=of five_three] 
        % (general_case_mid) {\( (u_i, v_i) \)};
        \node[draw=none, node distance = 0.3cm, minimum size=\minsz, below=of four_three] 
        (general_case_up) {};
        \node[state, node distance = \altdist, minimum size=\minsz, below=of general_case_up] 
        (general_case_mid) {\( (u_i, v_i) \)};

        \node[draw=none, node distance = \altdist, minimum size=\minsz, below=of general_case_mid] 
        (general_case_down) {};
        \node[draw=none, node distance = \altdist, minimum size=\minsz, left=of general_case_mid] 
        (general_case_left) {};
        \node[draw=none, node distance = \altdist, minimum size=\minsz, right=of general_case_mid] 
        (general_case_right) {};

        \draw[every loop]
            % First Horizontal Edges
            (zero) edge[bend left] node {\( \Lambda \)} (one)
            (one) edge[bend left] node {\( \mu \)} (zero)
            (one) edge[bend left] node {\( \Lambda \)} (two)
            (two) edge[bend left] node {\( 2 \mu \)} (one)
            (two) edge[bend left] node {\( \Lambda \)} (three)
            (three) edge[bend left] node {\( T \mu \)} (two)
            (three) edge[bend left] node {\( \lambda_1 \)} (four)
            (four) edge[bend left] node {\( (T+1) \mu \)} (three)
            (four) edge[bend left] node {\( \lambda_1 \)} (five)
            (five) edge[bend left] node {\( (T+2) \mu \)} (four)
            (five) edge[bend left] node {\( \lambda_1 \)} (six)
            (six) edge[bend left] node {\( C\mu \)} (five)
            (six) edge[bend left] node {\( \lambda_1 \)} (seven)
            (seven) edge[bend left] node {\( C\mu \)} (six)

            % Second Horizontal Edges
            (three_one) edge[bend left] node {\( \lambda_1 \)} (four_one)
            (four_one) edge[bend left] node {\( (T+1) \mu \)} (three_one)
            (four_one) edge[bend left] node {\( \lambda_1 \)} (five_one)
            (five_one) edge[bend left] node {\( (T+2) \mu \)} (four_one)
            (five_one) edge[bend left] node {\( \lambda_1 \)} (six_one)
            (six_one) edge[bend left] node {\( C\mu \)} (five_one)
            (six_one) edge[bend left] node {\( \lambda_1 \)} (seven_one)
            (seven_one) edge[bend left] node {\( C\mu \)} (six_one)

            % Third Horizontal Edges
            (three_two) edge[bend left] node {\( \lambda_1 \)} (four_two)
            (four_two) edge[bend left] node [below] {\( (T+1) \mu \)} (three_two)
            (four_two) edge[bend left] node {\( \lambda_1 \)} (five_two)
            (five_two) edge[bend left] node {\( (T+2) \mu \)} (four_two)
            (five_two) edge[bend left] node {\( \lambda_1 \)} (six_two)
            (six_two) edge[bend left] node {\( C\mu \)} (five_two)
            (six_two) edge[bend left] node {\( \lambda_1 \)} (seven_two)
            (seven_two) edge[bend left] node {\( C\mu \)} (six_two)

            % First Vertical Edges
            (three) edge[bend left] node {\( \lambda_2 \)} (three_one)
            (three_one) edge[bend left] node {\( T \mu \)} (three)
            (three_one) edge[bend left] node {\( \lambda_2 \)} (three_two)
            (three_two) edge[bend left] node {\( T\mu \)} (three_one)
            (three_two) edge[bend left] node {\( \lambda_2 \)} (three_three)
            (three_three) edge[bend left] node {\( T\mu \)} (three_two)

            % Second Vertical Edges
            (four) edge node {\( \lambda_2 \)} (four_one)
            (four_one) edge node {\( \lambda_2 \)} (four_two)
            (four_two) edge node {\( \lambda_2 \)} (four_three)

            % Fourth Vertical Edges
            (six) edge node {\( \lambda_2 \)} (six_one)
            (six_one) edge node {\( \lambda_2 \)} (six_two)
            (six_two) edge node {\( \lambda_2 \)} (six_three)

            % General Case
            (general_case_left) edge[bend left] node {\( \lambda_1 \)} (general_case_mid)
            (general_case_mid) edge[bend left] node {\( v_i \mu \)} (general_case_left)
            (general_case_right) edge[bend left] node {\( (v_i +1) \mu \)} (general_case_mid)
            (general_case_mid) edge[bend left] node {\( \lambda_1 \)} (general_case_right)
            % (five_three) edge node {\( \lambda_2 \)} (general_case_mid)
            (general_case_up) edge node {\( \lambda_2 \)} (general_case_mid)
            (general_case_mid) edge node {\( \lambda_2 \)} (general_case_down)
            ;
    \end{tikzpicture}
    \caption{Markov chain} 
    \label{markov_model}
\end{figure}

\subsubsection{Markov-chain state mapping function}
The transition matrix of the Markov-chain representation described above can be 
denoted by a state mapping function. 
The state space of this function is defined as:

\begin{align}
    S(T) =& S_1(T) \cup S_2(T) \text{ where:} \nonumber \\
    S_1(T) =& \left\{(0, v)\in\mathbb{N}_0^2 \; | \; v < T \right\} \label{eq:state_space} \\
    S_2(T) =& \{(u, v)\in\mathbb{N}_0^2 \; | \; v \geq T \} \nonumber
\end{align}

Therefore, the entries of the transition matrix \(Q\), can be given by 
\( q_{i,j} = q_{(u_i, v_i),(u_j, v_j)} \) which is the transition rate from state 
\( i = (u_i, v_i) \) to state \( j = (u_j , v_j) \) for all 
\( (u_i, v_i), (u_j, v_j) \in S \).

\begin{equation} \label{eq:markov_transition_rate}
    q_{i, j} = 
    \begin{cases}
        \Lambda, & \textbf{if } (u_i, v_i) - (u_j, v_j) = (0,-1) \textbf{ and } 
        v_i < \text{t} \\
        \lambda_1, & \textbf{if } (u_i, v_i) - (u_j, v_j) = (0,-1) \textbf{ and } 
        v_i \geq \text{t} \\
        \lambda_2, & \textbf{if } (u_i, v_i) - (u_j, v_j) = (-1,0) \\
        v_i \mu, & \textbf{if } (u_i, v_i) - (u_j, v_j) = (0,1) \textbf{ and } 
        v_i \leq C \textbf{ or} \\ & \hspace{0.37cm}(u_i, v_i) - (u_j, v_j) = (1,0) 
        \textbf{ and } v_i = T \leq C \\
        C \mu, & \textbf{if } (u_i, v_i) - (u_j, v_j) = (0,1) \textbf{ and } v_i > C 
        \textbf{ or} \\ & \hspace{0.37cm}(u_i, v_i) - (u_j, v_j) = (1,0) \textbf{ and } 
        v_i = T > C\\
        -\sum_{j=1}^{|Q|}{q_{i,j}} & \textbf{if } i = j \\
        0, & \textbf{otherwise}
    \end{cases}
\end{equation}

In order to acquire an exact solution of the problem a slight adjustment needs to 
be considered. 
The problem defined above assumes no upper boundary to the number of individuals 
that can wait for service or the ones that are blocked in the buffer centre. 
Therefore, a different state space \( \tilde S \) needs to be constructed where 
\( \tilde S \subseteq S \) and there is a maximum allowed number of people \( N \) 
that can be in the system and a maximum allowed number of people \( M \) that can
be blocked in the buffer centre:

\begin{equation}
    \tilde S = \left\{ (u, v) \in S\;| u \leq M, v\leq N \right\}
\end{equation}

\subsubsection{Steady State}
Having calculated the transition matrix \( Q \) for a given set of parameters the 
probability vector \( \pi \) needs to be considered. 
The vector \( \pi \) is commonly used to study such stochastic systems and it's 
main purpose is to keep track of the probability of being at any given state of 
the system. 
The term \textit{steady state} refers to the instance of the vector \( \pi \) where 
the probabilities of being at any state become stable over time. 
Thus, by considering the steady state vector \( \pi \) the relationship between 
it and \(Q \) is given by:

\[
\frac{d\pi}{dt} = \pi Q = 0
\]

There are numerous methods that can be used to solve problems of such kind. 
In this paper only numeric and algebraic approaches will be considered.

The first approach to be considered is to solve the differential equation numerically 
by observing the behaviour of the model over time. 
The solution is obtained via python's SciPy library. 
The functions odeint and solve\textunderscore ivp have been used in order to find 
a solution to the problem. 
Both of these functions can be used to solve any system of first order ODEs.

### 2021-03-19 tasks.py
Add github action to compile main.tex
Use the invoke module to run tasks from tasks.py

@@ -1,0 +1,9 @@
+
+from invoke import task
+
+
+@task
+def compile(c):
+    """ Compile the LaTeX document. """
+
+    c.run(f"latexmk main.tex")

### 2021-03-19 known.py
Add spellchecker for all .tex files
Use aspell to check that the latex files don't have any
spelling mistakes. An additional file known.py has been
created to store words that are incorrectly spelled on
purpose.

@@ -1,0 +1,6 @@
+""" A set of known words and end-of-word patterns for the spellchecker. """
+
+words = {
+    "Michalis",
+    "Panayides",
+}

### 2021-03-19 tasks.py

@@ -1,5 +1,11 @@
+import pathlib
+import re
+import subprocess
+import sys
 
 from invoke import task
+
+import known
 
 
 @task
@@ -7,3 +13,33 @@ def compile(c):
     """ Compile the LaTeX document. """
 
     c.run(f"latexmk main.tex")
+
+
+@task
+def spellcheck(c):
+    """
+    Check the spelling of all .tex files
+    """
+
+    all_tex_files = list(pathlib.Path().glob("**/*.tex"))
+    exit_codes = [0]
+    for path in all_tex_files:
+        latex = path.read_text()
+        aspell_output = subprocess.check_output(
+            ["aspell", "-t", "--list", "--lang=en_GB"], input=latex, text=True
+        )
+        errors = set(aspell_output.split("\n")) - {""}
+        incorrect_words = set()
+        for error in errors:
+            if not any(
+                re.fullmatch(word.lower(), error.lower())
+                for word in known.words
+            ):
+                incorrect_words.add(error)
+
+        if len(incorrect_words) > 0:
+            print(f"In {path} the following words are not known: ")
+            for string in sorted(incorrect_words):
+                print(string)
+            exit_codes.append(1)
+    sys.exit(max(exit_codes))

### 2021-03-29 sections/queueing_model/main.tex
Add initial structure
Create a sections directory with 6 sub-direcotires (one for each
section). Also add table of contents.

\section{A queueing models with 2 consecutive buffer centres}

### 2021-03-29 known.py
Add "queueing" to known words

@@ -3,4 +3,5 @@
 words = {
     "Michalis",
     "Panayides",
+    "queueing",
 }

### 2021-03-29 sections/healthcare_application/main.tex
Add subsections

\section{EMS - ED application}

\subsection{Application}

\subsection{Data Analysis}

### 2021-03-29 known.py
Add "abbrv" to known words

@@ -4,4 +4,5 @@ words = {
     "Michalis",
     "Panayides",
     "queueing",
+    "abbrv",
 }

### 2021-03-30 sections/methodology/main.tex

\section{Methodology}

\subsection{Backwards Induction}

\subsection{Nash Equilibrium}

\subsection{Learning Algorithms}

### 2021-04-13 sections/model_overview/main.tex
Write initial draft of game overview section

\section{Overview of game theoretic model}

% PAR: GENERAL
% Intro
The problem studied is a 3-player game theoretic scenario between two queueing 
systems and a service that distributes individuals to them. 
% General objectives of players
Each player in this game has its own objectives and cares about meeting its own 
targets.
% Specific objectives
More specifically, the queueing systems' objective is captured by an upper bound
of the time that a fixed proportion of individuals need to spend in the system, 
while the distribution service aims to minimise the time that its individuals 
are blocked.

% PAR: OBJECTIVES OF QUEUEING SYSTEMS
% Intro
The queueing systems are designed in such a way where they can accept two types
of individuals. 
These are the individuals that the distribution service allocates to them and 
other individuals from other sources. 
% Specific Formulation
Each queueing system may then choose to block the individuals that arrive from 
the service distribution when the system reaches a certain capacity. 
Thus, the set of strategies that they may choose to play in the game are defined 
as the set of possible choices that the two queueing systems have. 
In other words, each queueing system is given \( N_A \) and \( N_B \) number of 
strategies where \( N_A \) and \( N_B \) are the total capacities of the two 
queueing systems.
The \textit{threshold} parameter is thus used to capture the chosen 
strategy for each hospital where \( T_A \in \left[1, N_A \right] \) and 
\( T_B \in \left[1, N_B \right] \)
% Specific Objectives
Their choice of strategy will then rely solely on satisfying their own 
objective, which is to make sure that the waiting time of a proportion of 
individuals will be below the predefined target time.

\begin{equation}
    P(W < \textit{ Target}) \geq \hat{P}
\end{equation}

where \(W\) is the waiting time of all individuals, \textit{Target} is the time 
target and \(\hat{P}\) is the percentage of individuals need to be within that 
target. 
There are numerous objective functions that can be used to capture this 
behaviour. 
The first one would be to use the threshold that maximises the probability that 
the mean waiting is more than the target time, and completely ignore the 
percentage goal.

\begin{equation}
    \max_{T_i} \quad P(W_i < \textit{Target})
\end{equation}

Perhaps a more sophisticated objective function would be to get the proportion 
of individuals as close to the percentage aim. 
In other words, to find the threshold that minimises the difference between the 
probability and the percentage goal (or maximise its negation).

\begin{equation}
    \max_{T_i} \quad -\left( \hat{P} - P(W_i < \textit{Target}) \right)^2
\end{equation}

% PAR: OBJECTIVES OF DISTRIBUTION SERVICE
% Intro
On the other side of the spectrum, the service distribution has its own choices 
to make and its own goals to satisfy.
% Specific Formulation
The set of strategies it has can be defined as the different ways that it can 
distribute individuals to the two queueing system.
Therefore, unlike the queueing systems, the distribution service has a 
continuous set of strategies that goes from \( 0\% - 100\% \). 
For example, it may choose to send \(35\%\) of its individuals to the first 
queueing system and \(65\%\) to the second one.
% Specific Objectives
In addition, the distribution services aims to minimise any potential blockages
that may occur give the pair of thresholds chosen by the two queueing systems.
Thus, its objective is to minimise the blocked time of the individuals 
that they send to the two queueing systems.
Apart from the time being blocked, an additional aspect that may affect the 
decision of the distribution service is the proportion of lost individuals.
Equation \ref{eq:obj-distribution-service} can be used to capture a mixture 
between the two objectives.
systems.

\begin{equation}\label{eq:obj-distribution-service}
    \alpha P(L_A) + (1 - \alpha) B_A = 
    \alpha P(L_B) + (1 - \alpha) B_B
\end{equation}

Here, the purpose of \(\alpha\) is to tune the ``importance'' of each objective,
where high \(\alpha\) indicates a higher weight on the proportion of lost 
individuals and smaller \(\alpha\) a higher weight on the time blocked.

% PAR: COMBINED FORMULATION (Figure of 3-player game)
% Intro
% Payoff matrices??

\begin{figure}[h]
    \centering
    \begin{tikzpicture}[-, node distance = 3cm, scale=0.8]
        \node[anchor=north](H1){\(H_1\)};
        \node[anchor=north](H1_d1) at (3, 2){.};
        \node[anchor=north](H1_d2) at (3, -2){.};

        \path[->] (H1) edge node {}(H1_d1);
        \path[->] (H1) edge node {}(H1_d2);
        \path (H1_d1) edge [bend left] node {}(H1_d2);
        \path (H1_d1) [dashed] edge node {}(H1_d2);

        \node[anchor=north](H2) at (4.1, 0){\(H_2\)};
        \node[anchor=north](H2_d1) at (6.9, 2){.};
        \node[anchor=north](H2_d2) at (6.9, -2){.};

        \path[->] (H2) edge node {}(H2_d1);
        \path[->] (H2) edge node {}(H2_d2);
        \path(H2_d1) edge [bend left] node {}(H2_d2);

        \node[anchor=north](A) at (7.8, 0){\(A\)};
        \node[anchor=north](A_d1) at (10.8, 2){.};
        \node[anchor=north](A_d2) at (10.8, -2){.};

        \path[->] (A) edge node {}(A_d1);
        \path[->] (A) edge node {}(A_d2);
        \path(A_d1) edge [bend left] node {}(A_d2);
    \end{tikzpicture}
    \caption{}
\end{figure}

\begin{table}[ht]
    \centering
    A = 
    \begin{tabular}{|l|l|l|l|}
    \hline
    \( U_{1,1}^A \) & \( U_{1,2}^A \) & \dots & \( U_{1,N_B}^A \) \\ \hline
    \( U_{2,1}^A \) & \( U_{2,2}^A \) & \dots & \( U_{2,N_B}^A \) \\ \hline
    \vdots & \vdots & \( \ddots \) & \vdots \\ \hline
    \( U_{N_A,1}^A \) & \( U_{N_A,2}^A \) & \dots & \( U_{N_A,N_B}^A \) \\ \hline
    \end{tabular}
\end{table}

\begin{table}[ht]
    \centering
    B = 
    \begin{tabular}{|l|l|l|l|}
    \hline
    \( U_{1,1}^B \) & \( U_{1,2}^B \) & \dots & \( U_{1,N_B}^B \) \\ \hline
    \( U_{2,1}^B \) & \( U_{2,2}^B \) & \dots & \( U_{2,N_B}^B \) \\ \hline
    \vdots & \vdots & \( \ddots \) & \vdots \\ \hline
    \( U_{N_A,1}^B \) & \( U_{N_A,2}^B \) & \dots & \( U_{N_A,N_B}^B \) \\ \hline
    \end{tabular}
\end{table}

### 2021-04-13 sections/model_overview/main.tex
Apply minor changes and fix typos

@@
 
-% PAR: GENERAL
-% Intro
 The problem studied is a 3-player game theoretic scenario between two queueing 
 systems and a service that distributes individuals to them. 
-% General objectives of players
 Each player in this game has its own objectives and cares about meeting its own 
 targets.
-% Specific objectives
 More specifically, the queueing systems' objective is captured by an upper bound
 of the time that a fixed proportion of individuals need to spend in the system, 
-while the distribution service aims to minimise the time that its individuals 
+while the distributor aims to minimise the time that its individuals 
 are blocked.
 
-% PAR: OBJECTIVES OF QUEUEING SYSTEMS
-% Intro
 The queueing systems are designed in such a way where they can accept two types
 of individuals. 
-These are the individuals that the distribution service allocates to them and 
+These are the individuals that the distributor allocates to them and 
 other individuals from other sources. 
-% Specific Formulation
 Each queueing system may then choose to block the individuals that arrive from 
-the service distribution when the system reaches a certain capacity. 
+the distributor when the system reaches a certain capacity. 
 Thus, the set of strategies that they may choose to play in the game are defined 
@@
 \( T_B \in \left[1, N_B \right] \)
-% Specific Objectives
 Their choice of strategy will then rely solely on satisfying their own 
@@
 
-% PAR: OBJECTIVES OF DISTRIBUTION SERVICE
-% Intro
-On the other side of the spectrum, the service distribution has its own choices 
+On the other side of the spectrum, the distributor has its own choices 
 to make and its own goals to satisfy.
-% Specific Formulation
 The set of strategies it has can be defined as the different ways that it can 
 distribute individuals to the two queueing system.
-Therefore, unlike the queueing systems, the distribution service has a 
+Therefore, unlike the queueing systems, the distributor has a 
 continuous set of strategies that goes from \( 0\% - 100\% \). 
@@
 queueing system and \(65\%\) to the second one.
-% Specific Objectives
-In addition, the distribution services aims to minimise any potential blockages
-that may occur give the pair of thresholds chosen by the two queueing systems.
+In addition, the distributor aims to minimise any potential blockages
+that may occur, given the pair of thresholds chosen by the two queueing systems.
 Thus, its objective is to minimise the blocked time of the individuals 
@@
 between the two objectives.
-systems.
 

### 2021-04-13 sections/model_overview/main.tex
Finish writing of section and add referecne

@@
 \begin{equation}
-    \max_{T_i} \quad P(W_i < \textit{Target})
+    \arg \max_{T_i} \quad P(W_i < \textit{Target})
 \end{equation}
@@
 
-\begin{equation}
-    \max_{T_i} \quad -\left( \hat{P} - P(W_i < \textit{Target}) \right)^2
+\begin{equation}\label{eq:obj-queueing-systems}
+    \arg \max_{T_i} \quad -\left( \hat{P} - P(W_i < \textit{Target}) \right)^2
 \end{equation}
@@
 decision of the distribution service is the proportion of lost individuals.
-Equation \ref{eq:obj-distribution-service} can be used to capture a mixture 
+Equation \ref{eq:obj-distributor} can be used to capture a mixture 
 between the two objectives.
 
-\begin{equation}\label{eq:obj-distribution-service}
+\begin{equation}\label{eq:obj-distributor}
     \alpha P(L_A) + (1 - \alpha) B_A = 
@@
 % Intro
-% Payoff matrices??
+Using equations \ref{eq:obj-queueing-systems} and \ref{eq:obj-distributor}, an
+imperfect information extensive form game may arise. 
+An imperfect information game is defined as an extensive form game where some 
+of the information about the game state is hidden for at least one of the 
+players \cite{Berwanger2008}. In this study the state of the problem that is
+hidden is the threshold that each player chooses to play.
+In other words, each queueing system chooses to play a strategy without the 
+knowing the other system's strategy.
+The distributor then, fully aware of the chosen strategies are, distributes 
+individuals among the two systems in order to minimise the time that its 
+individuals will be blocked.
 
@@
     \begin{tikzpicture}[-, node distance = 3cm, scale=0.8]
-        \node[anchor=north](H1){\(H_1\)};
-        \node[anchor=north](H1_d1) at (3, 2){.};
-        \node[anchor=north](H1_d2) at (3, -2){.};
+        \node[anchor=north](HA){\(H_A\)};
+        \node[anchor=north](HA_d1) at (3, 2){.};
+        \node[anchor=north](HA_d2) at (3, -2){.};
 
-        \path[->] (H1) edge node {}(H1_d1);
-        \path[->] (H1) edge node {}(H1_d2);
-        \path (H1_d1) edge [bend left] node {}(H1_d2);
-        \path (H1_d1) [dashed] edge node {}(H1_d2);
+        \path[->] (HA) edge node {}(HA_d1);
+        \path[->] (HA) edge node {}(HA_d2);
+        \path (HA_d1) edge [bend left] node {}(HA_d2);
+        \path (HA_d1) [dashed] edge node {}(HA_d2);
 
-        \node[anchor=north](H2) at (4.1, 0){\(H_2\)};
-        \node[anchor=north](H2_d1) at (6.9, 2){.};
-        \node[anchor=north](H2_d2) at (6.9, -2){.};
+        \node[anchor=north](HB) at (4.1, 0){\(H_B\)};
+        \node[anchor=north](HB_d1) at (6.9, 2){.};
+        \node[anchor=north](HB_d2) at (6.9, -2){.};
 
-        \path[->] (H2) edge node {}(H2_d1);
-        \path[->] (H2) edge node {}(H2_d2);
-        \path(H2_d1) edge [bend left] node {}(H2_d2);
+        \path[->] (HB) edge node {}(HB_d1);
+        \path[->] (HB) edge node {}(HB_d2);
+        \path(HB_d1) edge [bend left] node {}(HB_d2);
 
-        \node[anchor=north](A) at (7.8, 0){\(A\)};
-        \node[anchor=north](A_d1) at (10.8, 2){.};
-        \node[anchor=north](A_d2) at (10.8, -2){.};
+        \node[anchor=north](D) at (7.8, 0){\(D\)};
+        \node[anchor=north](D_d1) at (10.8, 2){.};
+        \node[anchor=north](D_d2) at (10.8, -2){.};
 
-        \path[->] (A) edge node {}(A_d1);
-        \path[->] (A) edge node {}(A_d2);
-        \path(A_d1) edge [bend left] node {}(A_d2);
+        \path[->] (D) edge node {}(D_d1);
+        \path[->] (D) edge node {}(D_d2);
+        \path(D_d1) edge [bend left] node {}(D_d2);
     \end{tikzpicture}
-    \caption{}
+    \caption{Imperfect information Extensive Form Game between the distributor 
+    and the 2 queueing systems}
+    \label{fig:imperfect-info-game}
 \end{figure}
 
-\begin{table}[ht]
-    \centering
+Figure \ref{fig:imperfect-info-game} illustrates such a game works. The first 
+queueing system \(H_A\) decides on a threshold, then the second system \(H_B\)
+chooses its own threshold, without knowing the strategy of \(H_A\), and finally
+the distributor makes its choice. Note here that the dotted line represents the
+fact that \(H_B\) is unaware of the state of the game when making its own 
+decisions. The game can thus be partitioned into a normal form game between the
+two queueing systems and finding the distributor's best choice.
+
+In order to define the normal form game the two payoff matrices of the players 
+are required. From equation \ref{eq:obj-queueing-systems} the utilities of the
+players can be formulated as:
+
+\begin{equation}
+    U_{T_1, T_2}^i = \quad -\left( 
+        \hat{P} - P(W_i < \textit{Target}) 
+    \right)^2
+\end{equation}
+
+Consequently, the payoff matrices of the game can be populated by these 
+utilities:
+
+\begin{equation} \label{eq:payoff-matrices}
     A = 
-    \begin{tabular}{|l|l|l|l|}
-    \hline
-    \( U_{1,1}^A \) & \( U_{1,2}^A \) & \dots & \( U_{1,N_B}^A \) \\ \hline
-    \( U_{2,1}^A \) & \( U_{2,2}^A \) & \dots & \( U_{2,N_B}^A \) \\ \hline
-    \vdots & \vdots & \( \ddots \) & \vdots \\ \hline
-    \( U_{N_A,1}^A \) & \( U_{N_A,2}^A \) & \dots & \( U_{N_A,N_B}^A \) \\ \hline
-    \end{tabular}
-\end{table}
+    \begin{pmatrix}
+        U_{1,1}^A & U_{1,2}^A & \dots & U_{1,N_B}^A \\
+        U_{2,1}^A & U_{2,2}^A & \dots & U_{2,N_B}^A \\
+        \vdots & \vdots & \ddots & \vdots \\
+        U_{N_A,1}^A & U_{N_A,2}^A & \dots & U_{N_A,N_B}^A \\
+    \end{pmatrix},
+    B = 
+    \begin{pmatrix}
+        U_{1,1}^B & U_{1,2}^B & \dots & U_{1,N_B}^B \\
+        U_{2,1}^B & U_{2,2}^B & \dots & U_{2,N_B}^B \\
+        \vdots & \vdots & \ddots & \vdots \\
+        U_{N_A,1}^B & U_{N_A,2}^B & \dots & U_{N_A,N_B}^B \\
+    \end{pmatrix}
+\end{equation}
 
-\begin{table}[ht]
-    \centering
-    B = 
-    \begin{tabular}{|l|l|l|l|}
-    \hline
-    \( U_{1,1}^B \) & \( U_{1,2}^B \) & \dots & \( U_{1,N_B}^B \) \\ \hline
-    \( U_{2,1}^B \) & \( U_{2,2}^B \) & \dots & \( U_{2,N_B}^B \) \\ \hline
-    \vdots & \vdots & \( \ddots \) & \vdots \\ \hline
-    \( U_{N_A,1}^B \) & \( U_{N_A,2}^B \) & \dots & \( U_{N_A,N_B}^B \) \\ \hline
-    \end{tabular}
-\end{table}
+Based on the choice of strategy of these two players the distributor will then 
+make its own choice of proportion of individuals to send to each system.

### 2021-04-13 known.py
Update known.py

@@ -1,8 +1,9 @@
 """ A set of known words and end-of-word patterns for the spellchecker. """
 
 words = {
+    "abbrv",
+    "HB",
     "Michalis",
     "Panayides",
     "queueing",
-    "abbrv",
 }

### 2021-04-14 sections/model_overview/main.tex
Minor change

@@
 
-% PAR: COMBINED FORMULATION (Figure of 3-player game)
-% Intro
 Using equations \ref{eq:obj-queueing-systems} and \ref{eq:obj-distributor}, an
@@
 Based on the choice of strategy of these two players the distributor will then 
-make its own choice of proportion of individuals to send to each system.
+make its own choice of the proportion of individuals to send to each system.

### 2021-04-15 sections/model_overview/main.tex
Apply suggestions from code review
Co-authored-by: Vince Knight <vincent.knight@gmail.com>

@@
 
-The problem studied is a 3-player game theoretic scenario between two queueing 
-systems and a service that distributes individuals to them. 
+The problem studied is a 3-player normal form game.
+
+ The players are:
+
+ \begin{itemize}
+
+      \item The decision makers of two queueing 
+systems;
+      \item a service that distributes individuals to these two queueing systems.
+ \end{itemize}
+
 Each player in this game has its own objectives and cares about meeting its own 
@@
 More specifically, the queueing systems' objective is captured by an upper bound
-of the time that a fixed proportion of individuals need to spend in the system, 
+of the time that a fixed proportion of individuals  spend in the system, 
 while the distributor aims to minimise the time that its individuals 
-are blocked.
+are blocked.   % TODO Depending on how this is described earlier, we might need a little more here (as to what we mean by "blocked")
 
@@
 behaviour. 
-The first one would be to use the threshold that maximises the probability that 
+For example one approach is to use the threshold that maximises the probability that 
 the mean waiting is more than the target time, and completely ignore the 
@@
 
-Perhaps a more sophisticated objective function would be to get the proportion 
+A more sophisticated objective function would be to get the proportion 
 of individuals as close to the percentage aim. 
@@
 
-Here, the purpose of \(\alpha\) is to tune the ``importance'' of each objective,
+Here, \(\alpha\) represents the ``importance'' of each objective,
 where high \(\alpha\) indicates a higher weight on the proportion of lost 
@@
 players \cite{Berwanger2008}. In this study the state of the problem that is
-hidden is the threshold that each player chooses to play.
+hidden is the threshold that each of the first two players chooses to play.
 In other words, each queueing system chooses to play a strategy without the 
 knowing the other system's strategy.
-The distributor then, fully aware of the chosen strategies are, distributes 
+The distributor then, fully aware of the chosen threshold strategies, distributes 
 individuals among the two systems in order to minimise the time that its 
-individuals will be blocked.
+individuals will be blocked. Figure \ref{fig:imperfect-info-game} illustrates this.
 
@@
 
-Figure \ref{fig:imperfect-info-game} illustrates such a game works. The first 
+The first 
 queueing system \(H_A\) decides on a threshold, then the second system \(H_B\)
@@
 Based on the choice of strategy of these two players the distributor will then 
-make its own choice of the proportion of individuals to send to each system.
+make their own choice of the proportion of individuals to send to each system.

### 2021-04-15 sections/model_overview/main.tex
Apply suggestions from review
Rewording some sentences, restructure some paragraphs and add several
TODOs.

@@
 
-The problem studied is a 3-player normal form game.
-
- The players are:
+The problem studied is a 3-player normal form game. The players are:
 
 \begin{itemize}
-
-      \item The decision makers of two queueing 
-systems;
+    \item The decision makers of two queueing systems;
     \item a service that distributes individuals to these two queueing systems.
@@
 
-Each player in this game has its own objectives and cares about meeting its own 
-targets.
+his is a standard Normal form game~\cite{},  
+% TODO: Cite a Game Theory text book (Maschler et al. would do)
+in that each player in this game has their own objectives which they aim to 
+optimise.
 More specifically, the queueing systems' objective is captured by an upper bound
@@
 while the distributor aims to minimise the time that its individuals 
-are blocked.   % TODO Depending on how this is described earlier, we might need a little more here (as to what we mean by "blocked")
+are blocked.   
+% TODO: Depending on how this is described earlier, we might need a little more 
+% here (as to what we mean by "blocked")
 
@@
 the distributor when the system reaches a certain capacity. 
-Thus, the set of strategies that they may choose to play in the game are defined 
-as the set of possible choices that the two queueing systems have. 
-In other words, each queueing system is given \( N_A \) and \( N_B \) number of 
-strategies where \( N_A \) and \( N_B \) are the total capacities of the two 
-queueing systems.
-The \textit{threshold} parameter is thus used to capture the chosen 
-strategy for each hospital where \( T_A \in \left[1, N_A \right] \) and 
-\( T_B \in \left[1, N_B \right] \)
+The strategy sets for each queueing system is the set 
+\( \{T \in \mathbb{N} \;|\; 1 \leq T \leq N\} \) where \(N \in\{N_A, N_B\}\) are 
+the total capacities of the two queueing systems. We denote the chosen actions 
+from the strategy set as \(T_A, T_B\) and call these \textit{threshold}s.
 Their choice of strategy will then rely solely on satisfying their own 
@@
 
+This is shown diagrammatically in Figure %~ref{fig:diagram_of_queueing_system}.
+% TODO: Draw diagram of queueing system
+% This should include the parameters
+% and clearly show the decision variable.
+% Note: only do this for a single queueing system.
+
 \begin{equation}
-    P(W < \textit{ Target}) \geq \hat{P}
+    P(W < R) \geq \hat{P}
 \end{equation}
 
-where \(W\) is the waiting time of all individuals, \textit{Target} is the time 
+where \(W\) is the mean waiting time of all individuals, \(R\) is the time 
 target and \(\hat{P}\) is the percentage of individuals need to be within that 
@@
 behaviour. 
-For example one approach is to use the threshold that maximises the probability that 
+For example one approach is to use the threshold that maximises the probability 
+that 
 the mean waiting is more than the target time, and completely ignore the 
@@
 \begin{equation}
-    \arg \max_{T_i} \quad P(W_i < \textit{Target})
+    \arg \max_{T_i} \quad P(W_i < R)
 \end{equation}
@@
 \begin{equation}\label{eq:obj-queueing-systems}
-    \arg \max_{T_i} \quad -\left( \hat{P} - P(W_i < \textit{Target}) \right)^2
+    \arg \max_{T_i} \quad -\left( \hat{P} - P(W_i < R) \right)^2
 \end{equation}
 
-On the other side of the spectrum, the distributor has its own choices 
-to make and its own goals to satisfy.
-The set of strategies it has can be defined as the different ways that it can 
-distribute individuals to the two queueing system.
-Therefore, unlike the queueing systems, the distributor has a 
-continuous set of strategies that goes from \( 0\% - 100\% \). 
-For example, it may choose to send \(35\%\) of its individuals to the first 
-queueing system and \(65\%\) to the second one.
+The third player, the distributor has their own choices to make and their own 
+goals to satisfy.
+The strategy set of the third player is the proportion \(0 \leq p \leq 1\) of 
+individuals it sends to the first queueing system (the proportion \(1 - q\) is 
+sent to the second queueing system).
 In addition, the distributor aims to minimise any potential blockages
@@
 Apart from the time being blocked, an additional aspect that may affect the 
-decision of the distribution service is the proportion of lost individuals.
+decision of the distributor is the proportion of lost individuals.
+% TODO: Clarify above (somewhere near the diagram of the queueing system) that 
+% individuals can be lost at all.
 Equation \ref{eq:obj-distributor} can be used to capture a mixture 
@@
 
-Using equations \ref{eq:obj-queueing-systems} and \ref{eq:obj-distributor}, an
-imperfect information extensive form game may arise. 
+Using equations \ref{eq:obj-queueing-systems} and \ref{eq:obj-distributor} gives
+an imperfect information extensive form game. 
 An imperfect information game is defined as an extensive form game where some 
 of the information about the game state is hidden for at least one of the 
-players \cite{Berwanger2008}. In this study the state of the problem that is
+players~\cite{Berwanger2008}. In this study the state of the problem that is
 hidden is the threshold that each of the first two players chooses to play.
@@
     U_{T_1, T_2}^i = \quad -\left( 
-        \hat{P} - P(W_i < \textit{Target}) 
+        \hat{P} - P(W_i < R) 
     \right)^2

### 2021-04-15 known.py
Update known.py file

@@ -1,8 +1,8 @@
 """ A set of known words and end-of-word patterns for the spellchecker. """
 
 words = {
-    "abbrv",
     "HB",
+    "ieeetr",
     "Michalis",
     "Panayides",
     "queueing",

### 2021-04-23 sections/model_overview/main.tex
Add reference for normal form games
Add diagram of the queueing model
Added the diagram for the queueing model and some text to
accompany it. There were also minor changes to some of the
prewritten text.

@@
 \begin{itemize}
-    \item The decision makers of two queueing systems;
+    \item the decision makers of two queueing systems;
     \item a service that distributes individuals to these two queueing systems.
@@
 
-his is a standard Normal form game~\cite{},  
-% TODO: Cite a Game Theory text book (Maschler et al. would do)
+This is a standard Normal form game~\cite{Maschler2013},  
 in that each player in this game has their own objectives which they aim to 
@@
 from the strategy set as \(T_A, T_B\) and call these \textit{threshold}s.
-Their choice of strategy will then rely solely on satisfying their own 
-objective, which is to make sure that the waiting time of a proportion of 
-individuals will be below the predefined target time.
 
-This is shown diagrammatically in Figure %~ref{fig:diagram_of_queueing_system}.
-% TODO: Draw diagram of queueing system
-% This should include the parameters
-% and clearly show the decision variable.
-% Note: only do this for a single queueing system.
+Both queueing systems follow a queueing model that has two waiting spaces for 
+individuals. 
+The first waiting zone is where the individuals queue right before receiving 
+their service and has a capacity of \( N - C \), where \(N\) is the total 
+capacity of the waiting space and \(C\) is the number of servers. 
+The second waiting zone is where the individuals, that are sent from the 
+distributor, remain until they are allowed to enter the first waiting zone.
+The second waiting zone has a capacity of \(M\) and no servers.
+
+This is shown diagrammatically in Figure ~\ref{fig:diagram_of_queueing_system}.
+
+\begin{figure}[h]
+    \centering
+    \begin{tikzpicture}[>=stealth, scale=0.8],
+        % the rectangle of Queue 1
+        \draw (0,0) -- ++(2cm,0) -- ++(0,-1.5cm) -- ++(-2cm,0);
+        % The label above Queue 1 -> M
+        \node[anchor=north] at (1.5cm, 1cm) {\( 
+            \overbrace{\qquad \qquad \qquad \qquad}^{M} 
+        \)};
+        % the vertical lines in Queue 1
+        \foreach \i in {1,...,4, 5.7}
+        \draw (2cm-\i*10pt,0) -- +(0,-1.5cm);
+
+        % the circle in Queue 1
+        \draw (2.75,-0.75cm) circle [radius=0.75cm] node {\(0\)};
+
+        % the rectangle in Queue 2
+        \draw (5,1.25) -- ++(2cm,0) -- ++(0,-1.5cm) -- ++(-2cm,0);
+        % the vertical lines in Queue 2
+        \foreach \i in {1,...,4, 5.7}
+        \draw (7cm-\i*10pt,1.25) -- +(0,-1.5cm);
+        % The two vertical lines at the very start of Queue 2 
+        \draw (7cm-55pt,1.1) -- +(0,-1.2cm);
+        \draw (7cm-53pt,1) -- +(0,-1cm);
+        % The label above Queue 2 -> N
+        \node[anchor=north] at (6.6cm, 2.2cm) {\( 
+            \overbrace{\qquad \qquad \qquad \qquad}^{N} 
+        \)};
+
+        % the circle in Queue 2
+        \draw (7.75,0.5) circle [radius=0.75cm] node {\(C\)};
+
+        % Arrow line from Queue 2 outside
+        \draw[->] (8.5,0.525) -- +(20pt,0);
+
+        % Line from lambda_2 to Queue 1
+        \draw[<-] (-0.3,-0.75) -- +(-40pt,0) node[left] {\( \lambda_2 \)};
+        % First line (horizontal) after Queue 1
+        \draw[-] (3.5,-0.75) -- +(20pt,0);
+        % Second line (vertical) after Queue 1
+        \draw (4.2, 0.525) -- (4.2, -0.75);
+
+        % First line (horizontal) from lambda_1
+        \draw (4.2, 1.8) -- +(-169.5pt,0) node[left] {\( \lambda_1 \)};
+        % Second line (vertical) from lambda_1
+        \draw (4.2, 1.8) -- (4.2, 0.525);
+        % Arrow line to Queue 2
+        \draw[->] (4.2, 0.525) -- (4.8, 0.525);  
+    \end{tikzpicture}
+    \caption{Queueing Model}
+    \label{fig:diagram_of_queueing_system}
+\end{figure}
+
+Note here that both types of individuals can become lost to the system. 
+Individual allocated from the distributor become lost to the system whenever 
+an arrival occurs and the second waiting zone is at full capacity (\(M\) 
+individuals already waiting).
+Similarly, other individuals get lost whenever they arrive at the first waiting 
+zone and it is at full capacity (\(N - C\) individuals already waiting).
+
+Following this queuing model, the two queueing systems' choice of strategy will 
+then rely solely on satisfying their own 
+objective, which is to make sure that the waiting time in the first waiting zone 
+of a proportion of individuals will be below the predefined target time.
 
@@
 decision of the distributor is the proportion of lost individuals.
-% TODO: Clarify above (somewhere near the diagram of the queueing system) that 
-% individuals can be lost at all.
 Equation \ref{eq:obj-distributor} can be used to capture a mixture 
@@
 
-\begin{figure}[h]
+\begin{figure}[ht]
     \centering

### 2021-04-26 sections/queueing_model/main.tex
Write details of the Markov-chain model
- Define the model
- Define state space
- Define transition matrix and state-mapping function

@@
 \section{A queueing models with 2 consecutive buffer centres}
+
+% TODO: If this is to be one paper maybe the first two paragraphs do not need to
+% include so much details or even better omit some of the details in the game
+% overview section.
+In this section, a more in-depth explanation of the queueing model shown in 
+figure \ref{fig:diagram_of_queueing_system} will be given.
+This is a queuing model that consists of two waiting spaces, one for each type
+of patient.
+
+The model consists of two types of individuals; class 1 and class 2.
+Class 1 individuals arrive instantly at waiting zone 1 and proceed to wait to
+receive their service. 
+Class 2 individuals arrive at waiting zone 2 and wait there until they are 
+allowed to move to waiting zone 1. 
+They are allowed to proceed to the next waiting zone only when the number of 
+individuals in the next system (in waiting zone 1 and in service) is less than a 
+pre-determined threshold \(T\).
+When the threshold is reached, all class 2 individuals that arrive will remain 
+\textit{``blocked''} in the buffer centre until the number of people in the 
+system is reduced below \(T\).
+
+% TODO: Possibly worth including the diagram of the queueing model here
+
+In order to model such queueing system a Markov chain model was used.
+Markov chains are a special kind of memoryless stochastic systems where the 
+outcome of the next iteration depends only on the current state
+~\cite{kemeny1976markov}. 
+The way such models are formulated is through a directed graph where each vertex
+is consider a state of the system and each edge represents the transition rate
+between its two linking vertices.
+The states of the Markov chain are denoted by \((u,v)\) where:
+
+\begin{itemize}
+    \item \(u\) = number of individuals blocked
+    \item \(v\) = number of individuals either in waiting zone 1 or in the
+    service centre
+\end{itemize}
+
+The state space of the Markov chain \(S\) is defined as the union between
+\(S_1\) and \(S_2\), where \(S_1\) represents the set of states where the total 
+number of individuals is less than \(T\) and \(S_2\) the set of states where the
+total number of individuals is greater than \(T\).
+
+\begin{align}
+    S(T) =& S_1(T) \cup S_2(T) \text{ where:} \nonumber \\
+    S_1(T) =& \left\{(0, v)\in\mathbb{N}_0^2 \; | \; v < T \right\} 
+    \label{eq:state_space} \\
+    S_2(T) =& \{(u, v)\in\mathbb{N}_0^2 \; | \; v \geq T \} \nonumber
+\end{align}
+
+The transition matrix \(Q\) of the Markov chain consists of the transition rates
+between the numerous states of the model. Every entry \( q_{i,j} = 
+q_{(u_i, v_i),(u_j, v_j)} \) represents the transition rate from state 
+\( i = (u_i, v_i) \) to state \( j = (u_j , v_j) \) for all 
+\( (u_i, v_i), (u_j, v_j) \in S \).
+The entries of \(Q\) can be calculated using the state-mapping function 
+described in \ref{eq:markov_transition_rate}:
+
+\begin{equation} \label{eq:markov_transition_rate}
+    q_{i, j} = 
+    \begin{cases}
+        \Lambda, & \textbf{if } (u_i, v_i) - (u_j, v_j) = (0,-1) \textbf{ and } 
+        v_i < \text{t} \\
+        \lambda_1, & \textbf{if } (u_i, v_i) - (u_j, v_j) = (0,-1) \textbf{ and } 
+        v_i \geq \text{t} \\
+        \lambda_2, & \textbf{if } (u_i, v_i) - (u_j, v_j) = (-1,0) \\
+        v_i \mu, & \textbf{if } (u_i, v_i) - (u_j, v_j) = (0,1) \textbf{ and } 
+        v_i \leq C \textbf{ or} \\ & \hspace{0.37cm}(u_i, v_i) - (u_j, v_j) = (1,0) 
+        \textbf{ and } v_i = T \leq C \\
+        C \mu, & \textbf{if } (u_i, v_i) - (u_j, v_j) = (0,1) \textbf{ and } v_i > C 
+        \textbf{ or} \\ & \hspace{0.37cm}(u_i, v_i) - (u_j, v_j) = (1,0) \textbf{ and } 
+        v_i = T > C\\
+        -\sum_{j=1}^{|Q|}{q_{i,j}} & \textbf{if } i = j \\
+        0, & \textbf{otherwise}
+    \end{cases}
+\end{equation}
+
+% \input{sections/queueing_model/general-markov-model/main.tex}
+
+In order to acquire an exact solution of the problem a slight adjustment needs to 
+be considered. 
+The problem defined above assumes no upper boundary to the number of individuals 
+that can wait for service or for the ones that are blocked in the buffer centre. 
+Therefore, a different state space \( \tilde S \) needs to be constructed where 
+\( \tilde S \subseteq S \) and there is a maximum allowed number of people \(N\) 
+that can be in the system and a maximum allowed number of people \(M\) that can
+be blocked in the buffer centre:
+
+\begin{equation}
+    \tilde S = \left\{ (u, v) \in S\;| u \leq M, v\leq N \right\}
+\end{equation}
+
+\subsection{Performance Measures}
+
+\subsection{Example}

### 2021-04-26 sections/queueing_model/general-markov-model/main.tex
Add general Markov-chain picture

--- 2021-03-11 MarkovChain/markov_chain_model/main.tex
@@
-\section{A queueing model with 2 consecutive buffer centres}
-
-\subsection{System}
-The following Markov chain represents the transition between states of a service
-centre 
-while capturing the interactions between it and a buffer centre.
-The service centre accepts two types of individuals; Class 1 and Class 2.  
-Class 2 individuals are accepted until a pre-determined threshold \(T\) of 
-individuals is reached.
-When reached, all Class 2 individuals that arrive will remain \textit{``blocked''}
-in the buffer centre until the number of people in the system is 
-reduced below \(T\). 
-Additionally, if the people in the service centre keep rising, they may exceed
-the number 
-of servers \(C\) available, which will in turn mean that every new person will 
-have to wait for a server to become free. 
-The states of the Markov chain are denoted by \((u,v)\) where:
-
-\begin{itemize}
-    \item \(u\) = number of Class 2 individuals blocked
-    \item \(v\) = number of Class 1 individuals in the service centre
-\end{itemize}
-
-\begin{figure}
+\begin{figure}[H]
     \centering
+    \scalebox{.8}
+    {
         \begin{tikzpicture}[-, node distance = 0.9cm, auto, every node/.style={scale=0.7}]
@@
             % Fifth line
-        % \node[state, node distance = \altdist, minimum size=\minsz, below=of five_three] 
-        % (general_case_mid) {\( (u_i, v_i) \)};
             \node[draw=none, node distance = 0.3cm, minimum size=\minsz, below=of four_three] 
@@
         \end{tikzpicture}
+    }
     \caption{Markov chain} 
-    \label{markov_model}
+    \label{fig:general-markov_model}
 \end{figure}
-
-\subsubsection{Markov-chain state mapping function}
-The transition matrix of the Markov-chain representation described above can be 
-denoted by a state mapping function. 
-The state space of this function is defined as:
-
-\begin{align}
-    S(T) =& S_1(T) \cup S_2(T) \text{ where:} \nonumber \\
-    S_1(T) =& \left\{(0, v)\in\mathbb{N}_0^2 \; | \; v < T \right\} \label{eq:state_space} \\
-    S_2(T) =& \{(u, v)\in\mathbb{N}_0^2 \; | \; v \geq T \} \nonumber
-\end{align}
-
-Therefore, the entries of the transition matrix \(Q\), can be given by 
-\( q_{i,j} = q_{(u_i, v_i),(u_j, v_j)} \) which is the transition rate from state 
-\( i = (u_i, v_i) \) to state \( j = (u_j , v_j) \) for all 
-\( (u_i, v_i), (u_j, v_j) \in S \).
-
-\begin{equation} \label{eq:markov_transition_rate}
-    q_{i, j} = 
-    \begin{cases}
-        \Lambda, & \textbf{if } (u_i, v_i) - (u_j, v_j) = (0,-1) \textbf{ and } 
-        v_i < \text{t} \\
-        \lambda_1, & \textbf{if } (u_i, v_i) - (u_j, v_j) = (0,-1) \textbf{ and } 
-        v_i \geq \text{t} \\
-        \lambda_2, & \textbf{if } (u_i, v_i) - (u_j, v_j) = (-1,0) \\
-        v_i \mu, & \textbf{if } (u_i, v_i) - (u_j, v_j) = (0,1) \textbf{ and } 
-        v_i \leq C \textbf{ or} \\ & \hspace{0.37cm}(u_i, v_i) - (u_j, v_j) = (1,0) 
-        \textbf{ and } v_i = T \leq C \\
-        C \mu, & \textbf{if } (u_i, v_i) - (u_j, v_j) = (0,1) \textbf{ and } v_i > C 
-        \textbf{ or} \\ & \hspace{0.37cm}(u_i, v_i) - (u_j, v_j) = (1,0) \textbf{ and } 
-        v_i = T > C\\
-        -\sum_{j=1}^{|Q|}{q_{i,j}} & \textbf{if } i = j \\
-        0, & \textbf{otherwise}
-    \end{cases}
-\end{equation}
-
-In order to acquire an exact solution of the problem a slight adjustment needs to 
-be considered. 
-The problem defined above assumes no upper boundary to the number of individuals 
-that can wait for service or the ones that are blocked in the buffer centre. 
-Therefore, a different state space \( \tilde S \) needs to be constructed where 
-\( \tilde S \subseteq S \) and there is a maximum allowed number of people \( N \) 
-that can be in the system and a maximum allowed number of people \( M \) that can
-be blocked in the buffer centre:
-
-\begin{equation}
-    \tilde S = \left\{ (u, v) \in S\;| u \leq M, v\leq N \right\}
-\end{equation}
-
-\subsubsection{Steady State}
-Having calculated the transition matrix \( Q \) for a given set of parameters the 
-probability vector \( \pi \) needs to be considered. 
-The vector \( \pi \) is commonly used to study such stochastic systems and it's 
-main purpose is to keep track of the probability of being at any given state of 
-the system. 
-The term \textit{steady state} refers to the instance of the vector \( \pi \) where 
-the probabilities of being at any state become stable over time. 
-Thus, by considering the steady state vector \( \pi \) the relationship between 
-it and \(Q \) is given by:
-
-\[
-\frac{d\pi}{dt} = \pi Q = 0
-\]
-
-There are numerous methods that can be used to solve problems of such kind. 
-In this paper only numeric and algebraic approaches will be considered.
-
-The first approach to be considered is to solve the differential equation numerically 
-by observing the behaviour of the model over time. 
-The solution is obtained via python's SciPy library. 
-The functions odeint and solve\textunderscore ivp have been used in order to find 
-a solution to the problem. 
-Both of these functions can be used to solve any system of first order ODEs.

### 2021-04-28 known.py
Update known.py

@@ -1,9 +1,14 @@
 """ A set of known words and end-of-word patterns for the spellchecker. """
 
 words = {
+    "automata",
+    "calc",
     "HB",
     "ieeetr",
+    "math",
+    "memoryless",
     "Michalis",
     "Panayides",
+    "pre",
     "queueing",
 }

### 2021-04-29 sections/model_overview/main.tex
Minor changes in queueing diagram
Add a gap between the lines of the second queue and add T in that gab
Change caption of figure

@@
         % The two vertical lines at the very start of Queue 2 
-        \draw (7cm-55pt,1.1) -- +(0,-1.2cm);
-        \draw (7cm-53pt,1) -- +(0,-1cm);
+        \draw (7cm-54pt,1.2) -- +(0,-0.5cm);
+        \draw (7cm-54pt,0.3) -- +(0,-0.5cm);        
+        \draw (7cm-51pt,1.1) -- +(0,-0.4cm);
+        \draw (7cm-51pt,0.3) -- +(0,-0.4cm);
+
+        % The label between the lines for T
+        \node[anchor=north] at (5.15, 0.77 cm) {\small{\( T \)}};
+
         % The label above Queue 2 -> N
@@
     \end{tikzpicture}
-    \caption{Queueing Model}
+    \caption{A diagrammatic representation of the queueing model. 
+    The threshold \(T\) only applies to arrivals from the first buffer. 
+    If the second buffer is at that threshold only individuals of the first type 
+    are accepted (at a rate \(\lambda_1\)) and individuals of the second type 
+    (arriving at a rate \(\lambda_2\)) are held blocked in the first buffer.}
     \label{fig:diagram_of_queueing_system}

### 2021-04-29 sections/queueing_model/main.tex
Update known.py
Create subsections/ subdirectory
Minor edits on figures
Reference figure of previous section and change the caption of
the general Markov chain figure

@@
-\section{A queueing models with 2 consecutive buffer centres}
+\section{A queueing model with 2 consecutive buffer centres}
 
@@
 system is reduced below \(T\). 
-
-% TODO: Possibly worth including the diagram of the queueing model here
+This is shown diagrammatically in figure \ref{fig:diagram_of_queueing_system}.
 
@@
 
-% \input{sections/queueing_model/general-markov-model/main.tex}
+\input{sections/queueing_model/general-markov-model/main.tex}
 
@@
 
-\subsection{Performance Measures}
+\input{sections/queueing_model/subsections/performance_measures/main.tex}
 
-\subsection{Example}
+\input{sections/queueing_model/subsections/example/main.tex}

### 2021-04-29 sections/queueing_model/main.tex
Add paragraph for transition rates

@@
 This is shown diagrammatically in figure \ref{fig:diagram_of_queueing_system}.
+The parameters of the described queueing model are:
+
+\begin{itemize}
+    \item $\lambda_1$: The arrival rate of class 1 individuals
+    \item $\lambda_2$: The arrival rate of class 2 individuals
+    \item $\mu$: The service rate for individuals receiving service in waiting 
+    zone 1
+    \item $C$: The number of servers
+    \item $T$: The threshold where class 2 individuals will start being blocked 
+\end{itemize}
 
@@
         v_i < \text{t} \\
-        \lambda_1, & \textbf{if } (u_i, v_i) - (u_j, v_j) = (0,-1) \textbf{ and } 
-        v_i \geq \text{t} \\
+        \lambda_1, & \textbf{if } (u_i, v_i) - (u_j, v_j) = (0,-1) 
+        \textbf{ and } v_i \geq \text{t} \\
         \lambda_2, & \textbf{if } (u_i, v_i) - (u_j, v_j) = (-1,0) \\
         v_i \mu, & \textbf{if } (u_i, v_i) - (u_j, v_j) = (0,1) \textbf{ and } 
-        v_i \leq C \textbf{ or} \\ & \hspace{0.37cm}(u_i, v_i) - (u_j, v_j) = (1,0) 
-        \textbf{ and } v_i = T \leq C \\
-        C \mu, & \textbf{if } (u_i, v_i) - (u_j, v_j) = (0,1) \textbf{ and } v_i > C 
-        \textbf{ or} \\ & \hspace{0.37cm}(u_i, v_i) - (u_j, v_j) = (1,0) \textbf{ and } 
-        v_i = T > C\\
+        v_i \leq C \textbf{ or} \\ & \hspace{0.37cm}(u_i, v_i) - (u_j, v_j) = 
+        (1,0) \textbf{ and } v_i = T \leq C \\
+        C \mu, & \textbf{if } (u_i, v_i) - (u_j, v_j) = (0,1) \textbf{ and } 
+        v_i > C 
+        \textbf{ or} \\ & \hspace{0.37cm}(u_i, v_i) - (u_j, v_j) = (1,0) 
+        \textbf{ and } v_i = T > C\\
         -\sum_{j=1}^{|Q|}{q_{i,j}} & \textbf{if } i = j \\
@@
 \end{equation}
+
+Note that $\Lambda$ here denotes the overall arrival rate in the model by both 
+classes of individuals (i.e. $\Lambda = \lambda_1 + \lambda_2$). 
+A visualisation of how the transition rates relate to the states of the model 
+can be seen in the general Markov chain model shown in figure 
+\ref{fig:general-markov-model}.
 

### 2021-04-29 sections/queueing_model/main.tex
Apply minor edits

@@
 \begin{itemize}
-    \item $\lambda_1$: The arrival rate of class 1 individuals
-    \item $\lambda_2$: The arrival rate of class 2 individuals
-    \item $\mu$: The service rate for individuals receiving service in waiting 
+    \item \(\lambda_1\): The arrival rate of class 1 individuals
+    \item \(\lambda_2\): The arrival rate of class 2 individuals
+    \item \(\mu\): The service rate for individuals receiving service in waiting 
     zone 1
-    \item $C$: The number of servers
-    \item $T$: The threshold where class 2 individuals will start being blocked 
+    \item \(C\): The number of servers
+    \item \(T\): The threshold where class 2 individuals will start being blocked 
 \end{itemize}
@@
 
-Note that $\Lambda$ here denotes the overall arrival rate in the model by both 
-classes of individuals (i.e. $\Lambda = \lambda_1 + \lambda_2$). 
+Note that \(\Lambda\) here denotes the overall arrival rate in the model by both 
+classes of individuals (i.e. \(\Lambda = \lambda_1 + \lambda_2\)). 
 A visualisation of how the transition rates relate to the states of the model 

### 2021-04-29 sections/queueing_model/subsections/performance_measures/main.tex
Write main.tex for performance measures subsection

\subsection{Performance Measures}

The transition matrix \( Q \) defined in \ref{eq:markov_transition_rate} can be 
used to get the probability vector \( \pi \).
The vector \( \pi \) is commonly used to study stochastic systems and it's main
purpose is to keep track of the probability of being at any given state of 
the system.
The term \textit{steady state} refers to the instance of the vector \( \pi \) 
where the probabilities of being at any state become stable over time. 
Thus, by considering the steady state vector \( \pi \) the relationship between 
it and \( Q \) is given by:

\[
    \frac{d\pi}{dt} = \pi Q = 0
\]

Using vector \(\pi\) there are numerous performance measures of the model that 
can be calculated. 
The following equations utilise \(\pi\) to get performance measures on the 
average number of people at certain sets of state.

\begin{itemize}
    \item Average number of people in the system: 
        \[L = \sum_{i=1}^{|\pi|} \pi_i (u_i + v_i)\]
    \item Average number of people in the service centre: 
        \[L_H = \sum_{i=1}^{|\pi|} \pi_i v_i\]
    \item Average number of people in waiting zone 2:
        \[L_A = \sum_{i=1}^{|\pi|} \pi_i u_i\] 
\end{itemize}

Consequently, there are some additional performance measures of interest that
are not as straightforward to calculate.
Such performance measures are the mean waiting time in the system (for both 
class 1 and class 2 individuals), the mean time blocked in waiting zone 2 (only 
valid for class 2 individuals) and the proportion of individuals that wait in 
waiting zone 1 within a predefined time target.

### 2021-04-29 sections/queueing_model/subsections/performance_measures/waiting_time/main.tex
Write main.tex for waiting time subsubsection

\subsubsection{Waiting time}
% TODO: Include recursive formula as well??

Waiting time is the amount of time that individuals from either class wait in 
waiting zone 1 so that they can receive their service. 
For a given set of parameters there are three different performance measures 
around the mean waiting time that can be calculated; the mean waiting time of
class 1 individuals, the mean waiting time of class 2 individuals and the 
overall mean waiting time.

Since some of the individuals can be lost to the model, a new set of states 
needs to be defined; the set of \textit{accepting states}. 
That is the set of states that the model is able to accept a certain type of
individual. 
The set of accepting states for class 1 individuals is defined as:

\begin{equation}\label{eq:accepting-states-class-1}
    S_A^{(1)} = \{(u, v) \in S \; | \; v < N \}
\end{equation}

In essence, for class 1 individuals, this is the set of states that are not on 
the last column of states in the Markov chain.
Equivalently, the set of accepting states for class 2 individuals is defined as:

\begin{equation}\label{eq:accepting-states-class-2}
    S_A^{(2)}=
    \begin{cases}
        \{(u, v) \in S \; | \; u < M \}, & \textbf{if } T \leq N\\
        \{(u, v) \in S \; | \; v < N \}, & \textbf{otherwise}
    \end{cases}
\end{equation}

Note here that if the threshold is less than or equal the total capacity of the
system the set includes all states that are not on the last column of the 
Markov chain.
Otherwise, the set of accepting state is identical to 
\ref{eq:accepting-states-class-1}. Thus, the expressions for the waiting times 
for class 1 and class 2 individuals are given by:

\begin{equation} \label{eq:closed_form_waiting_others}
    W^{(1)} = \frac{\sum_{\substack{(u,v) \, \in S_A^{(1)} \\ v \geq C}} 
    \frac{1}{C \mu} \times (v-C+1) \times \pi(u,v)}{\sum_{(u,v) \, 
    \in S_A^{(1)}} \pi(u,v)}
\end{equation}

\begin{equation}\label{eq:closed_form_waiting_ambulance}
    W^{(2)} = \frac{\sum_{\substack{(u,v) \, \in S_A^{(2)} \\ min(v,T) \geq C}} 
    \frac{1}{C \mu} \times (\min(v+1,T)-C) \times \pi(u,v)}{\sum_{(u,v) \, 
    \in S_A^{(2)}} \pi(u,v)}
\end{equation}

Consequently, the overall waiting time can be estimated by a linear combination 
of \(W_1\) and \(W_2\). 
Thus, the overall waiting time can calculated by the following equation where 
\(c_1\) and \(c_2\) are the coefficients of the terms:

\begin{equation}\label{eq:overall_waiting_time_coeff}
    W = c_1 W^{(1)} + c_2 W^{(2)}
\end{equation}

The two coefficients represent the proportion of individuals of each type that 
did not get lost and traversed through the model.
Thus, one should account for the probability that an individual is lost to the 
system. 
This probability can be easily calculated by using the two sets of accepting 
states \(S_A^{(2)}\) and \(S_A^{(1)}\) defined in equations 
\ref{eq:accepting-states-class-1} and \ref{eq:accepting-states-class-2}. 
Using these equations the probability, for either class type, that an individual 
is not lost in the system is given by:

\begin{equation*}
    P(L'_1) = \sum_{(u,v) \, \in S_A^{(1)}} \pi(u,v) \hspace{2cm}
    P(L'_2) = \sum_{(u,v) \, \in S_A^{(2)}} \pi(u,v)
\end{equation*}

Thus, by using these values as the coefficient of equation 
\ref{eq:overall_waiting_time_coeff} the resultant equation can be used to get 
the overall waiting time.

\begin{equation}\label{overall_waiting_time}
    W = \frac{\lambda_1 P(L'_1)}{\lambda_2 P(L'_2) + \lambda_1 P(L'_1)} W^{(1)} + 
    \frac{\lambda_2 P(L'_2)}{\lambda_2 P(L'_2) + \lambda_1 P(L'_1)} W^{(2)}
\end{equation}

### 2021-04-29 known.py
Update known.py

@@ -3,6 +3,7 @@
 words = {
     "automata",
     "calc",
+    "dt",
     "HB",
     "ieeetr",
     "math",

### 2021-05-01 sections/queueing_model/main.tex
Fix typo
Apply suggestions from code review
Co-authored-by: Vince Knight <vincent.knight@gmail.com>

@@
 allowed to move to waiting zone 1. 
-They are allowed to proceed to the next waiting zone only when the number of 
-individuals in the next system (in waiting zone 1 and in service) is less than a 
+They are allowed to proceed only when the number of 
+individuals in waiting zone 1 \textbf{and} in service is less than a 
 pre-determined threshold \(T\).
-When the threshold is reached, all class 2 individuals that arrive will remain 
-\textit{``blocked''} in the buffer centre until the number of people in the 
+When the number of individuals is equal to or exceeds this threshold, all second type individuals that arrive will remain 
+\textit{``blocked''} in waiting zone 1 until the number of people in the 
 system is reduced below \(T\). 
@@
 \begin{itemize}
-    \item \(\lambda_1\): The arrival rate of class 1 individuals
-    \item \(\lambda_2\): The arrival rate of class 2 individuals
-    \item \(\mu\): The service rate for individuals receiving service in waiting 
-    zone 1
+    \item \(\lambda_i\): The arrival rate of individuals of type \(i\in\{1, 2\}\)
+    \item \(\mu\): The service rate for individuals receiving service
     \item \(C\): The number of servers
-    \item \(T\): The threshold where class 2 individuals will start being blocked 
+    \item \(T\): The threshold at which individuals of the second type are blocked
 \end{itemize}
@@
 \begin{itemize}
-    \item \(u\) = number of individuals blocked
-    \item \(v\) = number of individuals either in waiting zone 1 or in the
+    \item \(u\) is the number of individuals blocked
+    \item \(v\) is the number of individuals either in waiting zone 1 or in the
     service centre
@@
 
-\input{sections/queueing_model/general-markov-model/main.tex}
+\input{sections/queueing_model/general_markov_model/main.tex}
 

### 2021-05-01 sections/queueing_model/main.tex
Apply more siggestions from review
- Markov chains intro
- State space definition
- Replace q_{i,j} with Q_{ij}
- Minor changes

@@
 
-In order to model such queueing system a Markov chain model was used.
-Markov chains are a special kind of memoryless stochastic systems where the 
-outcome of the next iteration depends only on the current state
-~\cite{kemeny1976markov}. 
-The way such models are formulated is through a directed graph where each vertex
-is consider a state of the system and each edge represents the transition rate
-between its two linking vertices.
+Under the assumption that all rates (arrival and service) are Markovian the
+queuing system corresponds to a Markov chain~\cite{kemeny1976markov}.
 The states of the Markov chain are denoted by \((u,v)\) where:
@@
 
-The state space of the Markov chain \(S\) is defined as the union between
-\(S_1\) and \(S_2\), where \(S_1\) represents the set of states where the total 
-number of individuals is less than \(T\) and \(S_2\) the set of states where the
-total number of individuals is greater than \(T\).
+We denote the state space of the Markov chain as  \(S=S(T)\) which can be 
+written as the disjoint union~\ref{eq:definition_of_S_as_disjoint_union}.
 
@@
     S_1(T) =& \left\{(0, v)\in\mathbb{N}_0^2 \; | \; v < T \right\} 
-    \label{eq:state_space} \\
+    \label{eq:definition_of_S_as_disjoint_union} \\
     S_2(T) =& \{(u, v)\in\mathbb{N}_0^2 \; | \; v \geq T \} \nonumber
@@
 The transition matrix \(Q\) of the Markov chain consists of the transition rates
-between the numerous states of the model. Every entry \( q_{i,j} = 
-q_{(u_i, v_i),(u_j, v_j)} \) represents the transition rate from state 
+between the numerous states of the model. Every entry \( Q_{ij} = 
+Q_{(u_i, v_i),(u_j, v_j)} \) represents the transition rate from state 
 \( i = (u_i, v_i) \) to state \( j = (u_j , v_j) \) for all 
@@
 \begin{equation} \label{eq:markov_transition_rate}
-    q_{i, j} = 
+    Q_{ij} = 
     \begin{cases}
@@
         \textbf{ and } v_i = T > C\\
-        -\sum_{j=1}^{|Q|}{q_{i,j}} & \textbf{if } i = j \\
+        -\sum_{j=1}^{|Q|}{Q_{ij}} & \textbf{if } i = j \\
         0, & \textbf{otherwise}
@@
 
-In order to acquire an exact solution of the problem a slight adjustment needs to 
-be considered. 
+In order to acquire an exact solution of the problem a slight adjustment needs 
+to be considered. 
 The problem defined above assumes no upper boundary to the number of individuals 

### 2021-05-01 known.py
Update known.py

@@ -6,6 +6,8 @@ words = {
     "dt",
     "HB",
     "ieeetr",
+    "ij",
+    "Markovian",
     "math",
     "memoryless",
     "Michalis",

### 2021-05-14 sections/queueing_model/subsections/performance_measures/waiting_time/main.tex
Minor edits

@@
-\subsubsection{Waiting time}
-% TODO: Include recursive formula as well??
+\subsubsection{Waiting time} \label{sec:waiting-time}
 
@@
 
-\begin{equation} \label{eq:closed_form_waiting_others}
+\begin{equation} \label{eq:closed-form-waiting-class-1}
     W^{(1)} = \frac{\sum_{\substack{(u,v) \, \in S_A^{(1)} \\ v \geq C}} 
@@
 
-\begin{equation}\label{eq:closed_form_waiting_ambulance}
+\begin{equation}\label{eq:closed-form-waiting-class-2}
     W^{(2)} = \frac{\sum_{\substack{(u,v) \, \in S_A^{(2)} \\ min(v,T) \geq C}} 
@@
 
-\begin{equation}\label{eq:overall_waiting_time_coeff}
+\begin{equation}\label{eq:overall-waiting-time-coeff}
     W = c_1 W^{(1)} + c_2 W^{(2)}
@@
 Thus, by using these values as the coefficient of equation 
-\ref{eq:overall_waiting_time_coeff} the resultant equation can be used to get 
+\ref{eq:overall-waiting-time-coeff} the resultant equation can be used to get 
 the overall waiting time.
 
-\begin{equation}\label{overall_waiting_time}
+\begin{equation}\label{overall-waiting-time}
     W = \frac{\lambda_1 P(L'_1)}{\lambda_2 P(L'_2) + \lambda_1 P(L'_1)} W^{(1)} + 

### 2021-05-14 sections/queueing_model/subsections/performance_measures/blocking_time/main.tex
Add blocking time algorithm

\subsubsection{Blocking time}

% TODO: Possibly replace the contents of this section with the ones for the 
% closed form formula of the blocking time
% Currently the direct approach one is shown

Unlike the waiting time, the blocking time is only calculated for individuals of
the second type.  
That is because individuals of the first type cannot be blocked. 
Thus, one only needs to consider the pathway of type 2 individuals to get the 
mean blocking time of the system. 
The set of states where individuals can be blocked is defined as:

\begin{equation} \label{eq:set_of_blocking_states}
    S_b = \{(u,v) \in S \; | \; u > 0\}
\end{equation}

In order to not consider individuals that will be lost to the system, the set of 
accepting states needs to be taken into consideration. 
As defined in section \ref{sec:waiting-time}, the set of accepting states is 
given by \ref{eq:accepting-states-class-2}:

\begin{equation*}
    S_A^{(2)}=
    \begin{cases}
        \{(u, v) \in S \; | \; u < M \} & \textbf{if } T \leq N\\
        \{(u, v) \in S \; | \; v < N \} & \textbf{otherwise}
    \end{cases}
\end{equation*}

% For the waiting time formula in sections \ref{sec:recursive-waiting-time-others}
% and \ref{sec:recursive-waiting-time-ambulance}
% the mean sojourn time for each state was considered,
% ignoring any arrivals.
% Here, the same approach is used but ignoring only class 2
% arrivals. That is because for the waiting time formula, once an individual enters 
% the service centre (i.e. starts waiting) any individual arriving after them will 
% not affect their
% pathway. That is not the case for blocking time. When a class 2 individual is 
% blocked, 
% any class 1 individual that arrives will cause the blocked individual to remain 
% blocked for more time. Therefore, class 1 arrivals are considered here:

The mean sojourn time for each state is given by the inverse of the out-flow of
that state.
However, whenever a type 2 individual arrives at the system, no subsequent 
arrival of another type 2 individual can affect its pathway or total time in 
the system.
Therefore, looking at the mean time in the system from the perspective of an 
individual of the second type, all such type 2 arrivals need to be ignored.
Note here that this is not the case for individuals of the first type.
Whenever a type 2 individual is blocked and a type 1 individual arrives the type
2 individuals will remain blocked for some additional amount of time.
Thus, the mean time that a type 2 individual spends at each state is given by:

\begin{equation}\label{eq:time_in_state_blocking_time}
    c(u,v) = 
    \begin{cases}
        \frac{1}{\min(v,C) \mu}, & \text{if } v = N\\
        \frac{1}{\lambda_1 + \min(v,C) \mu}, & \text{otherwise}
    \end{cases}
\end{equation}

In equation \ref{eq:time_in_state_blocking_time}, both service completions and 
class 1 arrivals are considered. 
Thus, from a blocked individual's perspective whenever the system moves from one 
state \((u,v)\)
to another state it can either:

\begin{itemize}
    \item be because of a service being completed: we will denote the probability 
    of this happening by \(p_s(u,v)\). 
    \item be because of an arrival of an individual of class 1: denoting such 
    probability by \(p_o(u,v)\).
\end{itemize}
The probabilities are given by:

\begin{equation*}
    p_s(u,v) = \frac{\min(v,C)\mu}{\lambda_1 + \min(v,C)\mu}, \qquad
    p_o(u,v) = \frac{\lambda_1}{\lambda_1 + \min(v,C)\mu}
\end{equation*}

Having defined \(c(u,v)\) and \(S_b\) a formula for the blocking time that is
expected to occur at each state can be given by:

\begin{equation}\label{eq:general_blocking_time_at_each_state}
    b(u,v) = 
    \begin{cases} 
        0, & \textbf{if } (u,v) \notin S_b \\
        c(u,v) + b(u - 1, v), & \textbf{if } v = N = T\\
        c(u,v) + b(u, v-1), & \textbf{if } v = N \neq T \\
        c(u,v) + p_s(u,v) b(u-1, v) + p_o(u,v) b(u, v+1), & \textbf{if } u > 0 
        \textbf{ and } \vspace{-0.2cm} \\ 
        & \quad v = T \\
        c(u,v) + p_s(u,v) b(u, v-1) + p_o(u,v) b(u, v+1), & \textbf{otherwise} \\
    \end{cases}
\end{equation}

A direct approach will be used to solve this equation here. 
By enumerating all equations of (\ref{eq:general_blocking_time_at_each_state}) 
for all states \((u,v)\) that belong in \(S_b\) 
a system of linear equations arises where the unknown variables are all the 
\(b(u,v)\) terms. 
Note here that these equations correspond to all blocking states as defined in
\ref{eq:set_of_blocking_states}. 
Equations that correspond to non-blocking states have a value of \(0\) as 
defined in \ref{eq:general_blocking_time_at_each_state}
The general form of the equation in terms of \(C,T,N \text{ and } M\) is given by:

\begin{align}
    b(1,T) \quad &= \quad c(1, T) + p_o b(1, T + 1) \label{eq:first_eq_of_blocking_general}\\
    b(1,T + 1) \quad &= \quad c(1, T + 1) + p_s b(1, T) + p_o b(1, T + 1) \\
    b(1,T + 2) \quad &= \quad c(1, T + 2) + p_s b(1, T + 1) + p_o b(1, T + 3) \\
    & \ \, \vdots \nonumber \\
    b(1, N) \quad &= \quad c(1, N) + b(1, N - 1) \\
    b(2, T) \quad &= \quad c(2, T) + p_s b(1, T) + p_o b(2, T + 1) \\
    b(2, T + 1) \quad &= \quad c(2, T + 1) + p_s b(2, T) + p_o b(2, T + 2) \\
    & \ \, \vdots \nonumber \\
    b(M - 1, N) \quad &= \quad c(M, N - 1) + b(M, N-1) \\ 
    b(M, T) \quad &= \quad c(T, N) + p_s b(T-1, N) + p_o b(T, N+1) \\
    & \ \, \vdots \nonumber \\
    b(M, N) \quad &= \quad c(M, N) + b(M, N-1) \label{eq:last_eq_of_blocking_general}
\end{align}

The equivalent matrix notation of the linear system of equations 
(\ref{eq:first_eq_of_blocking_general}) - (\ref{eq:last_eq_of_blocking_general})
is given by \(Zx=y\), where:
\begin{equation}\label{eq:general_algebaric_approach_blocking_time}
    \scalebox{0.73}{\(
        Z = 
        \begin{pmatrix}
            -1 & p_o & 0 & \dots & 0 & 0 & 0 & 0 & 0 & \dots & 0 & 0 \\ %(1,T)
            p_s & -1 & p_o & \dots & 0 & 0 & 0 & 0 & 0 & \dots & 0 & 0 \\ %(1,T+1)
            0 & p_s & -1 & \dots & 0 & 0 & 0 & 0 & 0 & \dots & 0 & 0 \\ %(1,T+2)
            \vdots & \vdots & \vdots & \ddots & \vdots & \vdots & \vdots & 
            \vdots & \vdots & \ddots & \vdots & \vdots \\ 
            0 & 0 & 0 & \dots & 1 & -1 & 0 & 0 & 0 & \dots & 0 & 0 \\ %(1,N)
            p_s & 0 & 0 & \dots & 0 & 0 & -1 & p_o & 0 & \dots & 0 & 0 \\ %(2,T)
            0 & 0 & 0 & \dots & 0 & 0 & p_s & -1 & p_o & \dots & 0 & 0 \\ %(2,T+1)
            \vdots & \vdots & \vdots & \ddots & \vdots & \vdots & \vdots & 
            \vdots & \vdots & \ddots & \vdots & \vdots \\ 
            0 & 0 & 0 & \dots & 0 & 0 & 0 & 0 & 0 & \dots & 1 & -1 \\ %(M,N)
        \end{pmatrix},
        x = 
        \begin{pmatrix}
            b(1,T) \\
            b(1,T+1) \\
            b(1,T+2) \\
            \vdots \\
            b(1,N) \\
            b(2,T) \\
            b(2,T+1) \\
            \vdots \\
            b(M,N) \\
        \end{pmatrix}, 
        y= 
        \begin{pmatrix}
            -c(1,T) \\
            -c(1,T+1) \\
            -c(1,T+2) \\
            \vdots \\
            -c(1,N) \\
            -c(2,T) \\
            -c(2,T+1) \\
            \vdots \\
            -c(M,N) \\
        \end{pmatrix}
    \)}
\end{equation}

Thus, having calculated the mean blocking time for all blocking states \(b(u,v)\), 
it only remains to put them together in a formula.
The resultant formula for the mean blocking time is given by:

\begin{equation}\label{eq:algebraic_blocking_time}
    B = \frac{\sum_{(u,v) \in S_A} \pi_{(u,v)} \; b(u,v)}{\sum_{(u,v) \in S_A} 
    \pi_{(u,v)}}
\end{equation}

To illustrate how the described formula works consider a Markov model where 
\(C=2, T=2, N=4, M=2\) (figure \ref{fig:example-algeb-blocking}). 
The equations that correspond to such a model are shown in 
(\ref{eq:first_eq_of_blocking_example})-(\ref{eq:last_eq_of_blocking_example}) 
and their equivalent matrix notation form is shown in 
\ref{eq:example_algebaric_approach_blocking_time}.

\begin{minipage}{.5\textwidth}
    \begin{figure}[H]
        \scalebox{0.6}{\input{sections/queueing_model/subsections/example/example_2242/main.tex}}
        \caption{
            \centering{Example of Markov chain with \(C=2, T=2, N=4, M=2\)}
        }
        \label{fig:example-algeb-blocking}
    \end{figure}
\end{minipage}
\begin{minipage}{.43\textwidth}
    \begin{align}
        b(1,2) &= c(1,2) + p_o b(1,3) \label{eq:first_eq_of_blocking_example} \\
        b(1,3) &= c(1,3) + p_s b(1,2) \nonumber \\ &+ p_o b(1,4) \\
        b(1,4) &= c(1,4) + b(1,3) \\
        b(2,2) &= c(2,2) + p_s b(1,2) \nonumber \\ &+ p_o b(2,3) \\
        b(2,3) &= c(2,3) + p_s b(2,2) \nonumber \\ &+ p_o b(1,4) \\
        b(2,4) &= c(2,4) + b(2,3) \label{eq:last_eq_of_blocking_example}
    \end{align}
\end{minipage}

\begin{equation}\label{eq:example_algebaric_approach_blocking_time}
    Z=
    \begin{pmatrix}
        -1 & p_o & 0 & 0 & 0 & 0 \\ %(1,2)
        p_s & -1 & p_o & 0 & 0 & 0 \\ %(1,3)
        0 & 1 & -1 & 0 & 0 & 0 \\ %(1,4)
        p_s & 0 & 0 & -1 & p_o & 0\\ %(2,2)
        0 & 0 & 0 & p_s & -1 & p_o \\ %(2,3)
        0 & 0 & 0 & 0 & 1 & -1 \\ %(2,4)
    \end{pmatrix},
    x=
    \begin{pmatrix}
        b(1,2) \\
        b(1,3) \\
        b(1,4) \\
        b(2,2) \\
        b(2,3) \\
        b(2,4) \\
    \end{pmatrix}, 
    y=
    \begin{pmatrix}
        -c(1,2) \\
        -c(1,3) \\
        -c(1,4) \\
        -c(2,2) \\
        -c(2,3) \\
        -c(2,4) \\
    \end{pmatrix}
\end{equation}

### 2021-05-15 known.py
Update known.py

@@ -14,4 +14,5 @@ words = {
     "Panayides",
     "pre",
     "queueing",
+    "Zx",
 }

### 2021-05-17 sections/queueing_model/subsections/performance_measures/blocking_time/main.tex
Place all tikz pictures in imgs\ directory
Remove some un-needed comments
Apply minor changes to some .tex files

@@
 accepting states needs to be taken into consideration. 
-As defined in section \ref{sec:waiting-time}, the set of accepting states is 
-given by \ref{eq:accepting-states-class-2}:
+As defined in section \ref{sec:waiting_time}, the set of accepting states is 
+given by \ref{eq:accepting_states_class_2}:
 
@@
 \end{equation*}
-
-% For the waiting time formula in sections \ref{sec:recursive-waiting-time-others}
-% and \ref{sec:recursive-waiting-time-ambulance}
-% the mean sojourn time for each state was considered,
-% ignoring any arrivals.
-% Here, the same approach is used but ignoring only class 2
-% arrivals. That is because for the waiting time formula, once an individual enters 
-% the service centre (i.e. starts waiting) any individual arriving after them will 
-% not affect their
-% pathway. That is not the case for blocking time. When a class 2 individual is 
-% blocked, 
-% any class 1 individual that arrives will cause the blocked individual to remain 
-% blocked for more time. Therefore, class 1 arrivals are considered here:
 
@@
 To illustrate how the described formula works consider a Markov model where 
-\(C=2, T=2, N=4, M=2\) (figure \ref{fig:example-algeb-blocking}). 
+\(C=2, T=2, N=4, M=2\) (figure \ref{fig:example_algeb_blocking}). 
 The equations that correspond to such a model are shown in 
@@
     \begin{figure}[H]
-        \scalebox{0.6}{\input{sections/queueing_model/subsections/example/example_2242/main.tex}}
+        \scalebox{0.6}{\input{imgs/example_2242/main.tex}}
         \caption{
@@
         }
-        \label{fig:example-algeb-blocking}
+        \label{fig:example_algeb_blocking}
     \end{figure}

### 2021-05-17 sections/queueing_model/subsections/performance_measures/waiting_time/main.tex
Apply minor changes to some .tex files

--- 2021-04-29 sections/queueing_model/subsections/performance_measures/waiting_time/main.tex
@@
-\subsubsection{Waiting time}
-% TODO: Include recursive formula as well??
+\subsubsection{Waiting time} \label{sec:waiting_time}
 
@@
 
-\begin{equation}\label{eq:accepting-states-class-1}
+\begin{equation}\label{eq:accepting_states_class_1}
     S_A^{(1)} = \{(u, v) \in S \; | \; v < N \}
@@
 
-\begin{equation}\label{eq:accepting-states-class-2}
+\begin{equation}\label{eq:accepting_states_class_2}
     S_A^{(2)}=
@@
 Otherwise, the set of accepting state is identical to 
-\ref{eq:accepting-states-class-1}. Thus, the expressions for the waiting times 
+\ref{eq:accepting_states_class_1}. Thus, the expressions for the waiting times 
 for class 1 and class 2 individuals are given by:
 
-\begin{equation} \label{eq:closed_form_waiting_others}
+\begin{equation} \label{eq:closed_form_waiting_class_1}
     W^{(1)} = \frac{\sum_{\substack{(u,v) \, \in S_A^{(1)} \\ v \geq C}} 
@@
 
-\begin{equation}\label{eq:closed_form_waiting_ambulance}
+\begin{equation}\label{eq:closed_form_waiting_class_2}
     W^{(2)} = \frac{\sum_{\substack{(u,v) \, \in S_A^{(2)} \\ min(v,T) \geq C}} 
@@
 states \(S_A^{(2)}\) and \(S_A^{(1)}\) defined in equations 
-\ref{eq:accepting-states-class-1} and \ref{eq:accepting-states-class-2}. 
+\ref{eq:accepting_states_class_1} and \ref{eq:accepting_states_class_2}. 
 Using these equations the probability, for either class type, that an individual 
@@
 
-\begin{equation}\label{overall_waiting_time}
+\begin{equation}\label{eq:overall_waiting_time}
     W = \frac{\lambda_1 P(L'_1)}{\lambda_2 P(L'_2) + \lambda_1 P(L'_1)} W^{(1)} + 

### 2021-05-17 known.py
Add proportion within target subsubsection
Add subsubsection that explains how the proportion of individuals
is calculated. There are several subparagraphs to that section that
explain additional components that may or may not be left in at the
end.

@@ -5,6 +5,7 @@ words = {
     "calc",
     "dt",
     "HB",
+    "hypoexponential",
     "ieeetr",
     "ij",
     "Markovian",

### 2021-05-17 known.py
Add known words

@@ -3,11 +3,15 @@
 words = {
     "automata",
     "calc",
+    "CDF",
+    "CDFs",
     "dt",
+    "erlang",
     "HB",
     "hypoexponential",
     "ieeetr",
     "ij",
+    "LHS",
     "Markovian",
     "math",
     "memoryless",
@@ -15,5 +19,7 @@ words = {
     "Panayides",
     "pre",
     "queueing",
+    "RHS",
+    "th"
     "Zx",
 }

### 2021-05-17 known.py
Update CI and fix typo
Remove unwanted tex libraries

@@ -20,6 +20,6 @@ words = {
     "pre",
     "queueing",
     "RHS",
-    "th"
-    "Zx",
+    "th",
+    "Zx"
 }

### 2021-05-18 sections/queueing_model/main.tex
Place all tikz pictures in imgs\ directory
Apply suggestions from code review
Co-authored-by: Vince Knight <vincent.knight@gmail.com>

@@
 This is a queuing model that consists of two waiting spaces, one for each type
-of patient.
+of individual.
 
@@
 
-\input{sections/queueing_model/general_markov_model/main.tex}
+\input{imgs/general_markov_model/main.tex}
 
-In order to acquire an exact solution of the problem a slight adjustment needs 
-to be considered. 
+In order to consider this model numerically an adjustment needs 
+to be made. 
 The problem defined above assumes no upper boundary to the number of individuals 
@@
 Therefore, a different state space \( \tilde S \) needs to be constructed where 
-\( \tilde S \subseteq S \) and there is a maximum allowed number of people \(N\) 
-that can be in the system and a maximum allowed number of people \(M\) that can
+\( \tilde S \subseteq S \) and there is a maximum allowed number of individuals \(N\) 
+that can be in the system and a maximum allowed number of individuals \(M\) that can
 be blocked in the buffer centre:

### 2021-05-18 sections/queueing_model/subsections/performance_measures/main.tex
Write main.tex for waiting time subsubsection
Add python code that generates tikz picture
In order for the code to work, ambulance_game needs
to be imported first.
Comment out section
Include section that was commented out
Minor change on input
Apply suggestions from code review
Co-authored-by: Vince Knight <vincent.knight@gmail.com>

@@
 purpose is to keep track of the probability of being at any given state of 
-the system.
+the system. \(\pi_i\) is the steady state probability of being in state \((u_i, v_i)\in\tilde S\) which is the \(i\)th state of \(tilde S\) for some ordering of \(\tilde S\).
 The term \textit{steady state} refers to the instance of the vector \( \pi \) 
@@
 waiting zone 1 within a predefined time target.
+
+\input{sections/queueing_model/subsections/performance_measures/waiting_time/main.tex}
+
+\input{sections/queueing_model/subsections/performance_measures/blocking_time/main.tex}
+
+\input{sections/queueing_model/subsections/performance_measures/proportion_within_target/main.tex}

### 2021-05-18 sections/queueing_model/main.tex
Change the way equations are cited
Include brackets around cited equations

@@
 We denote the state space of the Markov chain as  \(S=S(T)\) which can be 
-written as the disjoint union~\ref{eq:definition_of_S_as_disjoint_union}.
+written as the disjoint union (\ref{eq:definition_of_S_as_disjoint_union}).
 
@@
 The entries of \(Q\) can be calculated using the state-mapping function 
-described in \ref{eq:markov_transition_rate}:
+described in (\ref{eq:markov_transition_rate}):
 
@@
 
-In order to consider this model numerically an adjustment needs 
-to be made. 
+In order to consider this model numerically an adjustment needs to be made. 
 The problem defined above assumes no upper boundary to the number of individuals 
 that can wait for service or for the ones that are blocked in the buffer centre. 
-Therefore, a different state space \( \tilde S \) needs to be constructed where 
-\( \tilde S \subseteq S \) and there is a maximum allowed number of individuals \(N\) 
-that can be in the system and a maximum allowed number of individuals \(M\) that can
-be blocked in the buffer centre:
+Therefore, a different state space \( \tilde S \) is constructed where 
+\( \tilde S \subseteq S \) and there is a maximum allowed number of individuals 
+\(N\) that can be in the system and a maximum allowed number of individuals 
+\(M\) that can be blocked in the buffer centre:
 

### 2021-05-18 sections/queueing_model/subsections/performance_measures/blocking_time/main.tex
Change the way equations are cited
Include brackets around cited equations

@@
 As defined in section \ref{sec:waiting_time}, the set of accepting states is 
-given by \ref{eq:accepting_states_class_2}:
+given by (\ref{eq:accepting_states_class_2}):
 
@@
 
-In equation \ref{eq:time_in_state_blocking_time}, both service completions and 
+In equation (\ref{eq:time_in_state_blocking_time}), both service completions and 
 class 1 arrivals are considered. 
@@
 A direct approach will be used to solve this equation here. 
-By enumerating all equations of (\ref{eq:general_blocking_time_at_each_state}) 
+By enumerating all equations of ((\ref{eq:general_blocking_time_at_each_state})) 
 for all states \((u,v)\) that belong in \(S_b\) 
@@
 Note here that these equations correspond to all blocking states as defined in
-\ref{eq:set_of_blocking_states}. 
+(\ref{eq:set_of_blocking_states}). 
 Equations that correspond to non-blocking states have a value of \(0\) as 
-defined in \ref{eq:general_blocking_time_at_each_state}
+defined in (\ref{eq:general_blocking_time_at_each_state})
 The general form of the equation in terms of \(C,T,N \text{ and } M\) is given by:
@@
 The equivalent matrix notation of the linear system of equations 
-(\ref{eq:first_eq_of_blocking_general}) - (\ref{eq:last_eq_of_blocking_general})
+((\ref{eq:first_eq_of_blocking_general})) - ((\ref{eq:last_eq_of_blocking_general}))
 is given by \(Zx=y\), where:
@@
 The equations that correspond to such a model are shown in 
-(\ref{eq:first_eq_of_blocking_example})-(\ref{eq:last_eq_of_blocking_example}) 
+((\ref{eq:first_eq_of_blocking_example}))-((\ref{eq:last_eq_of_blocking_example})) 
 and their equivalent matrix notation form is shown in 
-\ref{eq:example_algebaric_approach_blocking_time}.
+(\ref{eq:example_algebaric_approach_blocking_time}).
 

### 2021-05-18 sections/queueing_model/subsections/performance_measures/main.tex
Change the way equations are cited
Include brackets around cited equations

@@
 
-The transition matrix \( Q \) defined in \ref{eq:markov_transition_rate} can be 
-used to get the probability vector \( \pi \).
+The transition matrix \( Q \) defined in (\ref{eq:markov_transition_rate}) can 
+be used to get the probability vector \( \pi \).
 The vector \( \pi \) is commonly used to study stochastic systems and it's main
 purpose is to keep track of the probability of being at any given state of 
-the system. \(\pi_i\) is the steady state probability of being in state \((u_i, v_i)\in\tilde S\) which is the \(i\)th state of \(tilde S\) for some ordering of \(\tilde S\).
+the system. 
+\(\pi_i\) is the steady state probability of being in state \((u_i, v_i) \in 
+\tilde S\) which is the \(i^{\text{th}}\) state of \(\tilde S\) for some ordering of 
+\(\tilde S\).
 The term \textit{steady state} refers to the instance of the vector \( \pi \) 

### 2021-05-18 sections/queueing_model/subsections/performance_measures/waiting_time/main.tex
Change the way equations are cited
Include brackets around cited equations

@@
 Otherwise, the set of accepting state is identical to 
-\ref{eq:accepting_states_class_1}. Thus, the expressions for the waiting times 
+(\ref{eq:accepting_states_class_1}). Thus, the expressions for the waiting times 
 for class 1 and class 2 individuals are given by:
@@
 states \(S_A^{(2)}\) and \(S_A^{(1)}\) defined in equations 
-\ref{eq:accepting_states_class_1} and \ref{eq:accepting_states_class_2}. 
+(\ref{eq:accepting_states_class_1}) and (\ref{eq:accepting_states_class_2}). 
 Using these equations the probability, for either class type, that an individual 
@@
 Thus, by using these values as the coefficient of equation 
-\ref{eq:overall_waiting_time_coeff} the resultant equation can be used to get 
+(\ref{eq:overall_waiting_time_coeff}) the resultant equation can be used to get 
 the overall waiting time.

### 2021-05-18 sections/queueing_model/main.tex
Replace the word "class" with "type"
Class 1 and class 2 individulas are now referred to as
type 1 and type 2 individuals

@@
 
-The model consists of two types of individuals; class 1 and class 2.
-Class 1 individuals arrive instantly at waiting zone 1 and proceed to wait to
+The model consists of two types of individuals; type 1 and type 2.
+Type 1 individuals arrive instantly at waiting zone 1 and proceed to wait to
 receive their service. 
-Class 2 individuals arrive at waiting zone 2 and wait there until they are 
+Type 2 individuals arrive at waiting zone 2 and wait there until they are 
 allowed to move to waiting zone 1. 
@@
 Note that \(\Lambda\) here denotes the overall arrival rate in the model by both 
-classes of individuals (i.e. \(\Lambda = \lambda_1 + \lambda_2\)). 
+types of individuals (i.e. \(\Lambda = \lambda_1 + \lambda_2\)). 
 A visualisation of how the transition rates relate to the states of the model 

### 2021-05-18 sections/queueing_model/subsections/performance_measures/blocking_time/main.tex
Replace the word "class" with "type"
Class 1 and class 2 individulas are now referred to as
type 1 and type 2 individuals

@@
 As defined in section \ref{sec:waiting_time}, the set of accepting states is 
-given by (\ref{eq:accepting_states_class_2}):
+given by (\ref{eq:accepting_states_type_2}):
 
@@
 In equation (\ref{eq:time_in_state_blocking_time}), both service completions and 
-class 1 arrivals are considered. 
+type 1 arrivals are considered. 
 Thus, from a blocked individual's perspective whenever the system moves from one 
@@
     of this happening by \(p_s(u,v)\). 
-    \item be because of an arrival of an individual of class 1: denoting such 
+    \item be because of an arrival of an individual of type 1: denoting such 
     probability by \(p_o(u,v)\).

### 2021-05-18 sections/queueing_model/subsections/performance_measures/main.tex
Replace the word "class" with "type"
Class 1 and class 2 individulas are now referred to as
type 1 and type 2 individuals

@@
 Such performance measures are the mean waiting time in the system (for both 
-class 1 and class 2 individuals), the mean time blocked in waiting zone 2 (only 
-valid for class 2 individuals) and the proportion of individuals that wait in 
+type 1 and type 2 individuals), the mean time blocked in waiting zone 2 (only 
+valid for type 2 individuals) and the proportion of individuals that wait in 
 waiting zone 1 within a predefined time target.

### 2021-05-18 sections/queueing_model/subsections/performance_measures/waiting_time/main.tex
Replace the word "class" with "type"
Class 1 and class 2 individulas are now referred to as
type 1 and type 2 individuals

@@
 
-Waiting time is the amount of time that individuals from either class wait in 
+Waiting time is the amount of time that individuals from either type wait in 
 waiting zone 1 so that they can receive their service. 
@@
 around the mean waiting time that can be calculated; the mean waiting time of
-class 1 individuals, the mean waiting time of class 2 individuals and the 
+type 1 individuals, the mean waiting time of type 2 individuals and the 
 overall mean waiting time.
@@
 individual. 
-The set of accepting states for class 1 individuals is defined as:
+The set of accepting states for type 1 individuals is defined as:
 
-\begin{equation}\label{eq:accepting_states_class_1}
+\begin{equation}\label{eq:accepting_states_type_1}
     S_A^{(1)} = \{(u, v) \in S \; | \; v < N \}
@@
 
-In essence, for class 1 individuals, this is the set of states that are not on 
+In essence, for type 1 individuals, this is the set of states that are not on 
 the last column of states in the Markov chain.
-Equivalently, the set of accepting states for class 2 individuals is defined as:
+Equivalently, the set of accepting states for type 2 individuals is defined as:
 
-\begin{equation}\label{eq:accepting_states_class_2}
+\begin{equation}\label{eq:accepting_states_type_2}
     S_A^{(2)}=
@@
 Otherwise, the set of accepting state is identical to 
-(\ref{eq:accepting_states_class_1}). Thus, the expressions for the waiting times 
-for class 1 and class 2 individuals are given by:
+(\ref{eq:accepting_states_type_1}). Thus, the expressions for the waiting times 
+for type 1 and type 2 individuals are given by:
 
-\begin{equation} \label{eq:closed_form_waiting_class_1}
+\begin{equation} \label{eq:closed_form_waiting_type_1}
     W^{(1)} = \frac{\sum_{\substack{(u,v) \, \in S_A^{(1)} \\ v \geq C}} 
@@
 
-\begin{equation}\label{eq:closed_form_waiting_class_2}
+\begin{equation}\label{eq:closed_form_waiting_type_2}
     W^{(2)} = \frac{\sum_{\substack{(u,v) \, \in S_A^{(2)} \\ min(v,T) \geq C}} 
@@
 states \(S_A^{(2)}\) and \(S_A^{(1)}\) defined in equations 
-(\ref{eq:accepting_states_class_1}) and (\ref{eq:accepting_states_class_2}). 
-Using these equations the probability, for either class type, that an individual 
-is not lost in the system is given by:
+(\ref{eq:accepting_states_type_1}) and (\ref{eq:accepting_states_type_2}). 
+Using these equations the probability, for either individual type, that an 
+individual is not lost in the system is given by:
 

### 2021-05-20 sections/queueing_model/subsections/performance_measures/waiting_time/main.tex
Apply suggestions to waiting time section from code review
Co-authored-by: Vince Knight <vincent.knight@gmail.com>

@@
 of \(W_1\) and \(W_2\). 
-Thus, the overall waiting time can calculated by the following equation where 
+Thus, the overall waiting time can be calculated by the following equation where 
 \(c_1\) and \(c_2\) are the coefficients of the terms:
@@
 The two coefficients represent the proportion of individuals of each type that 
-did not get lost and traversed through the model.
+are not lost to the system.
 Thus, one should account for the probability that an individual is lost to the 

### 2021-05-20 sections/queueing_model/subsections/performance_measures/waiting_time/main.tex
Restructure waiting time formula section
The section is now structured in the
following way:

- Formula 1
- Formula 2
- Formula 3
- Defining necessary parameters

@@
 around the mean waiting time that can be calculated; the mean waiting time of
-type 1 individuals, the mean waiting time of type 2 individuals and the 
-overall mean waiting time.
+type 1 individuals:
 
-Since some of the individuals can be lost to the model, a new set of states 
-needs to be defined; the set of \textit{accepting states}. 
-That is the set of states that the model is able to accept a certain type of
-individual. 
-The set of accepting states for type 1 individuals is defined as:
+\begin{equation} \label{eq:closed_form_waiting_type_1}
+    W^{(1)} = \frac{\sum_{\substack{(u,v) \, \in S_A^{(1)} \\ v \geq C}} 
+    \frac{1}{C \mu} \times (v-C+1) \times \pi(u,v)}{\sum_{(u,v) \, 
+    \in S_A^{(1)}} \pi(u,v)}
+\end{equation}
+
+The mean waiting time of type 2 individuals:
+
+\begin{equation}\label{eq:closed_form_waiting_type_2}
+    W^{(2)} = \frac{\sum_{\substack{(u,v) \, \in S_A^{(2)} \\ min(v,T) \geq C}} 
+    \frac{1}{C \mu} \times (\min(v+1,T)-C) \times \pi(u,v)}{\sum_{(u,v) \, 
+    \in S_A^{(2)}} \pi(u,v)}
+\end{equation}
+
+The overall mean waiting time:
+
+\begin{equation}\label{eq:overall_waiting_time}
+    W = \frac{\lambda_1 P(L'_1)}{\lambda_2 P(L'_2) + \lambda_1 P(L'_1)} W^{(1)} 
+    + \frac{\lambda_2 P(L'_2)}{\lambda_2 P(L'_2) + \lambda_1 P(L'_1)} W^{(2)}
+\end{equation}
+
+Here \(S_A^{(1)}\) and \(S_A^{(2)}\) are the set of accepting states for type
+1 and type 2 individuals. These are the set of states that the model is able
+to accept a specific type of individuals.
 
@@
 \end{equation}
-
-In essence, for type 1 individuals, this is the set of states that are not on 
-the last column of states in the Markov chain.
-Equivalently, the set of accepting states for type 2 individuals is defined as:
 
@@
 
-Note here that if the threshold is less than or equal the total capacity of the
-system the set includes all states that are not on the last column of the 
-Markov chain.
-Otherwise, the set of accepting state is identical to 
-(\ref{eq:accepting_states_type_1}). Thus, the expressions for the waiting times 
-for type 1 and type 2 individuals are given by:
+Equation \ref{eq:overall_waiting_time} makes use of the proportion of type 1 
+and type 2 individuals that are not lost to the system. These probabilities are 
+given by \(P(L'_1)\) and \(P(L'_2)\) where:
 
-\begin{equation} \label{eq:closed_form_waiting_type_1}
-    W^{(1)} = \frac{\sum_{\substack{(u,v) \, \in S_A^{(1)} \\ v \geq C}} 
-    \frac{1}{C \mu} \times (v-C+1) \times \pi(u,v)}{\sum_{(u,v) \, 
-    \in S_A^{(1)}} \pi(u,v)}
-\end{equation}
-
-\begin{equation}\label{eq:closed_form_waiting_type_2}
-    W^{(2)} = \frac{\sum_{\substack{(u,v) \, \in S_A^{(2)} \\ min(v,T) \geq C}} 
-    \frac{1}{C \mu} \times (\min(v+1,T)-C) \times \pi(u,v)}{\sum_{(u,v) \, 
-    \in S_A^{(2)}} \pi(u,v)}
-\end{equation}
-
-Consequently, the overall waiting time can be estimated by a linear combination 
-of \(W_1\) and \(W_2\). 
-Thus, the overall waiting time can be calculated by the following equation where 
-\(c_1\) and \(c_2\) are the coefficients of the terms:
-
-\begin{equation}\label{eq:overall_waiting_time_coeff}
-    W = c_1 W^{(1)} + c_2 W^{(2)}
-\end{equation}
-
-The two coefficients represent the proportion of individuals of each type that 
-are not lost to the system.
-Thus, one should account for the probability that an individual is lost to the 
-system. 
-This probability can be easily calculated by using the two sets of accepting 
-states \(S_A^{(2)}\) and \(S_A^{(1)}\) defined in equations 
-(\ref{eq:accepting_states_type_1}) and (\ref{eq:accepting_states_type_2}). 
-Using these equations the probability, for either individual type, that an 
-individual is not lost in the system is given by:
-
-\begin{equation*}
+\begin{equation}
     P(L'_1) = \sum_{(u,v) \, \in S_A^{(1)}} \pi(u,v) \hspace{2cm}
     P(L'_2) = \sum_{(u,v) \, \in S_A^{(2)}} \pi(u,v)
-\end{equation*}
-
-Thus, by using these values as the coefficient of equation 
-(\ref{eq:overall_waiting_time_coeff}) the resultant equation can be used to get 
-the overall waiting time.
-
-\begin{equation}\label{eq:overall_waiting_time}
-    W = \frac{\lambda_1 P(L'_1)}{\lambda_2 P(L'_2) + \lambda_1 P(L'_1)} W^{(1)} + 
-    \frac{\lambda_2 P(L'_2)}{\lambda_2 P(L'_2) + \lambda_1 P(L'_1)} W^{(2)}
 \end{equation}

### 2021-05-21 sections/queueing_model/subsections/performance_measures/blocking_time/main.tex
Restructure blocking time formula
Remove most of text that focuses on the "how" part of the formula.
What's left now is just the formula and everything that's necessary to
use it.

--- 2021-05-17 sections/queueing_model/subsections/performance_measures/blocking_time/main.tex
@@
 mean blocking time of the system. 
-The set of states where individuals can be blocked is defined as:
+The mean blocking time can by calculated using:
+
+% TODO: Fix this equation by using the arriving state 
+\begin{equation}\label{eq:algebraic_blocking_time}
+    B = \frac{\sum_{(u,v) \in S_A^{(2)}} \pi_{(u,v)} \; 
+    b(u,v)}{\sum_{(u,v) \in S_A^{(2)}} \pi_{(u,v)}}
+\end{equation}
+
+Here \(S_A^{(2)}\) is the set of accepting states of type 2 individuals (defined
+in (\ref{eq:accepting_states_type_2})) and \(b(u,v)\) is the mean time that an 
+individual will be blocked when the system is at state \((u,v)\). 
+For all the states of the system \(b(u,v)\) is given by:
+
+\begin{equation}\label{eq:general_blocking_time_at_each_state}
+    b(u,v) = 
+    \begin{cases} 
+        0, & \textbf{if } (u,v) \notin S_b \\
+        c(u,v) + b(u - 1, v), & \textbf{if } v = N = T\\
+        c(u,v) + b(u, v-1), & \textbf{if } v = N \neq T \\
+        c(u,v) + p_s(u,v) b(u-1, v) + p_a(u,v) b(u, v+1), & \textbf{if } u > 0 
+        \textbf{ and } \vspace{-0.2cm} \\ 
+        & \quad v = T \\
+        c(u,v) + p_s(u,v) b(u, v-1) + p_a(u,v) b(u, v+1), & \textbf{otherwise} \\
+    \end{cases}
+\end{equation}
+
+Note that \(S_b\) is defined as the set of states where individuals can be
+blocked and is given by:
 
@@
 
-In order to not consider individuals that will be lost to the system, the set of 
-accepting states needs to be taken into consideration. 
-As defined in section \ref{sec:waiting_time}, the set of accepting states is 
-given by \ref{eq:accepting_states_class_2}:
+Additionally, \(c(u,v)\) is the mean sojourn time for each state and \(p_s\) 
+and \(p_a\) are the probabilities that the next event to occur will be a service completion or an arrival of a type 1 individual:
 
-\begin{equation*}
-    S_A^{(2)}=
-    \begin{cases}
-        \{(u, v) \in S \; | \; u < M \} & \textbf{if } T \leq N\\
-        \{(u, v) \in S \; | \; v < N \} & \textbf{otherwise}
-    \end{cases}
-\end{equation*}
-
-The mean sojourn time for each state is given by the inverse of the out-flow of
-that state.
-However, whenever a type 2 individual arrives at the system, no subsequent 
-arrival of another type 2 individual can affect its pathway or total time in 
-the system.
-Therefore, looking at the mean time in the system from the perspective of an 
-individual of the second type, all such type 2 arrivals need to be ignored.
-Note here that this is not the case for individuals of the first type.
-Whenever a type 2 individual is blocked and a type 1 individual arrives the type
-2 individuals will remain blocked for some additional amount of time.
-Thus, the mean time that a type 2 individual spends at each state is given by:
-
-\begin{equation}\label{eq:time_in_state_blocking_time}
+\begin{equation}\label{eq:sojourn_blocking_time}
     c(u,v) = 
@@
 
-In equation \ref{eq:time_in_state_blocking_time}, both service completions and 
-class 1 arrivals are considered. 
-Thus, from a blocked individual's perspective whenever the system moves from one 
-state \((u,v)\)
-to another state it can either:
-
-\begin{itemize}
-    \item be because of a service being completed: we will denote the probability 
-    of this happening by \(p_s(u,v)\). 
-    \item be because of an arrival of an individual of class 1: denoting such 
-    probability by \(p_o(u,v)\).
-\end{itemize}
-The probabilities are given by:
-
-\begin{equation*}
+\begin{equation}\label{eq:probs_of_service_and_arrival}
     p_s(u,v) = \frac{\min(v,C)\mu}{\lambda_1 + \min(v,C)\mu}, \qquad
-    p_o(u,v) = \frac{\lambda_1}{\lambda_1 + \min(v,C)\mu}
-\end{equation*}
-
-Having defined \(c(u,v)\) and \(S_b\) a formula for the blocking time that is
-expected to occur at each state can be given by:
-
-\begin{equation}\label{eq:general_blocking_time_at_each_state}
-    b(u,v) = 
-    \begin{cases} 
-        0, & \textbf{if } (u,v) \notin S_b \\
-        c(u,v) + b(u - 1, v), & \textbf{if } v = N = T\\
-        c(u,v) + b(u, v-1), & \textbf{if } v = N \neq T \\
-        c(u,v) + p_s(u,v) b(u-1, v) + p_o(u,v) b(u, v+1), & \textbf{if } u > 0 
-        \textbf{ and } \vspace{-0.2cm} \\ 
-        & \quad v = T \\
-        c(u,v) + p_s(u,v) b(u, v-1) + p_o(u,v) b(u, v+1), & \textbf{otherwise} \\
-    \end{cases}
+    p_a(u,v) = \frac{\lambda_1}{\lambda_1 + \min(v,C)\mu}
 \end{equation}
 
-A direct approach will be used to solve this equation here. 
-By enumerating all equations of (\ref{eq:general_blocking_time_at_each_state}) 
-for all states \((u,v)\) that belong in \(S_b\) 
-a system of linear equations arises where the unknown variables are all the 
-\(b(u,v)\) terms. 
-Note here that these equations correspond to all blocking states as defined in
-\ref{eq:set_of_blocking_states}. 
-Equations that correspond to non-blocking states have a value of \(0\) as 
-defined in \ref{eq:general_blocking_time_at_each_state}
-The general form of the equation in terms of \(C,T,N \text{ and } M\) is given by:
+% TODO: These might possibly need to be moved to the appendix 
+The system of equations produced by (\ref{eq:general_blocking_time_at_each_state}) can be solved by considering the linear system \(Zx=y\), where:
 
-\begin{align}
-    b(1,T) \quad &= \quad c(1, T) + p_o b(1, T + 1) \label{eq:first_eq_of_blocking_general}\\
-    b(1,T + 1) \quad &= \quad c(1, T + 1) + p_s b(1, T) + p_o b(1, T + 1) \\
-    b(1,T + 2) \quad &= \quad c(1, T + 2) + p_s b(1, T + 1) + p_o b(1, T + 3) \\
-    & \ \, \vdots \nonumber \\
-    b(1, N) \quad &= \quad c(1, N) + b(1, N - 1) \\
-    b(2, T) \quad &= \quad c(2, T) + p_s b(1, T) + p_o b(2, T + 1) \\
-    b(2, T + 1) \quad &= \quad c(2, T + 1) + p_s b(2, T) + p_o b(2, T + 2) \\
-    & \ \, \vdots \nonumber \\
-    b(M - 1, N) \quad &= \quad c(M, N - 1) + b(M, N-1) \\ 
-    b(M, T) \quad &= \quad c(T, N) + p_s b(T-1, N) + p_o b(T, N+1) \\
-    & \ \, \vdots \nonumber \\
-    b(M, N) \quad &= \quad c(M, N) + b(M, N-1) \label{eq:last_eq_of_blocking_general}
-\end{align}
-
-The equivalent matrix notation of the linear system of equations 
-(\ref{eq:first_eq_of_blocking_general}) - (\ref{eq:last_eq_of_blocking_general})
-is given by \(Zx=y\), where:
 \begin{equation}\label{eq:general_algebaric_approach_blocking_time}
@@
         \begin{pmatrix}
-            -1 & p_o & 0 & \dots & 0 & 0 & 0 & 0 & 0 & \dots & 0 & 0 \\ %(1,T)
-            p_s & -1 & p_o & \dots & 0 & 0 & 0 & 0 & 0 & \dots & 0 & 0 \\ %(1,T+1)
+            -1 & p_a & 0 & \dots & 0 & 0 & 0 & 0 & 0 & \dots & 0 & 0 \\ %(1,T)
+            p_s & -1 & p_a & \dots & 0 & 0 & 0 & 0 & 0 & \dots & 0 & 0 \\ %(1,T+1)
             0 & p_s & -1 & \dots & 0 & 0 & 0 & 0 & 0 & \dots & 0 & 0 \\ %(1,T+2)
@@
             0 & 0 & 0 & \dots & 1 & -1 & 0 & 0 & 0 & \dots & 0 & 0 \\ %(1,N)
-            p_s & 0 & 0 & \dots & 0 & 0 & -1 & p_o & 0 & \dots & 0 & 0 \\ %(2,T)
-            0 & 0 & 0 & \dots & 0 & 0 & p_s & -1 & p_o & \dots & 0 & 0 \\ %(2,T+1)
+            p_s & 0 & 0 & \dots & 0 & 0 & -1 & p_a & 0 & \dots & 0 & 0 \\ %(2,T)
+            0 & 0 & 0 & \dots & 0 & 0 & p_s & -1 & p_a & \dots & 0 & 0 \\ %(2,T+1)
             \vdots & \vdots & \vdots & \ddots & \vdots & \vdots & \vdots & 
@@
 
-Thus, having calculated the mean blocking time for all blocking states \(b(u,v)\), 
-it only remains to put them together in a formula.
-The resultant formula for the mean blocking time is given by:
+Matrix \(Z\) can be alternatively defined using \(Z_{ij}\) defined in equation 
+(\ref{eq:general_mapping_function_of_blocking_matrix}) where \(i\) and \(j\) 
+represent states \((u_i, v_i), (u_j, v_j) \in S_b\).
 
-\begin{equation}\label{eq:algebraic_blocking_time}
-    B = \frac{\sum_{(u,v) \in S_A} \pi_{(u,v)} \; b(u,v)}{\sum_{(u,v) \in S_A} 
-    \pi_{(u,v)}}
+\begin{equation}\label{eq:general_mapping_function_of_blocking_matrix}
+    Z_{ij} = 
+    \begin{cases}
+        p_a, & \textbf{if } j = i + 1 \textbf{ and } v_i \neq N \\
+        \\
+        p_s, & \textbf{if } j = i - 1 \textbf{ and } v_i \neq N, v_i \neq T \\
+             & \textbf{or } j = i - N + T \textbf{ and } u_i \geq 2,\,v_i = T \\
+        \\
+        1, & \textbf{if } j = i - 1 \textbf{ and } v_i = N \\
+        \\
+        -1, & \textbf{if } i = j \\
+        \\
+        0, & \textbf{otherwise} \\
+    \end{cases}
 \end{equation}
-
-To illustrate how the described formula works consider a Markov model where 
-\(C=2, T=2, N=4, M=2\) (figure \ref{fig:example_algeb_blocking}). 
-The equations that correspond to such a model are shown in 
-(\ref{eq:first_eq_of_blocking_example})-(\ref{eq:last_eq_of_blocking_example}) 
-and their equivalent matrix notation form is shown in 
-\ref{eq:example_algebaric_approach_blocking_time}.
-
-\begin{minipage}{.5\textwidth}
-    \begin{figure}[H]
-        \scalebox{0.6}{\input{imgs/example_2242/main.tex}}
-        \caption{
-            \centering{Example of Markov chain with \(C=2, T=2, N=4, M=2\)}
-        }
-        \label{fig:example_algeb_blocking}
-    \end{figure}
-\end{minipage}
-\begin{minipage}{.43\textwidth}
-    \begin{align}
-        b(1,2) &= c(1,2) + p_o b(1,3) \label{eq:first_eq_of_blocking_example} \\
-        b(1,3) &= c(1,3) + p_s b(1,2) \nonumber \\ &+ p_o b(1,4) \\
-        b(1,4) &= c(1,4) + b(1,3) \\
-        b(2,2) &= c(2,2) + p_s b(1,2) \nonumber \\ &+ p_o b(2,3) \\
-        b(2,3) &= c(2,3) + p_s b(2,2) \nonumber \\ &+ p_o b(1,4) \\
-        b(2,4) &= c(2,4) + b(2,3) \label{eq:last_eq_of_blocking_example}
-    \end{align}
-\end{minipage}
-
-\begin{equation}\label{eq:example_algebaric_approach_blocking_time}
-    Z=
-    \begin{pmatrix}
-        -1 & p_o & 0 & 0 & 0 & 0 \\ %(1,2)
-        p_s & -1 & p_o & 0 & 0 & 0 \\ %(1,3)
-        0 & 1 & -1 & 0 & 0 & 0 \\ %(1,4)
-        p_s & 0 & 0 & -1 & p_o & 0\\ %(2,2)
-        0 & 0 & 0 & p_s & -1 & p_o \\ %(2,3)
-        0 & 0 & 0 & 0 & 1 & -1 \\ %(2,4)
-    \end{pmatrix},
-    x=
-    \begin{pmatrix}
-        b(1,2) \\
-        b(1,3) \\
-        b(1,4) \\
-        b(2,2) \\
-        b(2,3) \\
-        b(2,4) \\
-    \end{pmatrix}, 
-    y=
-    \begin{pmatrix}
-        -c(1,2) \\
-        -c(1,3) \\
-        -c(1,4) \\
-        -c(2,2) \\
-        -c(2,3) \\
-        -c(2,4) \\
-    \end{pmatrix}
-\end{equation}

### 2021-05-21 sections/appendix/blocking_time_formula/main.tex
Add an appendix
Currently the appendix has some information of how to use the blocking
time formula. Soon to be added are information on the waiting time
formula (possibly the recursive method) and information on the
proportion within target formula.

\section{Mean blocking time} \label{sec:appendix_mean_blocking}

The set of states where individuals can be blocked is defined as:
\begin{equation*}
    S_b = \{(u,v) \in S \; | \; u > 0\} 
    \tag{\ref{eq:set_of_blocking_states} revisited}
\end{equation*}

The mean sojourn time for each state is given by the inverse of the out-flow of
that state ~\cite{Stewart2019}.
However, whenever a type 2 individual arrives at the system, no subsequent 
arrival of another type 2 individual can affect its pathway or total time in 
the system.
Therefore, looking at the mean time in the system from the perspective of an 
individual of the second type, all such type 2 arrivals need to be ignored.
Note here that this is not the case for individuals of the first type.
Whenever a type 2 individual is blocked and a type 1 individual arrives the type
2 individuals will remain blocked for some additional amount of time.
Thus, the mean time that a type 2 individual spends at each state is given by:

\begin{equation*}
    c(u,v) = 
    \begin{cases}
        \frac{1}{\min(v,C) \mu}, & \text{if } v = N\\
        \frac{1}{\lambda_1 + \min(v,C) \mu}, & \text{otherwise}
    \end{cases} 
    \tag{\ref{eq:sojourn_blocking_time} revisited}
\end{equation*}

In equation (\ref{eq:sojourn_blocking_time}), both service completions and 
type 1 arrivals are considered. 
Thus, from a blocked individual's perspective whenever the system moves from one 
state \((u,v)\)
to another state it can either:

\begin{itemize}
    \item be because of a service being completed: we will denote the probability 
    of this happening by \(p_s(u,v)\). 
    \item be because of an arrival of an individual of type 1: denoting such 
    probability by \(p_a(u,v)\).
\end{itemize}
The probabilities are given by:

\begin{equation*}
    p_s(u,v) = \frac{\min(v,C)\mu}{\lambda_1 + \min(v,C)\mu}, \qquad
    p_a(u,v) = \frac{\lambda_1}{\lambda_1 + \min(v,C)\mu}
    \tag{\ref{eq:probs_of_service_and_arrival} revisited} 
\end{equation*}

Having defined \(c(u,v)\) and \(S_b\) a formula for the blocking time that is
expected to occur at each state can be given by:

    \begin{equation*}
    b(u,v) = 
    \begin{cases} 
        0, & \textbf{if } (u,v) \notin S_b \\
        c(u,v) + b(u - 1, v), & \textbf{if } v = N = T\\
        c(u,v) + b(u, v-1), & \textbf{if } v = N \neq T \\
        c(u,v) + p_s(u,v) b(u-1, v) + p_a(u,v) b(u, v+1), & \textbf{if } u > 0 
        \textbf{ and } \vspace{-0.2cm} \\ 
        & \quad v = T \\
        c(u,v) + p_s(u,v) b(u, v-1) + p_a(u,v) b(u, v+1), & \textbf{otherwise} \\
    \end{cases}
    \tag{\ref{eq:general_blocking_time_at_each_state} revisited}
\end{equation*}

A direct approach will be used to solve this equation here. 
By enumerating all equations of (\ref{eq:general_blocking_time_at_each_state}) 
for all states \((u,v)\) that belong in \(S_b\) 
a system of linear equations arises where the unknown variables are all the 
\(b(u,v)\) terms. 
Note here that these equations correspond to all blocking states as defined in
(\ref{eq:set_of_blocking_states}). 
Equations that correspond to non-blocking states have a value of \(0\) as 
defined in (\ref{eq:general_blocking_time_at_each_state})
The general form of the equation in terms of \(C,T,N \text{ and } M\) is given by:

\begin{align}
    b(1,T) \quad &= \quad c(1, T) + p_a b(1, T + 1) \label{eq:first_eq_of_blocking_general}\\
    b(1,T + 1) \quad &= \quad c(1, T + 1) + p_s b(1, T) + p_a b(1, T + 1) \\
    b(1,T + 2) \quad &= \quad c(1, T + 2) + p_s b(1, T + 1) + p_a b(1, T + 3) \\
    & \ \, \vdots \nonumber \\
    b(1, N) \quad &= \quad c(1, N) + b(1, N - 1) \\
    b(2, T) \quad &= \quad c(2, T) + p_s b(1, T) + p_a b(2, T + 1) \\
    b(2, T + 1) \quad &= \quad c(2, T + 1) + p_s b(2, T) + p_a b(2, T + 2) \\
    & \ \, \vdots \nonumber \\
    b(M - 1, N) \quad &= \quad c(M, N - 1) + b(M, N-1) \\ 
    b(M, T) \quad &= \quad c(T, N) + p_s b(T-1, N) + p_a b(T, N+1) \\
    & \ \, \vdots \nonumber \\
    b(M, N) \quad &= \quad c(M, N) + b(M, N-1) \label{eq:last_eq_of_blocking_general}
\end{align}

The equivalent matrix notation of the linear system of equations 
(\ref{eq:first_eq_of_blocking_general}) - (\ref{eq:last_eq_of_blocking_general})
is given by \(Zx=y\), where:
\begin{equation}
    \scalebox{0.73}{\(
        Z = 
        \begin{pmatrix}
            -1 & p_a & 0 & \dots & 0 & 0 & 0 & 0 & 0 & \dots & 0 & 0 \\ %(1,T)
            p_s & -1 & p_a & \dots & 0 & 0 & 0 & 0 & 0 & \dots & 0 & 0 \\ %(1,T+1)
            0 & p_s & -1 & \dots & 0 & 0 & 0 & 0 & 0 & \dots & 0 & 0 \\ %(1,T+2)
            \vdots & \vdots & \vdots & \ddots & \vdots & \vdots & \vdots & 
            \vdots & \vdots & \ddots & \vdots & \vdots \\ 
            0 & 0 & 0 & \dots & 1 & -1 & 0 & 0 & 0 & \dots & 0 & 0 \\ %(1,N)
            p_s & 0 & 0 & \dots & 0 & 0 & -1 & p_a & 0 & \dots & 0 & 0 \\ %(2,T)
            0 & 0 & 0 & \dots & 0 & 0 & p_s & -1 & p_a & \dots & 0 & 0 \\ %(2,T+1)
            \vdots & \vdots & \vdots & \ddots & \vdots & \vdots & \vdots & 
            \vdots & \vdots & \ddots & \vdots & \vdots \\ 
            0 & 0 & 0 & \dots & 0 & 0 & 0 & 0 & 0 & \dots & 1 & -1 \\ %(M,N)
        \end{pmatrix},
        x = 
        \begin{pmatrix}
            b(1,T) \\
            b(1,T+1) \\
            b(1,T+2) \\
            \vdots \\
            b(1,N) \\
            b(2,T) \\
            b(2,T+1) \\
            \vdots \\
            b(M,N) \\
        \end{pmatrix}, 
        y= 
        \begin{pmatrix}
            -c(1,T) \\
            -c(1,T+1) \\
            -c(1,T+2) \\
            \vdots \\
            -c(1,N) \\
            -c(2,T) \\
            -c(2,T+1) \\
            \vdots \\
            -c(M,N) \\
        \end{pmatrix}
    \)} \tag{\ref{eq:general_algebaric_approach_blocking_time} revisited}
    \end{equation}

    The elements of the matrix \(Z\) can be acquired using \(Z_{ij}\) defined in 
    equation (\ref{eq:general_mapping_function_of_blocking_matrix}) where \(i\) 
    and \(j\) are states \((u_i, v_i), (u_j, v_j) \in S_b\) 
    (\ref{eq:set_of_blocking_states}).

    \begin{equation}
    Z_{ij} = 
    \begin{cases}
        p_a, & \textbf{if } j = i + 1 \textbf{ and } v_i \neq N \\
        \\
        p_s, & \textbf{if } j = i - 1 \textbf{ and } v_i \neq N, v_i \neq T \\
            & \textbf{or } j = i - N + T \textbf{ and } u_i \geq 2,\,v_i = T \\
        \\
        1, & \textbf{if } j = i - 1 \textbf{ and } v_i = N \\
        \\
        -1, & \textbf{if } i = j \\
        \\
        0, & \textbf{otherwise} \\
    \end{cases}
    \tag{\ref{eq:general_mapping_function_of_blocking_matrix} revisited}
\end{equation}

Thus, having calculated the mean blocking time for all blocking states 
\(b(u,v)\), it only remains to put them together in a formula.
The resultant formula for the mean blocking time is given by:

\begin{equation}
    B = \frac{\sum_{(u,v) \in S_A} \pi_{(u,v)} \; b(u,v)}{\sum_{(u,v) \in S_A} 
    \pi_{(u,v)}} \tag{\ref{eq:algebraic_blocking_time} revisited}
\end{equation}

To illustrate how the described formula works consider a Markov model where 
\(C=2, T=2, N=4, M=2\) (figure \ref{fig:example_algeb_blocking}). 
The equations that correspond to such a model are shown in 
(\ref{eq:first_eq_of_blocking_example})-(\ref{eq:last_eq_of_blocking_example}) 
and their equivalent matrix notation form is shown in 
(\ref{eq:example_algebaric_approach_blocking_time}).

\begin{minipage}{.5\textwidth}
    \begin{figure}[H]
        \scalebox{0.6}{\input{imgs/example_2242/main.tex}}
        \caption{
            \centering{Example of Markov chain with \(C=2, T=2, N=4, M=2\)}
        }
        \label{fig:example_algeb_blocking}
    \end{figure}
    \end{minipage}
    \begin{minipage}{.43\textwidth}
    \begin{align}
        b(1,2) &= c(1,2) + p_a b(1,3) \label{eq:first_eq_of_blocking_example} \\
        b(1,3) &= c(1,3) + p_s b(1,2) \nonumber \\ &+ p_a b(1,4) \\
        b(1,4) &= c(1,4) + b(1,3) \\
        b(2,2) &= c(2,2) + p_s b(1,2) \nonumber \\ &+ p_a b(2,3) \\
        b(2,3) &= c(2,3) + p_s b(2,2) \nonumber \\ &+ p_a b(1,4) \\
        b(2,4) &= c(2,4) + b(2,3) \label{eq:last_eq_of_blocking_example}
    \end{align}
\end{minipage}

\begin{equation}\label{eq:example_algebaric_approach_blocking_time}
    Z=
    \begin{pmatrix}
        -1 & p_a & 0 & 0 & 0 & 0 \\ %(1,2)
        p_s & -1 & p_a & 0 & 0 & 0 \\ %(1,3)
        0 & 1 & -1 & 0 & 0 & 0 \\ %(1,4)
        p_s & 0 & 0 & -1 & p_a & 0\\ %(2,2)
        0 & 0 & 0 & p_s & -1 & p_a \\ %(2,3)
        0 & 0 & 0 & 0 & 1 & -1 \\ %(2,4)
    \end{pmatrix},
    x=
    \begin{pmatrix}
        b(1,2) \\
        b(1,3) \\
        b(1,4) \\
        b(2,2) \\
        b(2,3) \\
        b(2,4) \\
    \end{pmatrix}, 
    y=
    \begin{pmatrix}
        -c(1,2) \\
        -c(1,3) \\
        -c(1,4) \\
        -c(2,2) \\
        -c(2,3) \\
        -c(2,4) \\
    \end{pmatrix}
\end{equation}

### 2021-05-21 sections/appendix/proportion_within_target_formula/main.tex
Add an appendix
Currently the appendix has some information of how to use the blocking
time formula. Soon to be added are information on the waiting time
formula (possibly the recursive method) and information on the
proportion within target formula.

\section{Mean blocking time} \label{sec:appendix_mean_proportion}

### 2021-05-21 sections/appendix/waiting_time_formula/main.tex
Add an appendix
Currently the appendix has some information of how to use the blocking
time formula. Soon to be added are information on the waiting time
formula (possibly the recursive method) and information on the
proportion within target formula.

\section{Mean waiting time}\label{sec:appendix_mean_waiting}

### 2021-05-21 sections/appendix/proportion_within_target_formula/main.tex
Restructure proportion within time target formula
Remove most parts of this section and move them to appendix

@@
 \section{Mean blocking time} \label{sec:appendix_mean_proportion}
+
+In order to consider such measure though one would need to obtain the 
+distribution of time in the system for all individuals. 
+The complexity of such task lies on the fact that different individuals arrive 
+at different states of the Markov model. 
+Consider the case when an arrival occurs when the model is at a specific state.
+
+\paragraph{Time distribution at specific state (1 server):}
+
+\begin{figure}[ht]
+    \centering
+    \scalebox{0.75}{
+        \input{imgs/example_1242/main.tex}
+    }
+    \caption{Example Markov model \(C=1, T=2, N=4, M=2\)}
+    \label{fig:distribution_of_time_at_specific_state_1_server}
+\end{figure}
+
+Consider the Markov model of figure 
+\ref{fig:distribution_of_time_at_specific_state_1_server} with one server and a 
+threshold of two individuals. 
+Assume that an individual of the first type arrives when the model is at state 
+\((0,3)\), thus forcing the model to move to state \((0,4)\). 
+The distribution of the time needed for the specified individual to exit the 
+system from state \((0,4)\) is given by the sum of exponentially distributed 
+random variables with the same parameter \(\mu\). 
+The sum of such random variables forms an Erlang distribution which is defined 
+by the number of random variables that are added and their exponential 
+parameter.
+Note here that these random variables represent the individual's pathway from 
+the perspective of the individual. 
+Thus, \(X_i\) represents the time that it takes to move from the 
+\(i^{\text{th}}\) position of the queue to the \((i-1)^{\text{th}}\) position 
+(i.e. for someone in front of them to finish their service) and \(X_0\) is the 
+time it takes to move from having a service to exiting the system.
+
+\begin{align}
+    (0,4) \Rightarrow \quad & X_3 \sim Exp(\mu) \nonumber \\
+    (0,3) \Rightarrow \quad & X_2 \sim Exp(\mu) \nonumber \\
+    (0,2) \Rightarrow \quad & X_1 \sim Exp(\mu) \nonumber \\
+    (0,1) \Rightarrow \quad & X_0 \sim Exp(\mu) \nonumber \\
+    S = X_3 + X_2 + & X_1 + X_0 = Erlang(4, \mu)
+\end{align}
+
+Thus, the waiting and service time of an individual in the model of figure 
+\ref{fig:distribution_of_time_at_specific_state_1_server} can be captured by an 
+erlang distributed random variable. 
+The general CDF of the erlang distribution \(Erlang(k, \mu)\) is given by:
+
+\begin{equation} \label{eq:cdf_erlang}
+    P(S < t) = 1 - \sum_{i=0}^{k-1} \frac{1}{i!} e^{-\mu t} (\mu t)^i
+\end{equation}
+
+Unfortunately, the erlang distribution can only be used for the sum of 
+identically distributed random variables from the exponential distribution. 
+Therefore, this approach cannot be used when one of the random variables has a 
+different parameter than the others. 
+In fact the only case where it can be used is only when the number of servers 
+are \(C=1\), or when an individual arrives and goes straight to service 
+(i.e. when there is no other individual waiting and there is an empty server).
+
+\paragraph{Time distribution at a state (multiple servers):}
+
+\begin{figure}[h]
+    \centering
+    \scalebox{0.75}{\input{imgs/example_2242/main.tex}}
+    \caption{Example Markov model \(C=2, T=2, N=4, M=2\)}
+    \label{fig:distribution_of_time_at_specific_state_2_servers}
+\end{figure}
+
+Figure \ref{fig:distribution_of_time_at_specific_state_2_servers} represents the 
+same Markov model as figure 
+\ref{fig:distribution_of_time_at_specific_state_1_server} with the only 
+exception that there are 2 servers here. 
+By applying the same logic, assuming that an individual arrives at state 
+\((0,4)\), the sum of the following random variables arises.
+
+\begin{align}
+    (0,4) \Rightarrow \quad & X_2 \sim Exp(2\mu) \nonumber \\
+    (0,3) \Rightarrow \quad & X_1 \sim Exp(2\mu) \\
+    (0,2) \Rightarrow \quad & X_0 \sim Exp(\mu) \nonumber
+\end{align}
+
+Since these exponentially distributed random variables do not share the same 
+parameter, an erlang distribution cannot be used. 
+In fact, the problem can now be viewed either as the sum of exponentially 
+distributed random variables with different parameters or as the sum of 
+erlang distributed random variables.
+The sum of erlang distributed random variables is said to follow the 
+hypoexponential distribution. 
+The hypoexponential distribution is defined with two vectors of size equal
+to the number of Erlang random variables \cite{Akkouchi2008}, \cite{Smaili2013}. 
+The vector \(\vec{r}\) contains all the \(k\)-values of the erlang distributions 
+and \(\vec{\lambda}\) is a vector of the distinct parameters as illustrated in
+equation (\ref{eq:connection_between_Hypoexponential_Erlang}).
+
+\begin{equation}\label{eq:connection_between_Hypoexponential_Erlang}
+    \begin{rcases}
+        Erlang(k_1, \lambda_1) \\
+        Erlang(k_2, \lambda_2) \\
+        \hspace{1cm} \vdots \\
+        Erlang(k_n, \lambda_n)
+    \end{rcases}
+    Hypo(
+        \underbrace{(k_1, k_2, \dots k_n)}_{\vec{k}}, 
+        \underbrace{(\lambda_1, \lambda_2, \dots \lambda_n)}_{\vec{\lambda}}
+    )
+\end{equation}
+
+Equivalently, for this particular example:
+\begin{align} \label{eq:multiple_servers_distribution_example}
+    \begin{rcases}
+        \begin{rcases}
+            \scriptstyle{X_2 \sim Exp(2\mu)} \\
+            \scriptstyle{X_1 \sim Exp(2\mu)}
+        \end{rcases}
+        \scriptstyle{X_1 + X_2 = S_1 \sim Erlang(2, 2\mu)} \\
+        \scriptstyle{X_0 \sim Exp(\mu) \Rightarrow 
+        \hspace{1cm} X_0 = S_2 \sim Erlang(1, \mu)}
+    \end{rcases}
+    \scriptstyle{S_1 + S_2 = H \sim Hypo((2,1), (2\mu, \mu))}
+\end{align}
+
+Therefore, the CDF of this distribution can be used to get the probability of 
+the time in spent in the system being less than a given target.
+The general CDF of the hypoexponential distribution \(Hypo(\vec{r}, 
+\vec{\lambda})\), is given by the following expression \cite{Favaro2010}:
+
+\begin{align} \label{eq:general_cdf_hypoexponential}
+    & P(H < t) = 1 - \left( \prod_{j=1}^{\mid \vec{r} \mid} \lambda_j^{r_j} \right) 
+    \sum_{k=1}^{\mid \vec{r} \mid} \sum_{l=1}^{r_k} \frac{\Psi_{k,l}(-\lambda_k)t^{r_k - l} 
+    e^{-\lambda_k t}}
+    {(r_k - l)! (l - 1)!} \nonumber \\ 
+    & \textbf{where} \qquad \Psi_{k,l}(t) = - \frac{\partial^{l - 1}}
+    {\partial t ^{l - 1}} \left( \prod_{j = 0, j \neq k}^{\mid \vec{r} \mid} 
+    (\lambda_j + t)^{-r_j} \right) \nonumber \\
+    & \textbf{and} \quad \qquad \lambda_0 = 0, r_0 = 1
+\end{align}
+
+The computation of the derivative makes equation 
+(\ref{eq:general_cdf_hypoexponential}) computationally expensive. 
+In \cite{Legros2015} an alternative linear version of that CDF is explored via 
+matrix analysis, and is given by the following formula:
+
+\begin{equation} \label{eq:linear_general_cdf_hypoexponential}
+    \begin{split}
+        F(x) = &1 - \sum_{k=1}^{n} \sum_{l=0}^{k-1} (-1)^{k-1} \binom{n}{k} 
+            \binom{k-1}{l} \sum_{j=1}^{n} \sum_{s=1}^{j-1} e^{-x \lambda_s} 
+            \prod_{l=1}^{s-1} \left( \frac{\lambda_l}{\lambda_l - \lambda_s} \right)
+            ^ {k_s} \\
+        & \times \sum_{s < a_1 < \dots < a_{l-1} < j} 
+            \left( \frac{\lambda_s}{\lambda_s - \lambda_{a_1}} \right) ^ {k_s}
+            \prod_{m=s+1}^{a_1-1} \left( \frac{\lambda_m}{\lambda_m - 
+            \lambda_{a_1}}\right) ^ {k_m} \\  
+        & \times \prod_{n=a_1}^{a_2-1} \left( \frac{\lambda_n}{\lambda_n - 
+            \lambda_{a_2}}\right) ^ {k_n} \dots 
+            \prod_{r=a_l-1}^{j-1} \left( \frac{\lambda_r}{\lambda_r - 
+            \lambda_{a_j}}\right) ^ {k_r}  
+            \sum_{q=0}^{k_s - 1} \frac{((\lambda_s - \lambda_{a_1})x)^q}{q!}, \\
+        & \text{for } x \geq 0
+    \end{split}
+\end{equation}
+
+\paragraph{Specific CDF of hypoexponential distribution}
+Equations (\ref{eq:general_cdf_hypoexponential}) and 
+(\ref{eq:linear_general_cdf_hypoexponential}) refers to the general CDF of the
+hypoexponential distribution where the size of the vector parameters can be of
+any size \cite{Favaro2010}.
+In the Markov chain models described in figures 
+\ref{fig:distribution_of_time_at_specific_state_1_server} and 
+\ref{fig:distribution_of_time_at_specific_state_2_servers} the parameter vectors 
+of the hypoexponential distribution are of size two, and in fact, for any 
+possible version of the investigated Markov chain model the vectors can only be 
+of size two.
+This is true since for any dimensions of this Markov chain model there will 
+always be at most two distinct exponential parameters; the parameter for 
+finishing a service (\(\mu\)) and the parameter for moving forward in the queue 
+(\(C \mu\)). 
+For the special case of \(C=1\) the hypoexponential distribution will not be 
+used as this is equivalent to an erlang distribution.
+Therefore, by fixing the sizes of \(\vec{r}\) and \(\vec{\lambda}\) to 2, the 
+following specific expression for the CDF of the hypoexponential distribution
+arises, where the derivative is removed:
+
+\begin{align} \label{eq:specific_cdf_hypoexponential}
+    & P(H < t) = 1 - \left( \prod_{j=1}^{\mid \vec{r} \mid} \lambda_j^{r_j} \right) 
+    \sum_{k=1}^{\mid \vec{r} \mid} \sum_{l=1}^{r_k} \frac{\Psi_{k,l}(-\lambda_k)t^{r_k - l} 
+    e^{-\lambda_k t}}{(r_k - l)! (l - 1)!} \nonumber \\ 
+    & \textbf{where} \qquad \Psi_{k,l}(t) = 
+    \begin{cases} 
+        \frac{(-1)^{l} (l-1)!}{\lambda_2} \left[\frac{1}{t^l} - \frac{1}
+        {(t + \lambda_2)^l}\right] , & k=1 \\
+        - \frac{1}{t (t + \lambda_1)^{r_1}}, & k=2
+    \end{cases} \nonumber \\
+    & \textbf{and} \quad \qquad \lambda_0 = 0, r_0 = 1
+\end{align}
+
+Note here that the only difference between equations
+(\ref{eq:general_cdf_hypoexponential}) and (\ref{eq:specific_cdf_hypoexponential}) 
+is the \(\Psi\) function. 
+The next part proves that the expression for \(\Psi\) can be simplified for the 
+cases of \(k = 1,2\). 
+Equation (\ref{eq:hypoexponential_expression_to_proof}) shows the expression to 
+be proved.
+
+\begin{equation} \label{eq:hypoexponential_expression_to_proof}
+    \Psi_{(k,l)}(t) = - \frac{\partial^{l - 1}}{\partial t ^{l - 1}} 
+    \left( \prod_{j = 0, j \neq k}^{\mid \vec{r} \mid} (\lambda_j + t)^{-r_j} \right) = 
+    \begin{cases} 
+        \frac{(-1)^{l} (l-1)!}{\lambda_2} \left[\frac{1}{t^l} - \frac{1}
+        {(t + \lambda_2)^l}\right] , & k=1 \\
+        - \frac{1}{t (t + \lambda_1)^{r_1}}, & k=2
+    \end{cases}
+\end{equation}
+
+\paragraph{Proof of equation (\ref{eq:hypoexponential_expression_to_proof})}
+
+This section aims to show that there exists a simplified version of equation 
+(\ref{eq:general_cdf_hypoexponential}) that is specific to the proposed Markov 
+model.
+Function \(\Psi\) is defined using the parameter \(t\) and the variables \(k\) 
+and \(l\).
+Given the Markov model, the range of values that \(k\) and \(l\) can take can be
+bounded.
+First of all, from the range of the double summation in equation 
+(\ref{eq:general_cdf_hypoexponential}), it can be seen that 
+\(k = 1, 2, \dots, \mid \vec{r} \mid\).
+Now, \(\mid \vec{r} \mid\) represents the size of the parameter vectors that, 
+for the Markov model, will always be 2. 
+That is because, for all the exponentially distributed random variables that are
+added together to form the new distribution, there only two distinct parameters,
+thus forming two erlang distributions. Therefore:
+
+\begin{equation*}
+    k = 1, 2
+\end{equation*}
+
+By observing equation (\ref{eq:general_cdf_hypoexponential}) once more, the range
+of values that \(l\) takes are \(l = 1, 2, \dots, r_k\), where \(r_1\) is 
+subject to the individual's position in the queue and \(r_2 = 1\).
+In essence, the hypoexponential distribution will be used with these bounds:
+
+\begin{align}
+    k = 1 & \qquad \Rightarrow \qquad l = 1, 2, \dots, r_1 \nonumber \\
+    k = 2 & \qquad \Rightarrow \qquad l = 1
+\end{align}
+
+Thus the left hand side of equation (\ref{eq:hypoexponential_expression_to_proof}) 
+needs only to be defined for these bounds. 
+The specific hypoexponential distribution investigated here is of the form
+\(Hypo((r_1, 1)(\lambda_1, \lambda_2))\).
+Note the initial conditions \(\lambda_0=0, r_0=1\) defined in equation 
+(\ref{eq:general_cdf_hypoexponential}) also hold here.
+Thus the proof is split into two parts, for \(k=1\) and \(k=2\).
+
+\begin{itemize}
+    \item \(k = 2, l = 1\)
+    \begin{equation*}
+        \begin{split}
+            LHS &= - \frac{\partial^{1-1}}{\partial t^{1-1}} 
+            \left( \prod_{j=0, j \neq 2}^{2} (\lambda_j + t)^{-r_j} \right) \\
+            &=-\left( (\lambda_0 + t)^{-r_0} \times (\lambda_1 + t)^{-r_1} \right) \\
+            &=-\left( t^{-1} \times (\lambda_1 + t)^{-r_1} \right) \\ 
+            &= - \frac{1}{t(t + \lambda_1)^{r_1}} \\
+            & \hspace{7cm} \square
+        \end{split}
+    \end{equation*}
+    \item \(k = 1, l = 1, \dots, r_1\)
+    \begin{equation*}
+        \begin{split}
+            LHS &= -\frac{\partial^{l-1}}{\partial t^{l-1}} 
+            \left( \prod_{j=0, j \neq 1}^{2} (\lambda_j + t)^{-r_j} \right) \\
+            &= -\frac{\partial^{l-1}}{\partial t^{l-1}}
+            \left( (\lambda_o + t)^{-r_0} \times (\lambda_2 + t)^{-r_2} \right) \\
+            &= -\frac{\partial^{l-1}}{\partial t^{l-1}}
+            \left( \frac{1}{t(t + \lambda_2)}\right)
+        \end{split}
+    \end{equation*}
+    In essence, it only remains to show that:
+    \[-\frac{\partial^{l-1}}{\partial t^{l-1}} 
+    \left( \frac{1}{t(t + \lambda_2)}\right) = \frac{(-1)^{l} (l-1)!}{\lambda_2}
+    \left[\frac{1}{t^l} - \frac{1}{(t + \lambda_2)^l}\right]\]
+
+    \textbf{Proof by Induction:}
+    \begin{enumerate}
+        \item Base case (\(l=1\)):
+        \begin{equation*}
+            \begin{split}
+                LHS &= -\frac{\partial^{1-1}}{\partial t^{1-1}} 
+                \left( \frac{1}{t(t + \lambda_2)}\right) = 
+                - \frac{1}{t(t + \lambda_2)} \\
+                RHS &= \frac{(-1)^{1} (1-1)!}{\lambda_2}
+                \left[\frac{1}{t^1} - \frac{1}{(t + \lambda_2)^1}\right] \\
+                &= - \frac{t + \lambda_2 - t}{\lambda_2 t (t + \lambda_2)} \\
+                &= - \frac{1}{t (t + \lambda_2)} \\
+                LHS &= RHS
+            \end{split}
+        \end{equation*}
+        \item Assume true for \(l = x\):
+        \begin{equation*}
+            -\frac{\partial^{x-1}}{\partial t^{x-1}} 
+            \left( \frac{1}{t(t + \lambda_2)}\right) = 
+            \frac{(-1)^{x} (x-1)!}{\lambda_2}
+            \left[\frac{1}{t^x} - \frac{1}{(t + \lambda_2)^x}\right]
+        \end{equation*}
+        \item Prove true for \(l = x + 1\). Need to show that:
+        \[ 
+            \frac{\partial^x}{\partial t ^ x} 
+            \left( \frac{-1}{t (t + \lambda_2)} \right) = 
+            \frac{(-1)^{x + 1} (x)!}{\lambda_2}
+            \left[ \frac{1}{t^{x+1}}-\frac{1}{(t + \lambda_2)^{x+1}} \right] 
+        \]
+        \begin{equation*}
+            \begin{split}
+                LHS &= \frac{\partial}{\partial t}
+                \left[ \frac{\partial^{x-1}}{\partial t ^ {x-1}} 
+                \left( \frac{-1}{t (t + \lambda_2)} \right) \right] \\
+                &= \frac{\partial}{\partial t} \left[
+                    \frac{(-1)^x (x-1)!}{\lambda_2} \left(
+                        \frac{1}{t^x} - \frac{1}{(t + \lambda_2)^x}
+                    \right)
+                \right] \\
+                &= \frac{(-1)^x (x-1)!}{\lambda_2} \left(
+                    \frac{(-x)}{t^{x+1}} - \frac{(-x)}{(t + \lambda_2)^x}
+                \right) \\
+                &= \frac{(-1)^x (x-1)! (-x)}{\lambda_2} \left(
+                    \frac{1}{t^{x+1}} - \frac{1}{(t + \lambda_2)^x}
+                \right) \\
+                &= \frac{(-1)^{x+1} (x)!}{\lambda_2} \left(
+                    \frac{1}{t^{x+1}} - \frac{1}{(t + \lambda_2)^x}
+                \right) \\
+                & = RHS \\
+                & \hspace{7cm} \square
+            \end{split}
+        \end{equation*}
+    \end{enumerate}
+\end{itemize}
+
+\paragraph{Proportion within target for both types of individuals}
+
+Given the two CDFs of the Erlang and Hypoexponential distributions a new 
+function has to be defined to decide which one to use among the two.
+Based on the state of the model, there can be three scenarios when an individual
+arrives.
+\begin{enumerate}
+    \item There is a free server and the individual does not have to wait
+    \begin{equation*}
+        X_{(u,v)} \sim Erlang(1, \mu) 
+    \end{equation*}
+    \item The individual arrives at a queue at the \(n^{th}\) position and the 
+    model has \(C > 1\) servers
+    \begin{equation*}
+        X_{(u,v)} \sim Hypo((n, 1), (C \mu, \mu)) 
+    \end{equation*}
+    \item The individual arrives at a queue at the \(n^{th}\) position and the 
+    model has \(C = 1\) servers
+    \begin{equation*}
+        X_{(u,v)} \sim Erlang(n + 1, \mu) 
+    \end{equation*}
+\end{enumerate}
+
+Note here that for the first case \(Erlang(1, \mu)\) is equivalent to 
+\(Exp(\mu)\). 
+Consider \(X_{(u,v)}^{(1)}\) to be the distribution of type 1 individuals and
+\(X_{(u,v)}^{(2)}\) the distribution of type 2 individuals, when arriving at 
+state \((u,v)\) of the model.
+
+\begin{equation}
+    X_{(u,v)}^{(1)} \sim 
+    \begin{cases}
+        \textbf{Erlang}(v, \mu), & \textbf{if } C = 1 \textbf{ and } v>1 \\
+        \textbf{Hypo} \left(
+            \left[v - C, 1\right], \left[C \mu, \mu \right]
+        \right), & \textbf{if } C > 1 \textbf{ and } v>C \\
+        \textbf{Erlang}(1, \mu), & \textbf{if } v \leq C
+    \end{cases}
+\end{equation}
+
+\begin{equation}
+    X_{(u,v)}^{(2)} \sim 
+    \begin{cases}
+        \textbf{Erlang}(\min(v, T), \mu), & \textbf{if } C = 1
+            \textbf{ and } v, T > 1 \\
+        \textbf{Hypo}\left(
+            \left[ \min(v, T) - C, 1 \right], \left[ C \mu, \mu \right]
+        \right), & \textbf{if } C > 1 \textbf{ and } v, T  > C \\
+        \textbf{Erlang}(1, \mu), & \textbf{if } v \leq C \textbf{ or } T \leq C
+    \end{cases}
+\end{equation}
+
+Thus, the CDF of the random variables \(X_{(u,v)}^{(1)}\) and 
+\(X_{(u,v)}^{(2)}\) can be calculated using equations (\ref{eq:cdf_erlang}) and 
+(\ref{eq:specific_cdf_hypoexponential}):
+
+\begin{equation}
+    P(X_{(u,v)}^{(1)} < t) = 
+    \begin{cases}
+        1 - \sum_{i=0}^{v-1} \frac{1}{i!} e^{-\mu t} (\mu t)^i, 
+            & \textbf{if } C = 1 \\
+            & \textbf{and } v>1 \\
+        & \\
+        1 - (\mu C)^{v-C} \mu  
+            \sum_{k=1}^{\mid \vec{r} \mid} \sum_{l=1}^{r_k}
+            \frac{\Psi_{k,l}(-\lambda_k)t^{r_k - l} 
+            e^{-\lambda_k t}}{(r_k - l)! (l - 1)!},
+            & \textbf{if } C > 1 \\
+        \textbf{where } \vec{r}=(v - C, 1) \textbf{ and } 
+            \vec{\lambda}=(C \mu, \mu) & \textbf{and } v > C \\
+        & \\
+        1 - e^{-\mu t},  & \textbf{if } v \leq C
+    \end{cases}
+    \tag{\ref{eq:proportion_within_target_type_1} revisited}
+\end{equation}
+
+\begin{equation}
+    P(X_{(u,v)}^{(2)} < t) = 
+    \begin{cases}
+        1 - \sum_{i=0}^{\min(v,T)-1} \frac{1}{i!} e^{-\mu t} (\mu t)^i,  
+            & \textbf{if } C = 1 \\ 
+            & \textbf{and } v, T > 1 \\
+            & \\
+        1 - (\mu C) ^ {\min(v,T) - C} \mu  & \textbf{if } C > 1 \\
+        \qquad \times \sum_{k=1}^{\mid \vec{r} \mid} \sum_{l=1}^{r_k} 
+            \frac{\Psi_{k,l}(-\lambda_k)t^{r_k - l} 
+            e^{-\lambda_k t}}{(r_k - l)! (l - 1)!}, 
+            & \textbf{and } v, T  > C \\
+        \textbf{where } \vec{r}=(\min(v, T) - C, 1) \\
+        \hspace{1.15cm} \vec{\lambda}=(C \mu, \mu) \\
+        & \\
+        1 - e^{-\mu t}, & \textbf{if } v \leq C \\ 
+        & \textbf{or } T \leq C \\
+    \end{cases}
+    \tag{\ref{eq:proportion_within_target_type_2} revisited}
+\end{equation}
+
+In addition, the set of accepting states for type 1 \(S_A^{(1)}\) and type 2 
+\(S_A^{(2)}\) individuals defined in (\ref{eq:accepting_states_type_1}) and 
+(\ref{eq:accepting_states_type_2}) are also needed here.
+Note here that, \(S\) denotes the set of all states of the Markov chain model.
+
+\begin{align*}
+    S_A^{(1)} &= \{(u, v) \in S \; | \; v < N \} \\
+    S_A^{(2)} &=
+    \begin{cases}
+        \{(u, v) \in S \; | \; u < M \}, & \textbf{if } T \leq N \\
+        \{(u, v) \in S \; | \; v < N \}, & \textbf{otherwise}
+    \end{cases}
+\end{align*}
+
+The following formula uses the state probability vector \(\pi\) to get the 
+weighted average of the probability below target of all states in the Markov
+model.
+
+\begin{equation}
+    P(X^{(1)} < t) = \frac{\sum_{(u,v) \in S_A^{(1)}} P(X_{u,v}^{(1)} < t) 
+    \pi_{u,v} }{\sum_{(u,v) \in S_A^{(1)}} \pi_{u,v}}
+\end{equation}
+
+\begin{equation}
+    P(X^{(2)} < t) = \frac{\sum_{(u,v) \in S_A^{(2)}} P(X_{u,v}^{(2)} < t) 
+    \pi_{u,v} }{\sum_{(u,v) \in S_A^{(2)}} \pi_{u,v}}
+\end{equation}
+
+\paragraph{Overall proportion within target}
+
+The overall proportion of individuals for both types of individuals is given by 
+the equivalent formula of equation (\ref{eq:overall_waiting_time}).
+The following formula uses the probability of lost individuals from both types
+to get the weighted sum of the two probabilities.
+
+\begin{equation*}
+    P_{L'_1} = \sum_{(u,v) \, \in S_A^{(1)}} \pi(u,v), \hspace{1.5cm}
+    P_{L'_2} = \sum_{(u,v) \, \in S_A^{(2)}} \pi(u,v)
+\end{equation*}
+
+\begin{align}
+    P(X < t) &= \frac{\lambda_1 P_{L'_1}}{\lambda_2 P_{L'_2}+\lambda_1 P_{L'_1}} 
+    P(X^{(1)} < t) \nonumber \\
+    &+ \frac{\lambda_2 P_{L'_2}}{\lambda_2 P_{L'_2} + \lambda_1 
+    P_{L'_1}} P(X^{(2)} < t) 
+    \tag{\ref{eq:overall_proportion_within_target} revisited}
+\end{align}

### 2021-05-21 sections/queueing_model/subsections/performance_measures/waiting_time/main.tex
Minor change in notation on waiting time formula
Restructure proportion within time target formula
Remove most parts of this section and move them to appendix

@@
 \begin{equation}\label{eq:overall_waiting_time}
-    W = \frac{\lambda_1 P(L'_1)}{\lambda_2 P(L'_2) + \lambda_1 P(L'_1)} W^{(1)} 
-    + \frac{\lambda_2 P(L'_2)}{\lambda_2 P(L'_2) + \lambda_1 P(L'_1)} W^{(2)}
+    W = \frac{\lambda_1 P_{L'_1}}{\lambda_2 P_{L'_2} + \lambda_1 P_{L'_1}} W^{(1)} 
+    + \frac{\lambda_2 P_{L'_2}}{\lambda_2 P_{L'_2} + \lambda_1 P_{L'_1}} W^{(2)}
 \end{equation}
@@
 and type 2 individuals that are not lost to the system. These probabilities are 
-given by \(P(L'_1)\) and \(P(L'_2)\) where:
+given by \(P_{L'_1}\) and \(P_{L'_2}\) where:
 
-\begin{equation}
-    P(L'_1) = \sum_{(u,v) \, \in S_A^{(1)}} \pi(u,v) \hspace{2cm}
-    P(L'_2) = \sum_{(u,v) \, \in S_A^{(2)}} \pi(u,v)
+\begin{equation}\label{eq:proportion_of_accepting_individuals}
+    P_{L'_1} = \sum_{(u,v) \, \in S_A^{(1)}} \pi(u,v) \hspace{2cm}
+    P_{L'_2} = \sum_{(u,v) \, \in S_A^{(2)}} \pi(u,v)
 \end{equation}

### 2021-05-24 imgs/markov_vs_des/blocking_time/main.py
Add python code to generate violinplots
Added 3 python files that will generate violinplots for
the waiting time, blocking time and proportion within target
using the simulation model. These are then compared in the
same plot with the analytical outcomes using the Markov
chains method.

@@ -1,0 +1,63 @@
+import matplotlib.pyplot as plt
+import numpy as np
+import ambulance_game as abg
+
+lambda_2 = 3
+lambda_1 = 4
+mu = 8
+num_of_servers = 1
+threshold = 8
+system_capacity = 10
+buffer_capacity = 10
+seed_num = None
+warm_up_time = 500
+num_of_trials = 100
+runtime = 100000
+
+
+simulation_results = abg.simulation.get_multiple_runs_results(
+    lambda_2=lambda_2,
+    lambda_1=lambda_1,
+    mu=mu,
+    num_of_servers=num_of_servers,
+    threshold=threshold,
+    system_capacity=system_capacity,
+    buffer_capacity=buffer_capacity,
+    seed_num=seed_num,
+    warm_up_time=warm_up_time,
+    num_of_trials=num_of_trials,
+    runtime=runtime,
+    class_type=1,
+)
+
+blocking_times_simulation = [np.mean(b.blocking_times) for b in simulation_results]
+
+mean_blocking_time_markov = (
+    abg.markov.get_mean_blocking_time_using_markov_state_probabilities(
+        lambda_2=lambda_2,
+        lambda_1=lambda_1,
+        mu=mu,
+        num_of_servers=num_of_servers,
+        threshold=threshold,
+        system_capacity=system_capacity,
+        buffer_capacity=buffer_capacity,
+    )
+)
+
+
+fig, ax = plt.subplots(nrows=1, ncols=1)
+plt.violinplot(
+    blocking_times_simulation,
+    showmeans=True,
+)
+ax.plot(
+    [0.85, 1.15],
+    [mean_blocking_time_markov, mean_blocking_time_markov],
+    color="red",
+)
+ax.set_xticks([1])
+ax.set_xticklabels(["Type 2 individuals"])
+ax.set_title("Blocking time")
+ax.legend(["Markov chain", "Simulation"])
+
+plt.savefig("main.pdf", transparent=True)

### 2021-05-24 imgs/markov_vs_des/proportion_within_time/main.py

@@ -1,0 +1,110 @@
+import matplotlib.pyplot as plt
+import numpy as np
+import ambulance_game as abg
+
+lambda_2 = 3
+lambda_1 = 4
+mu = 8
+num_of_servers = 1
+threshold = 8
+target = 0.5
+system_capacity = 10
+buffer_capacity = 10
+seed_num = None
+warm_up_time = 500
+num_of_trials = 100
+runtime = 100000
+
+
+(
+    simulation_results_overall,
+    simulation_results_type_1,
+    simulation_results_type_2,
+) = abg.simulation.get_mean_proportion_of_individuals_within_target_for_multiple_runs(
+    lambda_2=lambda_2,
+    lambda_1=lambda_1,
+    mu=mu,
+    num_of_servers=num_of_servers,
+    threshold=threshold,
+    system_capacity=system_capacity,
+    buffer_capacity=buffer_capacity,
+    seed_num=seed_num,
+    num_of_trials=num_of_trials,
+    runtime=runtime,
+    target=target,
+)
+
+mean_proportion_markov_overall = (
+    abg.markov.proportion_within_target_using_markov_state_probabilities(
+        lambda_1=lambda_1,
+        lambda_2=lambda_2,
+        mu=mu,
+        num_of_servers=num_of_servers,
+        threshold=threshold,
+        system_capacity=system_capacity,
+        buffer_capacity=buffer_capacity,
+        target=target,
+        class_type=None,
+    )
+)
+
+mean_proportion_markov_type_1 = (
+    abg.markov.proportion_within_target_using_markov_state_probabilities(
+        lambda_1=lambda_1,
+        lambda_2=lambda_2,
+        mu=mu,
+        num_of_servers=num_of_servers,
+        threshold=threshold,
+        system_capacity=system_capacity,
+        buffer_capacity=buffer_capacity,
+        target=target,
+        class_type=0,
+    )
+)
+
+mean_proportion_markov_type_2 = (
+    abg.markov.proportion_within_target_using_markov_state_probabilities(
+        lambda_1=lambda_1,
+        lambda_2=lambda_2,
+        mu=mu,
+        num_of_servers=num_of_servers,
+        threshold=threshold,
+        system_capacity=system_capacity,
+        buffer_capacity=buffer_capacity,
+        target=target,
+        class_type=1,
+    )
+)
+
+
[…]

### 2021-05-25 sections/queueing_model/subsections/performance_measures/blocking_time/main.tex
Add comparisons between Markov and DES
Include violinplots of waiting time, blocking time and proportion
within target time. The violinplots show the differences between
Markov values and simulated values.

@@
 \end{equation}
+
+Additional details on the blocking time formula 
+(\ref{eq:algebraic_blocking_time}) can be found in appendix 
+\ref{sec:appendix_mean_blocking}. 
+Figure \ref{fig:markov_vs_des_blocking_time_comparison} illustrates a comparison 
+between Markov chains and discrete event simulation of the blocking time of
+type 2 individuals.
+
+\begin{figure}[ht]
+    \centering
+    \scalebox{0.7}{\includegraphics{
+        imgs/markov_vs_des/blocking_time/main.pdf
+    }}
+    \caption{
+        Comparison of mean blocking time between values obtained from the Markov
+        chain formulas and values obtained from simulation. The simulation 
+        was ran 100 times and the recorded mean blocking time at each iteration
+        is used to populate the violin plots.
+    }
+    \label{fig:markov_vs_des_blocking_time_comparison}
+\end{figure}

### 2021-05-25 sections/queueing_model/subsections/performance_measures/waiting_time/main.tex
Add comparisons between Markov and DES
Include violinplots of waiting time, blocking time and proportion
within target time. The violinplots show the differences between
Markov values and simulated values.

@@
 \end{equation}
+
+Appendix \ref{sec:appendix_mean_waiting} gives more details on the recursive
+formula that equations (\ref{eq:closed_form_waiting_type_1}),
+(\ref{eq:closed_form_waiting_type_2}) and (\ref{eq:overall_waiting_time})
+originate from.
+
+Figure \ref{fig:markov_vs_des_waiting_time_comparison} shows a comparison 
+between the calculated mean waiting time using Markov chains and the simulated waiting time using discrete event simulation.
+
+\begin{figure}[ht]
+    \centering
+    \scalebox{0.7}{\includegraphics{
+        imgs/markov_vs_des/waiting_time/main.pdf
+    }}
+    \caption{
+        Comparison of mean waiting time between values obtained from the Markov
+        chain formulas and values obtained from simulation. The simulation 
+        was ran 100 times and the recorded mean waiting time at each iteration
+        is used to populate the violin plots.
+    }
+    \label{fig:markov_vs_des_waiting_time_comparison}
+\end{figure}

### 2021-05-26 imgs/markov_vs_des/all_types/blocking/main.py
Add new plots to compare Markov and DES
The comparisons are now made over different values of
lambda_2, for all performance measures for all possible
types of individuals.

@@ -1,0 +1,72 @@
+import matplotlib.pyplot as plt
+import numpy as np
+import ambulance_game as abg
+
+lambda_1 = 4
+mu = 3
+num_of_servers = 3
+threshold = 8
+system_capacity = 10
+buffer_capacity = 10
+seed_num = None
+warm_up_time = 500
+num_of_trials = 100
+runtime = 10000
+# warm_up_time = 10
+# num_of_trials = 10
+# runtime = 100
+
+all_sim_blocking_times_2 = []
+all_markov_blocking_times_2 = []
+lambda_2_space = np.linspace(2, 6, 6)
+for lambda_2 in lambda_2_space:
+    # Simulation - type 2
+    simulation_results_2 = abg.simulation.get_multiple_runs_results(
+        lambda_2=lambda_2,
+        lambda_1=lambda_1,
+        mu=mu,
+        num_of_servers=num_of_servers,
+        threshold=threshold,
+        system_capacity=system_capacity,
+        buffer_capacity=buffer_capacity,
+        seed_num=seed_num,
+        warm_up_time=warm_up_time,
+        num_of_trials=num_of_trials,
+        runtime=runtime,
+        class_type=1,
+    )
+    all_sim_blocking_times_2.append(
+        [np.mean(b.blocking_times) for b in simulation_results_2]
+    )
+
+    # Markov - type 2
+    markov_blocking_value_2 = (
+        abg.markov.get_mean_blocking_time_using_markov_state_probabilities(
+            lambda_2=lambda_2,
+            lambda_1=lambda_1,
+            mu=mu,
+            num_of_servers=num_of_servers,
+            threshold=threshold,
+            system_capacity=system_capacity,
+            buffer_capacity=buffer_capacity,
+        )
+    )
+    all_markov_blocking_times_2.append(markov_blocking_value_2)
+
+
+# Blocking time type 2 individuals
+fig, ax = plt.subplots(nrows=1, ncols=1)
+plt.violinplot(
+    all_sim_blocking_times_2, positions=lambda_2_space, showmeans=True, widths=0.3
+)
+ax.plot(
+    lambda_2_space,
+    all_markov_blocking_times_2,
+    color="red",
+)
+ax.set_title("Blocking time using Markov chain and simulation")
+ax.legend(["Markov chain", "Simulation"])
+ax.set_xlabel("$\lambda_2$")
+ax.set_ylabel("Time blocked")
+
+plt.savefig("blocking.pdf", transparent=True)

### 2021-05-26 imgs/markov_vs_des/all_types/waiting/main.py

@@ -1,0 +1,186 @@
+import matplotlib.pyplot as plt
+import numpy as np
+import ambulance_game as abg
+
+lambda_1 = 4
+mu = 3
+num_of_servers = 3
+threshold = 8
+system_capacity = 10
+buffer_capacity = 10
+seed_num = None
+warm_up_time = 500
+num_of_trials = 100
+runtime = 10000
+# warm_up_time = 10
+# num_of_trials = 10
+# runtime = 100
+
+all_sim_waiting_times_1 = []
+all_sim_waiting_times_2 = []
+all_sim_waiting_times_all = []
+
+all_markov_waiting_times_1 = []
+all_markov_waiting_times_2 = []
+all_markov_waiting_times_all = []
+lambda_2_space = np.linspace(2, 6, 6)
+for lambda_2 in lambda_2_space:
+    # Simulation - type 1
+    simulation_results_1 = abg.simulation.get_multiple_runs_results(
+        lambda_2=lambda_2,
+        lambda_1=lambda_1,
+        mu=mu,
+        num_of_servers=num_of_servers,
+        threshold=threshold,
+        system_capacity=system_capacity,
+        buffer_capacity=buffer_capacity,
+        seed_num=seed_num,
+        warm_up_time=warm_up_time,
+        num_of_trials=num_of_trials,
+        runtime=runtime,
+        class_type=0,
+    )
+    all_sim_waiting_times_1.append(
+        [np.mean(w.waiting_times) for w in simulation_results_1]
+    )
+
+    # Simulation - type 2
+    simulation_results_2 = abg.simulation.get_multiple_runs_results(
+        lambda_2=lambda_2,
+        lambda_1=lambda_1,
+        mu=mu,
+        num_of_servers=num_of_servers,
+        threshold=threshold,
+        system_capacity=system_capacity,
+        buffer_capacity=buffer_capacity,
+        seed_num=seed_num,
+        warm_up_time=warm_up_time,
+        num_of_trials=num_of_trials,
+        runtime=runtime,
+        class_type=1,
+    )
+    all_sim_waiting_times_2.append(
+        [np.mean(w.waiting_times) for w in simulation_results_2]
+    )
+
+    # Simulation - overall
+    simulation_results_all = abg.simulation.get_multiple_runs_results(
+        lambda_2=lambda_2,
+        lambda_1=lambda_1,
+        mu=mu,
+        num_of_servers=num_of_servers,
+        threshold=threshold,
[…]

### 2021-05-26 sections/appendix/descrete_event_simulation/main.tex
Add a todo to add description for DES

\section{Discrete Event Simulation}\label{sec:appendix_des}

% TODO: Include details of DES

### 2021-05-26 tasks.py
Chnage the way pdf compiles in CI
tasks.py are updated so that latexmk runs with the xelatex parameter

@@ -10,9 +10,9 @@ import known
 
 @task
 def compile(c):
-    """ Compile the LaTeX document. """
+    """Compile the LaTeX document."""
 
-    c.run(f"latexmk main.tex")
+    c.run(f"latexmk -xelatex main.tex")
 
 
 @task
@@ -32,8 +32,7 @@ def spellcheck(c):
         incorrect_words = set()
         for error in errors:
             if not any(
-                re.fullmatch(word.lower(), error.lower())
-                for word in known.words
+                re.fullmatch(word.lower(), error.lower()) for word in known.words
             ):
                 incorrect_words.add(error)
 

### 2021-05-26 sections/queueing_model/subsections/performance_measures/blocking_time/main.tex
Fix latex compile issue with pdfs (#8)
* Remove scalebox before \includegraphics

* Add updated .pdf

* Chnage the way pdf compiles in CI

tasks.py are updated so that latexmk runs with the xelatex parameter

* Update CI to install additional libraries

Specifically: texlive-xetex, texlive-science

* Restructure imgs/ directory
Add new violinplots
Include violin plots of performance measures over
different values of lambda_2 for type 1, type 2 and
overall individuals

--- 2021-05-21 sections/queueing_model/subsections/performance_measures/blocking_time/main.tex
@@
 \end{equation}
+
+Additional details on the blocking time formula 
+(\ref{eq:algebraic_blocking_time}) can be found in appendix 
+\ref{sec:appendix_mean_blocking}.
+
+Figure \ref{fig:markov_vs_des_blocking_time_comparison} illustrates a comparison 
+between the formulas that arise from the Markov chain model and the equivalent 
+values of the blocking time extracted from discrete event simulation.
+The blocking time is calculated using both methods for a range of values of
+\(\lambda_2\)
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=.8\textwidth]{imgs/blocking_time_comparison/blocking.pdf}
+    \caption{
+        Comparison of mean blocking time between values obtained from the Markov 
+        chain formulas and values obtained from simulation.
+    }
+    \label{fig:markov_vs_des_blocking_time_comparison}
+\end{figure}

### 2021-05-26 sections/queueing_model/subsections/performance_measures/waiting_time/main.tex
Fix latex compile issue with pdfs (#8)
* Remove scalebox before \includegraphics

* Add updated .pdf

* Chnage the way pdf compiles in CI

tasks.py are updated so that latexmk runs with the xelatex parameter

* Update CI to install additional libraries

Specifically: texlive-xetex, texlive-science

* Restructure imgs/ directory
Add new violinplots
Include violin plots of performance measures over
different values of lambda_2 for type 1, type 2 and
overall individuals

--- 2021-05-21 sections/queueing_model/subsections/performance_measures/waiting_time/main.tex
@@
 \end{equation}
+
+Appendix \ref{sec:appendix_mean_waiting} gives more details on the recursive
+formula that equations (\ref{eq:closed_form_waiting_type_1}),
+(\ref{eq:closed_form_waiting_type_2}) and (\ref{eq:overall_waiting_time})
+originate from.
+
+Figures \ref{fig:markov_vs_des_waiting_time_comparison_1},
+\ref{fig:markov_vs_des_waiting_time_comparison_2} and
+\ref{fig:markov_vs_des_waiting_time_comparison_overall} show a comparison 
+between the calculated mean waiting time using Markov chains and the simulated 
+waiting time using discrete event simulation over a range of values of 
+\(\lambda_2\).
+The simulation was ran 100 times and the recorded mean waiting time at each 
+iteration is used to populate the violin plots.
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=.8\textwidth]{imgs/waiting_time_comparison/waiting_1.pdf}
+    \caption{
+        Comparison of mean waiting time for type 1 individuals between values 
+        obtained from the Markov chain formulas and values obtained from 
+        simulation.
+    }
+    \label{fig:markov_vs_des_waiting_time_comparison_1}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=.8\textwidth]{imgs/waiting_time_comparison/waiting_2.pdf}
+    \caption{
+        Comparison of mean waiting time for type 2 individuals between values 
+        obtained from the Markov chain formulas and values obtained from 
+        simulation.
+    }
+    \label{fig:markov_vs_des_waiting_time_comparison_2}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=.8\textwidth]{imgs/waiting_time_comparison/waiting_overall.pdf}
+    \caption{
+        Comparison of mean waiting time for both types of individuals between 
+        values obtained from the Markov chain formulas and values obtained from 
+        simulation.
+    }
+    \label{fig:markov_vs_des_waiting_time_comparison_overall}
+\end{figure}
+
+% TODO: Possibly add another example that will be used in section 5

### 2021-05-26 sections/queueing_model/subsections/performance_measures/blocking_time/main.tex
Apply changes from code review

@@
 
-% TODO: These might possibly need to be moved to the appendix 
-The system of equations produced by (\ref{eq:general_blocking_time_at_each_state}) can be solved by considering the linear system \(Zx=y\), where:
+The system of equations produced by 
+(\ref{eq:general_blocking_time_at_each_state}) can be solved by considering the 
+linear system \(Zx=y\). 
+Assuming \(i\) and \(j\) represent states \((u_i, v_i), (u_j, v_j) \in S_b\) 
+then \(Z_{ij}\) is given by:
 
+\begin{equation}\label{eq:general_mapping_function_of_blocking_matrix}
+    Z_{ij} = 
+    \begin{cases}
+        p_a, & \textbf{if } j = i + 1 \textbf{ and } v_i \neq N \\
+        \\
+        p_s, & \textbf{if } j = i - 1 \textbf{ and } v_i \neq N, v_i \neq T \\
+             & \textbf{or } j = i - N + T \textbf{ and } u_i \geq 2,\,v_i = T \\
+        \\
+        1, & \textbf{if } j = i - 1 \textbf{ and } v_i = N \\
+        \\
+        -1, & \textbf{if } i = j \\
+        \\
+        0, & \textbf{otherwise} \\
+    \end{cases}
+\end{equation}
+
+Equation~(\ref{eq:general_algebaric_approach_blocking_time}) shows this.
 \begin{equation}\label{eq:general_algebaric_approach_blocking_time}
@@
 
-Matrix \(Z\) can be alternatively defined using \(Z_{ij}\) defined in equation 
-(\ref{eq:general_mapping_function_of_blocking_matrix}) where \(i\) and \(j\) 
-represent states \((u_i, v_i), (u_j, v_j) \in S_b\).
-
-\begin{equation}\label{eq:general_mapping_function_of_blocking_matrix}
-    Z_{ij} = 
-    \begin{cases}
-        p_a, & \textbf{if } j = i + 1 \textbf{ and } v_i \neq N \\
-        \\
-        p_s, & \textbf{if } j = i - 1 \textbf{ and } v_i \neq N, v_i \neq T \\
-             & \textbf{or } j = i - N + T \textbf{ and } u_i \geq 2,\,v_i = T \\
-        \\
-        1, & \textbf{if } j = i - 1 \textbf{ and } v_i = N \\
-        \\
-        -1, & \textbf{if } i = j \\
-        \\
-        0, & \textbf{otherwise} \\
-    \end{cases}
-\end{equation}
-
 Additional details on the blocking time formula 

### 2021-05-26 sections/queueing_model/blocking_time/main.tex
Restructure queueing model section
Remove performance measures subsection and change "waiting time",
"blocking time" and "proportion of inds" from subsubsections into
subsections. Also add example subsubsections

--- 2021-05-26 sections/queueing_model/subsections/performance_measures/blocking_time/main.tex
@@
-\subsubsection{Blocking time}
+\subsection{Blocking time}
 
@@
 
+\subsubsection{Example}
 Figure \ref{fig:markov_vs_des_blocking_time_comparison} illustrates a comparison 

### 2021-05-26 sections/queueing_model/main.tex
Restructure queueing model section
Remove performance measures subsection and change "waiting time",
"blocking time" and "proportion of inds" from subsubsections into
subsections. Also add example subsubsections

@@
 
-\input{sections/queueing_model/subsections/performance_measures/main.tex}
+The transition matrix \( Q \) defined in (\ref{eq:markov_transition_rate}) can 
+be used to get the probability vector \( \pi \).
+The vector \( \pi \) is commonly used to study stochastic systems and it's main
+purpose is to keep track of the probability of being at any given state of 
+the system. 
+\(\pi_i\) is the steady state probability of being in state \((u_i, v_i) \in 
+\tilde S\) which is the \(i^{\text{th}}\) state of \(\tilde S\) for some ordering of 
+\(\tilde S\).
+The term \textit{steady state} refers to the instance of the vector \( \pi \) 
+where the probabilities of being at any state become stable over time. 
+Thus, by considering the steady state vector \( \pi \) the relationship between 
+it and \( Q \) is given by:
 
-\input{sections/queueing_model/subsections/example/main.tex}
+\[
+    \frac{d\pi}{dt} = \pi Q = 0
+\]
+
+Using vector \(\pi\) there are numerous performance measures of the model that 
+can be calculated. 
+The following equations utilise \(\pi\) to get performance measures on the 
+average number of people at certain sets of state.
+
+\begin{itemize}
+    \item Average number of people in the system: 
+        \[L = \sum_{i=1}^{|\pi|} \pi_i (u_i + v_i)\]
+    \item Average number of people in the service centre: 
+        \[L_H = \sum_{i=1}^{|\pi|} \pi_i v_i\]
+    \item Average number of people in waiting zone 2:
+        \[L_A = \sum_{i=1}^{|\pi|} \pi_i u_i\] 
+\end{itemize}
+
+Consequently, there are some additional performance measures of interest that
+are not as straightforward to calculate.
+Such performance measures are the mean waiting time in the system (for both 
+type 1 and type 2 individuals), the mean time blocked in waiting zone 2 (only 
+valid for type 2 individuals) and the proportion of individuals that wait in 
+waiting zone 1 within a predefined time target.
+
+\input{sections/queueing_model/waiting_time/main.tex}
+
+\input{sections/queueing_model/blocking_time/main.tex}
+
+\input{sections/queueing_model/proportion_within_target/main.tex}

### 2021-05-26 sections/queueing_model/proportion_within_target/main.tex
Restructure queueing model section
Remove performance measures subsection and change "waiting time",
"blocking time" and "proportion of inds" from subsubsections into
subsections. Also add example subsubsections

\subsection{Proportion of individuals within target}

Another performance measure that is taken into consideration is the proportion 
of individuals whose waiting and service times lie within a specified 
time target \(t\).
Similar to section \ref{sec:waiting_time} three formulas are needed for this 
performance measure.

The proportion of type 1 individuals within a time target:

\begin{equation}\label{eq:proportion_within_target_type_1}
    P(X^{(1)} < t) = \frac{\sum_{(u,v) \in S_A^{(1)}} P(X_{(u,v)}^{(1)} < t) 
    \pi_{u,v} }{\sum_{(u,v) \in S_A^{(1)}} \pi_{u,v}}
\end{equation}

The proportion of type 2 individuals within a time target:

\begin{equation}\label{eq:proportion_within_target_type_2}
    P(X^{(2)} < t) = \frac{\sum_{(u,v) \in S_A^{(2)}} P(X_{(u,v)}^{(2)} < t) 
    \pi_{u,v} }{\sum_{(u,v) \in S_A^{(2)}} \pi_{u,v}}
\end{equation}

The overall proportion individuals within a time target (where \(P_{L'_1}\) and 
\(P_{L'_1}\) are defined in (\ref{eq:proportion_of_accepting_individuals})):

\begin{align}
    P(X < t) &= \frac{\lambda_1 P_{L'_1}}{\lambda_2 P_{L'_2}+\lambda_1 P_{L'_1}} 
    P(X^{(1)} < t) \nonumber \\
    &+ \frac{\lambda_2 P_{L'_2}}{\lambda_2 P_{L'_2} + \lambda_1 
    P_{L'_1}} P(X^{(2)} < t) \label{eq:overall_proportion_within_target}
\end{align}

Here \(P(X_{(u,v)}^{(1)})\) and \(P(X_{(u,v)}^{(2)})\) are defined as the
proportion of individuals within the time target \(t\) when starting from state 
\((u,v)\).
These expression can be calculated by:

\begin{equation}\label{eq:proportion_within_target_type_1_from_state}
    P(X_{(u,v)}^{(1)} < t) = 
    \begin{cases}
        1 - \sum_{i=0}^{v-1} \frac{1}{i!} e^{-\mu t} (\mu t)^i, 
            & \textbf{if } C = 1 \\
            & \textbf{and } v>1 \\
        & \\
        1 - (\mu C)^{v-C} \mu  
            \sum_{k=1}^{\mid \vec{r} \mid} \sum_{l=1}^{r_k}
            \frac{\Psi_{k,l}(-\lambda_k)t^{r_k - l} 
            e^{-\lambda_k t}}{(r_k - l)! (l - 1)!},
            & \textbf{if } C > 1 \\
        \textbf{where } \vec{r}=(v - C, 1) \textbf{ and } 
            \vec{\lambda}=(C \mu, \mu) & \textbf{and } v > C \\
            \hspace{1.15cm} \lambda_0 = 0, r_0 = 1 \\
        & \\
        1 - e^{-\mu t},  & \textbf{if } v \leq C
    \end{cases}
\end{equation}

\begin{equation}\label{eq:proportion_within_target_type_2_from_state}
    P(X_{(u,v)}^{(2)} < t) = 
    \begin{cases}
        1 - \sum_{i=0}^{\min(v,T)-1} \frac{1}{i!} e^{-\mu t} (\mu t)^i,  
            & \textbf{if } C = 1 \\ 
            & \textbf{and } v, T > 1 \\
            & \\
        1 - (\mu C) ^ {\min(v,T) - C} \mu  
            &  \\
        \qquad \times \sum_{k=1}^{\mid \vec{r} \mid} \sum_{l=1}^{r_k} 
        \frac{\Psi_{k,l}(-\lambda_k)t^{r_k - l} 
        e^{-\lambda_k t}}{(r_k - l)! (l - 1)!}, 
            & \textbf{if } C > 1 \\
        \textbf{where } \vec{r}=(\min(v, T) - C, 1) 
            & \textbf{and } v, T  > C\\
        \hspace{1.15cm} \vec{\lambda}=(C \mu, \mu) \\
        \hspace{1.15cm} \lambda_0 = 0, r_0 = 1 \\
            & \\
        1 - e^{-\mu t}, & \textbf{if } v \leq C \\ 
            & \textbf{or } T \leq C \\
    \end{cases}
\end{equation}

The function \(\Psi_{k,l}\) used in equations 
(\ref{eq:proportion_within_target_type_1_from_state}) and 
(\ref{eq:proportion_within_target_type_2_from_state}) is defined as:

\begin{equation}
    \Psi_{k,l}(t) = 
    \begin{cases} 
        \frac{(-1)^{l} (l-1)!}{\lambda_2} \left[\frac{1}{t^l} - \frac{1}
        {(t + \lambda_2)^l}\right] , & k=1 \\
        - \frac{1}{t (t + \lambda_1)^{r_1}}, & k=2
    \end{cases} \nonumber \\
    % & \textbf{and} \quad \qquad \lambda_0 = 0, r_0 = 1
\end{equation}

Refer to appendix \ref{sec:appendix_mean_proportion} for a more in-depth 
explanation of the origins of equations 
(\ref{eq:proportion_within_target_type_1}) - 
(\ref{eq:proportion_within_target_type_2_from_state}).

\subsubsection{Example}
Figures \ref{fig:markov_vs_des_proportion_comparison_1},
\ref{fig:markov_vs_des_proportion_comparison_2} and 
\ref{fig:markov_vs_des_proportion_comparison_overall} show a comparison of the
mean proportion of individuals within target when using Markov chains and 
discrete event simulation.
The simulation was ran 100 times and the recorded proportions at each iteration 
is used to populate the violin plots.

\begin{figure}[H]
    \centering
    \includegraphics[width=.8\textwidth]{imgs/proportion_within_target_comparison/proportion_1.pdf}
    \caption{
        Comparison of proportion within target time for type 1 individuals 
        between values obtained from the Markov chain formulas and values 
        obtained from simulation. 
    }
    \label{fig:markov_vs_des_proportion_comparison_1}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=.8\textwidth]{imgs/proportion_within_target_comparison/proportion_2.pdf}
    \caption{
        Comparison of proportion within target time for type 2 individuals 
        between values obtained from the Markov chain formulas and values 
        obtained from simulation. 
    }
    \label{fig:markov_vs_des_proportion_comparison_2}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=.8\textwidth]{imgs/proportion_within_target_comparison/proportion_overall.pdf}
    \caption{
        Comparison of proportion within target time for both type of 
        individuals between values obtained from the Markov chain formulas 
        and values obtained from simulation. 
    }
    \label{fig:markov_vs_des_proportion_comparison_overall}
\end{figure}

### 2021-05-26 sections/appendix/descrete_event_simulation/main.tex
Write appendix chapter for DES model

@@
 
-% TODO: Include details of DES
+For the purposes of this study, a discrete event simulation (DES) model was
+constructed to support the Markov chain version described in 
+section~\ref{sec:queueing_model}.
+The queueing model was built in python using the Ciw 
+library~\cite{ciwpython}.
+
+The constructed model simulates a queueing system with two waiting spaces and 
+two types of individuals. 
+The expected behaviour of the nodes in Ciw have been modified such that 
+individuals moving from waiting zone 2 into waiting zone 1 may remain blocked 
+if there are more than \(T\) individuals in waiting zone 1.
+
+The same performance measures described in sections 
+\ref{sec:waiting_time}, \ref{sec:blocking_time} and 
+\ref{sec:proportion_within_target} can also be calculated using the DES model.
+The simulation can be ran a number of times to eliminate stochasticity and the
+outcomes of the two methods can be directly comparable.
+
+% TODO: Include the queueing model diagram here?
+% TODO: Include python code here?

### 2021-05-26 sections/queueing_model/blocking_time/main.tex
Write appendix chapter for DES model

--- 2021-05-26 sections/queueing_model/subsections/performance_measures/blocking_time/main.tex
@@
-\subsubsection{Blocking time}
+\subsection{Blocking time}\label{sec:blocking_time}
 
@@
 
+\subsubsection{Example}
 Figure \ref{fig:markov_vs_des_blocking_time_comparison} illustrates a comparison 
 between the formulas that arise from the Markov chain model and the equivalent 
-values of the blocking time extracted from discrete event simulation.
+values of the blocking time extracted from discrete event simulation
+(appendix~\ref{sec:appendix_des}).
 The blocking time is calculated using both methods for a range of values of
@@
     \caption{
-        Comparison of mean blocking time between values obtained from the Markov 
-        chain formulas and values obtained from simulation.
+        Comparison of mean blocking time between values obtained from the 
+        Markov chain formulas and values obtained from simulation.
     }

### 2021-05-26 sections/queueing_model/proportion_within_target/main.tex
Write appendix chapter for DES model

@@
-\subsection{Proportion of individuals within target}
+\subsection{Proportion of individuals within target}\label{sec:proportion_within_target}
 
@@
 mean proportion of individuals within target when using Markov chains and 
-discrete event simulation.
+discrete event simulation (appendix~\ref{sec:appendix_des}).
 The simulation was ran 100 times and the recorded proportions at each iteration 

### 2021-05-26 known.py

@@ -5,6 +5,7 @@ words = {
     "calc",
     "CDF",
     "CDFs",
+    "Ciw",
     "dt",
     "erlang",
     "HB",
@@ -21,5 +22,5 @@ words = {
     "queueing",
     "RHS",
     "th",
-    "Zx"
+    "Zx",
 }

### 2021-05-26 known.py
Edit minor things

@@ -6,6 +6,7 @@ words = {
     "CDF",
     "CDFs",
     "Ciw",
+    "DES",
     "dt",
     "erlang",
     "HB",
@@ -21,6 +22,7 @@ words = {
     "pre",
     "queueing",
     "RHS",
+    "stochasticity",
     "th",
     "Zx",
 }

### 2021-06-02 sections/appendix/blocking_time_formula/main.tex
Section: A queueing model with 2 consecutive buffer centres (#6)
* Add bibliography entry

* Write details of the Markov-chain model

- Define the model
- Define state space
- Define transition matrix and state-mapping function

* Add general Markov-chain picture

* Update known.py

* Add .pdf file to GitHub repo

* Create subsections/ subdirectory

* Minor edits on figures

Reference figure of previous section and change the caption of
the general Markov chain figure

* Add paragraph for transition rates

* Apply minor edits

* Write main.tex for performance measures subsection

* Write main.

@@
         p_a, & \textbf{if } j = i + 1 \textbf{ and } v_i \neq N \\
-        \\
         p_s, & \textbf{if } j = i - 1 \textbf{ and } v_i \neq N, v_i \neq T \\
             & \textbf{or } j = i - N + T \textbf{ and } u_i \geq 2,\,v_i = T \\
-        \\
         1, & \textbf{if } j = i - 1 \textbf{ and } v_i = N \\
-        \\
         -1, & \textbf{if } i = j \\
-        \\
         0, & \textbf{otherwise} \\

### 2021-06-02 sections/appendix/waiting_time_formula/main.tex
Add comparisons between Markov and DES
Include violinplots of waiting time, blocking time and proportion
within target time. The violinplots show the differences between
Markov values and simulated values.
Section: A queueing model with 2 consecutive buffer centres (#6)
* Add bibliography entry

* Write details of the Markov-chain model

- Define the model
- Define state space
- Define transition matrix and state-mapping function

* Add general Markov-chain picture

* Update known.py

* Add .pdf file to GitHub repo

* Create subsections/ subdirectory

* Minor edits on figures

Reference figure

@@
 \section{Mean waiting time}\label{sec:appendix_mean_waiting}
+
+The recursive formula described here is the origin of the closed-form formula 
+described in section~\ref{sec:waiting_time}.
+
+To calculate the mean waiting time one must first identify the set of states 
+\((u, v)\) where a wait will occur. 
+For this particular Markov chain, this points to all states that satisfy 
+\(v > C\) i.e. all states where the number of individuals in the service centre 
+exceed the number of servers. 
+The set of such states is defined as \textit{waiting states} and can be denoted 
+as a subset of all the states, where:
+
+\begin{equation} \label{eq:waiting_states}
+    S_w = \{(u, v) \in S \; | \; v > C \}    
+\end{equation}
+
+Additionally, there are certain states in the model where arrivals cannot occur. 
+A type 1 individual cannot arrive whenever the model is at any state 
+\((u, N)\) 
+for all \(u\) where \(N\) is the system capacity. 
+Equivalently, a type 2 individual cannot arrive in the model when the model is 
+at any state \((M, v)\) for all \(v \geq T\).
+Therefore the set of all such states that an arrival may occur are defined as 
+\textit{accepting states} and are denoted as:
+
+\begin{equation*}
+    S_A^{(1)} = \{(u, v) \in S \; | \; v < N \}
+    \tag{\ref{eq:accepting_states_type_1} revisited}
+\end{equation*}
+
+\begin{equation}
+    S_A^{(2)}=
+    \begin{cases}
+        \{(u, v) \in S \; | \; u < M \} & \textbf{if } T \leq N\\
+        \{(u, v) \in S \; | \; v < N \} & \textbf{otherwise}
+    \end{cases}
+    \tag{\ref{eq:accepting_states_type_2} revisited}
+\end{equation}
+
+Moreover, another element that needs to be considered is the expected waiting time 
+% in each state \( c(u,v) \), otherwise known as sojourn time \cite{Raghunandanan}. 
+In order to do so a variation of the Markov model has to be considered where when 
+the individual arrives at any of the states of the model no more arrivals can 
+occur after that.
+
+Thus, one may acquire the desired time by calculating the inverse of the sum of 
+the out-flow rate of that state. 
+Since arrivals are ignored though the only way to exit the state will only be 
+via a service. 
+In essence this notion can be expressed as:
+
+\begin{equation} \label{eq:sojourn_type_1}
+    c^{(1)}(u,v) = 
+    \begin{cases}
+        0, & \textbf{if } u > 0 \textbf{ and } v = T \\
+        \frac{1}{\text{min}(v,C)\mu}, & \textbf{otherwise}
+    \end{cases}
+\end{equation}
+
+Now just like in the type 1 individuals case the sojourn time is needed. 
+For type 2 individuals whenever individuals are at any row apart from the 
+first one they automatically get a wait time of \(0\) since they are essentially 
+blocked.
+
+\begin{equation} \label{eq:sojourn_type_2}
+    c^{(2)}(u,v) = 
+    \begin{cases}
+        0, & \textbf{if } u > 0 \\
+        \frac{1}{\text{min}(v,C)\mu}, & \textbf{otherwise}
+    \end{cases}
+\end{equation}
+
+Note that whenever any type 1 individual is at a state \((u,v)\) where 
+\(u > 0\) 
+and \(v = T\) (i.e. all states \((1,T), (2,T) \dots, (M,T)\)) the sojourn time is 
+set to \(0\). 
+This is done to capture the trip thorough the Markov chain from the perspective 
+of individuals. 
+Meaning that they will visit all states of the threshold column but only the one 
+in the first row will return a non-zero sojourn time.
+Thus, the expected waiting time of type 1 and type 2 individuals when upon
+arriving at state \( (u,v) \) can be given by the following recursive formulas:
+
+\begin{equation} \label{eq:waiting-time-at-each-state-type-1}
+    w^{(1)}(u,v) = 
+    \begin{cases} 
+        0, \hspace{4.85cm} & \textbf{if } (u,v) \notin S_w \\
+        c^{(1)}(u,v) + w^{(1)}(u-1, v), & \textbf{if } u > 0 \textbf{ and } v = T \\
+        c^{(1)}(u,v) + w^{(1)}(u, v-1), & \textbf{otherwise}
+    \end{cases}
+\end{equation}
+
+\begin{equation} \label{eq:waiting-time-at-each-state-type-2}
+    w^{(2)}(u,v) = 
+    \begin{cases} 
+        0, \hspace{4.85cm} & \textbf{if } (u,v) \notin S_w \\
+        c^{(2)}(u,v) + w^{(2)}(u-1, v), & \textbf{if } u > 0 \textbf{ and } v = T \\
+        c^{(2)}(u,v) + w^{(2)}(u, v-1), & \textbf{otherwise}
+    \end{cases}
+\end{equation}
+
+Finally, the mean waiting time can be calculated by summing over all expected 
+waiting times of accepting states multiplied by the probability of being at that 
+state and dividing by the probability of being in any accepting state.
+
+\begin{equation} \label{eq:recursive-waiting-time-type-1}
+    W^{(1)} = \frac{\sum_{(u,v) \in S_A^{(1)}} w^{(1)}(u,v) 
+    \pi_{(u,v)}}{\sum_{(u,v) \in S_A^{(1)}} \pi_{(u,v)}}
+\end{equation}
+
+\begin{equation}\label{eq:recursive-waiting-time-type-2}
+    W^{(2)} = \frac{\sum_{(u,v) \in S_A^{(2)}} w^{(2)}(u,v) \pi_{(u,v)}}
+    {\sum_{(u,v) \in S_A^{(2)}} \pi_{(u,v)}}
+\end{equation}

### 2021-06-02 sections/queueing_model/blocking_time/main.tex
Section: A queueing model with 2 consecutive buffer centres (#6)
* Add bibliography entry

* Write details of the Markov-chain model

- Define the model
- Define state space
- Define transition matrix and state-mapping function

* Add general Markov-chain picture

* Update known.py

* Add .pdf file to GitHub repo

* Create subsections/ subdirectory

* Minor edits on figures

Reference figure of previous section and change the caption of
the general Markov chain figure

* Add paragraph for transition rates

* Apply minor edits

* Write main.tex for performance measures subsection

* Write main.

@@
         p_a, & \textbf{if } j = i + 1 \textbf{ and } v_i \neq N \\
-        \\
         p_s, & \textbf{if } j = i - 1 \textbf{ and } v_i \neq N, v_i \neq T \\
              & \textbf{or } j = i - N + T \textbf{ and } u_i \geq 2,\,v_i = T \\
-        \\
         1, & \textbf{if } j = i - 1 \textbf{ and } v_i = N \\
-        \\
         -1, & \textbf{if } i = j \\
-        \\
         0, & \textbf{otherwise} \\
@@
 
-\subsubsection{Example}
 Figure \ref{fig:markov_vs_des_blocking_time_comparison} illustrates a comparison 
@@
 The blocking time is calculated using both methods for a range of values of
-\(\lambda_2\)
+\(\lambda_2\).
+The simulation was ran 100 times and the recorded mean blocking time at each 
+iteration is used to populate the violin plots.
 

### 2021-06-02 sections/queueing_model/proportion_within_target/main.tex
Section: A queueing model with 2 consecutive buffer centres (#6)
* Add bibliography entry

* Write details of the Markov-chain model

- Define the model
- Define state space
- Define transition matrix and state-mapping function

* Add general Markov-chain picture

* Update known.py

* Add .pdf file to GitHub repo

* Create subsections/ subdirectory

* Minor edits on figures

Reference figure of previous section and change the caption of
the general Markov chain figure

* Add paragraph for transition rates

* Apply minor edits

* Write main.tex for performance measures subsection

* Write main.

@@
 
-\begin{align}
-    P(X < t) &= \frac{\lambda_1 P_{L'_1}}{\lambda_2 P_{L'_2}+\lambda_1 P_{L'_1}} 
-    P(X^{(1)} < t) \nonumber \\
-    &+ \frac{\lambda_2 P_{L'_2}}{\lambda_2 P_{L'_2} + \lambda_1 
-    P_{L'_1}} P(X^{(2)} < t) \label{eq:overall_proportion_within_target}
-\end{align}
+\begin{equation}\label{eq:overall_proportion_within_target}
+    P(X < t) = \frac{\lambda_1 P_{L'_1}}{\lambda_2 P_{L'_2}+\lambda_1 P_{L'_1}} 
+    P(X^{(1)} < t) + \frac{\lambda_2 P_{L'_2}}{\lambda_2 P_{L'_2} + 
+    \lambda_1 P_{L'_1}} P(X^{(2)} < t) 
+\end{equation}
 
@@
             & \textbf{and } v>1 \\
-        & \\
         1 - (\mu C)^{v-C} \mu  
@@
             & \textbf{if } C > 1 \\
-        \textbf{where } \vec{r}=(v - C, 1) \textbf{ and } 
-            \vec{\lambda}=(C \mu, \mu) & \textbf{and } v > C \\
-            \hspace{1.15cm} \lambda_0 = 0, r_0 = 1 \\
-        & \\
+            & \textbf{and } v > C \\
         1 - e^{-\mu t},  & \textbf{if } v \leq C
@@
 \end{equation}
+
+\noindent
+where \(\vec{r}=(v - C, 1)\), \(\vec{\lambda}=(C \mu, \mu)\) and 
+\(\lambda_0 = 0, r_0\) = 1.
 
@@
             & \textbf{and } v, T > 1 \\
-            & \\
         1 - (\mu C) ^ {\min(v,T) - C} \mu  
-            &  \\
-        \qquad \times \sum_{k=1}^{\mid \vec{r} \mid} \sum_{l=1}^{r_k} 
+        \sum_{k=1}^{\mid \vec{r} \mid} & \textbf{if } C > 1 \\
+        \qquad \times \sum_{l=1}^{r_k}
         \frac{\Psi_{k,l}(-\lambda_k)t^{r_k - l} 
         e^{-\lambda_k t}}{(r_k - l)! (l - 1)!}, 
-            & \textbf{if } C > 1 \\
-        \textbf{where } \vec{r}=(\min(v, T) - C, 1) 
             & \textbf{and } v, T  > C\\
-        \hspace{1.15cm} \vec{\lambda}=(C \mu, \mu) \\
-        \hspace{1.15cm} \lambda_0 = 0, r_0 = 1 \\
-            & \\
         1 - e^{-\mu t}, & \textbf{if } v \leq C \\ 
@@
 \end{equation}
+
+\noindent
+where \(\vec{r}=(\min(v, T) - C, 1)\), \(\vec{\lambda}=(C \mu, \mu)\) and
+\(\lambda_0 = 0, r_0 = 1\).
 
@@
     \end{cases} \nonumber \\
-    % & \textbf{and} \quad \qquad \lambda_0 = 0, r_0 = 1
 \end{equation}
@@
 
-\subsubsection{Example}
 Figures \ref{fig:markov_vs_des_proportion_comparison_1},

### 2021-06-02 imgs/markov_vs_des/waiting_time/main.py

@@ -1,0 +1,145 @@
+import matplotlib.pyplot as plt
+import numpy as np
+import ambulance_game as abg
+
+lambda_2 = 3
+lambda_1 = 4
+mu = 8
+num_of_servers = 1
+threshold = 8
+system_capacity = 10
+buffer_capacity = 10
+seed_num = 0
+warm_up_time = 500
+num_of_trials = 100
+runtime = 100000
+
+
+simulation_results_overall = abg.simulation.get_multiple_runs_results(
+    lambda_2=lambda_2,
+    lambda_1=lambda_1,
+    mu=mu,
+    num_of_servers=num_of_servers,
+    threshold=threshold,
+    system_capacity=system_capacity,
+    buffer_capacity=buffer_capacity,
+    seed_num=seed_num,
+    warm_up_time=warm_up_time,
+    num_of_trials=num_of_trials,
+    runtime=runtime,
+    class_type=None,
+)
+
+simulation_results_type_1 = abg.simulation.get_multiple_runs_results(
+    lambda_2=lambda_2,
+    lambda_1=lambda_1,
+    mu=mu,
+    num_of_servers=num_of_servers,
+    threshold=threshold,
+    system_capacity=system_capacity,
+    buffer_capacity=buffer_capacity,
+    seed_num=seed_num,
+    warm_up_time=warm_up_time,
+    num_of_trials=num_of_trials,
+    runtime=runtime,
+    class_type=0,
+)
+
+simulation_results_type_2 = abg.simulation.get_multiple_runs_results(
+    lambda_2=lambda_2,
+    lambda_1=lambda_1,
+    mu=mu,
+    num_of_servers=num_of_servers,
+    threshold=threshold,
+    system_capacity=system_capacity,
+    buffer_capacity=buffer_capacity,
+    seed_num=seed_num,
+    warm_up_time=warm_up_time,
+    num_of_trials=num_of_trials,
+    runtime=runtime,
+    class_type=1,
+)
+
+waiting_times_simulation_overall = [
+    np.mean(w.waiting_times) for w in simulation_results_overall
+]
+waiting_times_simulation_type_1 = [
+    np.mean(w.waiting_times) for w in simulation_results_type_1
+]
+waiting_times_simulation_type_2 = [
+    np.mean(w.waiting_times) for w in simulation_results_type_2
+]
+
+
+mean_waiting_time_markov_overall = (
+    abg.markov.get_mean_waiting_time_using_markov_state_probabilities(
[…]

### 2021-06-02 imgs/proportion_within_target_comparison/main.py

@@ -1,0 +1,147 @@
+import matplotlib.pyplot as plt
+import numpy as np
+import ambulance_game as abg
+
+lambda_1 = 4
+mu = 3
+num_of_servers = 3
+threshold = 8
+system_capacity = 10
+buffer_capacity = 10
+target = 0.5
+seed_num = None
+warm_up_time = 500
+num_of_trials = 100
+runtime = 10000
+# warm_up_time = 10
+# num_of_trials = 10
+# runtime = 100
+
+all_sim_prop_1 = []
+all_sim_prop_2 = []
+all_sim_prop_overall = []
+
+all_markov_prop_1 = []
+all_markov_prop_2 = []
+all_markov_prop_overall = []
+lambda_2_space = np.linspace(2, 6, 6)
+for lambda_2 in lambda_2_space:
+    # Simulation
+    (
+        sim_prop_overall,
+        sim_prop_1,
+        sim_prop_2,
+    ) = abg.simulation.get_mean_proportion_of_individuals_within_target_for_multiple_runs(
+        lambda_2=lambda_2,
+        lambda_1=lambda_1,
+        mu=mu,
+        num_of_servers=num_of_servers,
+        threshold=threshold,
+        system_capacity=system_capacity,
+        buffer_capacity=buffer_capacity,
+        seed_num=seed_num,
+        num_of_trials=num_of_trials,
+        runtime=runtime,
+        target=target,
+    )
+    all_sim_prop_overall.append(sim_prop_overall)
+    all_sim_prop_1.append(sim_prop_1)
+    all_sim_prop_2.append(sim_prop_2)
+
+    # Markov - type 1
+    markov_prop_1 = (
+        abg.markov.proportion_within_target_using_markov_state_probabilities(
+            lambda_1=lambda_1,
+            lambda_2=lambda_2,
+            mu=mu,
+            num_of_servers=num_of_servers,
+            threshold=threshold,
+            system_capacity=system_capacity,
+            buffer_capacity=buffer_capacity,
+            target=target,
+            class_type=0,
+        )
+    )
+    all_markov_prop_1.append(markov_prop_1)
+
+    # Markov - type 2
+    markov_prop_2 = (
+        abg.markov.proportion_within_target_using_markov_state_probabilities(
+            lambda_1=lambda_1,
+            lambda_2=lambda_2,
+            mu=mu,
+            num_of_servers=num_of_servers,
+            threshold=threshold,
[…]

### 2021-06-02 known.py

@@ -1,9 +1,28 @@
 """ A set of known words and end-of-word patterns for the spellchecker. """
 
 words = {
+    "automata",
+    "calc",
+    "CDF",
+    "CDFs",
+    "Ciw",
+    "DES",
+    "dt",
+    "erlang",
     "HB",
+    "hypoexponential",
     "ieeetr",
+    "ij",
+    "LHS",
+    "Markovian",
+    "math",
+    "memoryless",
     "Michalis",
     "Panayides",
+    "pre",
     "queueing",
+    "RHS",
+    "stochasticity",
+    "th",
+    "Zx",
 }

### 2021-06-08 sections/healthcare_application/main.tex
Add initial draft of Application section

@@
 
+The system defined in section [ ] 
+% TODO: Reference appropriate section
+can be directly applied to a healthcare scenario.
+The two queueing systems can be thought of as two Emergency Departments (ED) and 
+the distributor as the Emergency Medical Services (EMS) that distributes 
+individuals to them.
+These individuals are patients of the corresponding Emergency Department 
+that are sent to.
+
+The parameters of the model described in section [ ]
+% TODO: Reference appropriate section
+can also be mapped into parameters of the ED and the EMS.
+
+\begin{itemize}
+    \item \( \lambda_2 \): The rate of patients that the EMS receives
+    \item \( \lambda_{1_i} \): The arrival rate of other patients to ED \(i\)
+    \item \( \mu_i \): The service rate of patients the ED \(i\)
+    \item \( C_i \): The number of available resources in ED \(i\)  
+    \item \( T_i \): The strategy that ED \(i\) chooses to play
+    \item \( N_i \): The patient capacity of ED \(i\)
+    \item \( M_i \): The parking capacity of ED \(i\)
+    \item \( R \): The time target for both EDs
+    \item \( \alpha \in [0, 1] \) : \textit{Importance} of blocking time and lost 
+    individuals (equation \ref{eq:obj-distributor})
+\end{itemize}
+
+The patients that are distributed by the EMS arrive at the hospital via an 
+ambulance and are then either unloaded at the ED or remain blocked outside in 
+the ambulance.
+Whether or not the ambulance and the patient remain blocked is determined by 
+the threshold that the given ED chooses to play.
+High threshold indicates that the ED accepts patients even if it is relatively 
+full, while low threshold means that the ED blocks ambulances more easily.
+
+The game to be played now is between the two EDs and the EMS. 
+The strategies of the two EDs are the range of thresholds that they can choose
+from and their utilities is the proportion of individuals whose time in the 
+system lie within a predetermined target time.
+The EMS has to decide how to distribute its patients among the two EDs so that 
+the blocking time of ambulances is minimised. 
+Note that the formulated game here assumes that prior to making a choice the 
+EMS knows the strategies that each ED is playing.
+
+% TODO: Add a figure to show the applied game
+
 \subsection{Data Analysis}
+
+This subsection aims to analyse how the gaming framework can affect the 
+performance measures of the queueing systems and how to escape certain 
+inefficient situations.
+To study such effects a new concept is introduced that considers the ratio 
+between the best possible performance measure and the one that is being
+played by the players.
+This new concept is defined as the compartmentalised price of anarchy of the 
+players of the game and is defined as \(PoA_i(P, s)\), where \(i \in [1, 2]\) 
+to distinguish among the two players, \(P\) denotes the performance measure 
+function to be used and \(s\) is the strategy that is being played by player 
+\( i \). 
+The compartmentalised price of anarchy aims to measure inefficiencies in the 
+model.
+For instance the \(PoA\) for the blocking time of player \(i\) is given by:
+
+\begin{equation}\label{eq:poa_compartmentalised}
+    % TODO: Make sure this equation makes sense
+    PoA_{i}(B, s) = \frac{B_i(s)}{\min_{\bar{s} \in S_i} B_i(\bar{s})}
+\end{equation}
+
+% TODO: Remove \newpage from here
+\newpage
+Consider a game with the following parameters:
+
+\begin{multicols}{3}
+    \begin{itemize}        
+        \item \( \lambda_{1_1} \) = 4.5
+        \item \( \mu_1 \) = 2
+        \item \( C_1 \) = 3
+        \item \( T_1 \in [1, N_1] \) 
+        \item \( N_1 \) = 6
+        \item \( M_1 \) = 5
+
+        \columnbreak
+        \item \( \lambda_{1_2} \) = 6
+        \item \( \mu_2 \) = 3
+        \item \( C_2 \) = 2
+        \item \( T_2 \in [1, N_2] \)
+        \item \( N_2 \) = 7
+        \item \( M_2 \) = 4
+
+        \columnbreak
+        \item \( \lambda_2 \) = 10.7
+        \item \( R \) = 2
+        \item \( \alpha \) = 0.9
+    \end{itemize}
+\end{multicols}
+
+Using equation (\ref{eq:poa_compartmentalised}) and asymmetric replicator 
+dynamics (described in section [ ])
+% TODO: reference asymmetric replicator dynamics
+the game can be simulated and show the compartmentalised price of 
+anarchy at every iteration for each ED.
+Figure \ref{fig:ard_original} shows the strategies that are being played and 
+the values of \(PoA_1(B, s)\) and \(PoA_2(B, s)\) for all iterations of the 
+learning algorithm until it reaches an evolutionary stable pair of strategies.
+
+\begin{figure}[H]
+    \includegraphics[width=\textwidth, trim=0 400 0 0]{imgs/asymmetric_rd_and_PoA/asymmetric_original.pdf}
+    \caption{The strategies played when running asymmetric replicator dynamics
+    along with the compartmentalised price of anarchy of the blocking time at
+    each iteration of the learning algorithm}
+    \label{fig:ard_original}
+\end{figure}
+
+It can be observed that the learning algorithm reaches a stable pair of 
+strategies where \(T_1 = 5\) and \(T_2 = 6\). After a number of iterations the
+price of anarchy for both players stabilises and barely increases until the 
+final iteration.
+
+Figure \ref{fig:ard_lambda_2} shows a similar run of the
+algorithm but when the strategies begin to stabilise a huge increase in the
+arrival rate of ambulances occurs (i.e \( \lambda_2 = 10.7 \)).
+
+\begin{figure}[H]
+    \includegraphics[width=\textwidth, trim=0 400 0 0]{imgs/asymmetric_rd_and_PoA/asymmetric_flooding.pdf}
+    \caption{The strategies played when running asymmetric replicator dynamics
+    along with the compartmentalised price of anarchy of the blocking time at
+    each iteration of the learning algorithm. After a number of iterations the 
+    arrival rate of ambulance patients is significantly increased to flood the
+    system completely \( \lambda_2 = 10.7 \).}
+    \label{fig:ard_lambda_2}
+\end{figure}
+
+By increasing \(\lambda_2\) there is no change in the how the players behave
+(\(T_1 = 5, T_2 = 6\)), but the outcome of the system does change. 
+There is a decline in the price of anarchy of the blocking time which at first 
+glance indicates that upon flooding the system it becomes more efficient. 
+This is non-sensical though.
+What it really shows is that the steep increase in \( \lambda_2 \) simply leaves 
+less potential for improvement.
+
+Figure \ref{fig:ard_num_of_servers} shows a run of asymmetric replicator 
+dynamics with a change in the number of servers of both models.
+The number of servers are increased from \(C_1 = 3, C_2 = 2\) to 
+\(C_1 = 4, C_2 = 3\).
+
+\begin{figure}[H]
+    \includegraphics[width=\textwidth, trim=0 400 0 0]{imgs/asymmetric_rd_and_PoA/asymmetric_increase_C.pdf}
+    \caption{
+        The strategies played when running asymmetric replicator dynamics
+        along with the compartmentalised price of anarchy of the blocking time 
+        at each iteration of the learning algorithm. After a number of 
+        iterations the number of servers for both systems are increased by one.
+    }
+    \label{fig:ard_num_of_servers}
+\end{figure}
+
+In this case the both the behaviour as well as the price of anarchy change.
+The players change their strategies from \(T_1 = 5, T_2 = 6\) to 
+\(T_1 = 6, T_2 = 7\) and the \(PoA\) of the blocking time goes down.
+By adding more resources to the models they are able to increase their 
+efficiency.
+Although this is a good way to escape such inefficiencies, it might not always
+be cost efficient.
+
+Figure \ref{fig:ard_penalty} is slightly different than the previous ones.
+Once asymmetric replicator dynamics becomes stable on some inefficient 
+strategies (in terms of the blocking time) the payoff matrices of the two are
+scaled in such a way so that the selected strategy is penalised.
+
+\begin{figure}[H]
+    \includegraphics[width=\textwidth, trim=0 400 0 0]{imgs/asymmetric_rd_and_PoA/asymmetric_penalty.pdf}
+    \caption{
+        The strategies played when running asymmetric replicator dynamics
+        along with the compartmentalised price of anarchy of the blocking time 
+        at each iteration of the learning algorithm. After a number of 
+        iterations the most dominant strategy is being penalised.
+    }
+    \label{fig:ard_penalty}
+\end{figure}
+
+By incentivising the players in such a way the players change their strategies 
+and ambulance patients are accepted in the ED more often.
+Thus the blocking time \(PoA\) for both EDs drops down.

### 2021-06-08 known.py
Update known words

@@ -8,20 +8,24 @@ words = {
     "Ciw",
     "DES",
     "dt",
+    "EDs",
     "erlang",
     "HB",
     "hypoexponential",
     "ieeetr",
     "ij",
+    "incentivising",
     "LHS",
     "Markovian",
     "math",
     "memoryless",
     "Michalis",
     "Panayides",
+    "PoA",
     "pre",
     "queueing",
     "RHS",
+    "sensical",
     "stochasticity",
     "th",
     "Zx",

### 2021-08-13 sections/healthcare_application/main.tex
Add info about asymmetric replicator dynamics

@@
 
-The system defined in section [ ] 
-% TODO: Reference appropriate section
-can be directly applied to a healthcare scenario.
+The system defined in section \ref{sec:model_overview} can be directly applied 
+to a healthcare scenario with two such queueing systems.
 The two queueing systems can be thought of as two Emergency Departments (ED) and 
-the distributor as the Emergency Medical Services (EMS) that distributes 
-individuals to them.
-These individuals are patients of the corresponding Emergency Department 
-that are sent to.
-
-The parameters of the model described in section [ ]
-% TODO: Reference appropriate section
-can also be mapped into parameters of the ED and the EMS.
+the Emergency Medical Services (EMS) as a distributor that distributes 
+patients to them.
+The parameters of the model can also be mapped into parameters of the ED and 
+the EMS.
 
 \begin{itemize}
-    \item \( \lambda_2 \): The rate of patients that the EMS receives
+    \item \( \lambda_2 \): The rate of non-emergency patients that the EMS 
+    receives
     \item \( \lambda_{1_i} \): The arrival rate of other patients to ED \(i\)
-    \item \( \mu_i \): The service rate of patients the ED \(i\)
-    \item \( C_i \): The number of available resources in ED \(i\)  
+    \item \( \mu_i \): The service rate of patients at ED \(i\)
+    \item \( C_i \): The number of available resources (beds) in ED \(i\)  
     \item \( T_i \): The strategy that ED \(i\) chooses to play
-    \item \( N_i \): The patient capacity of ED \(i\)
-    \item \( M_i \): The parking capacity of ED \(i\)
+    \item \( N_i \): The total patient capacity of ED \(i\)
+    \item \( M_i \): The total parking capacity of ED \(i\)
     \item \( R \): The time target for both EDs
-    \item \( \alpha \in [0, 1] \) : \textit{Importance} of blocking time and lost 
-    individuals (equation \ref{eq:obj-distributor})
+    \item \( \alpha \in [0, 1] \) : \textit{Importance} of blocking time and 
+    lost individuals (equation \ref{eq:obj-distributor})
 \end{itemize}
@@
 the blocking time of ambulances is minimised. 
+As defined in \ref{sec:model_overview}, the interaction between the two EDs 
+is a Normal form game that is then used to inform the decision of the EMS.
 Note that the formulated game here assumes that prior to making a choice the 
-EMS knows the strategies that each ED is playing.
-
-% TODO: Add a figure to show the applied game
+EMS knows the strategies that each ED is playing (figure 
+\ref{fig:imperfect-info-game}).
 
@@
 This subsection aims to analyse how the gaming framework can affect the 
-performance measures of the queueing systems and how to escape certain 
-inefficient situations.
+performance measures of the two hospitals and how to avoid certain inefficient 
+situations.
+
+In order to analyse the strategies played by the two EDs, the learning algorithm
+asymmetric replicator dynamics is used.
+% TODO: Cite asymmetric replicator dynamics
+The use of a learning algorithm allows to investigate, not only the outcome of 
+the game, but also how that outcome is reached.
+Consider figure \ref{fig:ard-by-itself}. 
+By running asymmetric replicator dynamics on the system the behaviour that 
+emerges can be observed.
+It can be seen that for these particular set of parameters 
+(\ref{eq:ard-parameters}), the strategies of the two hospitals converge over 
+time. 
+Both hospital 1 (row player) and hospital 2 (column player) seem to be playing 
+the same strategy \(s_10\) which indicates that thresholds \(T_1 = 10\) and 
+\(T_2 = 10\) are played.
+What is more important in this example is how the two hospitals reached these
+decisions which also highlights the importance of using a learning algorithm.
+Hospital 2 is able to reach the decision in a very short time while hospital 1
+takes longer to get there.
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[scale=0.4, trim=120 0 120 0]{imgs/asymmetric_rd/asymmetric_rd.png}
+    \label{fig:ard-by-itself}
+    \caption{Asymmetric replicator dynamics run}
+\end{figure}
+
+\begin{multicols}{3}
+    \begin{itemize} \label{eq:ard-parameters}
+        \item \( \lambda_{1_1} \) = 1
+        \item \( \mu_1 \) = 2
+        \item \( C_1 \) = 2
+        \item \( N_1 \) = 10
+        \item \( M_1 \) = 6
+
+        \columnbreak
+        \item \( \lambda_{1_2} \) = 2
+        \item \( \mu_2 \) = 2.5
+        \item \( C_2 \) = 2
+        \item \( N_2 \) = 10
+        \item \( M_2 \) = 6
+
+        \columnbreak
+        \item \( \lambda_2 \) = 2
+        \item \( R \) = 2
+        \item \( \alpha \) = 0.5
+    \end{itemize}
+\end{multicols}
+
 To study such effects a new concept is introduced that considers the ratio 
-between the best possible performance measure and the one that is being
-played by the players.
+between each hospital's best achievable blocking time and the one that is being
+played.
 This new concept is defined as the compartmentalised price of anarchy of the 
-players of the game and is defined as \(PoA_i(P, s)\), where \(i \in [1, 2]\) 
-to distinguish among the two players, \(P\) denotes the performance measure 
-function to be used and \(s\) is the strategy that is being played by player 
-\( i \). 
+players of the game and is defined as \(PoA_i(\tilde{s})\), where 
+\(i \in [1, 2]\) to distinguish among the two players/hospitals where 
+\(\tilde{s}\) is the strategy that is being played by player \( i \). 
 The compartmentalised price of anarchy aims to measure inefficiencies in the 
 model.
-For instance the \(PoA\) for the blocking time of player \(i\) is given by:
+The \(PoA\) for the blocking time of player \(i\) for strategy \(\tilde{s}\) 
+is given by:
 
 \begin{equation}\label{eq:poa_compartmentalised}
-    % TODO: Make sure this equation makes sense
-    PoA_{i}(B, s) = \frac{B_i(s)}{\min_{\bar{s} \in S_i} B_i(\bar{s})}
+    PoA_{i}(\tilde{s}) = \frac{B_i(\tilde{s})}{\min_{s \in S_i} B_i(s)}
 \end{equation}
 
-% TODO: Remove \newpage from here
-\newpage
 Consider a game with the following parameters:
@@
 Using equation (\ref{eq:poa_compartmentalised}) and asymmetric replicator 
-dynamics (described in section [ ])
-% TODO: reference asymmetric replicator dynamics
-the game can be simulated and show the compartmentalised price of 
-anarchy at every iteration for each ED.
+dynamics the game can be simulated and show the compartmentalised price of 
+anarchy at every iteration for both players.
 Figure \ref{fig:ard_original} shows the strategies that are being played and 
-the values of \(PoA_1(B, s)\) and \(PoA_2(B, s)\) for all iterations of the 
+the values of \(PoA_1(s)\) and \(PoA_2(s)\) for all iterations of the 
 learning algorithm until it reaches an evolutionary stable pair of strategies.

### 2021-08-13 sections/model_overview/main.tex
Add info about asymmetric replicator dynamics

@@
-\section{Overview of game theoretic model}
+\section{Overview of game theoretic model} \label{sec:model_overview}
 
@@
 The second waiting zone is where the individuals, that are sent from the 
-distributor, remain until they are allowed to enter the first waiting zone.
+distributor, stay until they are allowed to enter the first waiting zone.
 The second waiting zone has a capacity of \(M\) and no servers.

### 2021-08-16 sections/healthcare_application/main.tex
Fix figure labels and include some citations

@@
 In order to analyse the strategies played by the two EDs, the learning algorithm
-asymmetric replicator dynamics is used.
-% TODO: Cite asymmetric replicator dynamics
+asymmetric replicator dynamics is used \cite{asymmetricreplicatordynamics}.
 The use of a learning algorithm allows to investigate, not only the outcome of 
@@
 emerges can be observed.
-It can be seen that for these particular set of parameters 
-(\ref{eq:ard-parameters}), the strategies of the two hospitals converge over 
-time. 
+It can be seen that for these particular set of parameters the strategies of 
+the two hospitals converge over time. 
 Both hospital 1 (row player) and hospital 2 (column player) seem to be playing 
@@
 decisions which also highlights the importance of using a learning algorithm.
-Hospital 2 is able to reach the decision in a very short time while hospital 1
-takes longer to get there.
+Hospital 2 is able to reach the decision in a very short amount of time while 
+hospital 1 takes longer and goes through numerous strategies to get there.
 
@@
     \includegraphics[scale=0.4, trim=120 0 120 0]{imgs/asymmetric_rd/asymmetric_rd.png}
+    \caption{Asymmetric replicator dynamics run}
     \label{fig:ard-by-itself}
-    \caption{Asymmetric replicator dynamics run}
 \end{figure}
@@
 \begin{multicols}{3}
-    \begin{itemize} \label{eq:ard-parameters}
+    \begin{itemize}
         \item \( \lambda_{1_1} \) = 1
@@
 
-To study such effects a new concept is introduced that considers the ratio 
-between each hospital's best achievable blocking time and the one that is being
-played.
+To study the efficiency of the strategies being played a new concept is 
+introduced that considers the ratio between each hospital's best achievable 
+blocking time and the one that is being played.
 This new concept is defined as the compartmentalised price of anarchy of the 
@@
 
+\textbf{Base run:}
 Using equation (\ref{eq:poa_compartmentalised}) and asymmetric replicator 
@@
 \begin{figure}[H]
-    \includegraphics[width=\textwidth, trim=0 400 0 0]{imgs/asymmetric_rd_and_PoA/asymmetric_original.pdf}
+    \includegraphics[width=\textwidth]{imgs/asymmetric_rd_and_PoA/asymmetric_original.pdf}
     \caption{The strategies played when running asymmetric replicator dynamics
@@
 
+\textbf{Increasing \(\lambda_2\):}
 Figure \ref{fig:ard_lambda_2} shows a similar run of the
@@
 \begin{figure}[H]
-    \includegraphics[width=\textwidth, trim=0 400 0 0]{imgs/asymmetric_rd_and_PoA/asymmetric_flooding.pdf}
+    \includegraphics[width=\textwidth]{imgs/asymmetric_rd_and_PoA/asymmetric_flooding.pdf}
     \caption{The strategies played when running asymmetric replicator dynamics
@@
 
-By increasing \(\lambda_2\) there is no change in the how the players behave
-(\(T_1 = 5, T_2 = 6\)), but the outcome of the system does change. 
+By increasing \(\lambda_2\) there is no change as to how players behave
+(\(T_1 = 5, T_2 = 6\)), but the efficiency of the system does change. 
 There is a decline in the price of anarchy of the blocking time which at first 
@@
 
+\textbf{Increasing number of servers \( C_1 and C_2 \):}
 Figure \ref{fig:ard_num_of_servers} shows a run of asymmetric replicator 
-dynamics with a change in the number of servers of both models.
+dynamics with a change in the number of servers of the hospitals.
 The number of servers are increased from \(C_1 = 3, C_2 = 2\) to 
@@
 \begin{figure}[H]
-    \includegraphics[width=\textwidth, trim=0 400 0 0]{imgs/asymmetric_rd_and_PoA/asymmetric_increase_C.pdf}
+    \includegraphics[width=\textwidth]{imgs/asymmetric_rd_and_PoA/asymmetric_increase_C.pdf}
     \caption{
@@
 
-In this case the both the behaviour as well as the price of anarchy change.
+In this case, both the behaviour as well as the price of anarchy change.
 The players change their strategies from \(T_1 = 5, T_2 = 6\) to 
@@
 
-Figure \ref{fig:ard_penalty} is slightly different than the previous ones.
-Once asymmetric replicator dynamics becomes stable on some inefficient 
-strategies (in terms of the blocking time) the payoff matrices of the two are
-scaled in such a way so that the selected strategy is penalised.
+\textbf{Incentivising players:}
+From figures \ref{fig:ard_lambda_2} and \ref{fig:ard_num_of_servers} it can be
+seen that we can change some parameters of the model to make it more efficient.
+The approach used on figure \ref{fig:ard_penalty} is slightly different than 
+the previous cases.
+Once the played strategies in asymmetric replicator dynamics strategies 
+converge the payoff matrices of the two are scaled in such a way so that the 
+utilities of the selected strategy is penalised.
 
 \begin{figure}[H]
-    \includegraphics[width=\textwidth, trim=0 400 0 0]{imgs/asymmetric_rd_and_PoA/asymmetric_penalty.pdf}
+    \includegraphics[width=\textwidth]{imgs/asymmetric_rd_and_PoA/asymmetric_penalty.pdf}
     \caption{
@@
 
+Figure \ref{fig:ard_penalty} shows that players start playing strategies 
+\( T_1 = 5\) and \( T_2 = 6 \) and mid-run of the learning algorithm a penalty
+is applied to these strategies on the payoff matrix.
 By incentivising the players in such a way the players change their strategies 
-and ambulance patients are accepted in the ED more often.
-Thus the blocking time \(PoA\) for both EDs drops down.
+to \(T_1 = 6\) and \(T_2 = 7\), and thus ambulance patients are accepted in the 
+ED more often.
+Hence, the \(PoA\) for both EDs is decreased, meaning that the whole system is
+more efficient in terms of the blocking time.

### 2021-08-16 tasks.py
Add proselint check as a task

@@ -4,6 +4,7 @@ import subprocess
 import sys
 
 from invoke import task
+import proselint as plnt
 
 import known
 
@@ -40,5 +41,40 @@ def spellcheck(c):
             print(f"In {path} the following words are not known: ")
             for string in sorted(incorrect_words):
                 print(string)
+            exit_codes.append(1)
+    sys.exit(max(exit_codes))
+
+
+@task
+def proselint(c):
+    """
+    Check the spelling of all .tex files
+    """
+
+    def remove_expected_errors(errors):
+        """
+        Remove errors that were expected from the error list
+        """
+        expected_errors = (
+            "annotations.misc",
+            "leonard.exclamation.30ppm",
+        )
+        updated_errors = []
+        for error in errors:
+            if error[0] not in expected_errors:
+                updated_errors.append(error)
+        return updated_errors
+
+    all_tex_files = list(pathlib.Path().glob("**/*.tex"))
+    exit_codes = [0]
+    for path in all_tex_files:
+        with open(path, "r") as f:
+            text = f.read()
+            errors = plnt.tools.lint(text)
+        errors = remove_expected_errors(errors)
+        if errors:
+            print(f"In {path} the following errors were found: ")
+            for error in errors:
+                print(error)
             exit_codes.append(1)
     sys.exit(max(exit_codes))

### 2021-08-17 sections/appendix/descrete_event_simulation/main.tex
Edit minor things
Apply minor changes from review
Apply changes based on Alex's suggestions

@@
 The expected behaviour of the nodes in Ciw have been modified such that 
-individuals moving from waiting zone 2 into waiting zone 1 may remain blocked 
+individuals moving from waiting zone 2 into waiting zone 1 get blocked 
 if there are more than \(T\) individuals in waiting zone 1.
@@
 outcomes of the two methods can be directly comparable. 
+% TODO Add more documentation (instructions on how to use code)
 
-% TODO: Include the queueing model diagram here?
-% TODO: Include python code here?
+% TODO: Archive simulation python code

### 2021-08-17 sections/appendix/proportion_within_target_formula/main.tex
Minor change
Make changes suggested by proselint
Apply changes based on Alex's suggestions

@@
 distribution of time in the system for all individuals. 
-The complexity of such task lies on the fact that different individuals arrive 
-at different states of the Markov model. 
+The complexity of such task is caused by the fact that different individuals 
+arrive at different states of the Markov model. 
 Consider the case when an arrival occurs when the model is at a specific state.
@@
 
-\begin{figure}[ht]
+\begin{figure}[H]
     \centering
@@
 
-\begin{figure}[h]
+\begin{figure}[H]
     \centering
@@
 (\(C \mu\)). 
-For the special case of \(C=1\) the hypoexponential distribution will not be 
+For the case of \(C=1\) the hypoexponential distribution will not be 
 used as this is equivalent to an erlang distribution.
@@
 bounded.
-First of all, from the range of the double summation in equation 
+First, from the range of the double summation in equation 
 (\ref{eq:general_cdf_hypoexponential}), it can be seen that 
@@
     \end{equation*}
-    In essence, it only remains to show that:
+    In essence, it is only needed to show that:
     \[-\frac{\partial^{l-1}}{\partial t^{l-1}} 

### 2021-08-17 sections/queueing_model/main.tex
Write appendix chapter for DES model
Apply changes based on Alex's suggestions

@@
-\section{A queueing model with 2 consecutive buffer centres}
-
+\section{A queueing model with 2 consecutive buffer centres}\label{sec:queueing_model}
 % TODO: If this is to be one paper maybe the first two paragraphs do not need to
@@
 pre-determined threshold \(T\).
-When the number of individuals is equal to or exceeds this threshold, all second type individuals that arrive will remain 
+When the number of individuals is equal to or exceeds this threshold, all 
+second type individuals that arrive will stay 
 \textit{``blocked''} in waiting zone 1 until the number of people in the 

### 2021-08-17 sections/queueing_model/proportion_within_target/main.tex
Include alex check as a task

@@
 Another performance measure that is taken into consideration is the proportion 
-of individuals whose waiting and service times lie within a specified 
+of individuals whose waiting and service times are within a specified 
 time target \(t\).
@@
 
-The proportion of type 2 individuals within a time target:
+The proportion of type 2 individuals within a time target remains as:
 

### 2021-08-17 tasks.py

@@ -11,7 +11,9 @@ import known
 
 @task
 def compile(c):
-    """Compile the LaTeX document."""
+    """
+    Compile the LaTeX document.
+    """
 
     c.run(f"latexmk -xelatex main.tex")
 
@@ -78,3 +80,13 @@ def proselint(c):
                 print(error)
             exit_codes.append(1)
     sys.exit(max(exit_codes))
+
+
+@task
+def alex(c):
+    """
+    Check for inconsiderate and insensitive writing of all .tex files
+    """
+    all_tex_files = list(pathlib.Path().glob("**/*.tex"))
+    for file in all_tex_files:
+        c.run(f"alex {file}")

### 2021-08-18 sections/appendix/blocking_time_formula/main.tex
Add extra checks (#12)
* Update environment to include proselint

* Add proselint check as a task

* Update CI to run proselint check

* Make changes suggested by proselint

* Fix typo in ci.yml

* Add alex to github actions checks

* Apply changes based on Alex's suggestions

* Include alex check as a task

* Apply alex's suggestion

@@
 Whenever a type 2 individual is blocked and a type 1 individual arrives the type
-2 individuals will remain blocked for some additional amount of time.
+2 individuals will stay blocked for some additional amount of time.
 Thus, the mean time that a type 2 individual spends at each state is given by:
@@
 Thus, having calculated the mean blocking time for all blocking states 
-\(b(u,v)\), it only remains to put them together in a formula.
+\(b(u,v)\), they can be combined together in a formula.
 The resultant formula for the mean blocking time is given by:

### 2021-08-18 tasks.py

@@ -4,13 +4,16 @@ import subprocess
 import sys
 
 from invoke import task
+import proselint as plnt
 
 import known
 
 
 @task
 def compile(c):
-    """Compile the LaTeX document."""
+    """
+    Compile the LaTeX document.
+    """
 
     c.run(f"latexmk -xelatex main.tex")
 
@@ -42,3 +45,48 @@ def spellcheck(c):
                 print(string)
             exit_codes.append(1)
     sys.exit(max(exit_codes))
+
+
+@task
+def proselint(c):
+    """
+    Check the spelling of all .tex files
+    """
+
+    def remove_expected_errors(errors):
+        """
+        Remove errors that were expected from the error list
+        """
+        expected_errors = (
+            "annotations.misc",
+            "leonard.exclamation.30ppm",
+        )
+        updated_errors = []
+        for error in errors:
+            if error[0] not in expected_errors:
+                updated_errors.append(error)
+        return updated_errors
+
+    all_tex_files = list(pathlib.Path().glob("**/*.tex"))
+    exit_codes = [0]
+    for path in all_tex_files:
+        with open(path, "r") as f:
+            text = f.read()
+            errors = plnt.tools.lint(text)
+        errors = remove_expected_errors(errors)
+        if errors:
+            print(f"In {path} the following errors were found: ")
+            for error in errors:
+                print(error)
+            exit_codes.append(1)
+    sys.exit(max(exit_codes))
+
+
+@task
+def alex(c):
+    """
+    Check for inconsiderate and insensitive writing of all .tex files
+    """
+    all_tex_files = list(pathlib.Path().glob("**/*.tex"))
+    for file in all_tex_files:
+        c.run(f"alex {file}")

### 2021-08-18 sections/healthcare_application/main.tex
Apply changes based on alex and proselint

@@
 The patients that are distributed by the EMS arrive at the hospital via an 
-ambulance and are then either unloaded at the ED or remain blocked outside in 
+ambulance and are then either unloaded at the ED or stay blocked outside in 
 the ambulance.
-Whether or not the ambulance and the patient remain blocked is determined by 
+Whether or not the ambulance and the patient stay blocked is determined by 
 the threshold that the given ED chooses to play.
 High threshold indicates that the ED accepts patients even if it is relatively 
-full, while low threshold means that the ED blocks ambulances more easily.
+full, while low threshold means that the ED blocks ambulances more frequently.
 
@@
 from and their utilities is the proportion of individuals whose time in the 
-system lie within a predetermined target time.
+system is within a predetermined target time.
 The EMS has to decide how to distribute its patients among the two EDs so that 
@@
 decisions which also highlights the importance of using a learning algorithm.
-Hospital 2 is able to reach the decision in a very short amount of time while 
+Hospital 2 is able to reach the decision in a short amount of time while 
 hospital 1 takes longer and goes through numerous strategies to get there.
@@
 This is non-sensical though.
-What it really shows is that the steep increase in \( \lambda_2 \) simply leaves 
+What it really shows is that the steep increase in \( \lambda_2 \) leaves 
 less potential for improvement.

### 2021-09-02 sections/appendix/descrete_event_simulation/simulation.py
Add script for simulation performance measures

@@ -1,0 +1,30 @@
+import numpy as np
+import ambulance_game as abg
+
+lambda_1 = 2
+lambda_2 = 3
+mu = 1
+num_of_servers = 6
+threshold = 10
+system_capacity = 20
+buffer_capacity = 10
+target = 1
+
+Simulation = abg.simulation.simulate_model(
+    lambda_2=lambda_2,
+    lambda_1=lambda_1,
+    mu=mu,
+    num_of_servers=num_of_servers,
+    threshold=threshold,
+    system_capacity=system_capacity,
+    buffer_capacity=buffer_capacity,
+    seed_num=0,
+    runtime=2000,
+)
+
+mean_wait = np.mean([w.waiting_time for w in Simulation.get_all_records()])
+mean_block = np.mean([b.time_blocked for b in Simulation.get_all_records()])
+mean_service = np.mean([s.service_time for s in Simulation.get_all_records()])
+proportion_within_target = np.mean(
+    [1 if w.waiting_time <= target else 0 for w in Simulation.get_all_records()]
+)

### 2021-09-02 sections/appendix/descrete_event_simulation/multiple_runs.py
Add scripts for multiple runs

@@ -1,0 +1,23 @@
+import numpy as np
+import ambulance_game as abg
+
+all_simulations = abg.simulation.get_multiple_runs_results(
+    lambda_1=3,
+    lambda_2=2,
+    mu=1,
+    num_of_servers=6,
+    threshold=10,
+    system_capacity=20,
+    buffer_capacity=10,
+    seed_num=0,
+    runtime=2000,
+    num_of_trials=10,
+)
+
+all_waits = [np.mean(w.waiting_times) for w in all_simulations]
+all_services = [np.mean(s.service_times) for s in mult_results]
+all_blocks = [np.mean(b.blocking_times) for b in mult_results]
+
+mean_wait = np.mean(all_waits)
+mean_service = np.mean(all_services)
+mean_block = np.mean(all_blocks)

### 2021-09-02 sections/appendix/descrete_event_simulation/multiple_runs_proportion.py

@@ -1,0 +1,20 @@
+import numpy as np
+import ambulance_game as abg
+
+(
+    overall_proportion,
+    class_1_proportion,
+    class_2_proportion,
+) = abg.simulation.get_mean_proportion_of_individuals_within_target_for_multiple_runs(
+    lambda_1=3,
+    lambda_2=2,
+    mu=1,
+    num_of_servers=6,
+    threshold=10,
+    system_capacity=20,
+    buffer_capacity=10,
+    seed_num=0,
+    runtime=2000,
+    num_of_trials=10,
+    target=1,
+)

### 2021-09-02 sections/appendix/descrete_event_simulation/simulation.py

@@ -1,30 +1,25 @@
 import numpy as np
 import ambulance_game as abg
 
-lambda_1 = 2
-lambda_2 = 3
-mu = 1
-num_of_servers = 6
-threshold = 10
-system_capacity = 20
-buffer_capacity = 10
-target = 1
-
 Simulation = abg.simulation.simulate_model(
-    lambda_2=lambda_2,
-    lambda_1=lambda_1,
-    mu=mu,
-    num_of_servers=num_of_servers,
-    threshold=threshold,
-    system_capacity=system_capacity,
-    buffer_capacity=buffer_capacity,
+    lambda_1=3,
+    lambda_2=2,
+    mu=1,
+    num_of_servers=6,
+    threshold=10,
+    system_capacity=20,
+    buffer_capacity=10,
     seed_num=0,
     runtime=2000,
 )
 
 mean_wait = np.mean([w.waiting_time for w in Simulation.get_all_records()])
+
 mean_block = np.mean([b.time_blocked for b in Simulation.get_all_records()])
+
 mean_service = np.mean([s.service_time for s in Simulation.get_all_records()])
+
+target = 1
 proportion_within_target = np.mean(
     [1 if w.waiting_time <= target else 0 for w in Simulation.get_all_records()]
 )

### 2021-09-02 sections/appendix/descrete_event_simulation/main.tex
Write more documentation around the code

@@
 outcomes of the two methods can be directly comparable.
-% TODO Add more documentation (instructions on how to use code)
+
+This discrete event simulation model was built in python and can be installed by 
+running the following command in the terminal:
+\begin{lstlisting}[language=bash, style=terminalstyle]
+    $ pip install ambulance_game
+\end{lstlisting}
+
+Having installed the package, the following script can be used to simulate, and 
+get all required performance measures, of a queueing system with two waiting 
+spaces and two types of individuals for a runtime of 2000 unit time with the 
+following parameters:
+
+\begin{multicols}{2}
+    \begin{itemize}
+        \centering
+        \item \( \lambda_1 = 2 \)
+        \item \( \lambda_2 = 3 \)
+        \item \( \mu = 1 \)
+        \item \( C = 6 \)
+        \columnbreak
+        \item \( T = 10 \)
+        \item \( N = 20 \)
+        \item \( M = 10 \)
+        \item \( R = 1 \)
+    \end{itemize}
+\end{multicols}
+
+\lstinputlisting[language=Python, style=pystyle]{sections/appendix/descrete_event_simulation/simulation.py}
+
+The script above shows the outcome of the DES model for a single run.
+To minimise the stochasticity of the simulation, the model can be simulated for 
+numerous trials. 
+The following script can be used to run the simulation for a number of times 
+and get the mean of the waiting, service and blocking times:
+
+\lstinputlisting[language=Python, style=pystyle]{sections/appendix/descrete_event_simulation/multiple_runs.py}
+
+Finally, the proportion of individuals within target for multiple runs can be
+calculated by running the following block of code:
+
+\lstinputlisting[language=Python, style=pystyle]{sections/appendix/descrete_event_simulation/multiple_runs_proportion.py}
 

### 2021-09-06 sections/appendix/descrete_event_simulation/main.tex
Include code Tutorial
Modify appendix based on Diataxis framework (Tutorial-Howto-Reference-
Explanation). This commit adds the initial draft of the Tutorial part.

--- 2021-08-17 sections/appendix/descrete_event_simulation/main.tex
@@
 outcomes of the two methods can be directly comparable.
-% TODO Add more documentation (instructions on how to use code)
+
+\subsection{Tutorial: building the DES model}
+
+The DES model is constructed in a generic way that so that it can be used for
+any queueing system with two waiting spaces and two types of individuals.
+For instance, consider a queueing system with the following parameters, as 
+described in section~\ref{sec:queueing_model}:
+
+\begin{multicols}{4}
+    \begin{itemize}
+        \item \( \lambda_1 = 2 \)
+        \item \( \lambda_2 = 3 \)
+        \columnbreak
+        \item \( \mu = 1 \)
+        \item \( C = 6 \)
+        \columnbreak
+        \item \( T = 10 \)
+        \item \( N = 20 \)
+        \columnbreak
+        \item \( M = 10 \)
+    \end{itemize}
+\end{multicols}
+
+\begin{figure}[h]
+    \centering
+    \begin{tikzpicture}[>=stealth, scale=0.8],
+        % the rectangle of parking queue
+        \draw (0,0) -- ++(3cm,0) -- ++(0,-1.5cm) -- ++(-3cm,0);
+        % the vertical lines of parking queue
+        \foreach \i in {1,...,4, 7.1}
+            \draw (3cm-\i*12pt,0) -- +(0,-1.5cm);
+
+        % The label above Queue 1 -> M
+        \node[anchor=north] at (1.5cm, 1cm) {\( 
+            \overbrace{\qquad \qquad \qquad \qquad}^{10} 
+        \)};
+
+        % the rectangle in Queue 2
+        \draw (5,1.25) -- ++(2cm,0) -- ++(0,-1.5cm) -- ++(-2cm,0);
+        % the vertical lines in Queue 2
+        \foreach \i in {1,...,4, 5.7}
+            \draw (7cm-\i*10pt,1.25) -- +(0,-1.5cm);
+        % The two vertical lines at the very start of Queue 2 
+        \draw (7cm-54pt,1.2) -- +(0,-0.5cm);
+        \draw (7cm-54pt,0.3) -- +(0,-0.5cm);        
+        \draw (7cm-51pt,1.1) -- +(0,-0.4cm);
+        \draw (7cm-51pt,0.3) -- +(0,-0.4cm);
+
+        % The label between the lines for T
+        \node[anchor=north] at (5.19, 0.78 cm) {\small{\( 10 \)}};
+
+        % The label above Queue 2 -> N
+        \node[anchor=north] at (6.6cm, 2.2cm) {\(
+            \overbrace{\qquad \qquad \qquad \qquad}^{20}
+        \)};
+
+        % the circle in Queue 2
+        \draw (7.75,0.5) circle [radius=0.75cm] node {\(6\)};
+
+        % Arrow line from Queue 2 outside
+        \draw[->] (8.5,0.525) -- +(20pt,0);
+
+        % Line from lambda_2 to Queue 1
+        \draw[<-] (-0.3,-0.75) -- +(-40pt,0) node[left] {\( 3 \)};
+
+        % Lines after Parking queue
+        \draw[-] (3,-0.75) -- +(34pt,0);
+        \draw (4.2, 0.525) -- (4.2, -0.75);
+
+        % Lines for lambda_1 arrivals
+        \draw (4.2, 1.8) -- +(-169.5pt,0) node[left] {\( 2 \)};
+        \draw (4.2, 1.8) -- (4.2, 0.525);
+
+        % Line from both individuals to Queue 2
+        \draw[->] (4.2, 0.525) -- (4.8, 0.525);  
+    \end{tikzpicture}
+    \caption{A diagrammatic representation of the queueing model example}
+    \label{fig:diagram_of_queueing_system_appendix_example}
+\end{figure}
+
+This model will be studied by using  
+\lstinline[style=pystyle]{ambulance_game}.
+Install the created library in your python environment, by running the 
+following command in the command line:
+\begin{lstlisting}[language=bash, style=terminalstyle]
+    $ pip install ambulance_game
+\end{lstlisting}
+
+Having installed the package, the following code can be used to simulate the 
+queueing system defined earlier and get all the data records for a single run.
+
+\begin{lstlisting}[style=pystyle]
+
+    >>> import ambulance_game as abg
+    >>> Simulation = abg.simulation.simulate_model(
+    ...     lambda_1=3,
+    ...     lambda_2=2,
+    ...     mu=1,
+    ...     num_of_servers=6,
+    ...     threshold=10,
+    ...     system_capacity=20,
+    ...     buffer_capacity=10,
+    ... )
+    >>> all_records = Simulation.get_all_records()
+    >>> all_records[3]
+    Record(id_number=1, customer_class=0, node=2, arrival_date=0.4728763843239206, waiting_time=0.0, service_start_date=0.4728763843239206, service_time=0.5457131455415929, service_end_date=1.0185895298655134, time_blocked=0.0, exit_date=1.0185895298655134, destination=-1, queue_size_at_arrival=0, queue_size_at_departure=4)
+\end{lstlisting}
+
+The above block code outputs the fourth individual record from the simulation
+object.
+The simulation object can be used to view the every event that occurred in the 
+simulation 
+The data records can then be used to get overall performance measures about the
+constructed queueing model.
+The overall waiting time that individuals wait in waiting zone 1 can be acquired 
+by running:
+
+\begin{lstlisting}[style=pystyle]
+    >>> import numpy as np
+    >>> mean_wait = np.mean(
+    ...    [record.waiting_time for record in all_records if record.node == 2]
+    ... )
+    0.2246928220731305
+\end{lstlisting}
+
+This value is the average waiting time of all the customers in the system for a
+single run. 
+By nature, discrete event simulation can output different results for different
+runs of the same set of parameters.
+This stochasticity can be reduced by running the simulation multiple times 
+and then getting the mean waiting time from all the runs.
+
+\begin{lstlisting}[style=pystyle]
+    >>> all_simulations = abg.simulation.get_multiple_runs_results(
+    ...     lambda_1=3,
+    ...     lambda_2=2,
+    ...     mu=1,
+    ...     num_of_servers=6,
+    ...     threshold=10,
+    ...     system_capacity=20,
+    ...     buffer_capacity=10,
+    ...     seed_num=0,
+    ...     num_of_trials=10,
+    ... )
+    >>> mean_wait = np.mean(
+    ...     [np.mean(w.waiting_times) for w in all_simulations]
+    ... )
+    0.35037759808989827
+\end{lstlisting}
+
+\subsection{How-to guide}
+
+\subsection{Reference}
+
+\subsection{Explanation}
 

### 2021-09-10 sections/healthcare_application/main.tex
Apply suggestions from code review
Co-authored-by: Vince Knight <vincent.knight@gmail.com>

@@
 
-The system defined in section \ref{sec:model_overview} can be directly applied 
+The system defined in section \ref{sec:model_overview} can be applied 
 to a healthcare scenario with two such queueing systems.
@@
 patients to them.
-The parameters of the model can also be mapped into parameters of the ED and 
-the EMS.
+The parameters of the model correspond to the following parameters of the ED and 
+the EMS:
 
@@
     receives
-    \item \( \lambda_{1_i} \): The arrival rate of other patients to ED \(i\)
-    \item \( \mu_i \): The service rate of patients at ED \(i\)
-    \item \( C_i \): The number of available resources (beds) in ED \(i\)  
-    \item \( T_i \): The strategy that ED \(i\) chooses to play
-    \item \( N_i \): The total patient capacity of ED \(i\)
-    \item \( M_i \): The total parking capacity of ED \(i\)
+    \item \( \lambda_{1_i} \): The arrival rate of other patients to ED \(i\in\{1, 2\}\)
+    \item \( \mu_i \): The service rate of patients at ED \(i\in\{1, 2\}\)
+    \item \( C_i \): The number of available resources (beds) in ED \(i\in\{1, 2\}\)  
+    \item \( T_i \): The action that ED \(i\in\{1, 2\\) chooses to play which corresponds to the threshold at which they do not accept EMS patients.
+    \item \( N_i \): The total patient capacity of ED \(i\in\{1, 2\\)
+    \item \( M_i \): The total parking capacity of ED \(i\in\{1, 2\\)
     \item \( R \): The time target for both EDs
-    \item \( \alpha \in [0, 1] \) : \textit{Importance} of blocking time and 
+    \item \( \alpha \in [0, 1] \) : \textit{Weighting} of blocking time and 
     lost individuals (equation \ref{eq:obj-distributor})
@@
 
-The game to be played now is between the two EDs and the EMS. 
 The strategies of the two EDs are the range of thresholds that they can choose
@@
 EMS knows the strategies that each ED is playing (figure 
-\ref{fig:imperfect-info-game}).
+\ref{fig:imperfect-info-game}). This corresponds to reacting to experienced delays.
 
-\subsection{Data Analysis}
+\subsection{Numerical Results}
 
@@
 emerges can be observed.
-It can be seen that for these particular set of parameters the strategies of 
+It can be seen that for this particular set of parameters the strategies of 
 the two hospitals converge over time. 
@@
 players of the game and is defined as \(PoA_i(\tilde{s})\), where 
-\(i \in [1, 2]\) to distinguish among the two players/hospitals where 
+\(i \in \{1, 2\}\) to distinguish among the two players/hospitals where 
 \(\tilde{s}\) is the strategy that is being played by player \( i \). 
@@
 
-\textbf{Base run:}
+\textbf{Initial scenario:}
 Using equation (\ref{eq:poa_compartmentalised}) and asymmetric replicator 
-dynamics the game can be simulated and show the compartmentalised price of 
+dynamics the emergent behaviour can be measured and the compartmentalised price of 
 anarchy at every iteration for both players.
@@
 
-It can be observed that the learning algorithm reaches a stable pair of 
+The learning algorithm reaches a stable pair of 
 strategies where \(T_1 = 5\) and \(T_2 = 6\). After a number of iterations the
@@
 Figure \ref{fig:ard_lambda_2} shows a similar run of the
-algorithm but when the strategies begin to stabilise a huge increase in the
+algorithm but when the strategies begin to stabilise an increase in the
 arrival rate of ambulances occurs (i.e \( \lambda_2 = 10.7 \)).
@@
 What it really shows is that the steep increase in \( \lambda_2 \) leaves 
-less potential for improvement.
+the system unable to cope regardless of the decisions made.
 
@@
 converge the payoff matrices of the two are scaled in such a way so that the 
-utilities of the selected strategy is penalised.
+utilities of the selected strategy are penalised. This corresponds to a precise
+policy change where more societally beneficial behaviours are incentivised.
 

### 2021-09-10 sections/appendix/descrete_event_simulation/main.tex
Add first draft of how-to guide

@@
 following command in the command line:
-\begin{lstlisting}[language=bash, style=terminalstyle]
+\begin{lstlisting}[style=terminalstyle]
     $ pip install ambulance_game
@@
 
+The package can be installed by either running:
+
+\begin{lstlisting}[style=terminalstyle]
+    $ pip install ambulance_game
+\end{lstlisting}
+
+in the command line or via the instructions provided in the GitHub repository.
+% TODO: Cite repository
+The required arguments that need to be passed to the simulate\_model() function
+are the following:
+\begin{itemize}
+    \item lambda\_1 (\(\lambda_1\)): The arrival rate of class 1 individuals.
+    \item lambda\_2 (\(\lambda_2\)): The arrival rate of class 2 individuals.
+    \item mu (\(\mu\)): The service rate of the servers.
+    \item num\_of\_servers (\(C\)): The number of servers in the system.
+    \item threshold (\(T\)): The threshold that indicates when to start blocking 
+    class 2 individuals.
+\end{itemize}
+
+For every service completion Ciw stores all data records in a simulation 
+object~\cite{ciwpython}.
+The records that are stored are the following:
+
+% TODO: Maybe move this to reference 
+\begin{multicols}{2}
+    \begin{itemize}
+        \item \textbf{id\_number} \(\in R\).
+        \item \textbf{customer\_class} \(= 0\)
+        \item \textbf{node} \(= \{0, 1, 2, -1 \} \)
+        \item \textbf{arrival\_date} \( \in R^+ \)
+        \item \textbf{waiting\_time} \( \in R^+ \)
+        \item \textbf{service\_start\_date} \( \in R^+ \)
+        \item \textbf{service\_time} \( \in R^+ \)
+        \item \textbf{service\_end\_time} \( \in R^+ \)
+        \item \textbf{time\_blocked} \( \in R^+ \)
+        \item \textbf{exit\_date} \( \in R^+ \)
+        \item \textbf{destination} \( = \{1, 2, -1\} \)
+        \item \textbf{queue\_size\_at\_arrival} \( \in N \)
+        \item \textbf{queue\_size\_at\_departure} \( \in N \)
+    \end{itemize}
+\end{multicols}
+
+To get the simulation object with all the data records, the following code can be
+used:
+\begin{lstlisting}[style=pystyle]
+    >>> import ambulance_game as abg
+    >>> Simulation = abg.simulation.simulate_model(
+    ...     lambda_1=3,
+    ...     lambda_2=2,
+    ...     mu=1,
+    ...     num_of_servers=6,
+    ...     threshold=10,
+    ... )
+    >>> Simulation.get_all_records()[1]
+    Record(id_number=1, customer_class=0, node=2, arrival_date=0.5391449803891563, waiting_time=0.0, service_start_date=0.5391449803891563, service_time=0.17003700443114755, service_end_date=0.7091819848203038, time_blocked=0.0, exit_date=0.7091819848203038, destination=-1, queue_size_at_arrival=0, queue_size_at_departure=0)
+\end{lstlisting}
+
+Additional arguments that can be passed to the function are:
+\begin{itemize}
+    \item \textit{system\_capacity}: The maximum number of individuals in 
+    waiting zone 2.
+    \item \textit{buffer\_capacity}: The maximum number of individuals in 
+    waiting zone 1.
+    \item \textit{seed\_num}: The seed number for the random number generator.
+    \item \textit{runtime}: How long to run the simulation for.
+\end{itemize}
+
+From a single run of the simulation the data records can be used the get the
+average for certain performance measures. 
+The following code can be used to get the mean waiting time, blocking time, 
+service time and the proportion of individuals within target.
+
+\begin{lstlisting}[style=pystyle]
+    >>> records = Simulation.get_all_records()
+    >>> mean_wait = np.mean(
+    ...     [w.waiting_time for w in records]
+    ... )
+    >>> mean_block = np.mean(
+    ...     [b.time_blocked for b in records]
+    ... )
+    >>> mean_service = np.mean(
+    ...     [s.service_time for s in records]
+    ... )
+    >>> target = 1
+    >>> proportion_within_target = np.mean(
+    ...     [w.waiting_time <= target for w in records]
+    ... )
+
+\end{lstlisting}
+
+To eliminate any stochasticity in the simulation, the simulation can be run
+numerous times and get the avergae performance measures out of all the runs.
+
+\begin{lstlisting}[style=pystyle]
+    >>> import numpy as np
+    >>> import ambulance_game as abg
+    >>> all_simulations = abg.simulation.get_multiple_runs_results(
+    ...     lambda_1=3,
+    ...     lambda_2=2,
+    ...     mu=1,
+    ...     num_of_servers=6,
+    ...     threshold=10,
+    ...     system_capacity=20,
+    ...     buffer_capacity=10,
+    ...     seed_num=0,
+    ...     runtime=2000,
+    ...     num_of_trials=10,
+    ... )
+    >>> mean_wait = np.mean([
+    ...     np.mean(w.waiting_times) for w in mean_simulations
+    ... ])
+    >>> mean_service = np.mean([
+    ...     np.mean(s.service_times) for s in mult_results
+    ... ])
+    >>> mean_block = np.mean([
+    ...     np.mean(b.blocking_times) for b in mult_results
+    ... ])
+\end{lstlisting}
+
+% TODO: Fix code for proportion of individuals within time target
+
+% Run multiple simulation results
+% Show all possible arguments
+% Get all performance measures
+
 \subsection{Reference}
 
-\subsection{Explanation}
+% This discrete event simulation model was built in python and can be installed by 
+% running the following command in the terminal:
+
+% Having installed the package, the following script can be used to simulate, and 
+% get all required performance measures, of a queueing system with two waiting 
+% spaces and two types of individuals for a runtime of 2000 unit time with the 
+% following parameters:
+
+% \lstinputlisting[language=Python, style=pystyle]{sections/appendix/descrete_event_simulation/simulation.py}
+
+% The script above shows the outcome of the DES model for a single run.
+% To minimise the stochasticity of the simulation, the model can be simulated for 
+% numerous trials. 
+% The following script can be used to run the simulation for a number of times 
+% and get the mean of the waiting, service and blocking times:
+
+% \lstinputlisting[language=Python, style=pystyle]{sections/appendix/descrete_event_simulation/multiple_runs.py}
+
+% Finally, the proportion of individuals within target for multiple runs can be
+% calculated by running the following block of code:
+
+% \lstinputlisting[language=Python, style=pystyle]{sections/appendix/descrete_event_simulation/multiple_runs_proportion.py}
 

### 2021-09-10 sections/healthcare_application/main.tex
Apply minor changes

@@
     \item \( C_i \): The number of available resources (beds) in ED \(i\in\{1, 2\}\)  
-    \item \( T_i \): The action that ED \(i\in\{1, 2\\) chooses to play which corresponds to the threshold at which they do not accept EMS patients.
-    \item \( N_i \): The total patient capacity of ED \(i\in\{1, 2\\)
-    \item \( M_i \): The total parking capacity of ED \(i\in\{1, 2\\)
+    \item \( T_i \): The action that ED \(i\in\{1, 2\} \) chooses to play which 
+    corresponds to the threshold at which they do not accept EMS patients.
+    \item \( N_i \): The total patient capacity of ED \(i\in\{1, 2\} \)
+    \item \( M_i \): The total parking capacity of ED \(i\in\{1, 2\} \)
     \item \( R \): The time target for both EDs
@@
 There is a decline in the price of anarchy of the blocking time which at first 
-glance indicates that upon flooding the system it becomes more efficient. 
+glance indicates that upon flooding the system it becomes the loss in efficiency
+due to rational individual behaviour decreases. 
 This is non-sensical though.

### 2021-09-10 known.py
Update known words for spellchecker

@@ -14,6 +14,7 @@ words = {
     "hypoexponential",
     "ieeetr",
     "ij",
+    "incentivised",
     "incentivising",
     "LHS",
     "Markovian",
@@ -26,6 +27,7 @@ words = {
     "queueing",
     "RHS",
     "sensical",
+    "societally",
     "stochasticity",
     "th",
     "Zx",

### 2021-09-10 sections/healthcare_application/main.tex
More changes form code review and fix minor typos

@@
 patients to them.
+
+The patients that are distributed by the EMS arrive at the hospital via an 
+ambulance and are then either unloaded at the ED or stay blocked outside in 
+the ambulance.
+Whether or not the ambulance and the patient stay blocked is determined by 
+the threshold that the given ED chooses to play.
+High threshold indicates that the ED accepts patients even if it is relatively 
+full, while low threshold means that the ED blocks ambulances more frequently.
+
 The parameters of the model correspond to the following parameters of the ED and 
@@
 
-The patients that are distributed by the EMS arrive at the hospital via an 
-ambulance and are then either unloaded at the ED or stay blocked outside in 
-the ambulance.
-Whether or not the ambulance and the patient stay blocked is determined by 
-the threshold that the given ED chooses to play.
-High threshold indicates that the ED accepts patients even if it is relatively 
-full, while low threshold means that the ED blocks ambulances more frequently.
-
 The strategies of the two EDs are the range of thresholds that they can choose
@@
 The EMS has to decide how to distribute its patients among the two EDs so that 
-the blocking time of ambulances is minimised. 
+the weighted combination of the ambulance blocking time and the percentage of 
+lost ambulances is minimised. 
 As defined in \ref{sec:model_overview}, the interaction between the two EDs 
@@
 
-Consider a game with the following parameters:
+Consider a game with two smaller (lower \( N_i, M_i \)) and busier (higher 
+\(\lambda_{1_i} \) and \(\lambda_2\)) hospitals with the following set of 
+parameters:
 
@@
 Using equation (\ref{eq:poa_compartmentalised}) and asymmetric replicator 
-dynamics the emergent behaviour can be measured and the compartmentalised price of 
-anarchy at every iteration for both players.
+dynamics the emergent behaviour can be measured and the compartmentalised price 
+of anarchy at every iteration for both players.
 Figure \ref{fig:ard_original} shows the strategies that are being played and 
@@
 algorithm but when the strategies begin to stabilise an increase in the
-arrival rate of ambulances occurs (i.e \( \lambda_2 = 10.7 \)).
+arrival rate of ambulances occurs (i.e \( \lambda_2 = 24 \)).
 
@@
     arrival rate of ambulance patients is significantly increased to flood the
-    system completely \( \lambda_2 = 10.7 \).}
+    system completely \( \lambda_2 = 24 \).}
     \label{fig:ard_lambda_2}
@@
 
-\textbf{Increasing number of servers \( C_1 and C_2 \):}
+\textbf{Increasing number of servers \( C_1 \) and \( C_2 \):}
 Figure \ref{fig:ard_num_of_servers} shows a run of asymmetric replicator 

### 2021-09-14 sections/healthcare_application/main.tex
Add small paragraph of news articles

@@
 patients to them.
+
+There are numerous new articles that focus on the problems that arise when 
+ambulances stay parked outside of the hospital for a long amount of time
+\cite{dailyrecords}, \cite{staffordshirelive}.
+Some news reports also comment on the long idle time of ambulances when 
+they are not in use \cite{herefordtimes} and there are several reports of 
+examples where this became an issue for new patients \cite{southwalesargus}.
 

### 2021-09-14 sections/healthcare_application/main.tex
Add more around analysing games
- Include short Nash equilibrium paragraph and why we will not use it
- Include small numeric example of NE
- Include mathematics around asymmetric replicator dynamics

@@
 
+The most commonly used method for analysing normal form games is the Nash 
+equilibrium \cite{kreps1989nash}. 
+The Nash equilibrium is the point of the game were players have no incentive to 
+deviate from their strategy.
+Consider the following game:
+
+\begin{multicols}{3}
+    \begin{itemize}
+        \item \( \lambda_{1_1} \) = 1
+        \item \( \mu_1 \) = 2
+        \item \( C_1 \) = 2
+        \item \( N_1 \) = 10
+        \item \( M_1 \) = 6
+        \columnbreak
+
+        \item \( \lambda_{1_2} \) = 2
+        \item \( \mu_2 \) = 2.5
+        \item \( C_2 \) = 2
+        \item \( N_2 \) = 10
+        \item \( M_2 \) = 6
+        \columnbreak
+
+        \item \( \lambda_2 \) = 2
+        \item \( R \) = 2
+        \item \( \alpha \) = 0.5
+    \end{itemize}
+\end{multicols}
+
+The set of possible actions to choose from for player 1 and player 2 is the
+set of thresholds that the EDs can choose from: 
+\begin{equation}
+    T_1 = \{ 0, \ldots, N_1 \}, \quad T_2 = \{ 0, \ldots, N_2 \}
+\end{equation}
+
+For this example the only Nash equilibrium of the game is achieved when both 
+players choose a threshold of \( T_1 = 10, T_2 = 10 \).
+This means that the two players' best response to each other is to only block
+ambulances when they are full.
+
+Although the Nash equilibria is a great theoretical measure it sometimes may be
+% TODO: great theoretical measure?
+inconsistent with our intuitive notions about what should be the outcome of a 
+game \cite{myerson1978refinements}.
+Therefore it might not be the best way to describe human behaviour.
+Since the work of Maynard Smith \cite{smith1986evolutionary} evolutionary game 
+theory gives the tools for the emergence of stable behaviour.
+One such model that allows for asymmetric payoffs, as is the case above, is 
+replicator dynamics.
+Stable outcomes of this algorithm will correspond to a subset of Nash
+equilibria but more importantly, will give a model of emergent behaviour.
+
 In order to analyse the strategies played by the two EDs, the learning algorithm
 asymmetric replicator dynamics is used \cite{asymmetricreplicatordynamics}.
+The two players are treated as two separate populations where each 
+individual in the population is assigned a strategy. 
+As the game progresses the proportion of each player playing each strategy 
+changes based on their previous interactions.
+The fitness of each each strategy is defined as:
+
+\begin{equation}\label{eq:asymmetric_fitness}
+    f_x = Ay, \quad f_y = x^T B
+\end{equation}
+
+Here, \(x \in \mathbb{R}^{m \times 1} \) and
+\(y \in \mathbb{R}^{n \times 1}\) correspond to the proportion of individuals 
+that play each strategy on the two populations.
+Similarly, the average fitness of each strategy is defined as:
+\begin{equation}
+    \phi_x = f_x x^T, \quad \phi_y = f_y y
+\end{equation}
+
+The rate of change of strategy \( i \) of both types of individuals is captured 
+by:
+\begin{equation}
+    \frac{dx}{dt}_i = x_i((f_x)_i - \phi_x), \quad \text{ for all }i
+\end{equation}
+
+\begin{equation}
+    \frac{dy}{dt}_i = y_i((f_y)_i - \phi_y), \quad \text{ for all }i
+\end{equation}
+% TODO: Too much info?
+
 The use of a learning algorithm allows to investigate, not only the outcome of 
@@
 Both hospital 1 (row player) and hospital 2 (column player) seem to be playing 
-the same strategy \(s_10\) which indicates that thresholds \(T_1 = 10\) and 
+the same strategy \(s_{10}\) which indicates that thresholds \(T_1 = 10\) and 
 \(T_2 = 10\) are played.
@@
 \end{figure}
-
-\begin{multicols}{3}
-    \begin{itemize}
-        \item \( \lambda_{1_1} \) = 1
-        \item \( \mu_1 \) = 2
-        \item \( C_1 \) = 2
-        \item \( N_1 \) = 10
-        \item \( M_1 \) = 6
-
-        \columnbreak
-        \item \( \lambda_{1_2} \) = 2
-        \item \( \mu_2 \) = 2.5
-        \item \( C_2 \) = 2
-        \item \( N_2 \) = 10
-        \item \( M_2 \) = 6
-
-        \columnbreak
-        \item \( \lambda_2 \) = 2
-        \item \( R \) = 2
-        \item \( \alpha \) = 0.5
-    \end{itemize}
-\end{multicols}
 

### 2021-09-14 sections/healthcare_application/main.tex
Apply proselint suggestion
Add dicussion for price of anarchy

@@
 changes based on their previous interactions.
-The fitness of each each strategy is defined as:
+The fitness of each strategy is defined as:
 
@@
 \end{figure}
+
+In order to analyse how efficient the strategies played at every iteration are, 
+the concept of the price of anarchy is used.
+Price of anarchy is a measure that is used to quantify the efficiency of a
+behaviour \cite{roughgarden2005selfish}.
+In other words the price of anarchy is the worst-case measure and it is
+defined as:
+
+\begin{equation}\label{eq:general_price_of_anarchy}
+    \text{PoA} = \frac{\max_{s \in E} F(s)}{\min_{s \in S} F(s)}
+\end{equation}
+
+Here, \(S\) is the set of all sets of strategies \((s_1, s_2)\), \(E\) is the 
+set of all possible sets of equilibria and \(F\) is the cost function to 
+measure the efficiency for.
 

### 2021-09-14 sections/healthcare_application/main.tex
Include payoff matrices

@@
 
+Matrices \(A\) and \(B\) represent the original payoff matrices while matrices
+\(\tilde{A}\) and \(\tilde{B}\) represent the incentivised payoff matrices.
+It can be observed that matrix \(\tilde{A}\) is a scaled version of matrix 
+\(A\) only on the row that is most frequently played and similarly matrix 
+\(\tilde{B}\) of matrix \(B\) only on the column that is most frequently played
+(see figure \ref{fig:ard_penalty}).
+
+\tiny
+\begin{equation*}
+    A = 
+    \begin{bmatrix}
+        0.9995052 & 0.9995052 & 0.9995052 & 0.9995052 & 0.9995052 & 0.9995052 & 0.9995052 \\
+        0.99954989 & 0.99954978 & 0.99954961 & 0.99954924 & 0.99954845 & 0.9995466 & 0.999539 \\
+        0.99968233 & 0.99968194 & 0.99968151 & 0.99968067 & 0.99967874 & 0.9996734 & 0.999649  \\
+        0.99990299 & 0.99990245 & 0.99990189 & 0.99990081 & 0.99989832 & 0.9998909 & 0.9998517 \\
+        0.99999996 & 0.99999994 & 0.99999992 & 0.99999988 & 0.99999973 & 0.9999989 & 0.9999859 \\
+        0.9998773 & 0.99987995 & 0.99988236 & 0.99988643 & 0.99989417 & 0.9999126 & 0.9999712
+    \end{bmatrix}
+\end{equation*}
+
+\begin{equation*}
+    B = 
+    \begin{bmatrix}
+        0.99917127 & 0.99925823 & 0.99946188 & 0.99968499 & 0.9998942 &  1.0 & 0.99982128 \\
+        0.99917127 & 0.99925479 & 0.99945638 & 0.99968051 & 0.99989153 & 0.99999997 & 0.9998333  \\
+        0.99917127 & 0.99924532 & 0.99943793 & 0.99966451 & 0.99988286 & 0.99999966 & 0.99985269 \\
+        0.99917127 & 0.99924146 & 0.99942878 & 0.99965484 & 0.99987667 & 0.99999921 & 0.99986701 \\
+        0.99917127 & 0.9992342 &  0.99941013 & 0.99963286 & 0.99986077 & 0.9999972 & 0.9998958  \\
+        0.99917127 & 0.99921279 & 0.99934961 & 0.99954933 & 0.99978407 & 0.99997106 & 0.99997276 \\
+    \end{bmatrix}
+\end{equation*}
+
+\begin{equation*}
+    \tilde{A} = 
+    \begin{bmatrix}
+        0.99950518 & 0.99950518 & 0.99950518 & 0.99950518 & 0.99950518 & 0.99950518 & 0.99950518 \\
+        0.99954989 & 0.99954978 & 0.99954961 & 0.99954924 & 0.99954845 & 0.99954656 & 0.99953879 \\
+        0.99968233 & 0.99968194 & 0.99968151 & 0.99968067 & 0.99967874 & 0.99967339 & 0.9996492  \\
+        0.99990299 & 0.99990245 & 0.99990189 & 0.99990081 & 0.99989832 & 0.9998909 & 0.99985171 \\
+        0.99969996 & 0.99969994 & 0.99969992 & 0.99969988 & 0.99969973 & 0.99969895 & 0.99968586 \\
+        0.9998773 &  0.99987995 & 0.99988236 & 0.99988643 & 0.99989417 & 0.99991264 & 0.99997122
+    \end{bmatrix}
+\end{equation*}
+
+\begin{equation*}
+    \tilde{B} = 
+    \begin{bmatrix}
+        0.99917127 & 0.99925823 & 0.99946188 & 0.99968499 & 0.9998942 &  0.9997 & 0.99982128 \\
+        0.99917127 & 0.99925479 & 0.99945638 & 0.99968051 & 0.99989153 & 0.99969997 & 0.9998333 \\
+        0.99917127 & 0.99924532 & 0.99943793 & 0.99966451 & 0.99988286 & 0.99969966 & 0.99985269 \\
+        0.99917127 & 0.99924146 & 0.99942878 & 0.99965484 & 0.99987667 & 0.99969921 & 0.99986701 \\
+        0.99917127 & 0.9992342 &  0.99941013 & 0.99963286 & 0.99986077 & 0.9996972 & 0.9998958 \\
+        0.99917127 & 0.99921279 & 0.99934961 & 0.99954933 & 0.99978407 & 0.99967106 & 0.99997276
+    \end{bmatrix}
+\end{equation*}
+\normalsize
+
 \begin{figure}[H]

### 2021-09-14 known.py
Update known words

@@ -2,14 +2,17 @@
 
 words = {
     "automata",
+    "Ay",
     "calc",
     "CDF",
     "CDFs",
     "Ciw",
     "DES",
     "dt",
+    "dx",
+    "dy",
     "EDs",
-    "erlang",
+    "equilibria" "erlang",
     "HB",
     "hypoexponential",
     "ieeetr",

### 2021-09-14 known.py
Fix typo

@@ -12,7 +12,8 @@ words = {
     "dx",
     "dy",
     "EDs",
-    "equilibria" "erlang",
+    "equilibria",
+    "erlang",
     "HB",
     "hypoexponential",
     "ieeetr",

### 2021-09-15 sections/healthcare_application/main.tex
Section: ED-EMS application (#11)
* Add ARD with PoA plots in imgs/ directory

Each added pdf has four plots on it:
- Asymmetric replicator dynamics stratgies for row player
- Asymmetric replicator dynamics stratgies for column player
- Blocking time price of anarchy over time for row player
- Blocking time price of anarchy over time for column player

* Add initial draft of Application section

* Update known words

* Add info about asymmetric replicator dynamics

* Improve asymmetric rd plots

Increase the granularity of the PoA curve so that it looks nicer

* Add jupyter notebook for the ba

--- 2021-09-14 sections/healthcare_application/main.tex
@@
 
-There are numerous new articles that focus on the problems that arise when 
+There are numerous news articles that focus on the problems that arise when 
 ambulances stay parked outside of the hospital for a long amount of time
-\cite{dailyrecords}, \cite{staffordshirelive}.
+~\cite{dailyrecords}, \cite{staffordshirelive}.
 Some news reports also comment on the long idle time of ambulances when 
-they are not in use \cite{herefordtimes} and there are several reports of 
-examples where this became an issue for new patients \cite{southwalesargus}.
+they are not in use~\cite{herefordtimes} and there are several reports of 
+examples where this became an issue for new patients~\cite{southwalesargus}.
+A particular article looked into this problem from the point of view of an 
+ambulance paramedic:
+
+\begin{quotation}
+    % <!--alex ignore he-she her-him-->
+    ``He knows if a patient arrives more urgently in need of help, his will be 
+    pushed back''~\cite{bbcwales}
+
+    ``We used to bring poorly patients in, and we were out on the road again in 15 minutes.''~\cite{bbcwales}
+\end{quotation}
 
@@
 
-Although the Nash equilibria is a great theoretical measure it sometimes may be
-% TODO: great theoretical measure?
-inconsistent with our intuitive notions about what should be the outcome of a 
+Nash equilibria is a theoretical measure which can be
+inconsistent with intuitive notions about what should be the outcome of a 
 game \cite{myerson1978refinements}.
@@
 \end{equation}
-% TODO: Too much info?
 
@@
 behaviour \cite{roughgarden2005selfish}.
-In other words the price of anarchy is the worst-case measure and it is
-defined as:
+In other words the price of anarchy is the worst-case equilibria measure and it 
+is defined as:
 
@@
 
+Matrices \(A\) and \(B\) represent the original payoff matrices while matrices
+\(\tilde{A}\) and \(\tilde{B}\) represent the incentivised payoff matrices.
+It can be observed that matrix \(\tilde{A}\) is a scaled version of matrix 
+\(A\) only on the row that is most frequently played and similarly matrix 
+\(\tilde{B}\) of matrix \(B\) only on the column that is most frequently played
+(matrix \(A\): row \(5\), matrix \(B\): column \(6\), see figure 
+\ref{fig:ard_penalty}).
+Note that the values of the payoff matrices only differ on the fourth digit
+which is the raw utility of the strategies played.
+
+\tiny
+\begin{equation*}
+    A = 
+    \begin{bmatrix}
+        0.9995052 & 0.9995052 & 0.9995052 & 0.9995052 & 0.9995052 
+        & 0.9995052 & 0.9995052 \\
+        0.99954989 & 0.99954978 & 0.99954961 & 0.99954924 & 0.99954845 
+        & 0.9995466 & 0.999539 \\
+        0.99968233 & 0.99968194 & 0.99968151 & 0.99968067 & 0.99967874 
+        & 0.9996734 & 0.999649  \\
+        0.99990299 & 0.99990245 & 0.99990189 & 0.99990081 & 0.99989832
+        & 0.9998909 & 0.9998517 \\
+        \color{blue}0.99999996 & \color{blue}0.99999994 & \color{blue}0.99999992 
+        & \color{blue}0.99999988 & \color{blue}0.99999973 & \color{blue}0.9999989 
+        & \color{blue}0.9999859 \\
+        0.9998773 & 0.99987995 & 0.99988236 & 0.99988643 & 0.99989417 
+        & 0.9999126 & 0.9999712
+    \end{bmatrix}
+\end{equation*}
+
+\begin{equation*}
+    B = 
+    \begin{bmatrix}
+        0.99917127 & 0.99925823 & 0.99946188 & 0.99968499 & 0.9998942 
+        & \color{red}1.0 & 0.99982128 \\
+        0.99917127 & 0.99925479 & 0.99945638 & 0.99968051 & 0.99989153 
+        & \color{red}0.99999997 & 0.9998333  \\
+        0.99917127 & 0.99924532 & 0.99943793 & 0.99966451 & 0.99988286 
+        & \color{red}0.99999966 & 0.99985269 \\
+        0.99917127 & 0.99924146 & 0.99942878 & 0.99965484 & 0.99987667 
+        & \color{red}0.99999921 & 0.99986701 \\
+        0.99917127 & 0.9992342 &  0.99941013 & 0.99963286 & 0.99986077 
+        & \color{red}0.9999972 & 0.9998958  \\
+        0.99917127 & 0.99921279 & 0.99934961 & 0.99954933 & 0.99978407 
+        & \color{red}0.99997106 & 0.99997276 \\
+    \end{bmatrix}
+\end{equation*}
+
+\begin{equation*}
+    \tilde{A} = 
+    \begin{bmatrix}
+        0.99950518 & 0.99950518 & 0.99950518 & 0.99950518 & 0.99950518
+        & 0.99950518 & 0.99950518 \\
+        0.99954989 & 0.99954978 & 0.99954961 & 0.99954924 & 0.99954845
+        & 0.99954656 & 0.99953879 \\
+        0.99968233 & 0.99968194 & 0.99968151 & 0.99968067 & 0.99967874
+        & 0.99967339 & 0.9996492  \\
+        0.99990299 & 0.99990245 & 0.99990189 & 0.99990081 & 0.99989832
+        & 0.9998909 & 0.99985171 \\
+        \color{blue}0.99969996 & \color{blue}0.99969994 & \color{blue}0.99969992 
+        & \color{blue}0.99969988 & \color{blue}0.99969973 & \color{blue}0.99969895 
+        & \color{blue}0.99968586 \\
+        0.9998773 &  0.99987995 & 0.99988236 & 0.99988643 & 0.99989417
+        & 0.99991264 & 0.99997122 \\
+    \end{bmatrix}
+\end{equation*}
+
+\begin{equation*}
+    \tilde{B} = 
+    \begin{bmatrix}
+        0.99917127 & 0.99925823 & 0.99946188 & 0.99968499 & 0.9998942
+        & \color{red}0.9997 & 0.99982128 \\
+        0.99917127 & 0.99925479 & 0.99945638 & 0.99968051 & 0.99989153
+        & \color{red}0.99969997 & 0.9998333 \\
+        0.99917127 & 0.99924532 & 0.99943793 & 0.99966451 & 0.99988286
+        & \color{red}0.99969966 & 0.99985269 \\
+        0.99917127 & 0.99924146 & 0.99942878 & 0.99965484 & 0.99987667
+        & \color{red}0.99969921 & 0.99986701 \\
+        0.99917127 & 0.9992342 &  0.99941013 & 0.99963286 & 0.99986077
+        & \color{red}0.9996972 & 0.9998958 \\
+        0.99917127 & 0.99921279 & 0.99934961 & 0.99954933 & 0.99978407
+        & \color{red}0.99967106 & 0.99997276 \\
+    \end{bmatrix}
+\end{equation*}
+\normalsize
+
 \begin{figure}[H]

### 2021-09-15 imgs/asymmetric_rd/main.py

@@ -1,0 +1,58 @@
+import nashpy as nash
+import numpy as np
+import matplotlib.pyplot as plt
+
+import ambulance_game as abg
+
+lambda_2 = 2
+lambda_1_1 = 1
+lambda_1_2 = 2
+mu_1 = 2
+mu_2 = 2.5
+num_of_servers_1 = 2
+num_of_servers_2 = 2
+system_capacity_1 = 10
+system_capacity_2 = 10
+buffer_capacity_1 = 6
+buffer_capacity_2 = 6
+target = 2
+alpha = 0.5
+
+
+A, B, R = abg.game.get_payoff_matrices(
+    lambda_2=lambda_2,
+    lambda_1_1=lambda_1_1,
+    lambda_1_2=lambda_1_2,
+    mu_1=mu_1,
+    mu_2=mu_2,
+    num_of_servers_1=num_of_servers_1,
+    num_of_servers_2=num_of_servers_2,
+    system_capacity_1=system_capacity_1,
+    system_capacity_2=system_capacity_2,
+    buffer_capacity_1=buffer_capacity_1,
+    buffer_capacity_2=buffer_capacity_2,
+    target=target,
+    alpha=alpha,
+)
+A += 1
+B += 1
+
+my_game = nash.Game(A, B)
+xs, ys = my_game.asymmetric_replicator_dynamics(timepoints=np.linspace(1, 200000, 100))
+
+plt.figure(figsize=(15, 5))
+plt.subplot(1, 2, 1)
+plt.plot(xs)
+plt.xlabel("Timepoints")
+plt.ylabel("Probability")
+plt.title("Row player")
+plt.legend([f"$s_{{{i + 1}}}$" for i in range(len(xs[0]))])
+
+plt.subplot(1, 2, 2)
+plt.plot(ys)
+plt.xlabel("Timepoints")
+plt.ylabel("Probability")
+plt.title("Column player")
+plt.legend([f"$s_{{{i + 1}}}$" for i in range(len(ys[0]))])
+
+plt.savefig("asymmetric_rd.png", transparent=True)

### 2021-09-15 known.py

@@ -2,26 +2,36 @@
 
 words = {
     "automata",
+    "Ay",
     "calc",
     "CDF",
     "CDFs",
     "Ciw",
     "DES",
     "dt",
+    "dx",
+    "dy",
+    "EDs",
+    "equilibria",
     "erlang",
     "HB",
     "hypoexponential",
     "ieeetr",
     "ij",
+    "incentivised",
+    "incentivising",
     "LHS",
     "Markovian",
     "math",
     "memoryless",
     "Michalis",
     "Panayides",
+    "PoA",
     "pre",
     "queueing",
     "RHS",
+    "sensical",
+    "societally",
     "stochasticity",
     "th",
     "Zx",

### 2021-09-15 sections/appendix/descrete_event_simulation/main.tex
Compile main.pdf after rebase
Make sure checks pass
- Update known words for apell spellcheck
- Add proselint expected_errors

@@
             \draw (7cm-\i*10pt,1.25) -- +(0,-1.5cm);
-        % The two vertical lines at the very start of Queue 2 
+        % The two vertical lines at the start of Queue 2 
         \draw (7cm-54pt,1.2) -- +(0,-0.5cm);
@@
 To eliminate any stochasticity in the simulation, the simulation can be run
-numerous times and get the avergae performance measures out of all the runs.
+numerous times and get the average performance measures out of all the runs.
 

### 2021-09-15 known.py

@@ -1,12 +1,21 @@
 """ A set of known words and end-of-word patterns for the spellchecker. """
 
 words = {
+    "abg",
+    "alsoletter",
     "automata",
     "Ay",
+    "backcolor",
+    "backgroundcolor",
+    "basicstyle",
+    "breaklines",
     "calc",
+    "captionpos",
     "CDF",
     "CDFs",
     "Ciw",
+    "codegreen",
+    "commentstyle",
     "DES",
     "dt",
     "dx",
@@ -20,19 +29,31 @@ words = {
     "ij",
     "incentivised",
     "incentivising",
+    "keepspaces",
+    "keywordcolor",
+    "keywordstyle",
     "LHS",
     "Markovian",
     "math",
     "memoryless",
     "Michalis",
+    "mult",
+    "np",
+    "num",
+    "numpy",
     "Panayides",
     "PoA",
     "pre",
+    "pystyle",
     "queueing",
+    "rgb",
+    "RGB",
     "RHS",
+    "runtime",
     "sensical",
     "societally",
     "stochasticity",
+    "terminalstyle",
     "th",
     "Zx",
 }

### 2021-09-15 tasks.py

@@ -60,6 +60,9 @@ def proselint(c):
         expected_errors = (
             "annotations.misc",
             "leonard.exclamation.30ppm",
+            "typography.symbols.ellipsis",
+            "typography.symbols.sentence_spacing",
+            "security.credit_card",
         )
         updated_errors = []
         for error in errors:

### 2021-09-16 sections/appendix/descrete_event_simulation/main.tex
Finish up How-to guide

@@
 
-For every service completion Ciw stores all data records in a simulation 
-object~\cite{ciwpython}.
-The records that are stored are the following:
-
-% TODO: Maybe move this to reference 
-\begin{multicols}{2}
-    \begin{itemize}
-        \item \textbf{id\_number} \(\in R\).
-        \item \textbf{customer\_class} \(= 0\)
-        \item \textbf{node} \(= \{0, 1, 2, -1 \} \)
-        \item \textbf{arrival\_date} \( \in R^+ \)
-        \item \textbf{waiting\_time} \( \in R^+ \)
-        \item \textbf{service\_start\_date} \( \in R^+ \)
-        \item \textbf{service\_time} \( \in R^+ \)
-        \item \textbf{service\_end\_time} \( \in R^+ \)
-        \item \textbf{time\_blocked} \( \in R^+ \)
-        \item \textbf{exit\_date} \( \in R^+ \)
-        \item \textbf{destination} \( = \{1, 2, -1\} \)
-        \item \textbf{queue\_size\_at\_arrival} \( \in N \)
-        \item \textbf{queue\_size\_at\_departure} \( \in N \)
-    \end{itemize}
-\end{multicols}
-
 To get the simulation object with all the data records, the following code can be
@@
 
+To get the average proportion of individuals within target, run the following
+code:
+
+\begin{lstlisting}[style=pystyle]
+    >>> import ambulance_game as abg
+    >>> (
+    ...     overall_proportion,
+    ...     class_1_proportion,
+    ...     class_2_proportion,
+    ... ) = abg.simulation.
+    get_mean_proportion_of_individuals_within_target_for_multiple_runs(    
+    ...     lambda_1=3,
+    ...     lambda_2=2,
+    ...     mu=1,
+    ...     num_of_servers=6,
+    ...     threshold=10,
+    ...     system_capacity=20,
+    ...     buffer_capacity=10,
+    ...     seed_num=0,
+    ...     num_of_trials=10,
+    ...     runtime=2000,
+    ...     target=1,
+    ... )
+\end{lstlisting}
 % TODO: Fix code for proportion of individuals within time target
-
-% Run multiple simulation results
-% Show all possible arguments
-% Get all performance measures
 
@@
 
-% This discrete event simulation model was built in python and can be installed by 
-% running the following command in the terminal:
+\subsection{Explanation}
 
-% Having installed the package, the following script can be used to simulate, and 
-% get all required performance measures, of a queueing system with two waiting 
-% spaces and two types of individuals for a runtime of 2000 unit time with the 
-% following parameters:
+For every service completion Ciw stores all data records in a simulation 
+object~\cite{ciwpython}.
+For the specific library the records that are stored, along with the 
+range of values that they can take are as follows:
 
-% \lstinputlisting[language=Python, style=pystyle]{sections/appendix/descrete_event_simulation/simulation.py}
-
-% The script above shows the outcome of the DES model for a single run.
-% To minimise the stochasticity of the simulation, the model can be simulated for 
-% numerous trials. 
-% The following script can be used to run the simulation for a number of times 
-% and get the mean of the waiting, service and blocking times:
-
-% \lstinputlisting[language=Python, style=pystyle]{sections/appendix/descrete_event_simulation/multiple_runs.py}
-
-% Finally, the proportion of individuals within target for multiple runs can be
-% calculated by running the following block of code:
-
-% \lstinputlisting[language=Python, style=pystyle]{sections/appendix/descrete_event_simulation/multiple_runs_proportion.py}
+\begin{multicols}{2}
+    \begin{itemize}
+        \item \textbf{id\_number} \(\in R\).
+        \item \textbf{customer\_class} \(= 0\)
+        \item \textbf{node} \(= \{0, 1, 2, -1 \} \)
+        \item \textbf{arrival\_date} \( \in R^+ \)
+        \item \textbf{waiting\_time} \( \in R^+ \)
+        \item \textbf{service\_start\_date} \( \in R^+ \)
+        \item \textbf{service\_time} \( \in R^+ \)
+        \item \textbf{service\_end\_time} \( \in R^+ \)
+        \item \textbf{time\_blocked} \( \in R^+ \)
+        \item \textbf{exit\_date} \( \in R^+ \)
+        \item \textbf{destination} \( = \{1, 2, -1\} \)
+        \item \textbf{queue\_size\_at\_arrival} \( \in N \)
+        \item \textbf{queue\_size\_at\_departure} \( \in N \)
+    \end{itemize}
+\end{multicols}
 

### 2021-09-16 sections/appendix/descrete_event_simulation/multiple_runs.py
Remove unnecessary python files

@@ -1,23 +1,0 @@
-import numpy as np
-import ambulance_game as abg
-
-all_simulations = abg.simulation.get_multiple_runs_results(
-    lambda_1=3,
-    lambda_2=2,
-    mu=1,
-    num_of_servers=6,
-    threshold=10,
-    system_capacity=20,
-    buffer_capacity=10,
-    seed_num=0,
-    runtime=2000,
-    num_of_trials=10,
-)
-
-all_waits = [np.mean(w.waiting_times) for w in all_simulations]
-all_services = [np.mean(s.service_times) for s in mult_results]
-all_blocks = [np.mean(b.blocking_times) for b in mult_results]
-
-mean_wait = np.mean(all_waits)
-mean_service = np.mean(all_services)
-mean_block = np.mean(all_blocks)

### 2021-09-16 sections/appendix/descrete_event_simulation/multiple_runs_proportion.py

@@ -1,20 +1,0 @@
-import numpy as np
-import ambulance_game as abg
-
-(
-    overall_proportion,
-    class_1_proportion,
-    class_2_proportion,
-) = abg.simulation.get_mean_proportion_of_individuals_within_target_for_multiple_runs(
-    lambda_1=3,
-    lambda_2=2,
-    mu=1,
-    num_of_servers=6,
-    threshold=10,
-    system_capacity=20,
-    buffer_capacity=10,
-    seed_num=0,
-    runtime=2000,
-    num_of_trials=10,
-    target=1,
-)

### 2021-09-16 sections/appendix/descrete_event_simulation/simulation.py

@@ -1,25 +1,0 @@
-import numpy as np
-import ambulance_game as abg
-
-Simulation = abg.simulation.simulate_model(
-    lambda_1=3,
-    lambda_2=2,
-    mu=1,
-    num_of_servers=6,
-    threshold=10,
-    system_capacity=20,
-    buffer_capacity=10,
-    seed_num=0,
-    runtime=2000,
-)
-
-mean_wait = np.mean([w.waiting_time for w in Simulation.get_all_records()])
-
-mean_block = np.mean([b.time_blocked for b in Simulation.get_all_records()])
-
-mean_service = np.mean([s.service_time for s in Simulation.get_all_records()])
-
-target = 1
-proportion_within_target = np.mean(
-    [1 if w.waiting_time <= target else 0 for w in Simulation.get_all_records()]
-)

### 2021-09-16 sections/appendix/descrete_event_simulation/main.tex
Add Reference and Explanation section

@@
 \subsection{Reference}
+The primary tool that was used in the construction of the discrete event 
+simulation model was the python library \texttt{ciw}.
+See Ciw's documentation for a more detailed explanation of how it works and 
+what are its capabilities~\cite{ciwpython}.
+
+Find below a detailed list of the functions that were created for the simulation
+model:
+
+\begin{itemize}
+    \item \lstinline[style=pystyle]{build_model}: \textit{Builds a ciw object 
+    that represents a model of a queuing network with two service centres.}
+    \item \lstinline[style=pystyle]{build_custom_node}: \textit{Build a custom 
+    node to replace the default ciw.Node. Inherits from the original ciw.Node 
+    class and replaces two methods.}
+    \item \lstinline[style=pystyle]{simulate_model}: \textit{Simulate the model
+    by using the custom node and returning the simulation object}
+    \item \lstinline[style=pystyle]{get_simulated_state_probabilities}: \textit{
+    Calculates the vector pi in a dictionary format or an array format}
+    \item \lstinline[style=pystyle]{extract_times_from_records}: \textit{Get the
+    required times (waiting, service, blocking) out of ciw's records where all 
+    individuals are treated the same way}
+    \item \lstinline[style=pystyle]{extract_times_from_individuals}: \textit{
+    Extract waiting times and service times for all individuals and proceed to 
+    extract blocking times for just class 2 individuals}
+    \item \lstinline[style=pystyle]{get_list_of_results}: \textit{Modify the 
+    outputs so that they are returned in a list format where it is sometimes 
+    easier to be used by other functions.}
+    \item \lstinline[style=pystyle]{get_multiple_runs_results}: \textit{Get the 
+    waiting times, service times and blocking times for multiple runs of the 
+    simulation}
+    \item \lstinline[style=pystyle]{get_average_simulated_state_probabilities}:
+    \textit{This function runs \hfill\break
+    get\_simulated\_state\_probabilities for multiple iterations to eliminate 
+    any stochasticity from the results}
+    \item \lstinline[style=pystyle]
+    {get_mean_blocking_difference_between_two_systems}: \textit{Given a 
+    predefined proportion of class's 2 arrival rate calculate the mean 
+    difference between blocking times of two systems with a given set of 
+    parameters}
+    \item \lstinline[style=pystyle]{calculate_class_2_individuals_best_response}
+    \textit{Obtains the optimal distribution of class 2 individuals such that 
+    the blocking times in the two systems are identical and thus minimised}
+    \item \lstinline[style=pystyle]
+    {extract_total_individuals_and_the_ones_within_target_for_both_classes}:
+    \hfill\break \textit{Extract the total number of individuals that pass 
+    through the model and the total number of individuals that exit the model 
+    within the given target.}
+    \item \lstinline[style=pystyle]
+    {get_mean_proportion_of_individuals_within_target_for_multiple_runs}: 
+    \textit{Get the average proportion of individuals within target by running 
+    the simulation multiple times}
+\end{itemize}
 
@@
 
-For every service completion Ciw stores all data records in a simulation 
-object~\cite{ciwpython}.
-For the specific library the records that are stored, along with the 
+Based on Ciw's functionality the simulation model stores all data records in a
+Record object. 
+For every event that takes place a record is created with all the relevant
+information.
+For this specific library, the records that are stored, along with the 
 range of values that they can take are as follows:

### 2021-09-16 sections/appendix/descrete_event_simulation/main.tex
Apply changes based on proselint and alex

@@
     \item \lstinline[style=pystyle]{build_model}: \textit{Builds a ciw object 
-    that represents a model of a queuing network with two service centres.}
+    that represents a model of a queuing network with two waiting spaces.}
     \item \lstinline[style=pystyle]{build_custom_node}: \textit{Build a custom 
@@
     Extract waiting times and service times for all individuals and proceed to 
-    extract blocking times for just class 2 individuals}
+    extract blocking times for only class 2 individuals}
     \item \lstinline[style=pystyle]{get_list_of_results}: \textit{Modify the 

### 2021-09-16 known.py
Update known.py

@@ -14,6 +14,8 @@ words = {
     "CDF",
     "CDFs",
     "Ciw",
+    "Ciw's",
+    "ciw's",
     "codegreen",
     "commentstyle",
     "DES",

### 2021-09-16 title.tex
Add separate files for packages and title

\title{A game theoretic model of the behavioural gaming that takes place at the EMS - ED interface}
\author{Michalis Panayides}
\date{}

### 2021-09-16 sections/appendix/descrete_event_simulation/main.tex
Add random seeds to python code

@@
 \begin{lstlisting}[style=pystyle]
-
     >>> import ambulance_game as abg
@@
     ...     buffer_capacity=10,
+    ...     seed_num=0,
     ... )
@@
     Record(id_number=1, customer_class=0, node=2, arrival_date=0.4728763843239206, waiting_time=0.0, service_start_date=0.4728763843239206, service_time=0.5457131455415929, service_end_date=1.0185895298655134, time_blocked=0.0, exit_date=1.0185895298655134, destination=-1, queue_size_at_arrival=0, queue_size_at_departure=4)
+
 \end{lstlisting}
@@
     ... )
-    0.2246928220731305
+    >>> mean_wait
+    0.3608431242229529
+
 \end{lstlisting}
@@
     ... )
-    0.35037759808989827
+    >>> mean_wait
+    0.3566390561071839
+
 \end{lstlisting}
@@
     ...     threshold=10,
+    ...     seed_num=0,
     ... )
-    >>> Simulation.get_all_records()[1]
-    Record(id_number=1, customer_class=0, node=2, arrival_date=0.5391449803891563, waiting_time=0.0, service_start_date=0.5391449803891563, service_time=0.17003700443114755, service_end_date=0.7091819848203038, time_blocked=0.0, exit_date=0.7091819848203038, destination=-1, queue_size_at_arrival=0, queue_size_at_departure=0)
+    >>> Simulation.get_all_records()[4]
+    Record(id_number=2, customer_class=0, node=2, arrival_date=0.5727571550618586, waiting_time=0.0, service_start_date=0.5727571550618586, service_time=0.7159547497671506, service_end_date=1.2887119048290092, time_blocked=0.0, exit_date=1.2887119048290092, destination=-1, queue_size_at_arrival=1, queue_size_at_departure=3)
+
 \end{lstlisting}
@@
     ... )
+    >>> mean_wait
+    0.23845862661827116
+
     >>> mean_block = np.mean(
@@
     ... )
+    >>> mean_block
+    0.08501727452006658
+
     >>> mean_service = np.mean(
@@
     ... )
+    >>> mean_service
+    0.7102610863960119
+
     >>> target = 1
@@
     ... )
+    >>> proportion_within_target
+    0.9387470071827614
 
@@
     >>> mean_wait = np.mean([
-    ...     np.mean(w.waiting_times) for w in mean_simulations
+    ...     np.mean(w.waiting_times) for w in all_simulations
     ... ])
+    >>> mean_wait
+    0.35585979549204577
+
     >>> mean_service = np.mean([
-    ...     np.mean(s.service_times) for s in mult_results
+    ...     np.mean(s.service_times) for s in all_simulations
     ... ])
+    >>> mean_service
+    1.002184850213415
+
     >>> mean_block = np.mean([
-    ...     np.mean(b.blocking_times) for b in mult_results
+    ...     np.mean(b.blocking_times) for b in all_simulations
     ... ])
+    >>> mean_block
+    0.3976966024549059
+
 \end{lstlisting}
@@
 \begin{lstlisting}[style=pystyle]
-    >>> import ambulance_game as abg
+    >>> import numpy as np
     >>> (
@@
     ...     class_2_proportion,
-    ... ) = abg.simulation.
-    get_mean_proportion_of_individuals_within_target_for_multiple_runs(    
+    ... ) = abg.simulation.get_mean_proportion_of_individuals_within_target_for_multiple_runs(    
     ...     lambda_1=3,
@@
     ... )
+    >>> np.mean(overall_proportion)
+    0.45785790578122043
+
+    >>> np.mean(class_1_proportion)
+    0.4406768928300989
+
+    >>> np.mean(class_2_proportion)
+    0.4840634188366037
+
 \end{lstlisting}

### 2021-09-16 tasks.py
Add doctests to tasks

@@ -93,3 +93,11 @@ def alex(c):
     all_tex_files = list(pathlib.Path().glob("**/*.tex"))
     for file in all_tex_files:
         c.run(f"alex {file}")
+
+
+@task
+def doctests(c):
+    """
+    Run doctests
+    """
+    c.run('python -m pytest --doctest-glob="*.tex"')

### 2021-09-17 sections/appendix/descrete_event_simulation/main.tex
Add documentation for 3 additional functions

@@
 
+To get the steady state probabilities of the model based on the simulation the
+following code can be used:
+\begin{lstlisting}[style=pystyle]
+    >>> import numpy as np
+    >>> import ambulance_game as abg
+    >>> simulation_object = abg.simulation.simulate_model(
+    ...     lambda_1=1,
+    ...     lambda_2=2,
+    ...     mu=2,
+    ...     num_of_servers=2,
+    ...     threshold=3,
+    ...     system_capacity=4,
+    ...     buffer_capacity=2,
+    ...     seed_num=0,
+    ...     runtime=2000,
+    ... )
+    >>> probs = abg.simulation.get_simulated_state_probabilities(
+    ...    simulation_object=simulation_object,
+    ... )
+    >>> np.round(probs, decimals=3)
+    array([[0.166, 0.266, 0.192, 0.147, 0.025],
+           [  nan,   nan,   nan, 0.094, 0.024],
+           [  nan,   nan,   nan, 0.058, 0.027]])
+
+    >>> np.nansum(probs)
+    1.0
+
+\end{lstlisting}
+
+Similarly to get the average steady state probabilities over multiple runs,
+one can use:
+
+\begin{lstlisting}[style=pystyle]
+    >>> import numpy as np
+    >>> import ambulance_game as abg
+    >>> probs = abg.simulation.get_average_simulated_state_probabilities(
+    ...     lambda_1=1,
+    ...     lambda_2=2,
+    ...     mu=2,
+    ...     num_of_servers=2,
+    ...     threshold=3,
+    ...     system_capacity=4,
+    ...     buffer_capacity=2,
+    ...     seed_num=0,
+    ...     runtime=2000,
+    ...     num_of_trials=10,
+    ... )
+    >>> np.round(probs, decimals=3)
+    array([[0.18 , 0.267, 0.197, 0.144, 0.024],
+           [  nan,   nan,   nan, 0.085, 0.022],
+           [  nan,   nan,   nan, 0.054, 0.026]])
+
+    >>> np.nansum(probs)
+    1.0
+
+\end{lstlisting}
+
+In the scenario where there are two queueing models and a service that 
+distributes individuals to the models, (i.e. the scenario described in this 
+paper) the simulation can be used to decide what proportion of individuals 
+to send to each the model.
+Note that the output of the function shows the value of \(p_1\), the proportion
+of class 2 individuals to be sent to queueing model 1.
+
+\begin{lstlisting}[style=pystyle]
+    >>> import ambulance_game as abg
+    >>> abg.simulation.calculate_class_2_individuals_best_response(
+    ...     lambda_2=4,
+    ...     lambda_1_1=1,
+    ...     lambda_1_2=1,
+    ...     mu_1=4,
+    ...     mu_2=3,
+    ...     num_of_servers_1=2,
+    ...     num_of_servers_2=2,
+    ...     threshold_1=3,
+    ...     threshold_2=3,
+    ...     system_capacity_1=3,
+    ...     system_capacity_2=3,
+    ...     buffer_capacity_1=2,
+    ...     buffer_capacity_2=2,
+    ...     seed_num_1=0,
+    ...     seed_num_2=0,
+    ...     num_of_trials=3,
+    ...     warm_up_time=100,
+    ...     runtime=1000,
+    ... )
+    0.6343260586929469
+
+\end{lstlisting}
+
 \subsection{Reference}
@@
     by using the custom node and returning the simulation object}
-    \item \lstinline[style=pystyle]{get_simulated_state_probabilities}: \textit{
-    Calculates the vector pi in a dictionary format or an array format}
     \item \lstinline[style=pystyle]{extract_times_from_records}: \textit{Get the
@@
     simulation}
+    \item \lstinline[style=pystyle]
+    {extract_total_individuals_and_the_ones_within_target_for_both_classes}:
+    \hfill\break \textit{Extract the total number of individuals that pass 
+    through the model and the total number of individuals that exit the model 
+    within the given target.}
+    \item \lstinline[style=pystyle]
+    {get_mean_proportion_of_individuals_within_target_for_multiple_runs}: 
+    \textit{Get the average proportion of individuals within target by running 
+    the simulation multiple times}
+    \item \lstinline[style=pystyle]{get_simulated_state_probabilities}: \textit{
+    Calculates the vector \(\pi\) in a dictionary format or an array format}
     \item \lstinline[style=pystyle]{get_average_simulated_state_probabilities}:
@@
     the blocking times in the two systems are identical and thus minimised}
-    \item \lstinline[style=pystyle]
-    {extract_total_individuals_and_the_ones_within_target_for_both_classes}:
-    \hfill\break \textit{Extract the total number of individuals that pass 
-    through the model and the total number of individuals that exit the model 
-    within the given target.}
-    \item \lstinline[style=pystyle]
-    {get_mean_proportion_of_individuals_within_target_for_multiple_runs}: 
-    \textit{Get the average proportion of individuals within target by running 
-    the simulation multiple times}
 \end{itemize}

### 2021-09-17 known.py
Update known words

@@ -40,12 +40,15 @@ words = {
     "memoryless",
     "Michalis",
     "mult",
+    "nan",
+    "nansum",
     "np",
     "num",
     "numpy",
     "Panayides",
     "PoA",
     "pre",
+    "probs",
     "pystyle",
     "queueing",
     "rgb",

### 2021-09-20 sections/appendix/descrete_event_simulation/main.tex
Fix failing doctests
Apply suggestions from code review
Co-authored-by: Vince Knight <vincent.knight@gmail.com>

@@
 \begin{lstlisting}[style=terminalstyle]
-    $ pip install ambulance_game
+    $ python -m pip install ambulance_game
 \end{lstlisting}
@@
 object.
-The simulation object can be used to view the every event that occurred in the 
+The simulation object can be used to view every event that occurred in the 
 simulation 
@@
 used:
+
 \begin{lstlisting}[style=pystyle]
@@
 
-From a single run of the simulation the data records can be used the get the
+From a single run of the simulation the data records can be used to get the
 average for certain performance measures. 
@@
 
-To eliminate any stochasticity in the simulation, the simulation can be run
+To reduce the effects of stochasticity in the simulation, the simulation can be run
 numerous times and get the average performance measures out of all the runs.
@@
 
-    >>> np.nansum(probs)
+    >>> total = np.nansum(probs)
+    >>> np.round(total, decimals=5)
     1.0

### 2021-09-20 sections/appendix/descrete_event_simulation/main.tex
Add subsections in How-to

@@
 
+\subsubsection{How to install:}
 The package can be installed by either running:
@@
 % TODO: Cite repository
-The required arguments that need to be passed to the simulate\_model() function
+
+\subsubsection{How to simulate the model:}
+The required arguments that need to be passed to the 
+\lstinline[style=pystyle]{simulate_model()} function
 are the following:
@@
 \begin{itemize}
-    \item \textit{system\_capacity}: The maximum number of individuals in 
+    \item \textit{system\_capacity} (\(N\)): The maximum number of individuals in 
     waiting zone 2.
-    \item \textit{buffer\_capacity}: The maximum number of individuals in 
+    \item \textit{buffer\_capacity} \(M\): The maximum number of individuals in 
     waiting zone 1.
@@
 
+\subsubsection{How to get the performance measures for a single run:}
 From a single run of the simulation the data records can be used to get the
@@
 
-To reduce the effects of stochasticity in the simulation, the simulation can be run
-numerous times and get the average performance measures out of all the runs.
+\subsubsection{How to get the average performance measures:}
+To reduce the effects of stochasticity in the simulation, the simulation can be 
+run numerous times and get the average performance measures out of all the runs.
 
@@
 
+\subsubsection{How to get the steady state probabilities vector \( \pi \):}
+
 To get the steady state probabilities of the model based on the simulation the
@@
 \end{lstlisting}
+
+\subsubsection{How to get the optimal distribution of class 2 individuals among 2 
+queuing models:}
 

### 2021-09-23 sections/appendix/descrete_event_simulation/main.tex
Change code based on ambulance_game v0.0.2

@@
     ...     num_of_trials=10,
+    ...     target=1,
     ... )
@@
 
-\end{lstlisting}
-
-To get the average proportion of individuals within target, run the following
-code:
-
-\begin{lstlisting}[style=pystyle]
-    >>> import numpy as np
-    >>> (
-    ...     overall_proportion,
-    ...     class_1_proportion,
-    ...     class_2_proportion,
-    ... ) = abg.simulation.get_mean_proportion_of_individuals_within_target_for_multiple_runs(    
-    ...     lambda_1=3,
-    ...     lambda_2=2,
-    ...     mu=1,
-    ...     num_of_servers=6,
-    ...     threshold=10,
-    ...     system_capacity=20,
-    ...     buffer_capacity=10,
-    ...     seed_num=0,
-    ...     num_of_trials=10,
-    ...     runtime=2000,
-    ...     target=1,
-    ... )
-    >>> np.mean(overall_proportion)
+    >>> np.mean([p.proportion_within_target for p in all_simulations])
     0.45785790578122043
-
-    >>> np.mean(class_1_proportion)
-    0.4406768928300989
-
-    >>> np.mean(class_2_proportion)
-    0.4840634188366037
 

### 2021-09-23 known.py
Include documentation for DES python code (#13)
* Add script for simulation performance measures

* Add scripts for multiple runs

* Write more documentation around the code

* Include code Tutorial

Modify appendix based on Diataxis framework (Tutorial-Howto-Reference-
Explanation). This commit adds the initial draft of the Tutorial part.

* Add first draft of how-to guide

* Compile main.pdf after rebase

* Make sure checks pass

- Update known words for apell spellcheck
- Add proselint expected_errors

* Finish up How-to guide

* Remove unnecessary python files

* Add Reference and Explanat

@@ -1,12 +1,23 @@
 """ A set of known words and end-of-word patterns for the spellchecker. """
 
 words = {
+    "abg",
+    "alsoletter",
     "automata",
     "Ay",
+    "backcolor",
+    "backgroundcolor",
+    "basicstyle",
+    "breaklines",
     "calc",
+    "captionpos",
     "CDF",
     "CDFs",
     "Ciw",
+    "Ciw's",
+    "ciw's",
+    "codegreen",
+    "commentstyle",
     "DES",
     "dt",
     "dx",
@@ -20,19 +31,34 @@ words = {
     "ij",
     "incentivised",
     "incentivising",
+    "keepspaces",
+    "keywordcolor",
+    "keywordstyle",
     "LHS",
     "Markovian",
     "math",
     "memoryless",
     "Michalis",
+    "mult",
+    "nan",
+    "nansum",
+    "np",
+    "num",
+    "numpy",
     "Panayides",
     "PoA",
     "pre",
+    "probs",
+    "pystyle",
     "queueing",
+    "rgb",
+    "RGB",
     "RHS",
+    "runtime",
     "sensical",
     "societally",
     "stochasticity",
+    "terminalstyle",
     "th",
     "Zx",
 }

### 2021-09-23 tasks.py

@@ -60,6 +60,9 @@ def proselint(c):
         expected_errors = (
             "annotations.misc",
             "leonard.exclamation.30ppm",
+            "typography.symbols.ellipsis",
+            "typography.symbols.sentence_spacing",
+            "security.credit_card",
         )
         updated_errors = []
         for error in errors:
@@ -90,3 +93,11 @@ def alex(c):
     all_tex_files = list(pathlib.Path().glob("**/*.tex"))
     for file in all_tex_files:
         c.run(f"alex {file}")
+
+
+@task
+def doctests(c):
+    """
+    Run doctests
+    """
+    c.run('python -m pytest --doctest-glob="*.tex"')

### 2021-09-24 sections/model_overview/main.tex
Make changes suggested by proselint
Apply changes based on Alex's suggestions
Minor changes to other sections

@@
 decision of the distributor is the proportion of lost individuals.
-Equation \ref{eq:obj-distributor} can be used to capture a mixture 
+Equation \ref{eq:obj_distributor} can be used to capture a mixture 
 between the two objectives.
 
-\begin{equation}\label{eq:obj-distributor}
+\begin{equation}\label{eq:obj_distributor}
     \alpha P(L_A) + (1 - \alpha) B_A = 
@@
 
-Using equations \ref{eq:obj-queueing-systems} and \ref{eq:obj-distributor} gives
+Using equations \ref{eq:obj-queueing-systems} and \ref{eq:obj_distributor} gives
 an imperfect information extensive form game. 
@@
     \begin{tikzpicture}[-, node distance = 3cm, scale=0.8]
-        \node[anchor=north](HA){\(H_A\)};
+        \node[anchor=north](HA){\(Q_A\)};
         \node[anchor=north](HA_d1) at (3, 2){.};
@@
 
-        \node[anchor=north](HB) at (4.1, 0){\(H_B\)};
+        \node[anchor=north](HB) at (4.1, 0){\(Q_B\)};
         \node[anchor=north](HB_d1) at (6.9, 2){.};
@@
 The first 
-queueing system \(H_A\) decides on a threshold, then the second system \(H_B\)
-chooses its own threshold, without knowing the strategy of \(H_A\), and finally
+queueing system \(Q_A\) decides on a threshold, then the second system \(Q_B\)
+chooses its own threshold, without knowing the strategy of \(Q_A\), and finally
 the distributor makes its choice. Note here that the dotted line represents the
-fact that \(H_B\) is unaware of the state of the game when making its own 
-decisions. The game can thus be partitioned into a normal form game between the
-two queueing systems and finding the distributor's best choice.
+fact that \(Q_B\) is unaware of the state of the game when making its own 
+decisions.
 
@@
 
-\begin{equation}
+\begin{equation} \label{eq:payoff-entry}
     U_{T_1, T_2}^i = \quad -\left( 
@@
 
-\begin{equation} \label{eq:payoff-matrices}
+\begin{equation} \label{eq:payoff_matrices}
     A = 

### 2021-09-28 sections/methodology/main.tex
Write intro for methodology section

@@
-\section{Methodology}
+\section{Methodology}\label{sec:methodology}
+
+Th problem defined in section \ref{sec:model_overview} describes a normal-form
+game between the decision makers of two queueing systems and a third player that 
+decides how to distribute individuals to the systems.
+The strategy space of the two queueing systems is defined as the possible values
+that the threshold parameter can take \(T_i \in (1, N_i)\).
+Then, the distributor has to decide on the proportion of individuals to send to 
+each queueing system \(p_A \text{ and } p_B\), where \(p_A, p_B \in [0, 1] \)
+and \(p_A + p_B = 1\).
+Figure \ref{fig:imperfect-info-game} shows a diagrammatic 
+representation of the game to be played and the decisions to be made.
+
+\begin{figure}[ht]
+    \centering
+    \begin{tikzpicture}[-, node distance = 3cm, scale=0.8]
+        \node[anchor=north](HA){\(Q_A\)};
+        \node[anchor=north](HA_d1) at (3, 2){.};
+        \node[anchor=north](HA_d2) at (3, -2){.};
+
+        \path[->] (HA) edge node {}(HA_d1);
+        \path[->] (HA) edge node {}(HA_d2);
+        \path (HA_d1) edge [bend left] node {}(HA_d2);
+        \path (HA_d1) [dashed] edge node {}(HA_d2);
+
+        \node[anchor=north](HB) at (4.1, 0){\(Q_B\)};
+        \node[anchor=north](HB_d1) at (6.9, 2){.};
+        \node[anchor=north](HB_d2) at (6.9, -2){.};
+
+        \path[->] (HB) edge node {}(HB_d1);
+        \path[->] (HB) edge node {}(HB_d2);
+        \path(HB_d1) edge [bend left] node {}(HB_d2);
+
+        \node[anchor=north](D) at (7.8, 0){\(D\)};
+        \node[anchor=north](D_d1) at (10.8, 2){.};
+        \node[anchor=north](D_d2) at (10.8, -2){.};
+
+        \path[->] (D) edge node {}(D_d1);
+        \path[->] (D) edge node {}(D_d2);
+        \path(D_d1) edge [bend left] node {}(D_d2);
+    \end{tikzpicture}
+    \caption*{Figure 2 (revisited): Imperfect information Extensive Form Game 
+    between the distributor and the 2 queueing systems}
+\end{figure}
+
+As described in section \ref{sec:model_overview} queueing system \(A\) decides
+on a strategy, then queueing system \(B\) chooses its own threshold, unaware 
+of the first queueing system's choice.
+Finally, the distributor makes its choice based on the strategies that the 
+queueing systems chose to play.
+
+The problem can be formulated by 3 matrices; the two payoff matrices of the 
+normal form game and the routing matrix.
+The payoff matrices and their utilities are defined by equations 
+(\ref{eq:payoff-entry}) and (\ref{eq:payoff_matrices}) is section 
+\ref{sec:model_overview}:
+
+\begin{equation*}
+    A = 
+    \begin{pmatrix}
+        U_{1,1}^A & U_{1,2}^A & \dots & U_{1,N_B}^A \\
+        U_{2,1}^A & U_{2,2}^A & \dots & U_{2,N_B}^A \\
+        \vdots & \vdots & \ddots & \vdots \\
+        U_{N_A,1}^A & U_{N_A,2}^A & \dots & U_{N_A,N_B}^A \\
+    \end{pmatrix},
+    B = 
+    \begin{pmatrix}
+        U_{1,1}^B & U_{1,2}^B & \dots & U_{1,N_B}^B \\
+        U_{2,1}^B & U_{2,2}^B & \dots & U_{2,N_B}^B \\
+        \vdots & \vdots & \ddots & \vdots \\
+        U_{N_A,1}^B & U_{N_A,2}^B & \dots & U_{N_A,N_B}^B \\
+    \end{pmatrix}
+    \tag{\ref{eq:payoff_matrices} revisited}
+\end{equation*}
+
+Similarly, the entries of the routing matrix are defined by equation 
+(\ref{eq:obj_distributor}):
+\begin{equation*}
+    p_A, p_B \quad s.t. \quad \alpha P(L_A) + (1 - \alpha) B_A = \alpha P(L_B) 
+    + (1 - \alpha) B_B \tag{\ref{eq:obj_distributor} revisited}
+\end{equation*}
+
+Equation \ref{eq:obj_distributor} is properly defined and explained in section 
+\ref{sec:model_overview}.
+Thus, using equation \ref{eq:obj_distributor} for all possible sets of 
+thresholds we can get the full routing matrix that consists of the proportions
+to send to queueing system A (\(p_A\)) and to queueing system B (\(p_B\)).
+
+\begin{equation}\label{eq:routing_matrix}
+    R_A = 
+    \begin{pmatrix}
+        (p_{1,1}^A, p_{1,1}^B) & (p_{1,2}^A, p_{1,2}^B) & \dots & 
+        (p_{1,N_B}^A, p_{1,N_B}^B) \\
+        (p_{2,1}^A, p_{2,1}^B) & (p_{2,2}^A, p_{2,2}^B) & \dots & 
+        (p_{2,N_B}^A, p_{2,N_B}^B) \\
+        \vdots & \vdots & \ddots & \vdots \\
+        (p_{N_A,1}^A, p_{N_A,1}^B) & (p_{N_A,2}^A, p_{N_A,2}^B) & \dots & 
+        (p_{N_A,N_B}^A, p_{N_A,N_B}^B) \\
+    \end{pmatrix}
+\end{equation}
+
+The game can thus be partitioned into a normal form game between the
+two queueing systems and then finding the distributor's best strategy.
 

### 2021-09-28 sections/methodology/main.tex
Minor change in some of the mathematics
Write Backwards Induction subsection

@@
 (\ref{eq:obj_distributor}):
+% TODO: Make sure this is defined PROPERLY and CONSISTENTLY in model_overview section or here in model_overview section or here
 \begin{equation*}
-    p_A, p_B \quad s.t. \quad \alpha P(L_A) + (1 - \alpha) B_A = \alpha P(L_B) 
-    + (1 - \alpha) B_B \tag{\ref{eq:obj_distributor} revisited}
+    (p_A, p_B) \quad s.t. \quad 
+    \alpha L_A(p_A) + (1 - \alpha) B_A(p_A) = 
+    \alpha L_B(p_B) + (1 - \alpha) B_B(p_B)
+    \tag{\ref{eq:obj_distributor} revisited}
 \end{equation*}
@@
 \begin{equation}\label{eq:routing_matrix}
-    R_A = 
+    R = 
     \begin{pmatrix}
@@
 
+Note that since \(p_{i,j}^A + p_{i,j}^B = 1\) the routing matrix needs only to
+store one of the two values; either \(p_{i,j}^A\) or \(p_{i,j}^B\).
+Thus, the routing matrix \(R\) can be simplified to:
+
+\begin{equation}\label{eq:routing_matrix_simplified}
+    R = 
+    \begin{pmatrix}
+        p_{1,1}^A & p_{1,2}^A & \dots & p_{1,N_B}^A \\
+        p_{2,1}^A & p_{2,2}^A & \dots & p_{2,N_B}^A \\
+        \vdots & \vdots & \ddots & \vdots \\
+        p_{N_A,1}^A & p_{N_A,2}^A & \dots & p_{N_A,N_B}^A \\
+    \end{pmatrix}
+\end{equation}
+
 The game can thus be partitioned into a normal form game between the
@@
 
+In order to populate the payoff matrices and the routing matrix the method
+of backwards induction is used.
+Consider figure \ref{fig:imperfect-info-game} and the flow of the game that was
+described (i.e. \(Q_A, Q_B \rightarrow D\)).
+Due to the fact that the payoff matrices \(A\) and \(B\) depend on the routing 
+matrix \(R\) the entries of the matrices are calculated in a backwards way 
+(\(D \rightarrow Q_A, Q_B\)). 
+Thus for every pair of strategies \(T_A, T_B\), the proportion of individuals 
+that are to be transported to each queueing system is calculated first.
+
+Consider a game where the capacities of the two systems are \(N_A = 4\) and 
+\(N_B = 3\).
+The strategy space of players \(Q_A\) and \(Q_B\) would then be 
+\(T_A = \{1, 2, 3, 4\}\) and \(T_B = \{1, 2, 3\}\) respectively.
+Now, starting from an arbitrary starting point of \(T_A=1\) and \(T_B=1\), the
+corresponding entry of the routing matrix the routing matrix can be calculated.
+Using equation \ref{eq:obj_distributor} for \(T_A=1\) and \(T_B=1\):
+
+\begin{equation*}
+    (p_A, p_B) \quad s.t. \quad 
+    \alpha L_A(p_A) + (1 - \alpha) B_A(p_A) = 
+    \alpha L_B(p_B) + (1 - \alpha) B_B(p_B)
+\end{equation*}
+
+The above equation can be solved by using Brent's bisection algorithm.
+% TODO: Cite Brent's algorithm
+The calculated value of \(p_A\) corresponds to the entry on the first row and 
+first column of the routing matrix:
+
+\begin{equation}\label{eq:routing_matrix_1_1}
+    R = 
+    \begin{pmatrix}
+        p_{1,1}^A & - & - \\
+        - & - & - \\
+        - & - & - \\
+        - & - & - \\
+    \end{pmatrix}
+\end{equation}
+
+In fact all remaining values of the routing matrix can be calculated by
+solving \(N \times M\) similar equations using Brent's bisection algorithm.
+Therefore, having calculated the entire routing matrix the payoff matrices can
+be calculated.
+Consider once again the case of \(T_A=1, T_B=1\).
+
+% TODO: Make sure this is defined PROPERLY and CONSISTENTLY in model_overview section or here
+\begin{equation*}
+    U_{1, 1}^A = \quad 1 -\left( 
+        \hat{P} - P(W_A < R) 
+    \right)^2,
+    \quad
+    U_{1, 1}^B = \quad 1 -\left( 
+        \hat{P} - P(W_B < R) 
+    \right)^2 \tag{\ref{eq:payoff-entry} revisited}
+\end{equation*}
+
+These are the utilities of players \(A\) and \(B\) when both players choose a
+strategy of \(T = 1\).
+% TODO: Change R everywhere to t
+Here \(R\) is the predefined waiting time target to be met by a percentage of 
+individuals \( \hat{P} \) and \(P(W_i < R)\) is properly defined in section
+\ref{sec:proportion_within_target}.
+
+\begin{equation}\label{eq:payoff_matrices_1_1}
+    A = 
+    \begin{pmatrix}
+        U_{1, 1}^A & - & - \\
+        - & - & - \\
+        - & - & - \\
+        - & - & - \\
+    \end{pmatrix}, \quad
+    B = 
+    \begin{pmatrix}
+        U_{1, 1}^B & - & - \\
+        - & - & - \\
+        - & - & - \\
+        - & - & - \\
+    \end{pmatrix}
+\end{equation}
+
+Similar to the routing matrix, the above procedure can be repeated for all 
+possible values of \(T_A\) and \(T_B\) to populate all entries of the payoff 
+matrices.
+
 \subsection{Nash Equilibrium}

### 2021-09-30 sections/appendix/waiting_time_formula/main.tex
Apply changes based on Alex's suggestions
Changes to Methodology and Model overview sections
- Chnages in some notation
- Define expressions only once and then just reference them
- Changes in some labels (including some more sections)
- Other minor rewordings

@@
 
-Now just like in the type 1 individuals case the sojourn time is needed. 
+Now, like in the type 1 individuals case, the sojourn time is needed. 
 For type 2 individuals whenever individuals are at any row apart from the 
@@
 
-\begin{equation} \label{eq:waiting-time-at-each-state-type-1}
+\begin{equation} \label{eq:waiting_time_at_each_state_type_1}
     w^{(1)}(u,v) = 
@@
 
-\begin{equation} \label{eq:waiting-time-at-each-state-type-2}
+\begin{equation} \label{eq:waiting_time_at_each_state_type_2}
     w^{(2)}(u,v) = 
@@
 
-\begin{equation} \label{eq:recursive-waiting-time-type-1}
+\begin{equation} \label{eq:recursive_waiting_time_type_1}
     W^{(1)} = \frac{\sum_{(u,v) \in S_A^{(1)}} w^{(1)}(u,v) 
@@
 
-\begin{equation}\label{eq:recursive-waiting-time-type-2}
+\begin{equation}\label{eq:recursive_waiting_time_type_2}
     W^{(2)} = \frac{\sum_{(u,v) \in S_A^{(2)}} w^{(2)}(u,v) \pi_{(u,v)}}

### 2021-09-30 sections/healthcare_application/main.tex
Minor changes to other sections
Changes to Methodology and Model overview sections
- Chnages in some notation
- Define expressions only once and then just reference them
- Changes in some labels (including some more sections)
- Other minor rewordings

@@
     \item \( \alpha \in [0, 1] \) : \textit{Weighting} of blocking time and 
-    lost individuals (equation \ref{eq:obj-distributor})
+    lost individuals (equation \ref{eq:obj_distributor})
 \end{itemize}
@@
 EMS knows the strategies that each ED is playing (figure 
-\ref{fig:imperfect-info-game}). This corresponds to reacting to experienced delays.
+\ref{fig:imperfect_info_game}). This corresponds to reacting to experienced delays.
 
@@
 the game, but also how that outcome is reached.
-Consider figure \ref{fig:ard-by-itself}. 
+Consider figure \ref{fig:ard_by_itself}. 
 By running asymmetric replicator dynamics on the system the behaviour that 
@@
     \caption{Asymmetric replicator dynamics run}
-    \label{fig:ard-by-itself}
+    \label{fig:ard_by_itself}
 \end{figure}

### 2021-09-30 sections/methodology/main.tex
Changes to Methodology and Model overview sections
- Chnages in some notation
- Define expressions only once and then just reference them
- Changes in some labels (including some more sections)
- Other minor rewordings

@@
 and \(p_A + p_B = 1\).
-Figure \ref{fig:imperfect-info-game} shows a diagrammatic 
-representation of the game to be played and the decisions to be made.
-
-\begin{figure}[ht]
-    \centering
-    \begin{tikzpicture}[-, node distance = 3cm, scale=0.8]
-        \node[anchor=north](HA){\(Q_A\)};
-        \node[anchor=north](HA_d1) at (3, 2){.};
-        \node[anchor=north](HA_d2) at (3, -2){.};
-
-        \path[->] (HA) edge node {}(HA_d1);
-        \path[->] (HA) edge node {}(HA_d2);
-        \path (HA_d1) edge [bend left] node {}(HA_d2);
-        \path (HA_d1) [dashed] edge node {}(HA_d2);
-
-        \node[anchor=north](HB) at (4.1, 0){\(Q_B\)};
-        \node[anchor=north](HB_d1) at (6.9, 2){.};
-        \node[anchor=north](HB_d2) at (6.9, -2){.};
-
-        \path[->] (HB) edge node {}(HB_d1);
-        \path[->] (HB) edge node {}(HB_d2);
-        \path(HB_d1) edge [bend left] node {}(HB_d2);
-
-        \node[anchor=north](D) at (7.8, 0){\(D\)};
-        \node[anchor=north](D_d1) at (10.8, 2){.};
-        \node[anchor=north](D_d2) at (10.8, -2){.};
-
-        \path[->] (D) edge node {}(D_d1);
-        \path[->] (D) edge node {}(D_d2);
-        \path(D_d1) edge [bend left] node {}(D_d2);
-    \end{tikzpicture}
-    \caption*{Figure 2 (revisited): Imperfect information Extensive Form Game 
-    between the distributor and the 2 queueing systems}
-\end{figure}
-
+Figure \ref{fig:imperfect_info_game} form section \ref{sec:model_overview} 
+shows a diagrammatic representation of the game to be played and the decisions 
+to be made.
 As described in section \ref{sec:model_overview} queueing system \(A\) decides
@@
 The payoff matrices and their utilities are defined by equations 
-(\ref{eq:payoff-entry}) and (\ref{eq:payoff_matrices}) is section 
-\ref{sec:model_overview}:
+(\ref{eq:payoff_entry}) and (\ref{eq:payoff_matrices}) in section 
+\ref{sec:model_overview}.
 
-\begin{equation*}
-    A = 
-    \begin{pmatrix}
-        U_{1,1}^A & U_{1,2}^A & \dots & U_{1,N_B}^A \\
-        U_{2,1}^A & U_{2,2}^A & \dots & U_{2,N_B}^A \\
-        \vdots & \vdots & \ddots & \vdots \\
-        U_{N_A,1}^A & U_{N_A,2}^A & \dots & U_{N_A,N_B}^A \\
-    \end{pmatrix},
-    B = 
-    \begin{pmatrix}
-        U_{1,1}^B & U_{1,2}^B & \dots & U_{1,N_B}^B \\
-        U_{2,1}^B & U_{2,2}^B & \dots & U_{2,N_B}^B \\
-        \vdots & \vdots & \ddots & \vdots \\
-        U_{N_A,1}^B & U_{N_A,2}^B & \dots & U_{N_A,N_B}^B \\
-    \end{pmatrix}
-    \tag{\ref{eq:payoff_matrices} revisited}
-\end{equation*}
-
-Similarly, the entries of the routing matrix are defined by equation 
-(\ref{eq:obj_distributor}):
-% TODO: Make sure this is defined PROPERLY and CONSISTENTLY in model_overview section or here in model_overview section or here
-\begin{equation*}
-    (p_A, p_B) \quad s.t. \quad 
-    \alpha L_A(p_A) + (1 - \alpha) B_A(p_A) = 
-    \alpha L_B(p_B) + (1 - \alpha) B_B(p_B)
-    \tag{\ref{eq:obj_distributor} revisited}
-\end{equation*}
-
-Equation \ref{eq:obj_distributor} is properly defined and explained in section 
+The routing matrix holds the values \((p_A, p_B)\) which are the proportion 
+of class 2 individuals to send to to queueing system \(A\) and \(B\).
+Each pair \((p_A, p_B)\) can be calculated using equation 
+(\ref{eq:obj_distributor}).
+Equation \ref{eq:obj_distributor} is defined and explained in section 
 \ref{sec:model_overview}.
@@
 of backwards induction is used.
-Consider figure \ref{fig:imperfect-info-game} and the flow of the game that was
+Consider figure \ref{fig:imperfect_info_game} and the flow of the game that was
 described (i.e. \(Q_A, Q_B \rightarrow D\)).
@@
 corresponding entry of the routing matrix the routing matrix can be calculated.
-Using equation \ref{eq:obj_distributor} for \(T_A=1\) and \(T_B=1\):
+Using equation (\ref{eq:obj_distributor}) for \(T_A=1\) and \(T_B=1\):
+\begin{align}
+    & \alpha L_A(p_A;T_A=1;T_B=1) + (1 - \alpha) B_A(p_A;T_A=1;T_B=1) = 
+    \nonumber \\
+    & \alpha L_B(p_B;T_A=1;T_B=1) + (1 - \alpha) B_B(p_B;T_A=1;T_B=1) 
+    \label{eq:obj_distributor_1_1}
+\end{align}
 
-\begin{equation*}
-    (p_A, p_B) \quad s.t. \quad 
-    \alpha L_A(p_A) + (1 - \alpha) B_A(p_A) = 
-    \alpha L_B(p_B) + (1 - \alpha) B_B(p_B)
-\end{equation*}
-
-The above equation can be solved by using Brent's bisection algorithm.
+The values of \(p_A\) and \(p_B\) that satisfy equation 
+(\ref{eq:obj_distributor_1_1}) can be found by using Brent's bisection 
+algorithm.
 % TODO: Cite Brent's algorithm
@@
 
-% TODO: Make sure this is defined PROPERLY and CONSISTENTLY in model_overview section or here
-\begin{equation*}
-    U_{1, 1}^A = \quad 1 -\left( 
-        \hat{P} - P(W_A < R) 
-    \right)^2,
-    \quad
-    U_{1, 1}^B = \quad 1 -\left( 
-        \hat{P} - P(W_B < R) 
-    \right)^2 \tag{\ref{eq:payoff-entry} revisited}
-\end{equation*}
+\begin{align}
+    U_{1, 1}^A = 1 -\left( 
+        \hat{P} - P(W_A(T_A=1, T_B=1) < t) 
+    \right)^2 \nonumber
+    \\
+    U_{1, 1}^B = 1 -\left( 
+        \hat{P} - P(W_B(T_A=1, T_B=1) < t) 
+    \right)^2 \label{eq:payoff_entry_1_1}
+\end{align}
 
@@
 strategy of \(T = 1\).
-% TODO: Change R everywhere to t
 Here \(R\) is the predefined waiting time target to be met by a percentage of 
-individuals \( \hat{P} \) and \(P(W_i < R)\) is properly defined in section
+individuals \( \hat{P} \) and \(P(W_i < t)\) is properly defined in section
 \ref{sec:proportion_within_target}.

### 2021-10-01 sections/healthcare_application/main.tex
Move asymmetric replicator dynamics to methodology
Move from ED-EMS appllication section to Methodology section

@@
 One such model that allows for asymmetric payoffs, as is the case above, is 
-replicator dynamics.
+replicator dynamics described in section 
+(\ref{sec:methodology_learning_algorithms}).
 Stable outcomes of this algorithm will correspond to a subset of Nash
 equilibria but more importantly, will give a model of emergent behaviour.
-
-In order to analyse the strategies played by the two EDs, the learning algorithm
-asymmetric replicator dynamics is used \cite{asymmetricreplicatordynamics}.
-The two players are treated as two separate populations where each 
-individual in the population is assigned a strategy. 
-As the game progresses the proportion of each player playing each strategy 
-changes based on their previous interactions.
-The fitness of each strategy is defined as:
-
-\begin{equation}\label{eq:asymmetric_fitness}
-    f_x = Ay, \quad f_y = x^T B
-\end{equation}
-
-Here, \(x \in \mathbb{R}^{m \times 1} \) and
-\(y \in \mathbb{R}^{n \times 1}\) correspond to the proportion of individuals 
-that play each strategy on the two populations.
-Similarly, the average fitness of each strategy is defined as:
-\begin{equation}
-    \phi_x = f_x x^T, \quad \phi_y = f_y y
-\end{equation}
-
-The rate of change of strategy \( i \) of both types of individuals is captured 
-by:
-\begin{equation}
-    \frac{dx}{dt}_i = x_i((f_x)_i - \phi_x), \quad \text{ for all }i
-\end{equation}
-
-\begin{equation}
-    \frac{dy}{dt}_i = y_i((f_y)_i - \phi_y), \quad \text{ for all }i
-\end{equation}
 

### 2021-10-01 sections/methodology/main.tex
Move asymmetric replicator dynamics to methodology
Move from ED-EMS appllication section to Methodology section

@@
 The routing matrix holds the values \((p_A, p_B)\) which are the proportion 
-of class 2 individuals to send to to queueing system \(A\) and \(B\).
+of class 2 individuals to send to queueing system \(A\) and \(B\).
 Each pair \((p_A, p_B)\) can be calculated using equation 
@@
 
-\subsection{Learning Algorithms}
+\subsection{Learning Algorithms}\label{sec:methodology_learning_algorithms}
+
+In order to analyse the strategies played by the two EDs, the learning algorithm
+asymmetric replicator dynamics is used \cite{asymmetricreplicatordynamics}.
+The two players are treated as two separate populations where each 
+individual in the population is assigned a strategy.
+As the game progresses the proportion of each player playing each strategy 
+changes based on their previous interactions.
+The fitness of each strategy is defined as:
+
+\begin{equation}\label{eq:asymmetric_fitness}
+    f_x = Ay, \quad f_y = x^T B
+\end{equation}
+
+Here, \(x \in \mathbb{R}^{m \times 1} \) and
+\(y \in \mathbb{R}^{n \times 1}\) correspond to the proportion of individuals 
+that play each strategy on the two populations.
+Similarly, the average fitness of each strategy is defined as:
+\begin{equation}
+    \phi_x = f_x x^T, \quad \phi_y = f_y y
+\end{equation}
+
+The rate of change of strategy \( i \) of both types of individuals is captured 
+by:
+\begin{equation}
+    \frac{dx}{dt}_i = x_i((f_x)_i - \phi_x), \quad \text{ for all }i
+\end{equation}
+
+\begin{equation}
+    \frac{dy}{dt}_i = y_i((f_y)_i - \phi_y), \quad \text{ for all }i
+\end{equation}

### 2021-10-03 sections/methodology/main.tex
Add Nash Equilibrium subsection

@@
 
-\subsection{Nash Equilibrium}
+\subsection{Nash Equilibrium}\label{sec:methodology_nash_equilibrium}
+
+Having calculated the payoff matrices \(A\) and \(B\), several algorithms can 
+be used to help us find the Nash equilibrium of the game. 
+The Nash equilibrium is the point of the game were both players have no 
+incentive to deviate from their played strategies \cite{kreps1989nash}.
+In other words their chosen strategies are a best response to each other.
+
+The Lemke-Howson algorithm is used to get all Nash equilibria of the game 
+\cite{LemkeHowson}.
+Lemke-Howson uses best response polytopes to get one of the Nash equilibrium of
+the game. 
+By iterating over all possible dropped labels of the best response polytope all
+Nash equilibria can be acquired.
+All game theoretic calculations were done in Python using the Nashpy library 
+\cite{axelrodproject}.
 

### 2021-10-03 known.py

@@ -43,6 +43,7 @@ words = {
     "nan",
     "nansum",
     "np",
+    "nashpy",
     "num",
     "numpy",
     "Panayides",

### 2021-10-03 known.py
Update known words

@@ -13,9 +13,9 @@ words = {
     "captionpos",
     "CDF",
     "CDFs",
-    "Ciw",
-    "Ciw's",
     "ciw's",
+    "Ciw's",
+    "Ciw",
     "codegreen",
     "commentstyle",
     "DES",
@@ -26,6 +26,7 @@ words = {
     "equilibria",
     "erlang",
     "HB",
+    "Howson",
     "hypoexponential",
     "ieeetr",
     "ij",
@@ -34,6 +35,7 @@ words = {
     "keepspaces",
     "keywordcolor",
     "keywordstyle",
+    "Lemke",
     "LHS",
     "Markovian",
     "math",
@@ -42,12 +44,14 @@ words = {
     "mult",
     "nan",
     "nansum",
-    "np",
     "nashpy",
+    "np",
     "num",
     "numpy",
     "Panayides",
     "PoA",
+    "polytope",
+    "polytopes",
     "pre",
     "probs",
     "pystyle",

### 2021-10-04 sections/methodology/main.tex
Mention additional learning algorithms
- Add a sentence for fictitious play and stochastic fictitious play
- Reference the book: Thoery of learning in games
Cite Brent's bisection algorithm

@@
 (\ref{eq:obj_distributor_1_1}) can be found by using Brent's bisection 
-algorithm.
-% TODO: Cite Brent's algorithm
+algorithm~\cite{brent1973algorithms}.
 The calculated value of \(p_A\) corresponds to the entry on the first row and 
@@
 \end{equation}
+
+In addition to asymmetric replicator dynamics, the learning algorithms
+fictitious play and stochastic fictitious play \cite{fudenberg1998theory}
+were used.

### 2021-10-04 sections/methodology/main.tex
Apply suggestions from code review
Co-authored-by: Vince Knight <vincent.knight@gmail.com>

@@
 As described in section \ref{sec:model_overview} queueing system \(A\) decides
-on a strategy, then queueing system \(B\) chooses its own threshold, unaware 
+on a strategy, at the same time, queueing system \(B\) chooses its own threshold, unaware 
 of the first queueing system's choice.
@@
 
-The problem can be formulated by 3 matrices; the two payoff matrices of the 
+The utilities to each player can be represented by 3 matrices; the two payoff matrices of the 
 normal form game and the routing matrix.
@@
 Each pair \((p_A, p_B)\) can be calculated using equation 
-(\ref{eq:obj_distributor}).
+(\ref{eq:obj_distributor}) and is essentially
+a best response to the actions of the queueing systems.
 Equation \ref{eq:obj_distributor} is defined and explained in section 
@@
 The values of \(p_A\) and \(p_B\) that satisfy equation 
-(\ref{eq:obj_distributor_1_1}) can be found by using Brent's bisection 
+(\ref{eq:obj_distributor_1_1}) are here found numerically using Brent's bisection
 algorithm~\cite{brent1973algorithms}.
@@
 Having calculated the payoff matrices \(A\) and \(B\), several algorithms can 
-be used to help us find the Nash equilibrium of the game. 
-The Nash equilibrium is the point of the game were both players have no 
+be used to measure some form of emergent behaviour.
+One possibility would be to compute the Nash equilibrium
+which is the point of the game were both players have no 
 incentive to deviate from their played strategies \cite{kreps1989nash}.
@@
 
-The Lemke-Howson algorithm is used to get all Nash equilibria of the game 
+Computation of Nash equilibria can be done relatively efficiently using the Lemke Howson algorithm
 \cite{LemkeHowson}.
@@
 the game. 
-By iterating over all possible dropped labels of the best response polytope all
-Nash equilibria can be acquired.
+Other algorithms exists that will compute all Nash equilibria but 
+for large games the computational complexity becomes problematic.
 All game theoretic calculations were done in Python using the Nashpy library 
@@
 
-In order to analyse the strategies played by the two EDs, the learning algorithm
+Another approach to measuring emergent behaviour is to consider 
+the emergence itself and not just stable end points. 
+Indeed, some Nash equilibria might not arise naturally. Thus, in order to analyse the strategies played by the two EDs, the learning algorithm:
 asymmetric replicator dynamics is used \cite{asymmetricreplicatordynamics}.
-The two players are treated as two separate populations where each 
+The two players are modelled as two separate populations where each 
 individual in the population is assigned a strategy.
@@
 \(y \in \mathbb{R}^{n \times 1}\) correspond to the proportion of individuals 
-that play each strategy on the two populations.
-Similarly, the average fitness of each strategy is defined as:
+that play each strategy in each population.
+Similarly, the average fitness of each strategy is given by:
 \begin{equation}

### 2021-10-04 sections/methodology/main.tex
Fix nashpy citation
Break lines at 80 characters

@@
 As described in section \ref{sec:model_overview} queueing system \(A\) decides
-on a strategy, at the same time, queueing system \(B\) chooses its own threshold, unaware 
-of the first queueing system's choice.
+on a strategy, at the same time, queueing system \(B\) chooses its own 
+threshold, unaware of the first queueing system's choice.
 Finally, the distributor makes its choice based on the strategies that the 
@@
 
-The utilities to each player can be represented by 3 matrices; the two payoff matrices of the 
-normal form game and the routing matrix.
+The utilities to each player can be represented by 3 matrices; the two payoff 
+matrices of the normal form game and the routing matrix.
 The payoff matrices and their utilities are defined by equations 
@@
 The values of \(p_A\) and \(p_B\) that satisfy equation 
-(\ref{eq:obj_distributor_1_1}) are here found numerically using Brent's bisection
-algorithm~\cite{brent1973algorithms}.
+(\ref{eq:obj_distributor_1_1}) are here found numerically using Brent's 
+bisection algorithm~\cite{brent1973algorithms}.
 The calculated value of \(p_A\) corresponds to the entry on the first row and 
@@
 
-Computation of Nash equilibria can be done relatively efficiently using the Lemke Howson algorithm
-\cite{LemkeHowson}.
+Computation of Nash equilibria can be done relatively efficiently using the 
+Lemke Howson algorithm~\cite{LemkeHowson}.
 Lemke-Howson uses best response polytopes to get one of the Nash equilibrium of
@@
 All game theoretic calculations were done in Python using the Nashpy library 
-\cite{axelrodproject}.
+\cite{thenashpyproject}.
 
@@
 Another approach to measuring emergent behaviour is to consider 
-the emergence itself and not just stable end points. 
-Indeed, some Nash equilibria might not arise naturally. Thus, in order to analyse the strategies played by the two EDs, the learning algorithm:
-asymmetric replicator dynamics is used \cite{asymmetricreplicatordynamics}.
+the emergence itself and not only stable end points. 
+Indeed, some Nash equilibria might not arise naturally. 
+Thus, in order to analyse the strategies played by the two EDs, the learning 
+algorithm: asymmetric replicator dynamics is 
+used~\cite{asymmetricreplicatordynamics}.
 The two players are modelled as two separate populations where each 

### 2021-10-04 sections/healthcare_application/main.tex
Methodology section (#15)
* Remove TODOs that were addressed

* Minor changes to other sections

* Write intro for methodology section

* Fix minor bibliography issue

* Minor change in some of the mathematics

* Write Backwards Induction subsection

* Changes to Methodology and Model overview sections

- Chnages in some notation
- Define expressions only once and then just reference them
- Changes in some labels (including some more sections)
- Other minor rewordings

* Move asymmetric replicator dynamics to methodology

Move from ED-EMS appllication section to Methodology section

* Add Nash

@@
 The most commonly used method for analysing normal form games is the Nash 
-equilibrium \cite{kreps1989nash}. 
-The Nash equilibrium is the point of the game were players have no incentive to 
-deviate from their strategy.
+equilibrium described in section \ref{sec:methodology_nash_equilibrium}
 Consider the following game:

### 2021-10-04 sections/model_overview/main.tex
Methodology section (#15)
* Remove TODOs that were addressed

* Minor changes to other sections

* Write intro for methodology section

* Fix minor bibliography issue

* Minor change in some of the mathematics

* Write Backwards Induction subsection

* Changes to Methodology and Model overview sections

- Chnages in some notation
- Define expressions only once and then just reference them
- Changes in some labels (including some more sections)
- Other minor rewordings

* Move asymmetric replicator dynamics to methodology

Move from ED-EMS appllication section to Methodology section

* Add Nash

@@
 
-This is a standard Normal form game~\cite{Maschler2013},  
+This is a standard normal form game~\cite{Maschler2013},  
 in that each player in this game has their own objectives which they aim to 
@@
 \begin{equation}
-    P(W < R) \geq \hat{P}
+    P(W < t) \geq \hat{P}
 \end{equation}
 
-where \(W\) is the mean waiting time of all individuals, \(R\) is the time 
+where \(W\) is the mean waiting time of all individuals, \(t\) is the time 
 target and \(\hat{P}\) is the percentage of individuals need to be within that 
@@
 \begin{equation}
-    \arg \max_{T_i} \quad P(W_i < R)
+    \arg \max_{T_i} \quad P(W_i < t)
 \end{equation}
@@
 
-\begin{equation}\label{eq:obj-queueing-systems}
-    \arg \max_{T_i} \quad -\left( \hat{P} - P(W_i < R) \right)^2
+\begin{equation}\label{eq:obj_queueing_systems}
+    \arg \max_{T_i} \quad -\left( \hat{P} - P(W_i < t) \right)^2
 \end{equation}
@@
 goals to satisfy.
-The strategy set of the third player is the proportion \(0 \leq p \leq 1\) of 
-individuals it sends to the first queueing system (the proportion \(1 - q\) is 
-sent to the second queueing system).
+The strategy set of the third player is the proportion \(0 \leq p_A \leq 1\) of 
+individuals it sends to the first queueing system (the proportion 
+\(p_B = 1 - p_A\) is sent to the second queueing system).
 In addition, the distributor aims to minimise any potential blockages
 that may occur, given the pair of thresholds chosen by the two queueing systems.
-Thus, its objective is to minimise the blocked time of the individuals 
+Thus, its objective is to minimise the blocked time of the individuals (\(B_i\))
 that they send to the two queueing systems.
 Apart from the time being blocked, an additional aspect that may affect the 
-decision of the distributor is the proportion of lost individuals.
+decision of the distributor is the proportion of lost individuals (\(L_i\)).
 Equation \ref{eq:obj_distributor} can be used to capture a mixture 
-between the two objectives.
-
-\begin{equation}\label{eq:obj_distributor}
-    \alpha P(L_A) + (1 - \alpha) B_A = 
-    \alpha P(L_B) + (1 - \alpha) B_B
-\end{equation}
+between the two objectives \(L_i\) and \(B_i\) where \(i \in \{A, B\}\).
+\begin{equation*}\label{eq:obj_distributor}
+    (p_A, p_B) \quad s.t. \quad 
+    \alpha L_A(p_A) + (1 - \alpha) B_A(p_A) = 
+    \alpha L_B(p_B) + (1 - \alpha) B_B(p_B)
+\end{equation*}
 
@@
 
-Using equations \ref{eq:obj-queueing-systems} and \ref{eq:obj_distributor} gives
-an imperfect information extensive form game. 
+Using equations (\ref{eq:obj_queueing_systems}) and (\ref{eq:obj_distributor}) 
+gives an imperfect information extensive form game. 
 An imperfect information game is defined as an extensive form game where some 
@@
 hidden is the threshold that each of the first two players chooses to play.
-In other words, each queueing system chooses to play a strategy without the 
+In other words, each queueing system chooses to play a strategy without 
 knowing the other system's strategy.
@@
 individuals among the two systems in order to minimise the time that its 
-individuals will be blocked. Figure \ref{fig:imperfect-info-game} illustrates this.
+individuals will be blocked. Figure \ref{fig:imperfect_info_game} illustrates this.
 
@@
     and the 2 queueing systems}
-    \label{fig:imperfect-info-game}
+    \label{fig:imperfect_info_game}
 \end{figure}
@@
 In order to define the normal form game the two payoff matrices of the players 
-are required. From equation \ref{eq:obj-queueing-systems} the utilities of the
+are required. From equation \ref{eq:obj_queueing_systems} the utilities of the
 players can be formulated as:
 
-\begin{equation} \label{eq:payoff-entry}
-    U_{T_1, T_2}^i = \quad -\left( 
-        \hat{P} - P(W_i < R) 
-    \right)^2
+\begin{equation} \label{eq:payoff_entry}
+    U_{T_1, T_2}^i = -\left( 
+        \hat{P} - P(W_i < t) 
+    \right)^2 \quad \textbf{where } i \in \{A, B\}
 \end{equation}
@@
         U_{N_A,1}^A & U_{N_A,2}^A & \dots & U_{N_A,N_B}^A \\
-    \end{pmatrix},
+    \end{pmatrix}, \,
     B = 

### 2021-10-04 known.py

@@ -13,9 +13,9 @@ words = {
     "captionpos",
     "CDF",
     "CDFs",
-    "Ciw",
-    "Ciw's",
     "ciw's",
+    "Ciw's",
+    "Ciw",
     "codegreen",
     "commentstyle",
     "DES",
@@ -26,6 +26,7 @@ words = {
     "equilibria",
     "erlang",
     "HB",
+    "Howson",
     "hypoexponential",
     "ieeetr",
     "ij",
@@ -34,6 +35,7 @@ words = {
     "keepspaces",
     "keywordcolor",
     "keywordstyle",
+    "Lemke",
     "LHS",
     "Markovian",
     "math",
@@ -42,11 +44,14 @@ words = {
     "mult",
     "nan",
     "nansum",
+    "nashpy",
     "np",
     "num",
     "numpy",
     "Panayides",
     "PoA",
+    "polytope",
+    "polytopes",
     "pre",
     "probs",
     "pystyle",

### 2021-10-11 sections/introduction/main.tex
Add initial draft of introduction
- First line (hook)
- Literature review methodology driven (game theory - queueing theory)
- Establish research problem
- Research objectives
- Map out the paper

\section{Introduction}

% 1. Introduce the topic (Write a hook) [X]
% 2. Describe the background [\]
%   - Literature review []
%       - Strategic gaming in healthcare []
%       - Wider search of news reports -> BMJ []
%       - Pressures in hospital system?? []
%   - Gap in the literature []
%   - Problem driven AND Methodology driven []
% 3. Establish the research problem [\]
%   - Bullet points about why paper is important []
% 4. Specify the objective(s) [\]
%   - What is the objective? []
%   - So what? []
% 5. Map out the paper []

% 1.
A huge issue for ambulances in the United Kingdom is that they stay 
parked outside hospitals for a huge amount of time. 
This is a problem for the ambulance service, since the longer ambulances are
blocked in the hospital's parking space the longer the patients in them will
have to wait to receive their treatment but also the longer future patients 
will be stuck waiting for an ambulance.
This paper aims to describe a game theoretic model that is informed by a 
queueing model motivated by this scenario.

% 2.1 Problem driven Literature
There are various news reports that indicate that this is in fact an ongoing 
issue that affects both the patients and the ambulance service.
% TODO: Reference papers/news reports

% 2.2 Methodology driven Literature
In the past a number of papers have been published that touch upon the use of 
queueing models together with game theoretic concepts.
In \cite{FirmCompetition} the authors study a simultaneous price competition 
between two firms and calculate the Nash equilibrium both for identical and 
heterogeneous firms. 
The authors have also extended their model in \cite{FirmCompetition2} by 
allowing the players (firms) to choose capacities. 
A main result from this paper was that equilibria, where both firms operate
together, are not socially optimal while when both firms operate as a monopoly 
they are.
Another extension of \cite{FirmCompetition} was introduced in 
\cite{FirmCompetitionExtension} where a long-run version of the competition was 
considered that also had capacity as a decision variable.
% Moreover, \cite{touati2004performance} analyse the case where there are two 
% M/M/1 queues with capacities \(\mu_1, \mu_2\) and prices \(p_1 > p_2\).
An additional paper that focuses on competition is \cite{fan2009short} where
the authors created a competition between 2 sellers with products having 
different implementation costs.
In \cite{sadat2015can} a healthcare application was studied where patients 
could choose between two hospitals, where a utility function is derived that is
based on patients' perceived quality of life.

% 3.
The emergency departments (EDs) in the United Kingdom have to follow some set 
of regulations imposed to them by the NHS.
One of these regulations is that 95\% of patients that arrive at the ED should 
be admitted, transferred or discharged within four hours.
This is where gaming behaviour might be observed between the EDs and the EMS.
An assumption of this work is that some managerial decision making is involved
in choosing when to start blocking ambulances.
This paper touches upon the following new aspects:
\begin{itemize}
    \item The emergence of gaming behaviour in the emergency department
    \item A queueing model with 2 consecutive waiting spaces
\end{itemize}

% 4.
The main focus of this research is the construction of a 3-player game 
theoretic model between two queueing systems and a service that distributes 
individuals to them. 
The resultant model will then be used to explore the emergent dynamics between 
the three players.

% 5.
This paper first gives an overview of the game theoretic model that was built, 
then goes on to describe how the queueing models were constructed and then 
follows with how the methodology that was used to build the game.
Finally, there is a section that describes how this game theoretic framework
can be applied at the interface between the Emergency Medical Services (EMS) 
and Emergency Department (EDs).

% TODO: If this is one paper remove the queueing model part

% Paper suggested by Paul:https://www.magonlinelibrary.com/doi/pdf/10.12968/prma.2021.31.4.28?casa_token=cuKE80im0tsAAAAA%3AFYuYJsk0Qd9XLvPAaDmZVUW-BPU8xJmHGeDRRPbfdCld4cJiBs3-mmoBxewtCLtSXndrZWTbqUbe1g&
% Paper suggested by Vince: Vince's and Izabella

### 2021-10-12 sections/introduction/main.tex
Cite papers on networks with tandem queues

@@
 
+Another specific part of this research is the construction of a queueing system
+with two tandem queues.
+In \cite{d2015pure} the authors explore threshold joining strategies in a 
+Markov model that has two tandem queues.
+Another great example is the one described in \cite{burnetas2013customer}
+where they investigated a network of multiple tandem queues where customers 
+decide which queue to attend before joining.
+Similarly, in \cite{bacsar2002stackelberg} the authors examine a network of 
+\(N\) tandem M/M/1 queues and with multi-type customers. 
+The customers in this paper react to a price \(p\) by picking demand rates that 
+maximise utility.
+In \cite{veltman2005equilibrium} a profit maximisation problem is studied that
+has an M/M/1 queue and a parking service providing complementary service while
+the customer is in service. 
+The problem was later extended by \cite{sun2009equilibrium} where they 
+considered arrivals of batches that can share the parking service.
+Finally, \cite{afeche2007decentralized} examines a tandem network of two M/M/1 
+queues that are ran by two different profit-maximising service providers and 
+receive three different types of customers.
+
 % 3.

### 2021-10-12 sections/introduction/main.tex
Remove unused citation
Minor changes
- Remove unnecessary comments
- Apply suggestions based on alex and proselint
- Reference a paper on ED pressures
- Reference paper on 2-dimensional Markov model with game theory
- Clearly state the objective and the "so what?"
- Other minor changes

@@
 
-% 1. Introduce the topic (Write a hook) [X]
-% 2. Describe the background [\]
-%   - Literature review []
-%       - Strategic gaming in healthcare []
-%       - Wider search of news reports -> BMJ []
-%       - Pressures in hospital system?? []
-%   - Gap in the literature []
-%   - Problem driven AND Methodology driven []
-% 3. Establish the research problem [\]
-%   - Bullet points about why paper is important []
-% 4. Specify the objective(s) [\]
-%   - What is the objective? []
-%   - So what? []
-% 5. Map out the paper []
-
-% 1.
 A huge issue for ambulances in the United Kingdom is that they stay 
@@
 
-% 2.1 Problem driven Literature
 There are various news reports that indicate that this is in fact an ongoing 
 issue that affects both the patients and the ambulance service.
-% TODO: Reference papers/news reports
+Emergency departments (EDs) are constantly under a lot of pressure to meet 
+targets and satisfy regulations \cite{EmergencyDepartmentWinterPressures}.
+These additional targets imply that the ED staff must also be able to manage 
+the flow of patients.
+% TODO: Reference papers/news reports + Wider search of news reports -> BMJ
 
-% 2.2 Methodology driven Literature
 In the past a number of papers have been published that touch upon the use of 
@@
 considered that also had capacity as a decision variable.
-% Moreover, \cite{touati2004performance} analyse the case where there are two 
-% M/M/1 queues with capacities \(\mu_1, \mu_2\) and prices \(p_1 > p_2\).
+In \cite{knight2017measuring} a normal form game is built that is informed by a 
+two-dimensional Markov chain in order to model interactions between critical
+care units.
 An additional paper that focuses on competition is \cite{fan2009short} where
@@
 receive three different types of customers.
+% TODO: State the gap in the literature
 
-% 3.
-The emergency departments (EDs) in the United Kingdom have to follow some set 
-of regulations imposed to them by the NHS.
+The EDs in the United Kingdom have to follow some set of regulations imposed to 
+them by the NHS.
 One of these regulations is that 95\% of patients that arrive at the ED should 
@@
     \item The emergence of gaming behaviour in the emergency department
-    \item A queueing model with 2 consecutive waiting spaces
+    \item A queueing model with 2 consecutive waiting spaces where one would 
+    serve as a parking space for the ambulances
 \end{itemize}
-
-% 4.
-The main focus of this research is the construction of a 3-player game 
-theoretic model between two queueing systems and a service that distributes 
-individuals to them. 
+The focus of this research is the construction of a 3-player game theoretic 
+model between two queueing systems and a service that distributes individuals
+to them. 
 The resultant model will then be used to explore the emergent dynamics between 
 the three players.
+The model is then applied to the healthcare scenario between two EDs and the 
+EMS while looking into the inefficiencies that emerge and ways to apply some 
+incentive mechanisms to improve them.
 
-% 5.
 This paper first gives an overview of the game theoretic model that was built, 
 then goes on to describe how the queueing models were constructed and then 
-follows with how the methodology that was used to build the game.
+follows with the methodology that was used to build the game.
 Finally, there is a section that describes how this game theoretic framework
-can be applied at the interface between the Emergency Medical Services (EMS) 
-and Emergency Department (EDs).
+can be applied at the interface between the EMS and EDs together with some 
+analysis on the behaviour that is observed.
 
 % TODO: If this is one paper remove the queueing model part
-
-% Paper suggested by Paul:https://www.magonlinelibrary.com/doi/pdf/10.12968/prma.2021.31.4.28?casa_token=cuKE80im0tsAAAAA%3AFYuYJsk0Qd9XLvPAaDmZVUW-BPU8xJmHGeDRRPbfdCld4cJiBs3-mmoBxewtCLtSXndrZWTbqUbe1g&
-% Paper suggested by Vince: Vince's and Izabella

### 2021-10-12 known.py
Update known words

@@ -45,6 +45,7 @@ words = {
     "nan",
     "nansum",
     "nashpy",
+    "NHS",
     "np",
     "num",
     "numpy",

### 2021-10-14 sections/introduction/main.tex
Include more references of news reports

@@
 
+Emergency departments (EDs) are constantly under a lot of pressure to meet 
+targets and satisfy regulations \cite{EmergencyDepartmentWinterPressures}.
 There are various news reports that indicate that this is in fact an ongoing 
 issue that affects both the patients and the ambulance service.
-Emergency departments (EDs) are constantly under a lot of pressure to meet 
-targets and satisfy regulations \cite{EmergencyDepartmentWinterPressures}.
-These additional targets imply that the ED staff must also be able to manage 
-the flow of patients.
-% TODO: Reference papers/news reports + Wider search of news reports -> BMJ
+Due to this blockage patients may spend a considerable amount of time in the 
+back of an ambulance waiting to be dispatched to the ED \cite{mirror}, 
+\cite{thenews}, \cite{bmj}.
+On the other hand though this can also cause ambulances to waste valuable time 
+where they could be attending to new patients \cite{eastanglia}.
 

### 2021-10-14 sections/introduction/main.tex
Some minor changes
- Discuss cited news report a bit more
- Rephrase one of the objectives
- Other minor changes

--- 2021-10-12 sections/introduction/main.tex
@@
 will be stuck waiting for an ambulance.
-This paper aims to describe a game theoretic model that is informed by a 
+This paper aims to describe a game theoretic model informed by an underlying 
 queueing model motivated by this scenario.
 
-There are various news reports that indicate that this is in fact an ongoing 
-issue that affects both the patients and the ambulance service.
 Emergency departments (EDs) are constantly under a lot of pressure to meet 
 targets and satisfy regulations \cite{EmergencyDepartmentWinterPressures}.
-These additional targets imply that the ED staff must also be able to manage 
-the flow of patients.
-% TODO: Reference papers/news reports + Wider search of news reports -> BMJ
+There are various news reports that indicate that this is in fact an ongoing 
+issue that affects both the patients and the emergency medical services (EMS).
+Due to this blockage patients may spend a considerable amount of time in the 
+back of an ambulance waiting to be dispatched to the ED.
+Examples of such reports are \cite{mirror}, \cite{thenews} and \cite{bmj} where
+the impact that this issue has on patients is shown. 
+Furthermore, this is also a huge issue for the EMS.
+By blocking the ambulances at the hospital's parking space, valuable time is 
+wasted where ambulances could be attending new patients \cite{eastanglia}.
 
@@
 receive three different types of customers.
-% TODO: State the gap in the literature
 
@@
 \begin{itemize}
-    \item The emergence of gaming behaviour in the emergency department
+    \item The emergence of gaming behaviour between EDs and the EMS.
     \item A queueing model with 2 consecutive waiting spaces where one would 

### 2021-10-18 sections/introduction/main.tex
Apply minor suggestions from code review
Co-authored-by: Vince Knight <vincent.knight@gmail.com>

@@
 
-A huge issue for ambulances in the United Kingdom is that they stay 
+An important issue for ambulances in the United Kingdom is that they stay 
 parked outside hospitals for a huge amount of time. 
@@
 Emergency departments (EDs) are constantly under a lot of pressure to meet 
-targets and satisfy regulations \cite{EmergencyDepartmentWinterPressures}.
+targets and satisfy regulations~\cite{EmergencyDepartmentWinterPressures}.
 There are various news reports that indicate that this is in fact an ongoing 
@@
 back of an ambulance waiting to be dispatched to the ED.
-Examples of such reports are \cite{mirror}, \cite{thenews} and \cite{bmj} where
+Examples of such reports are \cite{mirror, thenews, bmj} where
 the impact that this issue has on patients is shown. 
@@
 
-In the past a number of papers have been published that touch upon the use of 
+A number of papers have been published that touch upon the use of 
 queueing models together with game theoretic concepts.
@@
 The EDs in the United Kingdom have to follow some set of regulations imposed to 
-them by the NHS.
+them by the National Health Service (NHS).
 One of these regulations is that 95\% of patients that arrive at the ED should 

### 2021-10-18 sections/introduction/main.tex
Add additional changes based on PR review
- Add more citations
- Explain further some of the references
- Other minor changes

@@
 
+% TODO: If this is one paper remove the queueing model part
+
 An important issue for ambulances in the United Kingdom is that they stay 
-parked outside hospitals for a huge amount of time. 
+parked outside hospitals for a huge amount of time~\cite{clarey2014ambulance}. 
 This is a problem for the ambulance service, since the longer ambulances are
@@
 back of an ambulance waiting to be dispatched to the ED.
-Examples of such reports are \cite{mirror, thenews, bmj} where
+Examples of such reports are~\cite{mirror, thenews, bmj} where
 the impact that this issue has on patients is shown. 
@@
 By blocking the ambulances at the hospital's parking space, valuable time is 
-wasted where ambulances could be attending new patients \cite{eastanglia}.
+wasted where ambulances could be attending new patients~\cite{eastanglia}.
 
@@
 queueing models together with game theoretic concepts.
-In \cite{FirmCompetition} the authors study a simultaneous price competition 
-between two firms and calculate the Nash equilibrium both for identical and 
-heterogeneous firms. 
-The authors have also extended their model in \cite{FirmCompetition2} by 
+In~\cite{FirmCompetition} the authors study a simultaneous price competition 
+between two firms that are modelled as two distinct queueing systems with a 
+fixed capacity and a combined arrival rate.
+They calculate the Nash equilibrium both for identical and heterogeneous firms
+and show that for the former a pure NE always exist and for the latter a unique
+equilibrium exists where only one firm operates.
+The authors have also extended their model in~\cite{FirmCompetition2} by 
 allowing the players (firms) to choose capacities. 
@@
 they are.
-Another extension of \cite{FirmCompetition} was introduced in 
-\cite{FirmCompetitionExtension} where a long-run version of the competition was 
-considered that also had capacity as a decision variable.
-In \cite{knight2017measuring} a normal form game is built that is informed by a 
+Another extension of~\cite{FirmCompetition} was introduced 
+in~\cite{FirmCompetitionExtension} where a long-run version of the competition 
+was considered that also had capacity as a decision variable.
+In~\cite{knight2017measuring} a normal form game is built that is informed by a 
 two-dimensional Markov chain in order to model interactions between critical
 care units.
-An additional paper that focuses on competition is \cite{fan2009short} where
-the authors created a competition between 2 sellers with products having 
-different implementation costs.
-In \cite{sadat2015can} a healthcare application was studied where patients 
+An additional paper that focuses on competition is~\cite{fan2009short} where
+the authors created a competition between two sellers where seller 1 supplies 
+a product instantly and seller 2 is modelled as a make-to-order M/M/1 queue.
+The game that is played requires the two sellers to make a choice on the price 
+of the product and then seller 2 to set a capacity that guarantees a maximum 
+expected delay.
+In~\cite{sadat2015can} a healthcare application was studied where patients 
 could choose between two hospitals, where a utility function is derived that is
 based on patients' perceived quality of life.
+In~\cite{knight2013selfish} the impact that individual behaviour has on the 
+efficiency of public services is investigated.
+The authors place the individuals' choices between different public services 
+within the formulation of routing games and measure inefficiencies using a 
+concept known as the price of anarchy (\(PoA\))~\cite{koutsoupias1999worst}.
+They show that the price of anarchy increases with worth of service and that is
+low for systems with insufficient capacities.
+In \cite{deo2011centralized} the authors study the network effect of ambulance 
+diversion by proposing a non-cooperative game between two EDs that are modelled
+as a queueing network.
+Each ED's objective is to minimise its own waiting time and chooses a diversion
+threshold based on the patients it has.
+In equilibrium both EDs choose to divert ambulances in order to avoid getting
+arrivals from the other ED.
 
 Another specific part of this research is the construction of a queueing system
-with two tandem queues.
-In \cite{d2015pure} the authors explore threshold joining strategies in a 
+with a tandem buffer with a single service centre.
+In~\cite{d2015pure} the authors explore threshold joining strategies in a 
 Markov model that has two tandem queues.
-Another great example is the one described in \cite{burnetas2013customer}
+Another great example is the one described in~\cite{burnetas2013customer}
 where they investigated a network of multiple tandem queues where customers 
 decide which queue to attend before joining.
-Similarly, in \cite{bacsar2002stackelberg} the authors examine a network of 
+Similarly, in~\cite{bacsar2002stackelberg} the authors examine a network of 
 \(N\) tandem M/M/1 queues and with multi-type customers. 
@@
 maximise utility.
-In \cite{veltman2005equilibrium} a profit maximisation problem is studied that
-has an M/M/1 queue and a parking service providing complementary service while
-the customer is in service. 
-The problem was later extended by \cite{sun2009equilibrium} where they 
+In~\cite{veltman2005equilibrium} a profit maximisation problem is studied that
+has two servers; an M/M/1 queue and a parking service providing complementary 
+service while the customer is in the first service. 
+The providers gain a reward when customers complete both services and no reward 
+when they finish just one of them.
+One of the main conclusions of this study is that by increasing the general 
+demand both providers lower their prices to compensate for the increase in wait.
+The problem was later extended by~\cite{sun2009equilibrium} where they 
 considered arrivals of batches that can share the parking service.
-Finally, \cite{afeche2007decentralized} examines a tandem network of two M/M/1 
-queues that are ran by two different profit-maximising service providers and 
-receive three different types of customers.
+Finally,~\cite{afeche2007decentralized} examines a tandem network of two M/M/1 
+queues that are ran by two different profit-maximising service providers.
+The network receives three types of customers; those requiring both services, 
+customers requiring the first service and customers requiring the second service.
+The authors showed that optimal prices also maximise social welfare and that
+removing two types of customers that don't need both services leads to higher 
+profit and lower demand rate.
 
@@
 in choosing when to start blocking ambulances.
+This is similar to~\cite{deo2011centralized}.
 This paper touches upon the following new aspects:
@@
 the three players.
+The new thing here is the use of a learning algorithm to get to the Nash 
+equilibrium.
 The model is then applied to the healthcare scenario between two EDs and the 
@@
 incentive mechanisms to improve them.
+The EDs are modelled as two queueing systems each with a tandem buffer and a 
+service centre where their performance measures of the queueing models are then
+used as the utilities of the game.
 
-This paper first gives an overview of the game theoretic model that was built, 
-then goes on to describe how the queueing models were constructed and then 
-follows with the methodology that was used to build the game.
+This paper first gives an overview of the game theoretic model, then goes on 
+to describe a novel queueing model, and then follows with the methodology that 
+was used to build the game.
 Finally, there is a section that describes how this game theoretic framework
@@
 analysis on the behaviour that is observed.
-
-% TODO: If this is one paper remove the queueing model part

### 2021-10-18 sections/introduction/main.tex
Apply minor changes
- Changes based on proselint
- Changes based on alex
- State gap in literature

@@
 They calculate the Nash equilibrium both for identical and heterogeneous firms
-and show that for the former a pure NE always exist and for the latter a unique
-equilibrium exists where only one firm operates.
+and show that for the former a pure N.E. always exist and for the latter a 
+unique equilibrium exists where only one firm operates.
 The authors have also extended their model in~\cite{FirmCompetition2} by 
@@
 Another specific part of this research is the construction of a queueing system
-with a tandem buffer with a single service centre.
+with a tandem buffer and a single service centre.
 In~\cite{d2015pure} the authors explore threshold joining strategies in a 
@@
 The providers gain a reward when customers complete both services and no reward 
-when they finish just one of them.
+when they finish one of them.
 One of the main conclusions of this study is that by increasing the general 
@@
 customers requiring the first service and customers requiring the second service.
-The authors showed that optimal prices also maximise social welfare and that
+The authors showed that optimal prices also maximise social utility and that
 removing two types of customers that don't need both services leads to higher 
@@
 the three players.
-The new thing here is the use of a learning algorithm to get to the Nash 
-equilibrium.
+This study explores two new concepts; getting performance measures for a new
+queueing theoretic model with a tandem buffer and a single service centre and 
+using a learning algorithm to model the emergence of behaviour at the interface
+between Emergency Medical Services (EMS) and the Emergency Department (ED).
 The model is then applied to the healthcare scenario between two EDs and the 

### 2021-10-18 known.py
Update known words

@@ -22,6 +22,7 @@ words = {
     "dt",
     "dx",
     "dy",
+    "ED's",
     "EDs",
     "equilibria",
     "erlang",

### 2021-10-19 sections/introduction/main.tex
Further changes based on PR review

@@
 expected delay.
+In the above models, the players are attempting to increase their share of 
+individuals choosing to queue.
+In public healthcare type settings~\cite{knight2013selfish}, this is not 
+necessarily the case. 
+Players might not necessarily aim to maximise the so called `market share'.
+Rather, the overall service needs to be considered as players aim to minimise
+the overall congestion.
 In~\cite{sadat2015can} a healthcare application was studied where patients 
@@
 based on patients' perceived quality of life.
-In~\cite{knight2013selfish} the impact that individual behaviour has on the 
-efficiency of public services is investigated.
+How individual behaviour based on congestion impacts the efficiency of public 
+services is investigated in~\cite{knight2013selfish}.
 The authors place the individuals' choices between different public services 
 within the formulation of routing games and measure inefficiencies using a 
-concept known as the price of anarchy (\(PoA\))~\cite{koutsoupias1999worst}.
+concept known as the price of anarchy (PoA)~\cite{koutsoupias1999worst}.
 They show that the price of anarchy increases with worth of service and that is
 low for systems with insufficient capacities.
-In \cite{deo2011centralized} the authors study the network effect of ambulance 
+In~\cite{deo2011centralized} the authors study the network effect of ambulance 
 diversion by proposing a non-cooperative game between two EDs that are modelled
@@
 arrivals from the other ED.
+In this paper this concept is extended by allowing the ambulance service to 
+decide how to distribute its patients among the two EDs.
 
@@
 the three players.
+While giving some consideration to equilibrium behaviour similarly to the 
+work of~\cite{FirmCompetition, FirmCompetition2, deo2011centralized, 
+veltman2005equilibrium}, emergent behaviour is more precisely addressed by 
+considering a number of learning algorithms.
 This study explores two new concepts; getting performance measures for a new
 queueing theoretic model with a tandem buffer and a single service centre and 
-using a learning algorithm to model the emergence of behaviour at the interface
-between Emergency Medical Services (EMS) and the Emergency Department (ED).
+using a learning algorithm to model the emergence of behaviour.
 The model is then applied to the healthcare scenario between two EDs and the 
@@
 The EDs are modelled as two queueing systems each with a tandem buffer and a 
-service centre where their performance measures of the queueing models are then
-used as the utilities of the game.
+service centre. 
+The performance measures are then used as the utilities of the game.
+The novelty of the queueing model here is a contribution to not only the game 
+theoretic literature but also to the queueing theoretic literature.
+To the authors knowledge, no such model of a tandem queueing model controlled 
+by a strategic decision has been considered. 
+% TODO Be sure if this is correct
 
 This paper first gives an overview of the game theoretic model, then goes on 
-to describe a novel queueing model, and then follows with the methodology that 
-was used to build the game.
+to describe a novel queueing model, and then follows with a number of theoretic 
+results pertaining to the performance measures of the queuing model. 
+These are used to build the utilities of the game.
 Finally, there is a section that describes how this game theoretic framework

### 2021-10-22 sections/conclusion/main.tex
Write conclusion section
- Write the conclusion section in conclusion/main.tex
- Also add labels to healthacre application section

\section{Conclusion}

The motivation behind this study has been that emergency departments are 
constantly under a lot of pressure to satisfy some regulations. 
This paper shows how this can negatively impact the pathway of both the 
ambulance patients and the ambulance service itself.
Due to some managerial decision making that takes place at the ED, ambulances 
stay blocked outside of the ED at the hospital's parking space in an attempt
to satisfy these regulations.

This study explores a 3-player game theoretic model between the decision makers 
of two queueing systems and a service that distributes individuals to these two
systems (section \ref{sec:model_overview}).
It also describes the construction of the underlying queueing theoretic model 
that has a tandem buffer and a single service centre (section 
\ref{sec:queueing_model}).
Furthermore, the formulas for the performance measures of the queueing model 
are also derived (sections \ref{sec:waiting_time}, \ref{sec:blocking_time}, 
\ref{sec:proportion_within_target}). 
The game theoretic model is then applied to a healthcare scenario by looking at
the interface between the EDs and the EMS (section 
\ref{sec:ems_ed_application}).
The inefficiencies that emerge from the perspective of the EMS were explored 
along with ways to apply some incentive mechanisms to improve them.
The main takeaways from this paper that were observed when playing the game
between two EDs and the EMS (section \ref{sec:application}) are:
\begin{itemize}
    \item Inefficiencies can be learned and emerge naturally
    \item Targeted incentivisation of behaviours can help escape inefficiencies
\end{itemize}
The former relates to the results of asymmetric replicator dynamics that showed 
that inefficient scenarios can arise by playing the game while the latter 
implies that the learned inefficiencies can be escaped by carefully applying 
certain incentives to the players.

This work also has certain limitations that need to addressed.
The model presented here only assumes the presence of two players that can
receive individuals. 
However, in a realistic healthcare scenario an ambulance may have to decide 
among multiple EDs.
An immediate extension of this work would be to consider a multiplayer system
that could represent a group of hospitals in a concentrated area.
Additionally, the game theoretic model that was created uses a discrete 
strategy space for the EDs (something that is also present in various pieces of 
literature~\cite{deo2011centralized, knight2017measuring}).
The single threshold parameter that is used for the ED's decision may not be 
the best way to describe the model.
In reality ED managers could have far more complex parameters for their 
decision making process.
Finally this work assumes that ambulances and EDs act in a selfish and rational
way by only aiming to satisfy their own objectives.
In fact, modelling behaviour in a healthcare setting is a much more complex 
task where some cooperation is often observed.
Another extension would be to explore the behaviour of the ED staff via an 
agent-based model. 
This in turn can be used to model ED staff as agents each with their own 
behavioural traits.

### 2021-10-22 known.py
Update known.py

@@ -31,6 +31,7 @@ words = {
     "hypoexponential",
     "ieeetr",
     "ij",
+    "incentivisation",
     "incentivised",
     "incentivising",
     "keepspaces",

### 2021-10-25 sections/conclusion/main.tex
Add introduction and conclusion sections (#16)
* Update author names

* Update bibliography

Add papers that combine game theory and queueing theory

* Add initial draft of introduction

- First line (hook)
- Literature review methodology driven (game theory - queueing theory)
- Establish research problem
- Research objectives
- Map out the paper

* Cite papers on networks with tandem queues

* Remove unused citation

* Add some additional references

* Minor changes

- Remove unnecessary comments
- Apply suggestions based on alex and proselint
- Reference a paper on ED pressures
- Reference p

@@
 
-This study explores a 3-player game theoretic model between the decision makers 
-of two queueing systems and a service that distributes individuals to these two
-systems (section \ref{sec:model_overview}).
+This study explores a generic 3-player game theoretic model between the 
+decision makers of two queueing systems and a service that distributes 
+individuals to these two systems (section \ref{sec:model_overview}).
 It also describes the construction of the underlying queueing theoretic model 
@@
 \ref{sec:proportion_within_target}). 
+This novel queuing model is the first contribution of the paper.
 The game theoretic model is then applied to a healthcare scenario by looking at
@@
 certain incentives to the players.
+This applied game theoretic model is the second main contribution of this paper.
 
-This work also has certain limitations that need to addressed.
-The model presented here only assumes the presence of two players that can
-receive individuals. 
+The model presented here assumes the presence of two players that can receive 
+individuals. 
 However, in a realistic healthcare scenario an ambulance may have to decide 

### 2021-10-25 sections/introduction/main.tex
Add introduction and conclusion sections (#16)
* Update author names

* Update bibliography

Add papers that combine game theory and queueing theory

* Add initial draft of introduction

- First line (hook)
- Literature review methodology driven (game theory - queueing theory)
- Establish research problem
- Research objectives
- Map out the paper

* Cite papers on networks with tandem queues

* Remove unused citation

* Add some additional references

* Minor changes

- Remove unnecessary comments
- Apply suggestions based on alex and proselint
- Reference a paper on ED pressures
- Reference p

@@
 Rather, the overall service needs to be considered as players aim to minimise
-the overall congestion.
+their experienced congestion.
 In~\cite{sadat2015can} a healthcare application was studied where patients 
@@
 theoretic literature but also to the queueing theoretic literature.
-To the authors knowledge, no such model of a tandem queueing model controlled 
-by a strategic decision has been considered. 
+To the authors knowledge, no such model of a tandem queueing model with a pair 
+of parameters for the buffer has been considered.
 % TODO Be sure if this is correct

### 2021-10-25 known.py

@@ -22,6 +22,7 @@ words = {
     "dt",
     "dx",
     "dy",
+    "ED's",
     "EDs",
     "equilibria",
     "erlang",
@@ -30,6 +31,7 @@ words = {
     "hypoexponential",
     "ieeetr",
     "ij",
+    "incentivisation",
     "incentivised",
     "incentivising",
     "keepspaces",
@@ -45,6 +47,7 @@ words = {
     "nan",
     "nansum",
     "nashpy",
+    "NHS",
     "np",
     "num",
     "numpy",

### 2021-10-25 sections/appendix/proportion_within_target_formula/main.tex
Minor fix in Markov chain formulas
For all formulas consider the arriving state [A_i (u,v)] for individuals
from class i rather than just (u,v). Basically when an individual
arrives at state (u,v) the model will move to a new state based on
that individual's type. This is what this change corresponds to.

@@
-\section{Mean blocking time} \label{sec:appendix_mean_proportion}
+\section{Mean proportion of individuals within target} 
+\label{sec:appendix_mean_proportion}
 
@@
 
-In addition, the set of accepting states for type 1 \(S_A^{(1)}\) and type 2 
-\(S_A^{(2)}\) individuals defined in (\ref{eq:accepting_states_type_1}) and 
+In addition, the set of accepting states for type 1 (\(S_A^{(1)}\)) and type 2 
+(\(S_A^{(2)}\)) individuals defined in (\ref{eq:accepting_states_type_1}) and 
 (\ref{eq:accepting_states_type_2}) are also needed here.
@@
 \begin{equation}
-    P(X^{(1)} < t) = \frac{\sum_{(u,v) \in S_A^{(1)}} P(X_{u,v}^{(1)} < t) 
+    P(X^{(1)} < t) = \frac{\sum_{(u,v) \in S_A^{(1)}} 
+    P(X_{\mathcal{A}_1(u,v)}^{(1)} < t) 
     \pi_{u,v} }{\sum_{(u,v) \in S_A^{(1)}} \pi_{u,v}}
@@
 \begin{equation}
-    P(X^{(2)} < t) = \frac{\sum_{(u,v) \in S_A^{(2)}} P(X_{u,v}^{(2)} < t) 
+    P(X^{(2)} < t) = \frac{\sum_{(u,v) \in S_A^{(2)}} 
+    P(X_{\mathcal{A}_2(u,v)}^{(2)} < t) 
     \pi_{u,v} }{\sum_{(u,v) \in S_A^{(2)}} \pi_{u,v}}
 \end{equation}
+
+Note that \(\mathcal{A}_1(u,v)\) and \(\mathcal{A}_2(u,v)\) are defined in 
+section \ref{sec:blocking_time} by equations \ref{eq:arriving_state_class_1} 
+and \ref{eq:arriving_state_class_2}.
 

### 2021-10-25 sections/appendix/waiting_time_formula/main.tex
Minor fix in Markov chain formulas
For all formulas consider the arriving state [A_i (u,v)] for individuals
from class i rather than just (u,v). Basically when an individual
arrives at state (u,v) the model will move to a new state based on
that individual's type. This is what this change corresponds to.

@@
 state and dividing by the probability of being in any accepting state.
+Note here that \( \mathcal{A}_i \) is defined in section 
+\ref{sec:blocking_time} by equations \ref{eq:arriving_state_class_1} and
+\ref{eq:arriving_state_class_2}.
 
 \begin{equation} \label{eq:recursive_waiting_time_type_1}
-    W^{(1)} = \frac{\sum_{(u,v) \in S_A^{(1)}} w^{(1)}(u,v) 
-    \pi_{(u,v)}}{\sum_{(u,v) \in S_A^{(1)}} \pi_{(u,v)}}
+    W^{(1)} = \frac{\sum_{(u,v) \in S_A^{(1)}} w^{(1)}
+    (\mathcal{A}_1(u,v)) \pi_{(u,v)}}
+    {\sum_{(u,v) \in S_A^{(1)}} \pi_{(u,v)}}
 \end{equation}
@@
 \begin{equation}\label{eq:recursive_waiting_time_type_2}
-    W^{(2)} = \frac{\sum_{(u,v) \in S_A^{(2)}} w^{(2)}(u,v) \pi_{(u,v)}}
+    W^{(2)} = \frac{\sum_{(u,v) \in S_A^{(2)}} w^{(2)}
+    (\mathcal{A}_2(u,v)) \pi_{(u,v)}}
     {\sum_{(u,v) \in S_A^{(2)}} \pi_{(u,v)}}

### 2021-10-25 sections/queueing_model/blocking_time/main.tex
Minor fix in Markov chain formulas
For all formulas consider the arriving state [A_i (u,v)] for individuals
from class i rather than just (u,v). Basically when an individual
arrives at state (u,v) the model will move to a new state based on
that individual's type. This is what this change corresponds to.

@@
 
-% TODO: Fix this equation by using the arriving state 
 \begin{equation}\label{eq:algebraic_blocking_time}
     B = \frac{\sum_{(u,v) \in S_A^{(2)}} \pi_{(u,v)} \; 
-    b(u,v)}{\sum_{(u,v) \in S_A^{(2)}} \pi_{(u,v)}}
+    b(\mathcal{A}_2(u,v))}{\sum_{(u,v) \in S_A^{(2)}} \pi_{(u,v)}}
 \end{equation}
@@
 Here \(S_A^{(2)}\) is the set of accepting states of type 2 individuals (defined
-in (\ref{eq:accepting_states_type_2})) and \(b(u,v)\) is the mean time that an 
-individual will be blocked when the system is at state \((u,v)\). 
+in (\ref{eq:accepting_states_type_2})) and \(\mathcal{A}_i(u,v) \, i \in 
+\{1, 2\} \) is the state that the model would go to when the system is at state 
+\( (u,v) \) and a class \(i\) individual arrives.
+
+\begin{equation}\label{eq:arriving_state_class_1}
+    \mathcal{A}_1(u,v) = (u, v + 1)
+\end{equation}
+\begin{equation}\label{eq:arriving_state_class_2}
+    \mathcal{A}_2(u,v) = 
+    \begin{cases}
+        (u, v + 1), & \text{if } v < T \\
+        (u + 1, v), & \text{if } v \geq T \\
+    \end{cases}
+\end{equation}
+
+The term \(b(u,v)\) is the mean time that an individual will be blocked when 
+the system is at state \((u,v)\). 
 For all the states of the system \(b(u,v)\) is given by:

### 2021-10-25 sections/queueing_model/proportion_within_target/main.tex
Apply alex's suggestion
Minor fix in Markov chain formulas
For all formulas consider the arriving state [A_i (u,v)] for individuals
from class i rather than just (u,v). Basically when an individual
arrives at state (u,v) the model will move to a new state based on
that individual's type. This is what this change corresponds to.

@@
 \begin{equation}\label{eq:proportion_within_target_type_1}
-    P(X^{(1)} < t) = \frac{\sum_{(u,v) \in S_A^{(1)}} P(X_{(u,v)}^{(1)} < t) 
+    P(X^{(1)} < t) = \frac{\sum_{(u,v) \in S_A^{(1)}} 
+    P(X_{\mathcal{A}_1(u,v)}^{(1)} < t) 
     \pi_{u,v} }{\sum_{(u,v) \in S_A^{(1)}} \pi_{u,v}}
@@
 
-The proportion of type 2 individuals within a time target remains as:
+The proportion of type 2 individuals within a time target:
 
 \begin{equation}\label{eq:proportion_within_target_type_2}
-    P(X^{(2)} < t) = \frac{\sum_{(u,v) \in S_A^{(2)}} P(X_{(u,v)}^{(2)} < t) 
+    P(X^{(2)} < t) = \frac{\sum_{(u,v) \in S_A^{(2)}} 
+    P(X_{\mathcal{A}_2(u,v)}^{(2)} < t) 
     \pi_{u,v} }{\sum_{(u,v) \in S_A^{(2)}} \pi_{u,v}}
@@
 
+The terms \(\mathcal{A}_1(u,v)\) and \(\mathcal{A}_2(u,v)\) are defined by
+equations \ref{eq:arriving_state_class_1} and \ref{eq:arriving_state_class_2}
+in section \ref{sec:blocking_time}.
 The overall proportion individuals within a time target (where \(P_{L'_1}\) and 

### 2021-10-28 sections/appendix/descrete_event_simulation/main.tex
Add code archive (#14)
* Add repository archive to bibliography

* Cite archive

* Fix minor issue

* Recompile .pdf
Remove TODOs that were addressed
Minor changes on waiting zones
- Display waiting zones 1 and 2 on the queueing system
- Fix some text that listed the incorrect waiting zones

@@
 This model will be studied by using  
-\lstinline[style=pystyle]{ambulance_game}.
+\lstinline[style=pystyle]{ambulance_game}~\cite{AmbulanceGame}.
 Install the created library in your python environment, by running the 
@@
 in the command line or via the instructions provided in the GitHub repository.
-% TODO: Cite repository
 
@@
 \begin{itemize}
-    \item \textit{system\_capacity} (\(N\)): The maximum number of individuals in 
+    \item \textit{system\_capacity} (\(N\)): The maximum number of individuals 
+    in waiting zone 1.
+    \item \textit{buffer\_capacity} \(M\): The maximum number of individuals in 
     waiting zone 2.
-    \item \textit{buffer\_capacity} \(M\): The maximum number of individuals in 
-    waiting zone 1.
     \item \textit{seed\_num}: The seed number for the random number generator.
@@
 \end{lstlisting}
-% TODO: Fix code for proportion of individuals within time target
 
@@
 \end{multicols}
-
-% TODO: Archive simulation python code

### 2021-11-02 sections/healthcare_application/main.tex
Add introduction and conclusion sections (#16)
* Update author names

* Update bibliography

Add papers that combine game theory and queueing theory

* Add initial draft of introduction

- First line (hook)
- Literature review methodology driven (game theory - queueing theory)
- Establish research problem
- Research objectives
- Map out the paper

* Cite papers on networks with tandem queues

* Remove unused citation

* Add some additional references

* Minor changes

- Remove unnecessary comments
- Apply suggestions based on alex and proselint
- Reference a paper on ED pressures
- Reference p

@@
-\section{EMS - ED application}
+\section{EMS - ED application}\label{sec:ems_ed_application}
 
-\subsection{Application}
+\subsection{Application}\label{sec:application}
 
@@
 to a healthcare scenario with two such queueing systems.
-The two queueing systems can be thought of as two Emergency Departments (ED) and 
-the Emergency Medical Services (EMS) as a distributor that distributes 
+The two queueing systems can be thought of as two Emergency Departments (ED) 
+and the Emergency Medical Services (EMS) as a distributor that distributes 
 patients to them.
@@
 
-    ``We used to bring poorly patients in, and we were out on the road again in 15 minutes.''~\cite{bbcwales}
+    ``We used to bring poorly patients in, and we were out on the road again in
+    15 minutes.''~\cite{bbcwales}
 \end{quotation}
@@
 
-The parameters of the model correspond to the following parameters of the ED and 
-the EMS:
+The parameters of the model correspond to the following parameters of the ED 
+and the EMS:
 
@@
     \item \( \lambda_2 \): The rate of non-emergency patients that the EMS 
-    receives
-    \item \( \lambda_{1_i} \): The arrival rate of other patients to ED \(i\in\{1, 2\}\)
-    \item \( \mu_i \): The service rate of patients at ED \(i\in\{1, 2\}\)
-    \item \( C_i \): The number of available resources (beds) in ED \(i\in\{1, 2\}\)  
-    \item \( T_i \): The action that ED \(i\in\{1, 2\} \) chooses to play which 
+    receives and distributes to EDs
+    \item \( \lambda_{1_i} \): The arrival rate of other patients to ED 
+    \(i\in\{A, B\}\)
+    \item \( \mu_i \): The service rate of patients at ED \(i\in\{A, B\}\)
+    \item \( C_i \): The number of available resources (beds) in ED 
+    \(i\in\{A, B\}\)  
+    \item \( T_i \): The action that ED \(i\in\{A, B\} \) chooses to play which 
     corresponds to the threshold at which they do not accept EMS patients.
-    \item \( N_i \): The total patient capacity of ED \(i\in\{1, 2\} \)
-    \item \( M_i \): The total parking capacity of ED \(i\in\{1, 2\} \)
+    \item \( N_i \): The total patient capacity of ED \(i\in\{A, B\} \)
+    \item \( M_i \): The total parking capacity of ED \(i\in\{A, B\} \)
     \item \( R \): The time target for both EDs
@@
 As defined in \ref{sec:model_overview}, the interaction between the two EDs 
-is a Normal form game that is then used to inform the decision of the EMS.
+is a normal form game that is then used to inform the decision of the EMS.
 Note that the formulated game here assumes that prior to making a choice the 
 EMS knows the strategies that each ED is playing (figure 
-\ref{fig:imperfect_info_game}). This corresponds to reacting to experienced delays.
+\ref{fig:imperfect_info_game}). This corresponds to reacting to experienced 
+delays.
 
-\subsection{Numerical Results}
+\subsection{Numerical results}\label{sec:numerical_results}
 
 This subsection aims to analyse how the gaming framework can affect the 
-performance measures of the two hospitals and how to avoid certain inefficient 
+performance measures of the two hospitals and how to escape certain inefficient 
 situations.
@@
 The most commonly used method for analysing normal form games is the Nash 
-equilibrium described in section \ref{sec:methodology_nash_equilibrium}
+equilibrium described in section \ref{sec:methodology_nash_equilibrium}.
 Consider the following game:
@@
     \begin{itemize}
-        \item \( \lambda_{1_1} \) = 1
-        \item \( \mu_1 \) = 2
-        \item \( C_1 \) = 2
-        \item \( N_1 \) = 10
-        \item \( M_1 \) = 6
+        \item \( \lambda_{1_A} \) = 1
+        \item \( \mu_A \) = 2
+        \item \( C_A \) = 2
+        \item \( N_A \) = 10
+        \item \( M_A \) = 6
         \columnbreak
 
-        \item \( \lambda_{1_2} \) = 2
-        \item \( \mu_2 \) = 2.5
-        \item \( C_2 \) = 2
-        \item \( N_2 \) = 10
-        \item \( M_2 \) = 6
+        \item \( \lambda_{1_B} \) = 2
+        \item \( \mu_B \) = 2.5
+        \item \( C_B \) = 2
+        \item \( N_B \) = 10
+        \item \( M_B \) = 6
         \columnbreak
@@
 \begin{equation}
-    T_1 = \{ 0, \ldots, N_1 \}, \quad T_2 = \{ 0, \ldots, N_2 \}
+    T_A \in [1, N_A], \quad T_B \in [1, N_B]
 \end{equation}
@@
 For this example the only Nash equilibrium of the game is achieved when both 
-players choose a threshold of \( T_1 = 10, T_2 = 10 \).
+players choose a threshold of \( T_A = 10, T_B = 10 \).
 This means that the two players' best response to each other is to only block
@@
 Both hospital 1 (row player) and hospital 2 (column player) seem to be playing 
-the same strategy \(s_{10}\) which indicates that thresholds \(T_1 = 10\) and 
-\(T_2 = 10\) are played.
+the same strategy \(s_{10}\) which indicates that thresholds \(T_A = 10\) and 
+\(T_B = 10\) are played.
 What is more important in this example is how the two hospitals reached these
@@
 
-Here, \(S\) is the set of all sets of strategies \((s_1, s_2)\), \(E\) is the 
+Here, \(S\) is the set of all sets of strategies \((s_A, s_B)\), \(E\) is the 
 set of all possible sets of equilibria and \(F\) is the cost function to 
@@
 players of the game and is defined as \(PoA_i(\tilde{s})\), where 
-\(i \in \{1, 2\}\) to distinguish among the two players/hospitals where 
+\(i \in \{A, B\}\) to distinguish among the two players/hospitals where 
 \(\tilde{s}\) is the strategy that is being played by player \( i \). 
@@
     \begin{itemize}        
-        \item \( \lambda_{1_1} \) = 4.5
-        \item \( \mu_1 \) = 2
-        \item \( C_1 \) = 3
-        \item \( T_1 \in [1, N_1] \) 
-        \item \( N_1 \) = 6
-        \item \( M_1 \) = 5
+        \item \( \lambda_{1_A} \) = 4.5
+        \item \( \mu_A \) = 2
+        \item \( C_A \) = 3
+        \item \( T_A \in [1, N_A] \) 
+        \item \( N_A \) = 6
+        \item \( M_A \) = 5
 
         \columnbreak
-        \item \( \lambda_{1_2} \) = 6
-        \item \( \mu_2 \) = 3
-        \item \( C_2 \) = 2
-        \item \( T_2 \in [1, N_2] \)
-        \item \( N_2 \) = 7
-        \item \( M_2 \) = 4
+        \item \( \lambda_{1_B} \) = 6
+        \item \( \mu_B \) = 3
+        \item \( C_B \) = 2
+        \item \( T_B \in [1, N_B] \)
+        \item \( N_B \) = 7
+        \item \( M_B \) = 4
 
@@
 Figure \ref{fig:ard_original} shows the strategies that are being played and 
-the values of \(PoA_1(s)\) and \(PoA_2(s)\) for all iterations of the 
+the values of \(PoA_A(s)\) and \(PoA_B(s)\) for all iterations of the 
 learning algorithm until it reaches an evolutionary stable pair of strategies.
@@
 The learning algorithm reaches a stable pair of 
-strategies where \(T_1 = 5\) and \(T_2 = 6\). After a number of iterations the
+strategies where \(T_A = 5\) and \(T_B = 6\). After a number of iterations the
 price of anarchy for both players stabilises and barely increases until the 
@@
 By increasing \(\lambda_2\) there is no change as to how players behave
-(\(T_1 = 5, T_2 = 6\)), but the efficiency of the system does change. 
+(\(T_A = 5, T_B = 6\)), but the efficiency of the system does change. 
 There is a decline in the price of anarchy of the blocking time which at first 
@@
 
-\textbf{Increasing number of servers \( C_1 \) and \( C_2 \):}
+\textbf{Increasing number of servers \( C_A \) and \( C_B \):}
 Figure \ref{fig:ard_num_of_servers} shows a run of asymmetric replicator 
 dynamics with a change in the number of servers of the hospitals.
-The number of servers are increased from \(C_1 = 3, C_2 = 2\) to 
-\(C_1 = 4, C_2 = 3\).
+The number of servers are increased from \(C_A = 3, C_B = 2\) to 
+\(C_A = 4, C_B = 3\).
 
@@
 In this case, both the behaviour as well as the price of anarchy change.
-The players change their strategies from \(T_1 = 5, T_2 = 6\) to 
-\(T_1 = 6, T_2 = 7\) and the \(PoA\) of the blocking time goes down.
+The players change their strategies from \(T_A = 5, T_B = 6\) to 
+\(T_A = 6, T_B = 7\) and the \(PoA\) of the blocking time goes down.
 By adding more resources to the models they are able to increase their 
@@
 Figure \ref{fig:ard_penalty} shows that players start playing strategies 
-\( T_1 = 5\) and \( T_2 = 6 \) and mid-run of the learning algorithm a penalty
+\( T_A = 5\) and \( T_B = 6 \) and mid-run of the learning algorithm a penalty
 is applied to these strategies on the payoff matrix.
 By incentivising the players in such a way the players change their strategies 
-to \(T_1 = 6\) and \(T_2 = 7\), and thus ambulance patients are accepted in the 
+to \(T_A = 6\) and \(T_B = 7\), and thus ambulance patients are accepted in the 
 ED more often.

### 2021-11-02 sections/methodology/main.tex
Changes based on self review
I just read the whole thing and made some minor
changes here and there.

@@
 The strategy space of the two queueing systems is defined as the possible values
-that the threshold parameter can take \(T_i \in (1, N_i)\).
+that the threshold parameter can take \(T_i \in [1, N_i]\).
 Then, the distributor has to decide on the proportion of individuals to send to 
@@
 
-\subsection{Backwards Induction}
+\subsection{Backwards induction}
 
@@
 Here \(R\) is the predefined waiting time target to be met by a percentage of 
-individuals \( \hat{P} \) and \(P(W_i < t)\) is properly defined in section
+individuals \( \hat{P} \) and \(P(W_i < t)\) is defined in section
 \ref{sec:proportion_within_target}.
@@
 
-\subsection{Nash Equilibrium}\label{sec:methodology_nash_equilibrium}
+\subsection{Nash equilibrium}\label{sec:methodology_nash_equilibrium}
 
@@
 
-Computation of Nash equilibria can be done relatively efficiently using the 
-Lemke Howson algorithm~\cite{LemkeHowson}.
+Computation of Nash equilibria can be done in a relatively efficient way using 
+the Lemke Howson algorithm~\cite{LemkeHowson}.
 Lemke-Howson uses best response polytopes to get one of the Nash equilibrium of
@@
 
-\subsection{Learning Algorithms}\label{sec:methodology_learning_algorithms}
+\subsection{Learning algorithms}\label{sec:methodology_learning_algorithms}
 

### 2021-11-02 sections/model_overview/main.tex
Minor changes on waiting zones
- Display waiting zones 1 and 2 on the queueing system
- Fix some text that listed the incorrect waiting zones
Changes based on self review
I just read the whole thing and made some minor
changes here and there.

@@
 of individuals. 
-These are the individuals that the distributor allocates to them and 
+These are the individuals that are allocated by the distributor and 
 other individuals from other sources. 
@@
         % the rectangle of Queue 1
-        \draw (0,0) -- ++(2cm,0) -- ++(0,-1.5cm) -- ++(-2cm,0);
+        \draw (0,0) -- ++(3cm,0) -- ++(0,-1.5cm) -- ++(-3cm,0);
         % The label above Queue 1 -> M
@@
         \)};
+        % The label below Queue 1 -> Waiting zone 2
+        \node[anchor=north] at (1.5cm, -1.7cm) {\small{Waiting zone 2}};
+
         % the vertical lines in Queue 1
-        \foreach \i in {1,...,4, 5.7}
-        \draw (2cm-\i*10pt,0) -- +(0,-1.5cm);
+        \foreach \i in {1,...,5, 6.6}
+        \draw (3cm-\i*13pt,0) -- +(0,-1.5cm);
 
-        % the circle in Queue 1
-        \draw (2.75,-0.75cm) circle [radius=0.75cm] node {\(0\)};
+        % % the circle in Queue 1
+        % \draw (2.75,-0.75cm) circle [radius=0.75cm] node {\(0\)};
 
@@
         \)};
+        % The label below Queue 2 -> Waiting zone 1
+        \node[anchor=north] at (6.2cm, -0.5cm) {\small{Waiting zone 1}};
 
@@
         % First line (horizontal) after Queue 1
-        \draw[-] (3.5,-0.75) -- +(20pt,0);
+        \draw[-] (3,-0.75) -- +(34pt,0);
         % Second line (vertical) after Queue 1
@@
 
-where \(W\) is the mean waiting time of all individuals, \(t\) is the time 
+where \(W\) is the waiting time of a potential individual, \(t\) is the time 
 target and \(\hat{P}\) is the percentage of individuals need to be within that 
@@
 
-The third player, the distributor has their own choices to make and their own 
+The third player, the distributor, has their own choices to make and their own 
 goals to satisfy.
@@
 
-Using equations (\ref{eq:obj_queueing_systems}) and (\ref{eq:obj_distributor}) 
-gives an imperfect information extensive form game. 
+Using either equation (\ref{eq:obj_queueing_systems}) or equation
+(\ref{eq:obj_distributor}) gives an imperfect information extensive form game. 
 An imperfect information game is defined as an extensive form game where some 
@@
 knowing the other system's strategy.
-The distributor then, fully aware of the chosen threshold strategies, distributes 
-individuals among the two systems in order to minimise the time that its 
-individuals will be blocked. Figure \ref{fig:imperfect_info_game} illustrates this.
+The distributor then, fully aware of the chosen threshold strategies, 
+distributes individuals among the two systems in order to minimise the time 
+that its individuals will be blocked. Figure \ref{fig:imperfect_info_game} 
+illustrates this.
 
@@
 \begin{equation} \label{eq:payoff_entry}
-    U_{T_1, T_2}^i = -\left( 
+    U_{T_A, T_B}^i = -\left( 
         \hat{P} - P(W_i < t) 

### 2021-11-02 sections/queueing_model/main.tex
Changes to Methodology and Model overview sections
- Chnages in some notation
- Define expressions only once and then just reference them
- Changes in some labels (including some more sections)
- Other minor rewordings
Minor changes on waiting zones
- Display waiting zones 1 and 2 on the queueing system
- Fix some text that listed the incorrect waiting zones
Changes based on self review
I just read the whole thing and made some minor
changes here and there.

@@
 The model consists of two types of individuals; type 1 and type 2.
-Type 1 individuals arrive instantly at waiting zone 1 and proceed to wait to
-receive their service. 
+Type 1 individuals arrive instantly at waiting zone 1 and wait to receive their 
+service. 
 Type 2 individuals arrive at waiting zone 2 and wait there until they are 
@@
 second type individuals that arrive will stay 
-\textit{``blocked''} in waiting zone 1 until the number of people in the 
-system is reduced below \(T\). 
+\textit{``blocked''} in waiting zone 2 until the number of people in 
+the next queue and in service falls below \(T\). 
 This is shown diagrammatically in figure \ref{fig:diagram_of_queueing_system}.
@@
 \begin{itemize}
-    \item \(\lambda_i\): The arrival rate of individuals of type \(i\in\{1, 2\}\)
+    \item \(\lambda_i\): The arrival rate of individuals of type 
+    \(i\in\{1, 2\}\)
     \item \(\mu\): The service rate for individuals receiving service
     \item \(C\): The number of servers
-    \item \(T\): The threshold at which individuals of the second type are blocked
+    \item \(T\): The threshold at which individuals of the second type are 
+    blocked
 \end{itemize}
@@
 
-The transition matrix \(Q\) of the Markov chain consists of the transition rates
-between the numerous states of the model. Every entry \( Q_{ij} = 
-Q_{(u_i, v_i),(u_j, v_j)} \) represents the transition rate from state 
-\( i = (u_i, v_i) \) to state \( j = (u_j , v_j) \) for all 
+The generator matrix \(Q\) of the Markov chain consists of the 
+rates between the numerous states of the model. 
+Every entry \( Q_{ij} = Q_{(u_i, v_i),(u_j, v_j)} \) represents the rate from 
+state \( i = (u_i, v_i) \) to state \( j = (u_j , v_j) \) for all 
 \( (u_i, v_i), (u_j, v_j) \in S \).
@@
 can be seen in the general Markov chain model shown in figure 
-\ref{fig:general-markov-model}.
+\ref{fig:general_markov_model}.
 
@@
 
-The transition matrix \( Q \) defined in (\ref{eq:markov_transition_rate}) can 
+The generator matrix \( Q \) defined in (\ref{eq:markov_transition_rate}) can 
 be used to get the probability vector \( \pi \).
@@
 valid for type 2 individuals) and the proportion of individuals that wait in 
-waiting zone 1 within a predefined time target.
+waiting zone 1 within a predefined time target (for both types).
 

### 2021-11-05 sections/abstract/main.tex
Remove table of contents and add abstract

--- 2021-03-11 Abstract/main.tex
@@
 \begin{abstract}
-    The main focus of this research is the construction of a 3-player game theoretic model between two queueing systems and a service that distributes individuals to them.
+The focus of this research is the construction of a 3-player game theoretic 
+model between two queueing systems and a service that distributes individuals 
+to them. 
 The resultant model will then be used to explore dynamics between all players.
-
-    The first aspect of this work is the development of a queueing system with two consecutive waiting spaces.
-The strategic managerial behaviour corresponds to how individuals use these waiting spaces.
+The first aspect of this work is the development of a queueing system with two
+consecutive waiting spaces. 
+The strategic managerial behaviour corresponds to how individuals use these 
+waiting spaces. 
 Two modelling techniques were used: discrete event simulation and Markov chains.
-The state probabilities of the Markov chain system have been used to extract the performance measures of the queueing model (e.g.
-mean time in each waiting room, mean number of individuals in each room, etc.).
-
-    A 3-player game theoretic model is proposed between the two queueing systems and the service that distributes individuals to them.
-In particular this can be seen as a 2-player normal-form game where the utilities are determined by a third player with its own strategies and objectives.
-A backwards induction technique is used to get the utilities of the normal-form game between the two queueing systems.
-
-    This particular system can be applied in a healthcare scenario where it captures the emergent behaviour between, for example, the Emergency Medical Service (EMS) and the Emergency Department (ED).
-This will be used to investigate the impact of target measures on patient welfare.
+The state probabilities of the Markov chain system have been used to extract 
+the performance measures of the queueing model (e.g. mean time in each waiting
+room, mean number of individuals in each room, etc.).
+A 3-player game theoretic model is proposed between the two queueing systems
+and the service that distributes individuals to them.
+In particular this can be seen as a 2-player normal-form game where the 
+utilities are determined by a third player with its own strategies and 
+objectives. 
+A backwards induction technique is used to get the utilities of the normal-form
+game between the two queueing systems.
+This particular system can be applied in a healthcare scenario where it 
+captures the emergent behaviour between, for example, the Emergency Medical 
+Service (EMS) and the Emergency Department (ED). 
+This will be used to investigate the impact of target measures on patient 
+well-being.
 \end{abstract}

### 2021-11-05 sections/introduction/main.tex
Apply changes to introduction section

@@
 
-An important issue for ambulances in the United Kingdom is that they stay 
-parked outside hospitals for a huge amount of time~\cite{clarey2014ambulance}. 
-This is a problem for the ambulance service, since the longer ambulances are
-blocked in the hospital's parking space the longer the patients in them will
-have to wait to receive their treatment but also the longer future patients 
-will be stuck waiting for an ambulance.
-This paper aims to describe a game theoretic model informed by an underlying 
-queueing model motivated by this scenario.
-
-Emergency departments (EDs) are constantly under a lot of pressure to meet 
-targets and satisfy regulations~\cite{EmergencyDepartmentWinterPressures}.
-There are various news reports that indicate that this is in fact an ongoing 
-issue that affects both the patients and the emergency medical services (EMS).
-Due to this blockage patients may spend a considerable amount of time in the 
-back of an ambulance waiting to be dispatched to the ED.
-Examples of such reports are~\cite{mirror, thenews, bmj} where
-the impact that this issue has on patients is shown. 
-Furthermore, this is also a huge issue for the EMS.
-By blocking the ambulances at the hospital's parking space, valuable time is 
-wasted where ambulances could be attending new patients~\cite{eastanglia}.
+Emergency departments (EDs) are under increasing pressure to meet patient
+waiting time targets and satisfy 
+regulations~\cite{EmergencyDepartmentWinterPressures}.
+It is widely reported (e.g.~\cite{mirror, thenews, bmj}) that ED congestion 
+severely impacts not only patients in the ED but also Emergency Medical 
+Services (EMS).
+A major concern for ambulances is that they are held waiting parked outside the
+ED to offload (dispatch) their patient when the ED is particularly 
+busy~\cite{clarey2014ambulance}. 
+Since the patient waiting time in ED is measured from the time they enter the
+ED itself, there is no incentive, should the patient be stable in the
+ambulance, to offload them from EMS to ED services.
+As a result, ambulance blocking not only impacts on patients waiting for ED
+service, but has a major knock-on effect to delaying the ability of ambulances
+to respond to new EMS calls, thus placing lives at risk~\cite{eastanglia}.
+This paper aims to describe the EMS-ED interface using a game theoretic model
+informed by an underlying queueing model.
 
@@
 They calculate the Nash equilibrium both for identical and heterogeneous firms
-and show that for the former a pure N.E. always exist and for the latter a 
-unique equilibrium exists where only one firm operates.
+and show that for the former a pure Nash equilibrium always exist and for the 
+latter a unique equilibrium exists where only one firm operates.
 The authors have also extended their model in~\cite{FirmCompetition2} by 
 allowing the players (firms) to choose capacities. 
-A main result from this paper was that equilibria, where both firms operate
-together, are not socially optimal while when both firms operate as a monopoly 
-they are.
+A main result from this paper was that when both firms operate independently as
+a monopoly, the equilibria are socially optimal, but this is not the case when
+the firms operate together.
 Another extension of~\cite{FirmCompetition} was introduced 
@@
 expected delay.
+
 In the above models, the players are attempting to increase their share of 
@@
 
-Another specific part of this research is the construction of a queueing system
-with a tandem buffer and a single service centre.
+Another specific part of our research, as described later in the paper, is the 
+construction of a queueing system with a tandem buffer and a single service
+centre.
 In~\cite{d2015pure} the authors explore threshold joining strategies in a 
 Markov model that has two tandem queues.
-Another great example is the one described in~\cite{burnetas2013customer}
+Another example is the one described in~\cite{burnetas2013customer}
 where they investigated a network of multiple tandem queues where customers 
@@
 
-The EDs in the United Kingdom have to follow some set of regulations imposed to 
+EDs in the United Kingdom have to follow a set of regulations imposed to 
 them by the National Health Service (NHS).
@@
 This is similar to~\cite{deo2011centralized}.
-This paper touches upon the following new aspects:
+
+The novelty of our research contribution in this paper is to consider:
 \begin{itemize}
@@
 \end{itemize}
-The focus of this research is the construction of a 3-player game theoretic 
+Specifically, our focus is on the construction of a 3-player game theoretic 
 model between two queueing systems and a service that distributes individuals
 to them. 
-The resultant model will then be used to explore the emergent dynamics between 
+The resultant model is then used to explore the emergent dynamics between 
 the three players.
-While giving some consideration to equilibrium behaviour similarly to the 
+Whilst giving some consideration to equilibrium behaviour similarly to the 
 work of~\cite{FirmCompetition, FirmCompetition2, deo2011centralized, 
@@
 considering a number of learning algorithms.
-This study explores two new concepts; getting performance measures for a new
+This study explores two new concepts: getting performance measures for a new
 queueing theoretic model with a tandem buffer and a single service centre and 
 using a learning algorithm to model the emergence of behaviour.
-The model is then applied to the healthcare scenario between two EDs and the 
-EMS while looking into the inefficiencies that emerge and ways to apply some 
-incentive mechanisms to improve them.
+The developed theoretical model is then illustrated through the application to 
+a healthcare system of two EDs and the EMS, exploring the inefficiencies that 
+emerge and ways to apply some incentive mechanisms to improve them.
 The EDs are modelled as two queueing systems each with a tandem buffer and a 
@@
 The performance measures are then used as the utilities of the game.
-The novelty of the queueing model here is a contribution to not only the game 
+The novelty of the queueing model here is a contribution not only the game 
 theoretic literature but also to the queueing theoretic literature.
@@
 % TODO Be sure if this is correct
+Although our research is motivated by the particular EMS-ED example, our 
+developed modelling framework and behavioural insights has application to 
+similar systems across a range of sectors and settings.
 
@@
 to describe a novel queueing model, and then follows with a number of theoretic 
-results pertaining to the performance measures of the queuing model. 
+results pertaining to the performance measures of this model. 
 These are used to build the utilities of the game.

### 2021-11-05 sections/queueing_model/main.tex
Apply changes to queueing sections

@@
 figure \ref{fig:diagram_of_queueing_system} will be given.
-This is a queuing model that consists of two waiting spaces, one for each type
+This is a queueing model that consists of two waiting zones, one for each type
 of individual.
@@
 second type individuals that arrive will stay 
-\textit{``blocked''} in waiting zone 2 until the number of people in 
+\textit{blocked} in waiting zone 2 until the number of people in 
 the next queue and in service falls below \(T\). 
-This is shown diagrammatically in figure \ref{fig:diagram_of_queueing_system}.
+This is shown diagrammatically in Figure \ref{fig:diagram_of_queueing_system}.
 The parameters of the described queueing model are:
@@
 Under the assumption that all rates (arrival and service) are Markovian the
-queuing system corresponds to a Markov chain~\cite{kemeny1976markov}.
+queueing system corresponds to a Markov chain~\cite{kemeny1976markov}.
 The states of the Markov chain are denoted by \((u,v)\) where:
@@
 A visualisation of how the transition rates relate to the states of the model 
-can be seen in the general Markov chain model shown in figure 
+can be seen in the general Markov chain model shown in Figure 
 \ref{fig:general_markov_model}.
@@
 The following equations utilise \(\pi\) to get performance measures on the 
-average number of people at certain sets of state.
+average number of people at certain sets of state:
 

### 2021-11-05 sections/queueing_model/proportion_within_target/main.tex
Apply changes to queueing sections

@@
 time target \(t\).
-Similar to section \ref{sec:waiting_time} three formulas are needed for this 
+Similar to section \ref{sec:waiting_time}, three formulas are needed for this 
 performance measure.
@@
 
-Refer to appendix \ref{sec:appendix_mean_proportion} for a more in-depth 
+Please refer to appendix \ref{sec:appendix_mean_proportion} for a more in-depth 
 explanation of the origins of equations 

### 2021-11-05 sections/queueing_model/waiting_time/main.tex
Restructure queueing model section
Remove performance measures subsection and change "waiting time",
"blocking time" and "proportion of inds" from subsubsections into
subsections. Also add example subsubsections
Write appendix chapter for DES model
Section: A queueing model with 2 consecutive buffer centres (#6)
* Add bibliography entry

* Write details of the Markov-chain model

- Define the model
- Define state space
- Define transition matrix and state-mapping function

* Add general Markov-chain picture

* Update known.py

* Add .pdf file to GitHub repo

* Create subsections/ subdirectory

--- 2021-05-26 sections/queueing_model/subsections/performance_measures/waiting_time/main.tex
@@
-\subsubsection{Waiting time} \label{sec:waiting_time}
+\subsection{Waiting time} \label{sec:waiting_time}
 
@@
 For a given set of parameters there are three different performance measures 
-around the mean waiting time that can be calculated; the mean waiting time of
+around the mean waiting time that can be calculated. The mean waiting time of
 type 1 individuals:
@@
 waiting time using discrete event simulation over a range of values of 
-\(\lambda_2\).
+\(\lambda_2\) (details of the discrete event simulation model are given in 
+appendix~\ref{sec:appendix_des}).
 The simulation was ran 100 times and the recorded mean waiting time at each 
 iteration is used to populate the violin plots.
+For all three plots the waiting times generated by the simulation match the
+ones generated by the Markov chains model.
 

### 2021-11-05 sections/healthcare_application/main.tex
Apply changes to healthcare application section

@@
 There are numerous news articles that focus on the problems that arise when 
-ambulances stay parked outside of the hospital for a long amount of time
-~\cite{dailyrecords}, \cite{staffordshirelive}.
+ambulances stay blocked outside of the hospital for a long amount of 
+time~\cite{dailyrecords, staffordshirelive}.
 Some news reports also comment on the long idle time of ambulances when 
@@
 The patients that are distributed by the EMS arrive at the hospital via an 
-ambulance and are then either unloaded at the ED or stay blocked outside in 
+ambulance and are then either offloaded at the ED or stay blocked outside in 
 the ambulance.
@@
 lost ambulances is minimised. 
-As defined in \ref{sec:model_overview}, the interaction between the two EDs 
+As defined in Section \ref{sec:model_overview}, the interaction between the two EDs 
 is a normal form game that is then used to inform the decision of the EMS.
@@
 
-For this example the only Nash equilibrium of the game is achieved when both 
+For this example, the only Nash equilibrium of the game is achieved when both 
 players choose a threshold of \( T_A = 10, T_B = 10 \).
@@
 Therefore it might not be the best way to describe human behaviour.
-Since the work of Maynard Smith \cite{smith1986evolutionary} evolutionary game 
+Since the work of Maynard Smith \cite{smith1986evolutionary}, evolutionary game 
 theory gives the tools for the emergence of stable behaviour.
 One such model that allows for asymmetric payoffs, as is the case above, is 
-replicator dynamics described in section 
+replicator dynamics described in Section 
 (\ref{sec:methodology_learning_algorithms}).
@@
 the game, but also how that outcome is reached.
-Consider figure \ref{fig:ard_by_itself}. 
+Consider Figure \ref{fig:ard_by_itself}. 
 By running asymmetric replicator dynamics on the system the behaviour that 
@@
 
-To study the efficiency of the strategies being played a new concept is 
+To study the efficiency of the strategies being played, a new concept is 
 introduced that considers the ratio between each hospital's best achievable 
@@
 Using equation (\ref{eq:poa_compartmentalised}) and asymmetric replicator 
-dynamics the emergent behaviour can be measured and the compartmentalised price 
+dynamics, the emergent behaviour can be measured and the compartmentalised price 
 of anarchy at every iteration for both players.
@@
 \textbf{Incentivising players:}
-From figures \ref{fig:ard_lambda_2} and \ref{fig:ard_num_of_servers} it can be
+From Figures \ref{fig:ard_lambda_2} and \ref{fig:ard_num_of_servers} it can be
 seen that we can change some parameters of the model to make it more efficient.
-The approach used on figure \ref{fig:ard_penalty} is slightly different than 
+The approach used on Figure \ref{fig:ard_penalty} is slightly different than 
 the previous cases.
@@
 \(\tilde{B}\) of matrix \(B\) only on the column that is most frequently played
-(matrix \(A\): row \(5\), matrix \(B\): column \(6\), see figure 
+(matrix \(A\): row \(5\), matrix \(B\): column \(6\), see Figure 
 \ref{fig:ard_penalty}).

### 2021-11-11 sections/appendix/additional_figures/main.tex
Additional changes based on review
- Reword a sentence
- Move some plots from the main body to the appendix

\section{Type 1 and type 2 performance measure comparisons using simulation and
Markov chains}\label{sec:appendix_additional_figures}

\begin{figure}[H]
    \centering
    \includegraphics[width=.7\textwidth]{imgs/waiting_time_comparison/waiting_1.pdf}
    \caption{
        Comparison of mean waiting time for type 1 individuals between values 
        obtained from the Markov chain formulas and values obtained from 
        simulation.
    }
    \label{fig:markov_vs_des_waiting_time_comparison_1}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=.7\textwidth]{imgs/waiting_time_comparison/waiting_2.pdf}
    \caption{
        Comparison of mean waiting time for type 2 individuals between values 
        obtained from the Markov chain formulas and values obtained from 
        simulation.
    }
    \label{fig:markov_vs_des_waiting_time_comparison_2}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=.7\textwidth]{imgs/proportion_within_target_comparison/proportion_1.pdf}
    \caption{
        Comparison of proportion within target time for type 1 individuals 
        between values obtained from the Markov chain formulas and values 
        obtained from simulation. 
    }
    \label{fig:markov_vs_des_proportion_comparison_1}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=.7\textwidth]{imgs/proportion_within_target_comparison/proportion_2.pdf}
    \caption{
        Comparison of proportion within target time for type 2 individuals 
        between values obtained from the Markov chain formulas and values 
        obtained from simulation. 
    }
    \label{fig:markov_vs_des_proportion_comparison_2}
\end{figure}

### 2021-11-11 sections/queueing_model/proportion_within_target/main.tex
Additional changes based on review
- Reword a sentence
- Move some plots from the main body to the appendix

@@
 
-Figures \ref{fig:markov_vs_des_proportion_comparison_1},
-\ref{fig:markov_vs_des_proportion_comparison_2} and 
-\ref{fig:markov_vs_des_proportion_comparison_overall} show a comparison of the
-mean proportion of individuals within target when using Markov chains and 
-discrete event simulation (appendix~\ref{sec:appendix_des}).
+Figure \ref{fig:markov_vs_des_proportion_comparison_overall} shows a comparison
+of the mean proportion of individuals within target when using Markov chains 
+and discrete event simulation (appendix~\ref{sec:appendix_des}).
 The simulation was ran 100 times and the recorded proportions at each iteration 
 is used to populate the violin plots.
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=.8\textwidth]{imgs/proportion_within_target_comparison/proportion_1.pdf}
-    \caption{
-        Comparison of proportion within target time for type 1 individuals 
-        between values obtained from the Markov chain formulas and values 
-        obtained from simulation. 
-    }
-    \label{fig:markov_vs_des_proportion_comparison_1}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=.8\textwidth]{imgs/proportion_within_target_comparison/proportion_2.pdf}
-    \caption{
-        Comparison of proportion within target time for type 2 individuals 
-        between values obtained from the Markov chain formulas and values 
-        obtained from simulation. 
-    }
-    \label{fig:markov_vs_des_proportion_comparison_2}
-\end{figure}
+The proportions generated by the simulation match the ones generated by the 
+Markov chains model.
+Note that this comparison includes both type 1 and type 2 individuals.
+A separate comparison of only type 1 and only type 2 individuals can be found 
+in appendix~\ref{sec:appendix_additional_figures}.
 

### 2021-11-11 sections/queueing_model/waiting_time/main.tex
Additional changes based on review
- Reword a sentence
- Move some plots from the main body to the appendix

@@
 
-Figures \ref{fig:markov_vs_des_waiting_time_comparison_1},
-\ref{fig:markov_vs_des_waiting_time_comparison_2} and
-\ref{fig:markov_vs_des_waiting_time_comparison_overall} show a comparison 
-between the calculated mean waiting time using Markov chains and the simulated 
-waiting time using discrete event simulation over a range of values of 
+Figure \ref{fig:markov_vs_des_waiting_time_comparison_overall} shows a 
+comparison between the calculated mean waiting time using Markov chains and the
+simulated waiting time using discrete event simulation over a range of values of 
 \(\lambda_2\) (details of the discrete event simulation model are given in 
@@
 iteration is used to populate the violin plots.
-For all three plots the waiting times generated by the simulation match the
-ones generated by the Markov chains model.
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=.8\textwidth]{imgs/waiting_time_comparison/waiting_1.pdf}
-    \caption{
-        Comparison of mean waiting time for type 1 individuals between values 
-        obtained from the Markov chain formulas and values obtained from 
-        simulation.
-    }
-    \label{fig:markov_vs_des_waiting_time_comparison_1}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=.8\textwidth]{imgs/waiting_time_comparison/waiting_2.pdf}
-    \caption{
-        Comparison of mean waiting time for type 2 individuals between values 
-        obtained from the Markov chain formulas and values obtained from 
-        simulation.
-    }
-    \label{fig:markov_vs_des_waiting_time_comparison_2}
-\end{figure}
+The waiting times generated by the simulation match the ones generated by the 
+Markov chains model.
+Note that this comparison includes both type 1 and type 2 individuals.
+A separate comparison of only type 1 and only type 2 individuals can be found 
+in appendix~\ref{sec:appendix_additional_figures}.
 
@@
 \end{figure}
-
-% TODO: Possibly add another example that will be used in section 5

### 2021-11-19 title.tex
Update author names
Add changes suggested by guide for authors
- Add abstract
- Add acknowledgements
- Fix the title page
- Change bibliogrpahy style

@@
-\title{A game theoretic model of the behavioural gaming that takes place at the EMS - ED interface}
-\author{Michalis Panayides}
-\date{}
+\title{A game theoretic model of the behavioural gaming that takes place at the 
+EMS - ED interface\tnoteref{t1}}
+\tnotetext[t1]{This document is the results of the research project funded by 
+the heathcare improvement studies institute.}
+
+\author[1]{Michalis Panayides\corref{cor1}}
+\ead{panayidesM@cardiff.ac.uk}
+
+\author[2]{Vince Knight}
+\ead{knightva@cardiff.ac.uk}
+
+\author[3]{Paul Harper}
+\ead{harper@cardiff.ac.uk}
+
+\address[1]{The Abacws 2.67, Senghennydd Rd, Cardiff CF24 4AX, United Kingdom}
+\address[2]{The Abacws 2.52, Senghennydd Rd, Cardiff CF24 4AX, United Kingdom}
+\address[3]{The Abacws 2.56, Senghennydd Rd, Cardiff CF24 4AX, United Kingdom}
+
+\cortext[cor1]{Corresponding author}

### 2021-11-19 known.py
Make changes based on spellchecker
- Update known words
- Fix a minor typo

@@ -1,9 +1,11 @@
 """ A set of known words and end-of-word patterns for the spellchecker. """
 
 words = {
+    "Abacws",
     "abg",
     "alsoletter",
     "automata",
+    "Ax",
     "Ay",
     "backcolor",
     "backgroundcolor",
@@ -63,6 +65,7 @@ words = {
     "RGB",
     "RHS",
     "runtime",
+    "Senghennydd",
     "sensical",
     "societally",
     "stochasticity",

### 2021-11-19 known.py
Add `apalike` to known words

@@ -4,6 +4,7 @@ words = {
     "Abacws",
     "abg",
     "alsoletter",
+    "apalike",
     "automata",
     "Ax",
     "Ay",

### 2021-11-22 sections/abstract/main.tex
Add changes suggested by guide for authors
- Add abstract
- Add acknowledgements
- Fix the title page
- Change bibliogrpahy style
Minor changes based on subsequent review
- Changes in title page (addresses)
- Changes in abstract
- Changes in acknowledgements

@@
 \begin{abstract}
-The focus of this research is the construction of a 3-player game theoretic 
-model between two queueing systems and a service that distributes individuals 
-to them. 
-The resultant model will then be used to explore dynamics between all players.
+This research describes the development and application of a 3-player game 
+theoretic model between two queueing systems and a service that distributes 
+individuals to them. 
+The resultant model is used to explore dynamics between all players.
 The first aspect of this work is the development of a queueing system with two
-consecutive waiting spaces. 
-The strategic managerial behaviour corresponds to how individuals use these 
+consecutive waiting spaces where
+the strategic managerial behaviour corresponds to how individuals use these 
 waiting spaces. 
-Two modelling techniques were used: discrete event simulation and Markov chains.
-The state probabilities of the Markov chain system have been used to extract 
+Two modelling techniques are deployed: discrete event simulation and Markov 
+chains.
+The state probabilities of the Markov chain system are used to extract 
 the performance measures of the queueing model (e.g. mean time in each waiting
 room, mean number of individuals in each room, etc.).
-A 3-player game theoretic model is proposed between the two queueing systems
-and the service that distributes individuals to them.
-In particular this can be seen as a 2-player normal-form game where the 
+A 3-player game theoretic model is subsequently proposed between the two 
+queueing systems and the service that distributes individuals to them.
+In particular this can be viewed as a 2-player normal-form game where the 
 utilities are determined by a third player with its own strategies and 
@@
 game between the two queueing systems.
-This particular system can be applied in a healthcare scenario where it 
-captures the emergent behaviour between, for example, the Emergency Medical 
+This particular system has many applications, including those in healthcare
+where it captures the emergent behaviour between the Emergency Medical 
 Service (EMS) and the Emergency Department (ED). 
-This will be used to investigate the impact of target measures on patient 
-well-being.
+The impact of time-target measures on patient well-being is explored in this 
+paper.
 \end{abstract}
+
+\begin{keyword}
+    Game theory \sep Queueing theory \sep OR in healthcare
+\end{keyword}

### 2021-11-22 title.tex
Make changes based on spellchecker
- Update known words
- Fix a minor typo
Minor changes based on subsequent review
- Changes in title page (addresses)
- Changes in abstract
- Changes in acknowledgements

@@
 \tnotetext[t1]{This document is the results of the research project funded by 
-the heathcare improvement studies institute.}
+the healthcare improvement studies institute.}
 
@@
 
-\author[2]{Vince Knight}
+\author[1]{Vince Knight}
 \ead{knightva@cardiff.ac.uk}
 
-\author[3]{Paul Harper}
+\author[1]{Paul Harper}
 \ead{harper@cardiff.ac.uk}
 
-\address[1]{The Abacws 2.67, Senghennydd Rd, Cardiff CF24 4AX, United Kingdom}
-\address[2]{The Abacws 2.52, Senghennydd Rd, Cardiff CF24 4AX, United Kingdom}
-\address[3]{The Abacws 2.56, Senghennydd Rd, Cardiff CF24 4AX, United Kingdom}
+\address[1]{School of Mathematics, Cardiff University, Cardiff CF24 4AX, United Kingdom}
 

### 2021-11-25 title.tex
Final changes before submitting paper

@@
 \tnotetext[t1]{This document is the results of the research project funded by 
-the healthcare improvement studies institute.}
+The Healthcare Improvement Studies (THIS) institute.}
 
-\author[1]{Michalis Panayides\corref{cor1}}
+\author{Michalis Panayides\corref{cor1}}
 \ead{panayidesM@cardiff.ac.uk}
 
-\author[1]{Vince Knight}
+\author{Vince Knight}
 \ead{knightva@cardiff.ac.uk}
 
-\author[1]{Paul Harper}
+\author{Paul Harper}
 \ead{harper@cardiff.ac.uk}
 
-\address[1]{School of Mathematics, Cardiff University, Cardiff CF24 4AX, United Kingdom}
+\address{School of Mathematics, Cardiff University, Cardiff CF24 4AX, United Kingdom}
 

### 2021-11-25 sections/appendix/proportion_within_target_formula/main.tex
Fix some of the `TODOs` (#17)
* Add sections to README.md

* Minor fix in Markov chain formulas

For all formulas consider the arriving state [A_i (u,v)] for individuals
from class i rather than just (u,v). Basically when an individual
arrives at state (u,v) the model will move to a new state based on
that individual's type. This is what this change corresponds to.

* Minor changes on waiting zones

- Display waiting zones 1 and 2 on the queueing system
- Fix some text that listed the incorrect waiting zones

* Changes based on self review

I just read the whole thing and made some minor
chang

@@
 
-Consider the Markov model of figure 
+Consider the Markov model of Figure 
 \ref{fig:distribution_of_time_at_specific_state_1_server} with one server and a 
@@
 
-Thus, the waiting and service time of an individual in the model of figure 
+Thus, the waiting and service time of an individual in the model of Figure 
 \ref{fig:distribution_of_time_at_specific_state_1_server} can be captured by an 
@@
 Figure \ref{fig:distribution_of_time_at_specific_state_2_servers} represents the 
-same Markov model as figure 
+same Markov model as Figure 
 \ref{fig:distribution_of_time_at_specific_state_1_server} with the only 
@@
 any size \cite{Favaro2010}.
-In the Markov chain models described in figures 
+In the Markov chain models described in Figures 
 \ref{fig:distribution_of_time_at_specific_state_1_server} and 

### 2021-11-25 sections/conclusion/main.tex
Fix some of the `TODOs` (#17)
* Add sections to README.md

* Minor fix in Markov chain formulas

For all formulas consider the arriving state [A_i (u,v)] for individuals
from class i rather than just (u,v). Basically when an individual
arrives at state (u,v) the model will move to a new state based on
that individual's type. This is what this change corresponds to.

* Minor changes on waiting zones

- Display waiting zones 1 and 2 on the queueing system
- Fix some text that listed the incorrect waiting zones

* Changes based on self review

I just read the whole thing and made some minor
chang

@@
 The motivation behind this study has been that emergency departments are 
-constantly under a lot of pressure to satisfy some regulations. 
+under a lot of pressure to satisfy some regulations. 
 This paper shows how this can negatively impact the pathway of both the 
@@
 Due to some managerial decision making that takes place at the ED, ambulances 
-stay blocked outside of the ED at the hospital's parking space in an attempt
+stay blocked outside of the ED at the hospital's parking zone in an attempt
 to satisfy these regulations.
@@
 along with ways to apply some incentive mechanisms to improve them.
-The main takeaways from this paper that were observed when playing the game
+The key findings from this paper that were observed when playing the game
 between two EDs and the EMS (section \ref{sec:application}) are:
@@
 Additionally, the game theoretic model that was created uses a discrete 
-strategy space for the EDs (something that is also present in various pieces of 
+strategy space for the EDs (something that is also present in various related 
 literature~\cite{deo2011centralized, knight2017measuring}).
@@
 decision making process.
-Finally this work assumes that ambulances and EDs act in a selfish and rational
+Finally this work assumes that the EMS and EDs act in a selfish and rational
 way by only aiming to satisfy their own objectives.
 In fact, modelling behaviour in a healthcare setting is a much more complex 
-task where some cooperation is often observed.
+task where some cooperation may often be observed.
 Another extension would be to explore the behaviour of the ED staff via an 

### 2021-11-25 sections/methodology/main.tex
Fix some of the `TODOs` (#17)
* Add sections to README.md

* Minor fix in Markov chain formulas

For all formulas consider the arriving state [A_i (u,v)] for individuals
from class i rather than just (u,v). Basically when an individual
arrives at state (u,v) the model will move to a new state based on
that individual's type. This is what this change corresponds to.

* Minor changes on waiting zones

- Display waiting zones 1 and 2 on the queueing system
- Fix some text that listed the incorrect waiting zones

* Changes based on self review

I just read the whole thing and made some minor
chang

@@
 
-Th problem defined in section \ref{sec:model_overview} describes a normal-form
+The problem defined in section \ref{sec:model_overview} describes a normal-form
 game between the decision makers of two queueing systems and a third player that 
@@
 and \(p_A + p_B = 1\).
-Figure \ref{fig:imperfect_info_game} form section \ref{sec:model_overview} 
+Figure \ref{fig:imperfect_info_game} 
 shows a diagrammatic representation of the game to be played and the decisions 
 to be made.
-As described in section \ref{sec:model_overview} queueing system \(A\) decides
-on a strategy, at the same time, queueing system \(B\) chooses its own 
-threshold, unaware of the first queueing system's choice.
+As described in Section \ref{sec:model_overview}, queueing system \(A\) decides
+on a strategy and at the same time, queueing system \(B\) chooses its own 
+threshold but unaware of the first queueing system's choice.
 Finally, the distributor makes its choice based on the strategies that the 
@@
 The payoff matrices and their utilities are defined by equations 
-(\ref{eq:payoff_entry}) and (\ref{eq:payoff_matrices}) in section 
-\ref{sec:model_overview}.
+(\ref{eq:payoff_entry}) and (\ref{eq:payoff_matrices}).
 
@@
 a best response to the actions of the queueing systems.
-Equation \ref{eq:obj_distributor} is defined and explained in section 
-\ref{sec:model_overview}.
 Thus, using equation \ref{eq:obj_distributor} for all possible sets of 
@@
 of backwards induction is used.
-Consider figure \ref{fig:imperfect_info_game} and the flow of the game that was
+Consider Figure \ref{fig:imperfect_info_game} and the flow of the game that was
 described (i.e. \(Q_A, Q_B \rightarrow D\)).
@@
 Indeed, some Nash equilibria might not arise naturally. 
-Thus, in order to analyse the strategies played by the two EDs, the learning 
-algorithm: asymmetric replicator dynamics is 
+Thus in order to analyse the strategies played by the two EDs, the learning 
+algorithm asymmetric replicator dynamics is 
 used~\cite{asymmetricreplicatordynamics}.

### 2021-11-25 sections/model_overview/main.tex
Fix some of the `TODOs` (#17)
* Add sections to README.md

* Minor fix in Markov chain formulas

For all formulas consider the arriving state [A_i (u,v)] for individuals
from class i rather than just (u,v). Basically when an individual
arrives at state (u,v) the model will move to a new state based on
that individual's type. This is what this change corresponds to.

* Minor changes on waiting zones

- Display waiting zones 1 and 2 on the queueing system
- Fix some text that listed the incorrect waiting zones

* Changes based on self review

I just read the whole thing and made some minor
chang

@@
 are blocked.
+Although we generalise for any such system, relating this back to the
+motivating case study, here the decision makers of the queueing systems
+represent the ED managers and the distributor is the EMS who allocate (send)
+ambulances to one of the EDs (see Section \ref{sec:ems_ed_application}). 
 % TODO: Depending on how this is described earlier, we might need a little more 
@@
 
-Both queueing systems follow a queueing model that has two waiting spaces for 
+Both queueing systems follow a queueing model that has two waiting zones for 
 individuals. 
@@
     The threshold \(T\) only applies to arrivals from the first buffer. 
-    If the second buffer is at that threshold only individuals of the first type 
+    If the second buffer is at that threshold, only individuals of the first type 
     are accepted (at a rate \(\lambda_1\)) and individuals of the second type 
-    (arriving at a rate \(\lambda_2\)) are held blocked in the first buffer.}
+    (arriving at a rate \(\lambda_2\)) are blocked in the first buffer.}
     \label{fig:diagram_of_queueing_system}
@@
 Note here that both types of individuals can become lost to the system. 
-Individual allocated from the distributor become lost to the system whenever 
+An individual allocated from the distributor becomes lost to the system whenever 
 an arrival occurs and the second waiting zone is at full capacity (\(M\) 
 individuals already waiting).
-Similarly, other individuals get lost whenever they arrive at the first waiting 
+Similarly, individuals get lost whenever they arrive at the first waiting 
 zone and it is at full capacity (\(N - C\) individuals already waiting).
@@
 Equation \ref{eq:obj_distributor} can be used to capture a mixture 
-between the two objectives \(L_i\) and \(B_i\) where \(i \in \{A, B\}\).
+between the two objectives \(L_i\) and \(B_i\) where \(i \in \{A, B\}\):
 \begin{equation*}\label{eq:obj_distributor}
@@
 
-Using either equation (\ref{eq:obj_queueing_systems}) or equation
-(\ref{eq:obj_distributor}) gives an imperfect information extensive form game. 
+Using either equation (\ref{eq:obj_distributor}) or 
+(\ref{eq:obj_queueing_systems}) gives an imperfect information extensive form 
+game. 
 An imperfect information game is defined as an extensive form game where some 
@@
 
-Based on the choice of strategy of these two players the distributor will then 
+Based on the choice of strategy of these two players, the distributor will then 
 make their own choice of the proportion of individuals to send to each system.

### 2021-11-25 sections/queueing_model/blocking_time/main.tex
Changes based on self review
I just read the whole thing and made some minor
changes here and there.
Fix some of the `TODOs` (#17)
* Add sections to README.md

* Minor fix in Markov chain formulas

For all formulas consider the arriving state [A_i (u,v)] for individuals
from class i rather than just (u,v). Basically when an individual
arrives at state (u,v) the model will move to a new state based on
that individual's type. This is what this change corresponds to.

* Minor changes on waiting zones

- Display waiting zones 1 and 2 on the queueing system
- Fix some text that listed the incorrect

@@
 
-The term \(b(u,v)\) is the mean time that an individual will be blocked when 
-the system is at state \((u,v)\). 
+The term \(b(u,v)\) is the mean time that an individual will be blocked for, 
+when the individual arrives in the system at state \((u,v)\). 
 For all the states of the system \(b(u,v)\) is given by:
@@
 Additionally, \(c(u,v)\) is the mean sojourn time for each state and \(p_s\) 
-and \(p_a\) are the probabilities that the next event to occur will be a service completion or an arrival of a type 1 individual:
+and \(p_a\) are the probabilities that the next event to occur will be a 
+service completion or an arrival of a type 1 individual:
 
@@
 iteration is used to populate the violin plots.
+It can be seen that the blocking times generated by the simulation match the
+ones generated by the Markov chains model.
 

### 2021-11-25 known.py

@@ -1,9 +1,12 @@
 """ A set of known words and end-of-word patterns for the spellchecker. """
 
 words = {
+    "Abacws",
     "abg",
     "alsoletter",
+    "apalike",
     "automata",
+    "Ax",
     "Ay",
     "backcolor",
     "backgroundcolor",
@@ -63,6 +66,7 @@ words = {
     "RGB",
     "RHS",
     "runtime",
+    "Senghennydd",
     "sensical",
     "societally",
     "stochasticity",

### 2022-02-21 sections/model_overview/main.tex
Change vocabulary in game section

@@
 \begin{itemize}
-    \item the decision makers of two queueing systems;
-    \item a service that distributes individuals to these two queueing systems.
+    \item the decision makers of two Emergency Departments (EDs);
+    \item the Emergency Medical Services (EMS) that distribute individuals in ambulances to the EDs.
 \end{itemize}
@@
 optimise.
-More specifically, the queueing systems' objective is captured by an upper bound
+More specifically, the EDs' objective is captured by an upper bound
 of the time that a fixed proportion of individuals spend in the system, 
-while the distributor aims to minimise the time that its individuals 
+while the EMS aims to minimise the time that its ambulances 
 are blocked.
-Although we generalise for any such system, relating this back to the
-motivating case study, here the decision makers of the queueing systems
-represent the ED managers and the distributor is the EMS who allocate (send)
-ambulances to one of the EDs (see Section \ref{sec:ems_ed_application}). 
-% TODO: Depending on how this is described earlier, we might need a little more 
-% here (as to what we mean by "blocked")
+This can be generalised for any such system where instead of EDs there are some
+queueing systems and instead of the EMS there is some distributor that allocates individuals to the queueing systems.
 
-The queueing systems are designed in such a way where they can accept two types
+The queueing systems of the hospitals are designed in such a way where they can
+accept two types
 of individuals. 
-These are the individuals that are allocated by the distributor and 
-other individuals from other sources. 
-Each queueing system may then choose to block the individuals that arrive from 
-the distributor when the system reaches a certain capacity. 
-The strategy sets for each queueing system is the set 
+Type 2 individuals are the ones arriving in ambulances that are allocated by
+the ambulance service and 
+type 1 individuals from other sources (e.g walk-in patients, urgent patients).
+Each hospital may then choose to block the individuals that arrive in
+ambulances when the hospital reaches a certain capacity. 
+The strategy sets for each hospital is the set 
 \( \{T \in \mathbb{N} \;|\; 1 \leq T \leq N\} \) where \(N \in\{N_A, N_B\}\) are 
-the total capacities of the two queueing systems. We denote the chosen actions 
+the total capacities of hospitals \(A\) and \(B\). We denote the chosen actions 
 from the strategy set as \(T_A, T_B\) and call these \textit{threshold}s.
 
-Both queueing systems follow a queueing model that has two waiting zones for 
+Both hospitals follow a queueing model with two waiting zones for 
 individuals. 
-The first waiting zone is where the individuals queue right before receiving 
+The first waiting zone (i.e. the waiting space of the hospital) is where the 
+patients queue right before receiving 
 their service and has a capacity of \( N - C \), where \(N\) is the total 
 capacity of the waiting space and \(C\) is the number of servers. 
-The second waiting zone is where the individuals, that are sent from the 
-distributor, stay until they are allowed to enter the first waiting zone.
+% TODO: Mention what we mean by servers here?
+The second waiting zone (i.e. the parking space for ambulances) is where 
+ambulances, that are sent from the
+EMS, stay until they are allowed to enter the first waiting zone.
 The second waiting zone has a capacity of \(M\) and no servers.
@@
     \caption{A diagrammatic representation of the queueing model. 
-    The threshold \(T\) only applies to arrivals from the first buffer. 
-    If the second buffer is at that threshold, only individuals of the first type 
+    The threshold \(T\) only applies to type 2 individuals.
+    If the number of individuals in waiting zone 2 is \(T\), only 
+    individuals of the first type 
     are accepted (at a rate \(\lambda_1\)) and individuals of the second type 
-    (arriving at a rate \(\lambda_2\)) are blocked in the first buffer.}
+    (arriving at a rate \(\lambda_2\)) are blocked in waiting zone 2.}
     \label{fig:diagram_of_queueing_system}
@@
 Note here that both types of individuals can become lost to the system. 
-An individual allocated from the distributor becomes lost to the system whenever 
-an arrival occurs and the second waiting zone is at full capacity (\(M\) 
-individuals already waiting).
-Similarly, individuals get lost whenever they arrive at the first waiting 
-zone and it is at full capacity (\(N - C\) individuals already waiting).
+An individual allocated from the ambulance service becomes lost to the system 
+whenever 
+an arrival occurs and the waiting zone 2 is at full capacity (\(M\) 
+ambulances already parked).
+Similarly, individuals get lost whenever they arrive at the waiting 
+zone 1 and it is at full capacity (\(N - C\) individuals already waiting).
 
@@
 then rely solely on satisfying their own 
-objective, which is to make sure that the waiting time in the first waiting zone 
-of a proportion of individuals will be below the predefined target time.
+objective, which is to satisfy:
 
@@
 
-The third player, the distributor, has their own choices to make and their own 
+The third player, the ambulance service, has their own choices to make and 
+their own 
 goals to satisfy.
 The strategy set of the third player is the proportion \(0 \leq p_A \leq 1\) of 
-individuals it sends to the first queueing system (the proportion 
-\(p_B = 1 - p_A\) is sent to the second queueing system).
-In addition, the distributor aims to minimise any potential blockages
-that may occur, given the pair of thresholds chosen by the two queueing systems.
-Thus, its objective is to minimise the blocked time of the individuals (\(B_i\))
-that they send to the two queueing systems.
+individuals to send to hospital A.
+Similarly the proportion of individuals to send to hospital B is given by
+\(p_B = 1 - p_A\).
+In addition, the ambulance service aims to minimise any potential blockages
+that may occur, given the pair of thresholds chosen by the two hospitals.
+Thus, its objective is to minimise the blocked time of the individuals 
+(\(B_A\) and \(B_B\))
+that they send to hospitals \(A\) and \(B\).
 Apart from the time being blocked, an additional aspect that may affect the 
-decision of the distributor is the proportion of lost individuals (\(L_i\)).
+decision of the distributor is the proportion of lost individuals 
+\(L_A\) and \(L_B\).
 Equation \ref{eq:obj_distributor} can be used to capture a mixture 
@@
 players~\cite{Berwanger2008}. In this study the state of the problem that is
-hidden is the threshold that each of the first two players chooses to play.
-In other words, each queueing system chooses to play a strategy without 
-knowing the other system's strategy.
-The distributor then, fully aware of the chosen threshold strategies, 
+hidden is the threshold that each of the hospitals chooses to play.
+In other words, each hospital chooses to play a strategy without 
+knowing the other hospital's strategy.
+The ambulance service then, fully aware of the chosen threshold strategies, 
 distributes individuals among the two systems in order to minimise the time 
-that its individuals will be blocked. Figure \ref{fig:imperfect_info_game} 
-illustrates this.
+that its ambulances will be blocked. 
+Figure \ref{fig:imperfect_info_game} illustrates this.
 
@@
     \begin{tikzpicture}[-, node distance = 3cm, scale=0.8]
-        \node[anchor=north](HA){\(Q_A\)};
+        \node[anchor=north](HA){\(H_A\)};
         \node[anchor=north](HA_d1) at (3, 2){.};
@@
 
-        \node[anchor=north](HB) at (4.1, 0){\(Q_B\)};
+        \node[anchor=north](HB) at (4.1, 0){\(H_B\)};
         \node[anchor=north](HB_d1) at (6.9, 2){.};
@@
 The first 
-queueing system \(Q_A\) decides on a threshold, then the second system \(Q_B\)
-chooses its own threshold, without knowing the strategy of \(Q_A\), and finally
+queueing system \(H_A\) decides on a threshold, then the second system \(H_B\)
+chooses its own threshold, without knowing the strategy of \(H_A\), and finally
 the distributor makes its choice. Note here that the dotted line represents the
-fact that \(Q_B\) is unaware of the state of the game when making its own 
+fact that \(H_B\) is unaware of the state of the game when making its own 
 decisions.
 
-In order to define the normal form game the two payoff matrices of the players 
+In order to define the normal form game the two payoff matrices of the hospitals 
 are required. From equation \ref{eq:obj_queueing_systems} the utilities of the
-players can be formulated as:
+hospitals can be formulated as:
 
@@
 
-Based on the choice of strategy of these two players, the distributor will then 
+Based on the choice of strategy of these two hospitals, the ambulance service 
+will then 
 make their own choice of the proportion of individuals to send to each system.

### 2022-02-21 sections/methodology/main.tex
Change vocabulary in methodology section

@@
 The problem defined in section \ref{sec:model_overview} describes a normal-form
-game between the decision makers of two queueing systems and a third player that 
+game between the decision makers of two hospitals and a third player, the 
+ambulance service, that 
 decides how to distribute individuals to the systems.
-The strategy space of the two queueing systems is defined as the possible values
+The strategy space of the two hospitals is defined as the possible values
 that the threshold parameter can take \(T_i \in [1, N_i]\).
-Then, the distributor has to decide on the proportion of individuals to send to 
-each queueing system \(p_A \text{ and } p_B\), where \(p_A, p_B \in [0, 1] \)
+Then, the ambulance service has to decide on the proportion of individuals to 
+send to 
+each hospital \(p_A \text{ and } p_B\), where \(p_A, p_B \in [0, 1] \)
 and \(p_A + p_B = 1\).
@@
 to be made.
-As described in Section \ref{sec:model_overview}, queueing system \(A\) decides
-on a strategy and at the same time, queueing system \(B\) chooses its own 
-threshold but unaware of the first queueing system's choice.
-Finally, the distributor makes its choice based on the strategies that the 
-queueing systems chose to play.
+As described in Section \ref{sec:model_overview}, hospital \(A\) decides
+on a strategy and at the same time, hospital \(B\) chooses its own 
+threshold but unaware of the first hospital's choice.
+Finally, the ambulance service makes its choice based on the strategies that the 
+hospitals chose to play.
 
@@
 The routing matrix holds the values \((p_A, p_B)\) which are the proportion 
-of class 2 individuals to send to queueing system \(A\) and \(B\).
+of ambulance patients to send to queueing systems \(A\) and \(B\).
 Each pair \((p_A, p_B)\) can be calculated using equation 
 (\ref{eq:obj_distributor}) and is essentially
-a best response to the actions of the queueing systems.
+a best response to the actions of the hospitals.
 Thus, using equation \ref{eq:obj_distributor} for all possible sets of 
 thresholds we can get the full routing matrix that consists of the proportions
-to send to queueing system A (\(p_A\)) and to queueing system B (\(p_B\)).
+to send to hospital A (\(p_A\)) and to hospital B (\(p_B\)).
 
@@
 The game can thus be partitioned into a normal form game between the
-two queueing systems and then finding the distributor's best strategy.
+two hospitals and then finding the ambulance service's best strategy.
 
@@
 Consider Figure \ref{fig:imperfect_info_game} and the flow of the game that was
-described (i.e. \(Q_A, Q_B \rightarrow D\)).
+described (i.e. \(H_A, H_B \rightarrow D\)).
 Due to the fact that the payoff matrices \(A\) and \(B\) depend on the routing 
 matrix \(R\) the entries of the matrices are calculated in a backwards way 
-(\(D \rightarrow Q_A, Q_B\)). 
+(\(D \rightarrow H_A, H_B\)). 
 Thus for every pair of strategies \(T_A, T_B\), the proportion of individuals 
@@
 \(N_B = 3\).
-The strategy space of players \(Q_A\) and \(Q_B\) would then be 
+The strategy space of players \(H_A\) and \(H_B\) would then be 
 \(T_A = \{1, 2, 3, 4\}\) and \(T_B = \{1, 2, 3\}\) respectively.
@@
 
-These are the utilities of players \(A\) and \(B\) when both players choose a
+These are the utilities of hospitals \(A\) and \(B\) when both players choose a
 strategy of \(T = 1\).
@@
 Indeed, some Nash equilibria might not arise naturally. 
-Thus in order to analyse the strategies played by the two EDs, the learning 
+Thus in order to analyse the strategies played by the two hospitals, the 
+learning 
 algorithm asymmetric replicator dynamics is 
 used~\cite{asymmetricreplicatordynamics}.
-The two players are modelled as two separate populations where each 
+The two hospitals are modelled as two separate populations where each 
 individual in the population is assigned a strategy.

### 2022-02-23 imgs/truncation_effect/blocking/main.py
Get initial plots of truncation effects
Plots added on unbounded simulation VS Markov chain (while
increasing capacity):
- Waiting time
- Blocking time
- Proportion of individuals within time

@@ -1,0 +1,91 @@
+import matplotlib.pyplot as plt
+import numpy as np
+import ambulance_game as abg
+
+lambda_1 = 2
+mu = 3
+num_of_servers = 3
+threshold = 8
+seed_num = 1
+warm_up_time = 100
+num_of_trials = 20
+runtime = 10000
+# warm_up_time = 10
+# num_of_trials = 10
+# runtime = 100
+
+all_sim_blocking_times = []
+all_markov_blocking_times_low = []
+all_markov_blocking_times_mid = []
+all_markov_blocking_times_high = []
+lambda_2_space = np.linspace(2, 6, 6)
+all_capacity_values = (10, 30, 50)
+for lambda_2 in lambda_2_space:
+    # Simulation
+    simulation_results = abg.simulation.get_multiple_runs_results(
+        lambda_2=lambda_2,
+        lambda_1=lambda_1,
+        mu=mu,
+        num_of_servers=num_of_servers,
+        threshold=threshold,
+        system_capacity=float("inf"),
+        buffer_capacity=float("inf"),
+        seed_num=seed_num,
+        warm_up_time=warm_up_time,
+        num_of_trials=num_of_trials,
+        runtime=runtime,
+        class_type=None,
+    )
+    all_sim_blocking_times.append(
+        [np.mean(b.blocking_times) for b in simulation_results]
+    )
+
+    # Markov
+    for capacity_value in all_capacity_values:
+        markov_blocking_time = (
+            abg.markov.get_mean_blocking_time_using_markov_state_probabilities(
+                lambda_2=lambda_2,
+                lambda_1=lambda_1,
+                mu=mu,
+                num_of_servers=num_of_servers,
+                threshold=threshold,
+                system_capacity=capacity_value,
+                buffer_capacity=capacity_value,
+            )
+        )
+        if capacity_value == all_capacity_values[0]:
+            all_markov_blocking_times_low.append(markov_blocking_time)
+        elif capacity_value == all_capacity_values[1]:
+            all_markov_blocking_times_mid.append(markov_blocking_time)
+        elif capacity_value == all_capacity_values[2]:
+            all_markov_blocking_times_high.append(markov_blocking_time)
+        else:
+            raise ValueError("Invalid capacity value")
+
+# Waiting time both individuals
+fig, (ax1, ax2, ax3) = plt.subplots(nrows=1, ncols=3, figsize=(15, 5))
[…]

### 2022-02-23 imgs/truncation_effect/proportion/main.py

@@ -1,0 +1,93 @@
+import matplotlib.pyplot as plt
+import numpy as np
+import ambulance_game as abg
+
+lambda_1 = 2
+mu = 3
+num_of_servers = 3
+threshold = 8
+target = 0.5
+seed_num = 1
+warm_up_time = 0
+num_of_trials = 20
+runtime = 10000
+# warm_up_time = 10
+# num_of_trials = 10
+# runtime = 100
+
+all_sim_props = []
+all_markov_props_low = []
+all_markov_props_mid = []
+all_markov_props_high = []
+lambda_2_space = np.linspace(2, 6, 6)
+all_capacity_values = (10, 30, 50)
+for lambda_2 in lambda_2_space:
+    # Simulation
+    (
+        simulation_results,
+        _,
+        _,
+    ) = abg.simulation.get_mean_proportion_of_individuals_within_target_for_multiple_runs(
+        lambda_2=lambda_2,
+        lambda_1=lambda_1,
+        mu=mu,
+        num_of_servers=num_of_servers,
+        threshold=threshold,
+        system_capacity=float("inf"),
+        buffer_capacity=float("inf"),
+        seed_num=seed_num,
+        num_of_trials=num_of_trials,
+        runtime=runtime,
+        target=target,
+    )
+    all_sim_props.append(simulation_results)
+
+    # Markov
+    for capacity_value in all_capacity_values:
+        markov_proportions = (
+            abg.markov.proportion_within_target_using_markov_state_probabilities(
+                lambda_2=lambda_2,
+                lambda_1=lambda_1,
+                mu=mu,
+                num_of_servers=num_of_servers,
+                threshold=threshold,
+                system_capacity=capacity_value,
+                buffer_capacity=capacity_value,
+                class_type=None,
+                target=target,
+            )
+        )
+        if capacity_value == all_capacity_values[0]:
+            all_markov_props_low.append(markov_proportions)
+        elif capacity_value == all_capacity_values[1]:
+            all_markov_props_mid.append(markov_proportions)
+        elif capacity_value == all_capacity_values[2]:
+            all_markov_props_high.append(markov_proportions)
+        else:
+            raise ValueError("Invalid capacity value")
+
+# Waiting time both individuals
+fig, (ax1, ax2, ax3) = plt.subplots(nrows=1, ncols=3, figsize=(15, 5))
+for index, (ax, all_markov_times) in enumerate(
[…]

### 2022-02-23 imgs/truncation_effect/waiting/main.py

@@ -1,0 +1,90 @@
+import matplotlib.pyplot as plt
+import numpy as np
+import ambulance_game as abg
+
+lambda_1 = 2
+mu = 3
+num_of_servers = 3
+threshold = 8
+seed_num = 1
+warm_up_time = 100
+num_of_trials = 20
+runtime = 10000
+# warm_up_time = 10
+# num_of_trials = 10
+# runtime = 100
+
+all_sim_waiting_times = []
+all_markov_waiting_times_low = []
+all_markov_waiting_times_mid = []
+all_markov_waiting_times_high = []
+lambda_2_space = np.linspace(2, 6, 6)
+all_capacity_values = (10, 30, 50)
+for lambda_2 in lambda_2_space:
+    # Simulation
+    simulation_results = abg.simulation.get_multiple_runs_results(
+        lambda_2=lambda_2,
+        lambda_1=lambda_1,
+        mu=mu,
+        num_of_servers=num_of_servers,
+        threshold=threshold,
+        system_capacity=float("inf"),
+        buffer_capacity=float("inf"),
+        seed_num=seed_num,
+        warm_up_time=warm_up_time,
+        num_of_trials=num_of_trials,
+        runtime=runtime,
+        class_type=None,
+    )
+    all_sim_waiting_times.append([np.mean(w.waiting_times) for w in simulation_results])
+
+    # Markov
+    for capacity_value in all_capacity_values:
+        markov_waiting_time = (
+            abg.markov.get_mean_waiting_time_using_markov_state_probabilities(
+                lambda_2=lambda_2,
+                lambda_1=lambda_1,
+                mu=mu,
+                num_of_servers=num_of_servers,
+                threshold=threshold,
+                system_capacity=capacity_value,
+                buffer_capacity=capacity_value,
+                class_type=None,
+            )
+        )
+        if capacity_value == all_capacity_values[0]:
+            all_markov_waiting_times_low.append(markov_waiting_time)
+        elif capacity_value == all_capacity_values[1]:
+            all_markov_waiting_times_mid.append(markov_waiting_time)
+        elif capacity_value == all_capacity_values[2]:
+            all_markov_waiting_times_high.append(markov_waiting_time)
+        else:
+            raise ValueError("Invalid capacity value")
+
+# Waiting time both individuals
[…]

### 2022-02-25 sections/model_overview/main.tex
Minor typo
Fix proselint failure by removing the word very from a comment
Additional changes in game section
- Replace waiting zone 1 with hospital
- Replace waiting zone 2 with parking space
- Use type 2 patients everywhere instead of ambulance patients

@@
 \begin{itemize}
-    \item the decision makers of two Emergency Departments (EDs);
-    \item the Emergency Medical Services (EMS) that distribute individuals in ambulances to the EDs.
+    \item the decision makers of two Emergency Departments (EDs)
+    \item the Emergency Medical Services (EMS) that distribute individuals in 
+    ambulances to the EDs
 \end{itemize}
@@
 This can be generalised for any such system where instead of EDs there are some
-queueing systems and instead of the EMS there is some distributor that allocates individuals to the queueing systems.
+queueing systems and instead of the EMS there is some distributor that allocates 
+individuals to the queueing systems.
 
@@
 of individuals. 
-Type 2 individuals are the ones arriving in ambulances that are allocated by
-the ambulance service and 
-type 1 individuals from other sources (e.g walk-in patients, urgent patients).
-Each hospital may then choose to block the individuals that arrive in
-ambulances when the hospital reaches a certain capacity. 
+% TODO: Decide whether to define type 1, 2 only in game section, only in queueing section, or both
+Type 2 individuals are defined as non-urgent patients arriving in ambulances 
+that are allocated by the ambulance service and 
+type 1 individuals are individuals arriving from other sources 
+(e.g walk-in patients, urgent patients from either walk-ins or ambulances).
+Each hospital may then choose to block type 2 individuals 
+when the hospital reaches a certain capacity. 
 The strategy sets for each hospital is the set 
@@
 patients queue right before receiving 
-their service and has a capacity of \( N - C \), where \(N\) is the total 
-capacity of the waiting space and \(C\) is the number of servers. 
+their service and has a queue capacity of \( N - C \), where \(N\) is the total 
+capacity of the hospital and \(C\) is the number of servers. 
 % TODO: Mention what we mean by servers here?
@@
 ambulances, that are sent from the
-EMS, stay until they are allowed to enter the first waiting zone.
-The second waiting zone has a capacity of \(M\) and no servers.
+ambulance service, stay until their patients are allowed to enter the hospital.
+The parking space has a capacity of \(M\) and no servers.
 
@@
         \)};
-        % The label below Queue 1 -> Waiting zone 2
-        \node[anchor=north] at (1.5cm, -1.7cm) {\small{Waiting zone 2}};
+        % The label below Queue 1 -> Parking space
+        \node[anchor=north] at (1.5cm, -1.7cm) {\small{Parking space}};
 
@@
         \draw (7cm-\i*10pt,1.25) -- +(0,-1.5cm);
-        % The two vertical lines at the very start of Queue 2 
+        % The two vertical lines at the start of Queue 2 
         \draw (7cm-54pt,1.2) -- +(0,-0.5cm);
@@
         % The label between the lines for T
-        \node[anchor=north] at (5.15, 0.77 cm) {\small{\( T \)}};
+        \node[anchor=north] at (5.15, 0.80 cm) {\small{\( T \)}};
 
@@
         \)};
-        % The label below Queue 2 -> Waiting zone 1
-        \node[anchor=north] at (6.2cm, -0.5cm) {\small{Waiting zone 1}};
+        % The label below Queue 2 -> Hospital
+        \node[anchor=north] at (6.2cm, -0.5cm) {\small{Hospital}};
 
@@
     The threshold \(T\) only applies to type 2 individuals.
-    If the number of individuals in waiting zone 2 is \(T\), only 
-    individuals of the first type 
-    are accepted (at a rate \(\lambda_1\)) and individuals of the second type 
-    (arriving at a rate \(\lambda_2\)) are blocked in waiting zone 2.}
+    If the number of individuals in the hospital is \(T\), only 
+    individuals of type 1 
+    are accepted (at a rate \(\lambda_1\)) and individuals of type 2
+    (arriving at a rate \(\lambda_2\)) are blocked in the parking space.}
     \label{fig:diagram_of_queueing_system}
@@
 whenever 
-an arrival occurs and the waiting zone 2 is at full capacity (\(M\) 
+an arrival occurs and the parking space is at full capacity (\(M\) 
 ambulances already parked).
-Similarly, individuals get lost whenever they arrive at the waiting 
-zone 1 and it is at full capacity (\(N - C\) individuals already waiting).
+Similarly, type 1 individuals get lost whenever they arrive at the waiting 
+space of the hospital and it is at full capacity (\(N - C\) individuals already
+waiting).
 
@@
 the mean waiting is more than the target time, and completely ignore the 
-percentage goal.
+percentage goal \(\hat{P}\).
 

### 2022-02-25 sections/queueing_model/blocking_time/main.tex
Change vocabulary in queueing section

@@
 
-Unlike the waiting time, the blocking time is only calculated for individuals of
-the second type.  
-That is because individuals of the first type cannot be blocked. 
+Blocking time is the amount of time that type 2 patients wait in the parking 
+space before they are allowed to proceed to the hospital.
+Unlike the waiting time, the blocking time is only calculated for type 2 
+individuals.  
+That is because type 1 individuals cannot be blocked. 
 Thus, one only needs to consider the pathway of type 2 individuals to get the 

### 2022-02-25 sections/queueing_model/main.tex
Change vocabulary in queueing section

@@
 figure \ref{fig:diagram_of_queueing_system} will be given.
-This is a queueing model that consists of two waiting zones, one for each type
-of individual.
+This is a queueing model that consists of two waiting zones; the parking space
+and the hospital waiting space.
 
 The model consists of two types of individuals; type 1 and type 2.
-Type 1 individuals arrive instantly at waiting zone 1 and wait to receive their 
+% TODO: Decide whether to define type 1, 2 only in queueing section, only in game section, or both
+Type 2 individuals are non-urgent patients arriving in ambulances (i.e. patients
+in ambulances ).
+and type 1 individuals are individuals arriving from other sources 
+(e.g walk-in patients, urgent patients from either walk-ins or ambulances).
+Type 1 individuals arrive instantly at the hospital's waiting space and wait to
+receive their 
 service. 
-Type 2 individuals arrive at waiting zone 2 and wait there until they are 
-allowed to move to waiting zone 1. 
+Type 2 individuals arrive at the parking space and wait there until they are 
+allowed to move to the hospital.
 They are allowed to proceed only when the number of 
-individuals in waiting zone 1 \textbf{and} in service is less than a 
+individuals in the hospital is less than the
 pre-determined threshold \(T\).
 When the number of individuals is equal to or exceeds this threshold, all 
-second type individuals that arrive will stay 
-\textit{blocked} in waiting zone 2 until the number of people in 
-the next queue and in service falls below \(T\). 
+type 2 individuals that arrive will stay 
+\textit{blocked} in the parking space until the number of patients in 
+the hospital falls below \(T\). 
 This is shown diagrammatically in Figure \ref{fig:diagram_of_queueing_system}.
@@
     \item \(C\): The number of servers
-    \item \(T\): The threshold at which individuals of the second type are 
-    blocked
+    \item \(T\): The threshold at which type 2 individuals are blocked
 \end{itemize}
@@
 \begin{itemize}
-    \item \(u\) is the number of individuals blocked
-    \item \(v\) is the number of individuals either in waiting zone 1 or in the
-    service centre
+    \item \(u\) is the number of individuals blocked in the parking space
+    \item \(v\) is the number of individuals waiting or being served in the
+    hospital
 \end{itemize}
@@
 The problem defined above assumes no upper boundary to the number of individuals 
-that can wait for service or for the ones that are blocked in the buffer centre. 
+that can wait in the hospital or for the ones that are blocked in the parking 
+space. 
 Therefore, a different state space \( \tilde S \) is constructed where 
 \( \tilde S \subseteq S \) and there is a maximum allowed number of individuals 
-\(N\) that can be in the system and a maximum allowed number of individuals 
-\(M\) that can be blocked in the buffer centre:
+\(N\) that can be in the hospital and a maximum allowed number of individuals 
+\(M\) that can be blocked in the parking space:
 
@@
 The following equations utilise \(\pi\) to get performance measures on the 
-average number of people at certain sets of state:
+average number of patients at certain sets of state:
 
 \begin{itemize}
-    \item Average number of people in the system: 
+    \item Average number of patients in the entire system: 
         \[L = \sum_{i=1}^{|\pi|} \pi_i (u_i + v_i)\]
-    \item Average number of people in the service centre: 
+    \item Average number of patients in the hospital: 
         \[L_H = \sum_{i=1}^{|\pi|} \pi_i v_i\]
-    \item Average number of people in waiting zone 2:
+    \item Average number of patients in the parking space:
         \[L_A = \sum_{i=1}^{|\pi|} \pi_i u_i\] 
@@
 Such performance measures are the mean waiting time in the system (for both 
-type 1 and type 2 individuals), the mean time blocked in waiting zone 2 (only 
-valid for type 2 individuals) and the proportion of individuals that wait in 
-waiting zone 1 within a predefined time target (for both types).
+type 1 and type 2 individuals), the mean time blocked in the parking space (only
+valid for type 2 individuals) and the proportion of individuals in the hospital
+whose waiting time falls within a predefined time target (for both types).
 

### 2022-03-03 imgs/truncation_effect/blocking/main.py
Add bounded simulation to same plot

@@ -1,3 +1,5 @@
+from matplotlib.lines import Line2D
+from matplotlib.patches import Patch
 import matplotlib.pyplot as plt
 import numpy as np
 import ambulance_game as abg
@@ -10,19 +12,21 @@ seed_num = 1
 warm_up_time = 100
 num_of_trials = 20
 runtime = 10000
-# warm_up_time = 10
-# num_of_trials = 10
-# runtime = 100
 
-all_sim_blocking_times = []
+lambda_2_space = np.linspace(2, 6, 6)
+all_capacity_values = (10, 30, 50)
+
+all_sim_unbound_blocking_times = []
+all_sim_bound_blocking_times_low = []
+all_sim_bound_blocking_times_mid = []
+all_sim_bound_blocking_times_high = []
+
 all_markov_blocking_times_low = []
 all_markov_blocking_times_mid = []
 all_markov_blocking_times_high = []
-lambda_2_space = np.linspace(2, 6, 6)
-all_capacity_values = (10, 30, 50)
 for lambda_2 in lambda_2_space:
-    # Simulation
-    simulation_results = abg.simulation.get_multiple_runs_results(
+    # Unbounded simulation
+    unbounded_simulation_results = abg.simulation.get_multiple_runs_results(
         lambda_2=lambda_2,
         lambda_1=lambda_1,
         mu=mu,
@@ -36,12 +40,12 @@ for lambda_2 in lambda_2_space:
         runtime=runtime,
         class_type=None,
     )
-    all_sim_blocking_times.append(
-        [np.mean(b.blocking_times) for b in simulation_results]
+    all_sim_unbound_blocking_times.append(
+        [np.mean(b.blocking_times) for b in unbounded_simulation_results]
     )
 
-    # Markov
     for capacity_value in all_capacity_values:
+        # Markov
         markov_blocking_time = (
             abg.markov.get_mean_blocking_time_using_markov_state_probabilities(
                 lambda_2=lambda_2,
@@ -53,18 +57,43 @@ for lambda_2 in lambda_2_space:
                 buffer_capacity=capacity_value,
             )
         )
+        # Bounded simulation
+        bounded_simulation_results = abg.simulation.get_multiple_runs_results(
+            lambda_2=lambda_2,
+            lambda_1=lambda_1,
+            mu=mu,
+            num_of_servers=num_of_servers,
+            threshold=threshold,
+            system_capacity=capacity_value,
+            buffer_capacity=capacity_value,
[…]

### 2022-03-03 imgs/truncation_effect/proportion/main.py

@@ -1,3 +1,5 @@
+from matplotlib.lines import Line2D
+from matplotlib.patches import Patch
 import matplotlib.pyplot as plt
 import numpy as np
 import ambulance_game as abg
@@ -11,20 +13,22 @@ seed_num = 1
 warm_up_time = 0
 num_of_trials = 20
 runtime = 10000
-# warm_up_time = 10
-# num_of_trials = 10
-# runtime = 100
 
-all_sim_props = []
+lambda_2_space = np.linspace(2, 6, 6)
+all_capacity_values = (10, 30, 50)
+
+all_sim_unbound_props = []
+all_sim_bound_props_low = []
+all_sim_bound_props_mid = []
+all_sim_bound_props_high = []
+
 all_markov_props_low = []
 all_markov_props_mid = []
 all_markov_props_high = []
-lambda_2_space = np.linspace(2, 6, 6)
-all_capacity_values = (10, 30, 50)
 for lambda_2 in lambda_2_space:
-    # Simulation
+    # Unbounded simulation
     (
-        simulation_results,
+        unbounded_simulation_results,
         _,
         _,
     ) = abg.simulation.get_mean_proportion_of_individuals_within_target_for_multiple_runs(
@@ -40,10 +44,10 @@ for lambda_2 in lambda_2_space:
         runtime=runtime,
         target=target,
     )
-    all_sim_props.append(simulation_results)
+    all_sim_unbound_props.append(unbounded_simulation_results)
 
-    # Markov
     for capacity_value in all_capacity_values:
+        # Markov
         markov_proportions = (
             abg.markov.proportion_within_target_using_markov_state_probabilities(
                 lambda_2=lambda_2,
@@ -57,18 +61,40 @@ for lambda_2 in lambda_2_space:
                 target=target,
             )
         )
+
+        # Bounded simulation
+        (
+            bounded_simulation_results,
+            _,
+            _,
+        ) = abg.simulation.get_mean_proportion_of_individuals_within_target_for_multiple_runs(
+            lambda_2=lambda_2,
+            lambda_1=lambda_1,
+            mu=mu,
+            num_of_servers=num_of_servers,
+            threshold=threshold,
+            system_capacity=capacity_value,
+            buffer_capacity=capacity_value,
+            seed_num=seed_num,
+            num_of_trials=num_of_trials,
+            runtime=runtime,
+            target=target,
+        )
         if capacity_value == all_capacity_values[0]:
[…]

### 2022-03-03 imgs/truncation_effect/waiting/main.py

@@ -1,3 +1,5 @@
+from matplotlib.lines import Line2D
+from matplotlib.patches import Patch
 import matplotlib.pyplot as plt
 import numpy as np
 import ambulance_game as abg
@@ -10,19 +12,21 @@ seed_num = 1
 warm_up_time = 100
 num_of_trials = 20
 runtime = 10000
-# warm_up_time = 10
-# num_of_trials = 10
-# runtime = 100
 
-all_sim_waiting_times = []
+lambda_2_space = np.linspace(2, 6, 6)
+all_capacity_values = (10, 30, 50)
+
+all_sim_unbound_waiting_times = []
+all_sim_bound_waiting_times_low = []
+all_sim_bound_waiting_times_mid = []
+all_sim_bound_waiting_times_high = []
+
 all_markov_waiting_times_low = []
 all_markov_waiting_times_mid = []
 all_markov_waiting_times_high = []
-lambda_2_space = np.linspace(2, 6, 6)
-all_capacity_values = (10, 30, 50)
 for lambda_2 in lambda_2_space:
-    # Simulation
-    simulation_results = abg.simulation.get_multiple_runs_results(
+    # Unbounded simulation
+    unbounded_simulation_results = abg.simulation.get_multiple_runs_results(
         lambda_2=lambda_2,
         lambda_1=lambda_1,
         mu=mu,
@@ -36,10 +40,12 @@ for lambda_2 in lambda_2_space:
         runtime=runtime,
         class_type=None,
     )
-    all_sim_waiting_times.append([np.mean(w.waiting_times) for w in simulation_results])
+    all_sim_unbound_waiting_times.append(
+        [np.mean(w.waiting_times) for w in unbounded_simulation_results]
+    )
 
-    # Markov
     for capacity_value in all_capacity_values:
+        # Markov
         markov_waiting_time = (
             abg.markov.get_mean_waiting_time_using_markov_state_probabilities(
                 lambda_2=lambda_2,
@@ -52,18 +58,43 @@ for lambda_2 in lambda_2_space:
                 class_type=None,
             )
         )
+        # Bounded simulation
+        bounded_simulation_results = abg.simulation.get_multiple_runs_results(
+            lambda_2=lambda_2,
+            lambda_1=lambda_1,
+            mu=mu,
+            num_of_servers=num_of_servers,
+            threshold=threshold,
+            system_capacity=capacity_value,
+            buffer_capacity=capacity_value,
+            seed_num=seed_num,
+            warm_up_time=warm_up_time,
[…]

### 2022-03-03 sections/model_overview/main.tex
Change vocabulary to be more focused on the application (#33)
* Change vocabulary in game section

* Minor typo

Fix proselint failure by removing the word very from a comment

* Change vocabulary in methodology section

* Additional changes in game section

- Replace waiting zone 1 with hospital
- Replace waiting zone 2 with parking space
- Use type 2 patients everywhere instead of ambulance patients

* Change vocabulary in queueing section

@@
 of individuals. 
-% TODO: Decide whether to define type 1, 2 only in game section, only in queueing section, or both
 Type 2 individuals are defined as non-urgent patients arriving in ambulances 
@@
 their service and has a queue capacity of \( N - C \), where \(N\) is the total 
-capacity of the hospital and \(C\) is the number of servers. 
-% TODO: Mention what we mean by servers here?
+capacity of the hospital and \(C\) is the number of healthcare 
+professionals able to see them.
+% TODO: Should this be healthcare professionals or available beds?
 The second waiting zone (i.e. the parking space for ambulances) is where 

### 2022-03-03 sections/queueing_model/proportion_within_target/main.tex
Change vocabulary to be more focused on the application (#33)
* Change vocabulary in game section

* Minor typo

Fix proselint failure by removing the word very from a comment

* Change vocabulary in methodology section

* Additional changes in game section

- Replace waiting zone 1 with hospital
- Replace waiting zone 2 with parking space
- Use type 2 patients everywhere instead of ambulance patients

* Change vocabulary in queueing section

@@
 Another performance measure that is taken into consideration is the proportion 
-of individuals whose waiting and service times are within a specified 
-time target \(t\).
+of individuals whose time in the hospital (waiting and service time) is within
+a specified time target \(t\).
 Similar to section \ref{sec:waiting_time}, three formulas are needed for this 

### 2022-03-04 sections/conclusion/main.tex
Change the overall structure
New structure:
1. Intro + Motvation + Major cotnributions
2. Lit review + Major contributions
3. Queueing model (with performance measures formulas)
4. Game model (with methodology and numerical results)
5. Conclusion

@@
 The game theoretic model is then applied to a healthcare scenario by looking at
-the interface between the EDs and the EMS (section 
-\ref{sec:ems_ed_application}).
+the interface between the EDs and the EMS.
 The inefficiencies that emerge from the perspective of the EMS were explored 
@@
 The key findings from this paper that were observed when playing the game
-between two EDs and the EMS (section \ref{sec:application}) are:
+between two EDs and the EMS are:
 \begin{itemize}

### 2022-03-04 sections/introduction/main.tex
Fix some of the `TODOs` (#17)
* Add sections to README.md

* Minor fix in Markov chain formulas

For all formulas consider the arriving state [A_i (u,v)] for individuals
from class i rather than just (u,v). Basically when an individual
arrives at state (u,v) the model will move to a new state based on
that individual's type. This is what this change corresponds to.

* Minor changes on waiting zones

- Display waiting zones 1 and 2 on the queueing system
- Fix some text that listed the incorrect waiting zones

* Changes based on self review

I just read the whole thing and made some minor
chang

@@
 
-% TODO: If this is one paper remove the queueing model part
-
+% Introduction + motivation
 Emergency departments (EDs) are under increasing pressure to meet patient
@@
 
-A number of papers have been published that touch upon the use of 
-queueing models together with game theoretic concepts.
-In~\cite{FirmCompetition} the authors study a simultaneous price competition 
-between two firms that are modelled as two distinct queueing systems with a 
-fixed capacity and a combined arrival rate.
-They calculate the Nash equilibrium both for identical and heterogeneous firms
-and show that for the former a pure Nash equilibrium always exist and for the 
-latter a unique equilibrium exists where only one firm operates.
-The authors have also extended their model in~\cite{FirmCompetition2} by 
-allowing the players (firms) to choose capacities. 
-A main result from this paper was that when both firms operate independently as
-a monopoly, the equilibria are socially optimal, but this is not the case when
-the firms operate together.
-Another extension of~\cite{FirmCompetition} was introduced 
-in~\cite{FirmCompetitionExtension} where a long-run version of the competition 
-was considered that also had capacity as a decision variable.
-In~\cite{knight2017measuring} a normal form game is built that is informed by a 
-two-dimensional Markov chain in order to model interactions between critical
-care units.
-An additional paper that focuses on competition is~\cite{fan2009short} where
-the authors created a competition between two sellers where seller 1 supplies 
-a product instantly and seller 2 is modelled as a make-to-order M/M/1 queue.
-The game that is played requires the two sellers to make a choice on the price 
-of the product and then seller 2 to set a capacity that guarantees a maximum 
-expected delay.
+% ED + EMS application
+The system defined in section \ref{sec:model_overview} can be applied 
+to a healthcare scenario with two such queueing systems.
+The two queueing systems can be thought of as two Emergency Departments (ED) 
+and the Emergency Medical Services (EMS) as a distributor that distributes 
+patients to them.
 
-In the above models, the players are attempting to increase their share of 
-individuals choosing to queue.
-In public healthcare type settings~\cite{knight2013selfish}, this is not 
-necessarily the case. 
-Players might not necessarily aim to maximise the so called `market share'.
-Rather, the overall service needs to be considered as players aim to minimise
-their experienced congestion.
-In~\cite{sadat2015can} a healthcare application was studied where patients 
-could choose between two hospitals, where a utility function is derived that is
-based on patients' perceived quality of life.
-How individual behaviour based on congestion impacts the efficiency of public 
-services is investigated in~\cite{knight2013selfish}.
-The authors place the individuals' choices between different public services 
-within the formulation of routing games and measure inefficiencies using a 
-concept known as the price of anarchy (PoA)~\cite{koutsoupias1999worst}.
-They show that the price of anarchy increases with worth of service and that is
-low for systems with insufficient capacities.
-In~\cite{deo2011centralized} the authors study the network effect of ambulance 
-diversion by proposing a non-cooperative game between two EDs that are modelled
-as a queueing network.
-Each ED's objective is to minimise its own waiting time and chooses a diversion
-threshold based on the patients it has.
-In equilibrium both EDs choose to divert ambulances in order to avoid getting
-arrivals from the other ED.
-In this paper this concept is extended by allowing the ambulance service to 
-decide how to distribute its patients among the two EDs.
+There are numerous news articles that focus on the problems that arise when 
+ambulances stay blocked outside of the hospital for a long amount of 
+time~\cite{dailyrecords, staffordshirelive}.
+Some news reports also comment on the long idle time of ambulances when 
+they are not in use~\cite{herefordtimes} and there are several reports of 
+examples where this became an issue for new patients~\cite{southwalesargus}.
+A particular article looked into this problem from the point of view of an 
+ambulance paramedic:
 
-Another specific part of our research, as described later in the paper, is the 
-construction of a queueing system with a tandem buffer and a single service
-centre.
-In~\cite{d2015pure} the authors explore threshold joining strategies in a 
-Markov model that has two tandem queues.
-Another example is the one described in~\cite{burnetas2013customer}
-where they investigated a network of multiple tandem queues where customers 
-decide which queue to attend before joining.
-Similarly, in~\cite{bacsar2002stackelberg} the authors examine a network of 
-\(N\) tandem M/M/1 queues and with multi-type customers. 
-The customers in this paper react to a price \(p\) by picking demand rates that 
-maximise utility.
-In~\cite{veltman2005equilibrium} a profit maximisation problem is studied that
-has two servers; an M/M/1 queue and a parking service providing complementary 
-service while the customer is in the first service. 
-The providers gain a reward when customers complete both services and no reward 
-when they finish one of them.
-One of the main conclusions of this study is that by increasing the general 
-demand both providers lower their prices to compensate for the increase in wait.
-The problem was later extended by~\cite{sun2009equilibrium} where they 
-considered arrivals of batches that can share the parking service.
-Finally,~\cite{afeche2007decentralized} examines a tandem network of two M/M/1 
-queues that are ran by two different profit-maximising service providers.
-The network receives three types of customers; those requiring both services, 
-customers requiring the first service and customers requiring the second service.
-The authors showed that optimal prices also maximise social utility and that
-removing two types of customers that don't need both services leads to higher 
-profit and lower demand rate.
+\begin{quotation}
+    % <!--alex ignore he-she her-him-->
+    ``He knows if a patient arrives more urgently in need of help, his will be 
+    pushed back''~\cite{bbcwales}
 
-EDs in the United Kingdom have to follow a set of regulations imposed to 
-them by the National Health Service (NHS).
+    ``We used to bring poorly patients in, and we were out on the road again in
+    15 minutes.''~\cite{bbcwales}
+\end{quotation}
+
+The patients that are distributed by the EMS arrive at the hospital via an 
+ambulance and are then either offloaded at the ED or stay blocked outside in 
+the ambulance.
+Whether or not the ambulance and the patient stay blocked is determined by 
+the threshold that the given ED chooses to play.
+High threshold indicates that the ED accepts patients even if it is relatively 
+full, while low threshold means that the ED blocks ambulances more frequently.
+
+% Major contributions
+In the United Kingdom the National Heath Services (NHS) sets some regulations 
+on ED performance.
 One of these regulations is that 95\% of patients that arrive at the ED should 
@@
 
+% Sign posting
 This paper first gives an overview of the game theoretic model, then goes on 

### 2022-03-04 sections/literature_review/main.tex
Change the overall structure
New structure:
1. Intro + Motvation + Major cotnributions
2. Lit review + Major contributions
3. Queueing model (with performance measures formulas)
4. Game model (with methodology and numerical results)
5. Conclusion

\section{Literature review}

% Literature review
A number of papers have been published that touch upon the use of 
queueing models together with game theoretic concepts.
In~\cite{FirmCompetition} the authors study a simultaneous price competition 
between two firms that are modelled as two distinct queueing systems with a 
fixed capacity and a combined arrival rate.
They calculate the Nash equilibrium both for identical and heterogeneous firms
and show that for the former a pure Nash equilibrium always exist and for the 
latter a unique equilibrium exists where only one firm operates.
The authors have also extended their model in~\cite{FirmCompetition2} by 
allowing the players (firms) to choose capacities. 
A main result from this paper was that when both firms operate independently as
a monopoly, the equilibria are socially optimal, but this is not the case when
the firms operate together.
Another extension of~\cite{FirmCompetition} was introduced 
in~\cite{FirmCompetitionExtension} where a long-run version of the competition 
was considered that also had capacity as a decision variable.
In~\cite{knight2017measuring} a normal form game is built that is informed by a 
two-dimensional Markov chain in order to model interactions between critical
care units.
An additional paper that focuses on competition is~\cite{fan2009short} where
the authors created a competition between two sellers where seller 1 supplies 
a product instantly and seller 2 is modelled as a make-to-order M/M/1 queue.
The game that is played requires the two sellers to make a choice on the price 
of the product and then seller 2 to set a capacity that guarantees a maximum 
expected delay.

In the above models, the players are attempting to increase their share of 
individuals choosing to queue.
In public healthcare type settings~\cite{knight2013selfish}, this is not 
necessarily the case. 
Players might not necessarily aim to maximise the so called `market share'.
Rather, the overall service needs to be considered as players aim to minimise
their experienced congestion.
In~\cite{sadat2015can} a healthcare application was studied where patients 
could choose between two hospitals, where a utility function is derived that is
based on patients' perceived quality of life.
How individual behaviour based on congestion impacts the efficiency of public 
services is investigated in~\cite{knight2013selfish}.
The authors place the individuals' choices between different public services 
within the formulation of routing games and measure inefficiencies using a 
concept known as the price of anarchy (PoA)~\cite{koutsoupias1999worst}.
They show that the price of anarchy increases with worth of service and that is
low for systems with insufficient capacities.
In~\cite{deo2011centralized} the authors study the network effect of ambulance 
diversion by proposing a non-cooperative game between two EDs that are modelled
as a queueing network.
Each ED's objective is to minimise its own waiting time and chooses a diversion
threshold based on the patients it has.
In equilibrium both EDs choose to divert ambulances in order to avoid getting
arrivals from the other ED.
In this paper this concept is extended by allowing the ambulance service to 
decide how to distribute its patients among the two EDs.

Another specific part of our research, as described later in the paper, is the 
construction of a queueing system with a tandem buffer and a single service
centre.
In~\cite{d2015pure} the authors explore threshold joining strategies in a 
Markov model that has two tandem queues.
Another example is the one described in~\cite{burnetas2013customer}
where they investigated a network of multiple tandem queues where customers 
decide which queue to attend before joining.
Similarly, in~\cite{bacsar2002stackelberg} the authors examine a network of 
\(N\) tandem M/M/1 queues and with multi-type customers. 
The customers in this paper react to a price \(p\) by picking demand rates that 
maximise utility.
In~\cite{veltman2005equilibrium} a profit maximisation problem is studied that
has two servers; an M/M/1 queue and a parking service providing complementary 
service while the customer is in the first service. 
The providers gain a reward when customers complete both services and no reward 
when they finish one of them.
One of the main conclusions of this study is that by increasing the general 
demand both providers lower their prices to compensate for the increase in wait.
The problem was later extended by~\cite{sun2009equilibrium} where they 
considered arrivals of batches that can share the parking service.
Finally,~\cite{afeche2007decentralized} examines a tandem network of two M/M/1 
queues that are ran by two different profit-maximising service providers.
The network receives three types of customers; those requiring both services, 
customers requiring the first service and customers requiring the second service.
The authors showed that optimal prices also maximise social utility and that
removing two types of customers that don't need both services leads to higher 
profit and lower demand rate.

% Major contributions
% TODO: Write major contributions in relation to the literature review

### 2022-03-04 sections/model_overview/main.tex
Change the overall structure
New structure:
1. Intro + Motvation + Major cotnributions
2. Lit review + Major contributions
3. Queueing model (with performance measures formulas)
4. Game model (with methodology and numerical results)
5. Conclusion

@@
 individuals to the queueing systems.
+
+The parameters of the model correspond to the following parameters of the ED 
+and the EMS:
+
+\begin{itemize}
+    \item \( \lambda_2 \): The rate of non-emergency patients that the EMS 
+    receives and distributes to EDs
+    \item \( \lambda_{1_i} \): The arrival rate of other patients to ED 
+    \(i\in\{A, B\}\)
+    \item \( \mu_i \): The service rate of patients at ED \(i\in\{A, B\}\)
+    \item \( C_i \): The number of available resources (beds) in ED 
+    \(i\in\{A, B\}\)  
+    \item \( T_i \): The action that ED \(i\in\{A, B\} \) chooses to play which 
+    corresponds to the threshold at which they do not accept EMS patients.
+    \item \( N_i \): The total patient capacity of ED \(i\in\{A, B\} \)
+    \item \( M_i \): The total parking capacity of ED \(i\in\{A, B\} \)
+    \item \( R \): The time target for both EDs
+    \item \( \alpha \in [0, 1] \) : \textit{Weighting} of blocking time and 
+    lost individuals (equation \ref{eq:obj_distributor})
+\end{itemize}
+
+The strategies of the two EDs are the range of thresholds that they can choose
+from and their utilities is the proportion of individuals whose time in the 
+system is within a predetermined target time.
+The EMS has to decide how to distribute its patients among the two EDs so that 
+the weighted combination of the ambulance blocking time and the percentage of 
+lost ambulances is minimised. 
+As defined in Section \ref{sec:model_overview}, the interaction between the two EDs 
+is a normal form game that is then used to inform the decision of the EMS.
+Note that the formulated game here assumes that prior to making a choice the 
+EMS knows the strategies that each ED is playing (figure 
+\ref{fig:imperfect_info_game}). This corresponds to reacting to experienced 
+delays.
 
@@
 make their own choice of the proportion of individuals to send to each system.
+
+\input{sections/model_overview/methodology/main.tex}
+
+\input{sections/model_overview/numerical_results/main.tex}

### 2022-03-04 sections/model_overview/numerical_results/main.tex
Change the overall structure
New structure:
1. Intro + Motvation + Major cotnributions
2. Lit review + Major contributions
3. Queueing model (with performance measures formulas)
4. Game model (with methodology and numerical results)
5. Conclusion

--- 2021-11-05 sections/healthcare_application/main.tex
@@
-\section{EMS - ED application}\label{sec:ems_ed_application}
-
-\subsection{Application}\label{sec:application}
-
-The system defined in section \ref{sec:model_overview} can be applied 
-to a healthcare scenario with two such queueing systems.
-The two queueing systems can be thought of as two Emergency Departments (ED) 
-and the Emergency Medical Services (EMS) as a distributor that distributes 
-patients to them.
-
-There are numerous news articles that focus on the problems that arise when 
-ambulances stay blocked outside of the hospital for a long amount of 
-time~\cite{dailyrecords, staffordshirelive}.
-Some news reports also comment on the long idle time of ambulances when 
-they are not in use~\cite{herefordtimes} and there are several reports of 
-examples where this became an issue for new patients~\cite{southwalesargus}.
-A particular article looked into this problem from the point of view of an 
-ambulance paramedic:
-
-\begin{quotation}
-    % <!--alex ignore he-she her-him-->
-    ``He knows if a patient arrives more urgently in need of help, his will be 
-    pushed back''~\cite{bbcwales}
-
-    ``We used to bring poorly patients in, and we were out on the road again in
-    15 minutes.''~\cite{bbcwales}
-\end{quotation}
-
-The patients that are distributed by the EMS arrive at the hospital via an 
-ambulance and are then either offloaded at the ED or stay blocked outside in 
-the ambulance.
-Whether or not the ambulance and the patient stay blocked is determined by 
-the threshold that the given ED chooses to play.
-High threshold indicates that the ED accepts patients even if it is relatively 
-full, while low threshold means that the ED blocks ambulances more frequently.
-
-The parameters of the model correspond to the following parameters of the ED 
-and the EMS:
-
-\begin{itemize}
-    \item \( \lambda_2 \): The rate of non-emergency patients that the EMS 
-    receives and distributes to EDs
-    \item \( \lambda_{1_i} \): The arrival rate of other patients to ED 
-    \(i\in\{A, B\}\)
-    \item \( \mu_i \): The service rate of patients at ED \(i\in\{A, B\}\)
-    \item \( C_i \): The number of available resources (beds) in ED 
-    \(i\in\{A, B\}\)  
-    \item \( T_i \): The action that ED \(i\in\{A, B\} \) chooses to play which 
-    corresponds to the threshold at which they do not accept EMS patients.
-    \item \( N_i \): The total patient capacity of ED \(i\in\{A, B\} \)
-    \item \( M_i \): The total parking capacity of ED \(i\in\{A, B\} \)
-    \item \( R \): The time target for both EDs
-    \item \( \alpha \in [0, 1] \) : \textit{Weighting} of blocking time and 
-    lost individuals (equation \ref{eq:obj_distributor})
-\end{itemize}
-
-The strategies of the two EDs are the range of thresholds that they can choose
-from and their utilities is the proportion of individuals whose time in the 
-system is within a predetermined target time.
-The EMS has to decide how to distribute its patients among the two EDs so that 
-the weighted combination of the ambulance blocking time and the percentage of 
-lost ambulances is minimised. 
-As defined in Section \ref{sec:model_overview}, the interaction between the two EDs 
-is a normal form game that is then used to inform the decision of the EMS.
-Note that the formulated game here assumes that prior to making a choice the 
-EMS knows the strategies that each ED is playing (figure 
-\ref{fig:imperfect_info_game}). This corresponds to reacting to experienced 
-delays.
-
 \subsection{Numerical results}\label{sec:numerical_results}

### 2022-03-04 sections/model_overview/main.tex
Minor changes
- Minor changes to sections and subsections
- Move figure from game section to queueing section

@@
 
-\begin{figure}[ht]
-    \centering
-    \begin{tikzpicture}[>=stealth, scale=0.8],
-        % the rectangle of Queue 1
-        \draw (0,0) -- ++(3cm,0) -- ++(0,-1.5cm) -- ++(-3cm,0);
-        % The label above Queue 1 -> M
-        \node[anchor=north] at (1.5cm, 1cm) {\( 
-            \overbrace{\qquad \qquad \qquad \qquad}^{M} 
-        \)};
-        % The label below Queue 1 -> Parking space
-        \node[anchor=north] at (1.5cm, -1.7cm) {\small{Parking space}};
-
-        % the vertical lines in Queue 1
-        \foreach \i in {1,...,5, 6.6}
-        \draw (3cm-\i*13pt,0) -- +(0,-1.5cm);
-
-        % % the circle in Queue 1
-        % \draw (2.75,-0.75cm) circle [radius=0.75cm] node {\(0\)};
-
-        % the rectangle in Queue 2
-        \draw (5,1.25) -- ++(2cm,0) -- ++(0,-1.5cm) -- ++(-2cm,0);
-        % the vertical lines in Queue 2
-        \foreach \i in {1,...,4, 5.7}
-        \draw (7cm-\i*10pt,1.25) -- +(0,-1.5cm);
-        % The two vertical lines at the start of Queue 2 
-        \draw (7cm-54pt,1.2) -- +(0,-0.5cm);
-        \draw (7cm-54pt,0.3) -- +(0,-0.5cm);        
-        \draw (7cm-51pt,1.1) -- +(0,-0.4cm);
-        \draw (7cm-51pt,0.3) -- +(0,-0.4cm);
-
-        % The label between the lines for T
-        \node[anchor=north] at (5.15, 0.80 cm) {\small{\( T \)}};
-
-        % The label above Queue 2 -> N
-        \node[anchor=north] at (6.6cm, 2.2cm) {\( 
-            \overbrace{\qquad \qquad \qquad \qquad}^{N} 
-        \)};
-        % The label below Queue 2 -> Hospital
-        \node[anchor=north] at (6.2cm, -0.5cm) {\small{Hospital}};
-
-        % the circle in Queue 2
-        \draw (7.75,0.5) circle [radius=0.75cm] node {\(C\)};
-
-        % Arrow line from Queue 2 outside
-        \draw[->] (8.5,0.525) -- +(20pt,0);
-
-        % Line from lambda_2 to Queue 1
-        \draw[<-] (-0.3,-0.75) -- +(-40pt,0) node[left] {\( \lambda_2 \)};
-        % First line (horizontal) after Queue 1
-        \draw[-] (3,-0.75) -- +(34pt,0);
-        % Second line (vertical) after Queue 1
-        \draw (4.2, 0.525) -- (4.2, -0.75);
-
-        % First line (horizontal) from lambda_1
-        \draw (4.2, 1.8) -- +(-169.5pt,0) node[left] {\( \lambda_1 \)};
-        % Second line (vertical) from lambda_1
-        \draw (4.2, 1.8) -- (4.2, 0.525);
-        % Arrow line to Queue 2
-        \draw[->] (4.2, 0.525) -- (4.8, 0.525);  
-    \end{tikzpicture}
-    \caption{A diagrammatic representation of the queueing model. 
-    The threshold \(T\) only applies to type 2 individuals.
-    If the number of individuals in the hospital is \(T\), only 
-    individuals of type 1 
-    are accepted (at a rate \(\lambda_1\)) and individuals of type 2
-    (arriving at a rate \(\lambda_2\)) are blocked in the parking space.}
-    \label{fig:diagram_of_queueing_system}
-\end{figure}
+% TODO: Add figure here of the game as described by issue #32
 

### 2022-03-04 sections/model_overview/methodology/main.tex
Minor changes
- Minor changes to sections and subsections
- Move figure from game section to queueing section

--- 2022-02-21 sections/methodology/main.tex
@@
-\section{Methodology}\label{sec:methodology}
+\subsection{Methodology}\label{sec:methodology}
 
@@
 and \(p_A + p_B = 1\).
+In practice this would correspond to a learned behaviour through experience of
+waiting at each hospital.
 Figure \ref{fig:imperfect_info_game} 
@@
 
-\subsection{Backwards induction}
+\subsubsection{Backwards induction}
 
@@
 
-\subsection{Nash equilibrium}\label{sec:methodology_nash_equilibrium}
+\subsubsection{Nash equilibrium}\label{sec:methodology_nash_equilibrium}
 
@@
 
-\subsection{Learning algorithms}\label{sec:methodology_learning_algorithms}
+\subsubsection{Learning algorithms}\label{sec:methodology_learning_algorithms}
 

### 2022-03-04 sections/queueing_model/main.tex
Minor changes
- Minor changes to sections and subsections
- Move figure from game section to queueing section

@@
 and the hospital waiting space.
+
+\begin{figure}[ht]
+    \centering
+    \begin{tikzpicture}[>=stealth, scale=0.8],
+        % the rectangle of Queue 1
+        \draw (0,0) -- ++(3cm,0) -- ++(0,-1.5cm) -- ++(-3cm,0);
+        % The label above Queue 1 -> M
+        \node[anchor=north] at (1.5cm, 1cm) {\( 
+            \overbrace{\qquad \qquad \qquad \qquad}^{M} 
+        \)};
+        % The label below Queue 1 -> Parking space
+        \node[anchor=north] at (1.5cm, -1.7cm) {\small{Parking space}};
+
+        % the vertical lines in Queue 1
+        \foreach \i in {1,...,5, 6.6}
+        \draw (3cm-\i*13pt,0) -- +(0,-1.5cm);
+
+        % % the circle in Queue 1
+        % \draw (2.75,-0.75cm) circle [radius=0.75cm] node {\(0\)};
+
+        % the rectangle in Queue 2
+        \draw (5,1.25) -- ++(2cm,0) -- ++(0,-1.5cm) -- ++(-2cm,0);
+        % the vertical lines in Queue 2
+        \foreach \i in {1,...,4, 5.7}
+        \draw (7cm-\i*10pt,1.25) -- +(0,-1.5cm);
+        % The two vertical lines at the start of Queue 2 
+        \draw (7cm-54pt,1.2) -- +(0,-0.5cm);
+        \draw (7cm-54pt,0.3) -- +(0,-0.5cm);        
+        \draw (7cm-51pt,1.1) -- +(0,-0.4cm);
+        \draw (7cm-51pt,0.3) -- +(0,-0.4cm);
+
+        % The label between the lines for T
+        \node[anchor=north] at (5.15, 0.80 cm) {\small{\( T \)}};
+
+        % The label above Queue 2 -> N
+        \node[anchor=north] at (6.6cm, 2.2cm) {\( 
+            \overbrace{\qquad \qquad \qquad \qquad}^{N} 
+        \)};
+        % The label below Queue 2 -> Hospital
+        \node[anchor=north] at (6.2cm, -0.5cm) {\small{Hospital}};
+
+        % the circle in Queue 2
+        \draw (7.75,0.5) circle [radius=0.75cm] node {\(C\)};
+
+        % Arrow line from Queue 2 outside
+        \draw[->] (8.5,0.525) -- +(20pt,0);
+
+        % Line from lambda_2 to Queue 1
+        \draw[<-] (-0.3,-0.75) -- +(-40pt,0) node[left] {\( \lambda_2 \)};
+        % First line (horizontal) after Queue 1
+        \draw[-] (3,-0.75) -- +(34pt,0);
+        % Second line (vertical) after Queue 1
+        \draw (4.2, 0.525) -- (4.2, -0.75);
+
+        % First line (horizontal) from lambda_1
+        \draw (4.2, 1.8) -- +(-169.5pt,0) node[left] {\( \lambda_1 \)};
+        % Second line (vertical) from lambda_1
+        \draw (4.2, 1.8) -- (4.2, 0.525);
+        % Arrow line to Queue 2
+        \draw[->] (4.2, 0.525) -- (4.8, 0.525);  
+    \end{tikzpicture}
+    \caption{A diagrammatic representation of the queueing model. 
+    The threshold \(T\) only applies to type 2 individuals.
+    If the number of individuals in the hospital is \(T\), only 
+    individuals of type 1 
+    are accepted (at a rate \(\lambda_1\)) and individuals of type 2
+    (arriving at a rate \(\lambda_2\)) are blocked in the parking space.}
+    \label{fig:diagram_of_queueing_system}
+\end{figure}
 

### 2022-03-07 sections/introduction/main.tex
Modify introduction section

@@
 to respond to new EMS calls, thus placing lives at risk~\cite{eastanglia}.
-This paper aims to describe the EMS-ED interface using a game theoretic model
-informed by an underlying queueing model.
-
-% ED + EMS application
-The system defined in section \ref{sec:model_overview} can be applied 
-to a healthcare scenario with two such queueing systems.
-The two queueing systems can be thought of as two Emergency Departments (ED) 
-and the Emergency Medical Services (EMS) as a distributor that distributes 
-patients to them.
 
@@
 
+% ED + EMS application
+This paper aims to describe the EMS-ED interface using a game theoretic model
+informed by an underlying queueing model.
+The model describes the situation where an ambulance service would
+have to distribute its patients between two EDs.
+The two EDs can be thought of as two queueing systems and the EMS as a 
+distributor that distributes patients to them, aiming to minimise some
+performance measure.
 The patients that are distributed by the EMS arrive at the hospital via an 
@@
 the ambulance.
-Whether or not the ambulance and the patient stay blocked is determined by 
+Whether or not the ambulance and its patient stay blocked is determined by 
 the threshold that the given ED chooses to play.
-High threshold indicates that the ED accepts patients even if it is relatively 
-full, while low threshold means that the ED blocks ambulances more frequently.
-
-% Major contributions
+High threshold indicates that the ED accepts ambulance patients even if it is 
+relatively full, while low threshold means that the ED blocks ambulances more 
+frequently.
 In the United Kingdom the National Heath Services (NHS) sets some regulations 
@@
 
+% Major contributions
 The novelty of our research contribution in this paper is to consider:
@@
 of parameters for the buffer has been considered.
-% TODO Be sure if this is correct
 Although our research is motivated by the particular EMS-ED example, our 
@@
 % Sign posting
-This paper first gives an overview of the game theoretic model, then goes on 
-to describe a novel queueing model, and then follows with a number of theoretic 
-results pertaining to the performance measures of this model. 
-These are used to build the utilities of the game.
-Finally, there is a section that describes how this game theoretic framework
-can be applied at the interface between the EMS and EDs together with some 
-analysis on the behaviour that is observed.
+This paper consists of two main sections.
+The first section presents a novel queueing model for a hospital with two
+types of patients and two waiting zones.
+A detailed description of how to acquire the performance measure formulas of 
+such queueing system is given.
+The next section gives an overview of the game theoretic model and several
+theoretic results pertaining to the performance measures of this model which 
+are used to build the utilities of the game.

### 2022-03-09 sections/model_overview/main.tex
Restructure game theoretic model section

@@
-\section{Overview of game theoretic model} \label{sec:model_overview}
+\section{Strategic manipulation of the ED-EMS interface} \label{sec:model_overview}
 
@@
     receives and distributes to EDs
+    % TODO: Use consistent notation of non-urgent/non-emergency patients
     \item \( \lambda_{1_i} \): The arrival rate of other patients to ED 
@@
     \item \( \mu_i \): The service rate of patients at ED \(i\in\{A, B\}\)
-    \item \( C_i \): The number of available resources (beds) in ED 
-    \(i\in\{A, B\}\)  
+    \item \( C_i \): The number of available resources (healthcare 
+    professionals) in the ED \(i\in\{A, B\}\)
+    % TODO: Make sure that servers are defined the same way throughout
     \item \( T_i \): The action that ED \(i\in\{A, B\} \) chooses to play which 
     corresponds to the threshold at which they do not accept EMS patients.
-    \item \( N_i \): The total patient capacity of ED \(i\in\{A, B\} \)
-    \item \( M_i \): The total parking capacity of ED \(i\in\{A, B\} \)
-    \item \( R \): The time target for both EDs
-    \item \( \alpha \in [0, 1] \) : \textit{Weighting} of blocking time and 
+    \item \( N_i \): The total patient capacity of the ED \(i\in\{A, B\} \)
+    \item \( M_i \): The total parking capacity of the ED \(i\in\{A, B\} \)
+    \item \( t \): The time target for both EDs
+    \item \( \alpha \in [0, 1] \) : Weighted average of blocking time and 
     lost individuals (equation \ref{eq:obj_distributor})
@@
 lost ambulances is minimised. 
-As defined in Section \ref{sec:model_overview}, the interaction between the two EDs 
-is a normal form game that is then used to inform the decision of the EMS.
+As defined in section \ref{sec:model_overview}, the interaction between the two
+EDs is a normal form game that is then used to inform the decision of the EMS.
 Note that the formulated game here assumes that prior to making a choice the 
 EMS knows the strategies that each ED is playing (figure 
-\ref{fig:imperfect_info_game}). This corresponds to reacting to experienced 
-delays.
+\ref{fig:imperfect_info_game}). 
+This corresponds to reacting to experienced delays.
 
@@
 (e.g walk-in patients, urgent patients from either walk-ins or ambulances).
+% TODO: Type 1 - type 2 definition defined on queueing section as well
 Each hospital may then choose to block type 2 individuals 
@@
 
-Both hospitals follow a queueing model with two waiting zones for 
+Both hospitals follow a queueing model with two waiting spaces for 
 individuals. 
-The first waiting zone (i.e. the waiting space of the hospital) is where the 
+The first waiting space (i.e. the waiting space of the hospital) is where the 
 patients queue right before receiving 
@@
 % TODO: Should this be healthcare professionals or available beds?
-The second waiting zone (i.e. the parking space for ambulances) is where 
+The second waiting space (i.e. the parking space for ambulances) is where 
 ambulances, that are sent from the
@@
 
+% TODO: Maybe only this equation is needed here. Remove the previous two?
 \begin{equation}\label{eq:obj_queueing_systems}
@@
 between the two objectives \(L_i\) and \(B_i\) where \(i \in \{A, B\}\):
-\begin{equation*}\label{eq:obj_distributor}
+\begin{equation}\label{eq:obj_distributor}
     (p_A, p_B) \quad s.t. \quad 
@@
     \alpha L_B(p_B) + (1 - \alpha) B_B(p_B)
-\end{equation*}
+\end{equation}
 
@@
 
-The first 
-queueing system \(H_A\) decides on a threshold, then the second system \(H_B\)
+Hospital \(H_A\) decides on a threshold, then the hospital \(H_B\)
 chooses its own threshold, without knowing the strategy of \(H_A\), and finally
-the distributor makes its choice. Note here that the dotted line represents the
+the ambulance service makes its choice. 
+Note here that the dotted line represents the
 fact that \(H_B\) is unaware of the state of the game when making its own 
@@
 \begin{equation} \label{eq:payoff_entry}
-    U_{T_A, T_B}^i = -\left( 
+    U_{T_A, T_B}^i = 1 - \left( 
         \hat{P} - P(W_i < t) 
@@
 \end{equation}
+% TODO: Define here the normal form game properly
 

### 2022-03-09 sections/model_overview/methodology/main.tex
Restructure game theoretic model section

@@
-\subsection{Methodology}\label{sec:methodology}
+\subsection{Building the game}\label{sec:methodology}
 
-The problem defined in section \ref{sec:model_overview} describes a normal-form
+The problem defined in this section describes a normal-form
 game between the decision makers of two hospitals and a third player, the 
 ambulance service, that 
-decides how to distribute individuals to the systems.
+decides how to distribute individuals to the two systems.
 The strategy space of the two hospitals is defined as the possible values
@@
 to be made.
-As described in Section \ref{sec:model_overview}, hospital \(A\) decides
+As described in section \ref{sec:model_overview}, hospital \(A\) decides
 on a strategy and at the same time, hospital \(B\) chooses its own 
@@
 a best response to the actions of the hospitals.
-Thus, using equation \ref{eq:obj_distributor} for all possible sets of 
+Thus, using equation (\ref{eq:obj_distributor}) for all possible sets of 
 thresholds we can get the full routing matrix that consists of the proportions
@@
 
-\subsubsection{Backwards induction}
-
-In order to populate the payoff matrices and the routing matrix the method
-of backwards induction is used.
 Consider Figure \ref{fig:imperfect_info_game} and the flow of the game that was
@@
 (\(D \rightarrow H_A, H_B\)). 
-Thus for every pair of strategies \(T_A, T_B\), the proportion of individuals 
-that are to be transported to each queueing system is calculated first.
-
-Consider a game where the capacities of the two systems are \(N_A = 4\) and 
-\(N_B = 3\).
-The strategy space of players \(H_A\) and \(H_B\) would then be 
-\(T_A = \{1, 2, 3, 4\}\) and \(T_B = \{1, 2, 3\}\) respectively.
-Now, starting from an arbitrary starting point of \(T_A=1\) and \(T_B=1\), the
-corresponding entry of the routing matrix the routing matrix can be calculated.
-Using equation (\ref{eq:obj_distributor}) for \(T_A=1\) and \(T_B=1\):
-\begin{align}
-    & \alpha L_A(p_A;T_A=1;T_B=1) + (1 - \alpha) B_A(p_A;T_A=1;T_B=1) = 
-    \nonumber \\
-    & \alpha L_B(p_B;T_A=1;T_B=1) + (1 - \alpha) B_B(p_B;T_A=1;T_B=1) 
-    \label{eq:obj_distributor_1_1}
-\end{align}
-
-The values of \(p_A\) and \(p_B\) that satisfy equation 
-(\ref{eq:obj_distributor_1_1}) are here found numerically using Brent's 
-bisection algorithm~\cite{brent1973algorithms}.
-The calculated value of \(p_A\) corresponds to the entry on the first row and 
-first column of the routing matrix:
-
-\begin{equation}\label{eq:routing_matrix_1_1}
-    R = 
-    \begin{pmatrix}
-        p_{1,1}^A & - & - \\
-        - & - & - \\
-        - & - & - \\
-        - & - & - \\
-    \end{pmatrix}
-\end{equation}
-
-In fact all remaining values of the routing matrix can be calculated by
-solving \(N \times M\) similar equations using Brent's bisection algorithm.
-Therefore, having calculated the entire routing matrix the payoff matrices can
-be calculated.
-Consider once again the case of \(T_A=1, T_B=1\).
-
-\begin{align}
-    U_{1, 1}^A = 1 -\left( 
-        \hat{P} - P(W_A(T_A=1, T_B=1) < t) 
-    \right)^2 \nonumber
-    \\
-    U_{1, 1}^B = 1 -\left( 
-        \hat{P} - P(W_B(T_A=1, T_B=1) < t) 
-    \right)^2 \label{eq:payoff_entry_1_1}
-\end{align}
-
-These are the utilities of hospitals \(A\) and \(B\) when both players choose a
-strategy of \(T = 1\).
-Here \(R\) is the predefined waiting time target to be met by a percentage of 
-individuals \( \hat{P} \) and \(P(W_i < t)\) is defined in section
-\ref{sec:proportion_within_target}.
-
-\begin{equation}\label{eq:payoff_matrices_1_1}
-    A = 
-    \begin{pmatrix}
-        U_{1, 1}^A & - & - \\
-        - & - & - \\
-        - & - & - \\
-        - & - & - \\
-    \end{pmatrix}, \quad
-    B = 
-    \begin{pmatrix}
-        U_{1, 1}^B & - & - \\
-        - & - & - \\
-        - & - & - \\
-        - & - & - \\
-    \end{pmatrix}
-\end{equation}
-
-Similar to the routing matrix, the above procedure can be repeated for all 
-possible values of \(T_A\) and \(T_B\) to populate all entries of the payoff 
-matrices.
-
-\subsubsection{Nash equilibrium}\label{sec:methodology_nash_equilibrium}
+This is done using backwards induction, by first solving the game from the
+ambulance's point of view and then from the hospital's point of view.
+Thus, for every pair of strategies \(T_A, T_B\), the values of \(p_A\) and 
+\(p_B\) that satisfy equation (\ref{eq:obj_distributor}) are found
+numerically using Brent's bisection algorithm~\cite{brent1973algorithms}.
+Each pair \((p_A, p_B)\) corresponds to the best response of the ambulance
+service to the two hospitals' played strategies.
+Finally, using the routing matrix, equation (\ref{eq:payoff_entry}) can also be
+used to populate the payoff matrices of the hospitals since we now know the 
+arrival rate of each hospital.
 
 Having calculated the payoff matrices \(A\) and \(B\), several algorithms can 
-be used to measure some form of emergent behaviour.
+be used to measure some form of the emergent behaviour.
 One possibility would be to compute the Nash equilibrium
@@
 In other words their chosen strategies are a best response to each other.
-
 Computation of Nash equilibria can be done in a relatively efficient way using 
@@
 \cite{thenashpyproject}.
-
-\subsubsection{Learning algorithms}\label{sec:methodology_learning_algorithms}
 

### 2022-03-09 sections/model_overview/numerical_results/main.tex
Restructure game theoretic model section

@@
-\subsection{Numerical results}\label{sec:numerical_results}
+\subsection{Results}\label{sec:numerical_results}
 
@@
 The most commonly used method for analysing normal form games is the Nash 
-equilibrium described in section \ref{sec:methodology_nash_equilibrium}.
+equilibrium described in section \ref{sec:methodology}.
 Consider the following game:
@@
 One such model that allows for asymmetric payoffs, as is the case above, is 
-replicator dynamics described in Section 
-(\ref{sec:methodology_learning_algorithms}).
+replicator dynamics described in section 
+(\ref{sec:methodology}).
 Stable outcomes of this algorithm will correspond to a subset of Nash
@@
 
+% TODO: Make clear that we are speaking about a flooded model here.
 Consider a game with two smaller (lower \( N_i, M_i \)) and busier (higher 

### 2022-03-09 sections/queueing_model/main.tex
Minor changes on queueing section

@@
-\section{A queueing model with 2 consecutive buffer centres}\label{sec:queueing_model}
+\section{A queueing model for the ED-EMS interface}\label{sec:queueing_model}
 % TODO: If this is to be one paper maybe the first two paragraphs do not need to
@@
         % The label between the lines for T
-        \node[anchor=north] at (5.15, 0.80 cm) {\small{\( T \)}};
+        \node[anchor=north] at (5.15, 0.81 cm) {\small{\( T \)}};
 
@@
 Type 2 individuals are non-urgent patients arriving in ambulances (i.e. patients
-in ambulances ).
-and type 1 individuals are individuals arriving from other sources 
+in ambulances that would not be at risk if they were blocked at the parking 
+space) and type 1 individuals are individuals arriving from other sources 
 (e.g walk-in patients, urgent patients from either walk-ins or ambulances).
 Type 1 individuals arrive instantly at the hospital's waiting space and wait to
-receive their 
-service. 
+receive their service. 
 Type 2 individuals arrive at the parking space and wait there until they are 
@@
 They are allowed to proceed only when the number of 
-individuals in the hospital is less than the
+patients in the hospital is less than the
 pre-determined threshold \(T\).
 When the number of individuals is equal to or exceeds this threshold, all 
-type 2 individuals that arrive will stay 
+type 2 patients that arrive will stay 
 \textit{blocked} in the parking space until the number of patients in 
@@
 In order to consider this model numerically an adjustment needs to be made. 
-The problem defined above assumes no upper boundary to the number of individuals 
-that can wait in the hospital or for the ones that are blocked in the parking 
+The problem defined above assumes no upper boundary to the number of patients 
+that can wait in the hospital or to the ones that are blocked in the parking 
 space.
 Therefore, a different state space \( \tilde S \) is constructed where
-\( \tilde S \subseteq S \) and there is a maximum allowed number of individuals 
-\(N\) that can be in the hospital and a maximum allowed number of individuals 
+\( \tilde S \subseteq S \) and there is a maximum allowed number of patients 
+\(N\) that can be in the hospital and a maximum allowed number of ambulances 
 \(M\) that can be blocked in the parking space:
@@
 \(\pi_i\) is the steady state probability of being in state \((u_i, v_i) \in 
-\tilde S\) which is the \(i^{\text{th}}\) state of \(\tilde S\) for some ordering of 
-\(\tilde S\).
+\tilde S\) which is the \(i^{\text{th}}\) state of \(\tilde S\) for some 
+ordering of \(\tilde S\).
 The term \textit{steady state} refers to the instance of the vector \( \pi \) 
@@
 can be calculated. 
-The following equations utilise \(\pi\) to get performance measures on the 
-average number of patients at certain sets of state:
+The following equations utilise \(\pi\) to get performance measures for the 
+average number of patients at the different nodes of the queueing model:
 
@@
         \[L_H = \sum_{i=1}^{|\pi|} \pi_i v_i\]
-    \item Average number of patients in the parking space:
+    \item Average number of patients/ambulances in the parking space:
         \[L_A = \sum_{i=1}^{|\pi|} \pi_i u_i\] 
@@
 whose waiting time falls within a predefined time target (for both types).
+% TODO: Explain why these performance measures are needed? (for the game)
 

### 2022-03-09 sections/model_overview/main.tex
Change some of the definitions

@@
 The queueing systems of the hospitals are designed in such a way where they can
-accept two types
-of individuals. 
-Type 2 individuals are defined as non-urgent patients arriving in ambulances 
-that are allocated by the ambulance service and 
-type 1 individuals are individuals arriving from other sources 
-(e.g walk-in patients, urgent patients from either walk-ins or ambulances).
-% TODO: Type 1 - type 2 definition defined on queueing section as well
+accept two types of individuals (section \ref{sec:queueing_model}). 
 Each hospital may then choose to block type 2 individuals 

### 2022-03-09 sections/queueing_model/blocking_time/main.tex
Minor changes on queueing section
Change some of the definitions

@@
 Here \(S_A^{(2)}\) is the set of accepting states of type 2 individuals (defined
-in (\ref{eq:accepting_states_type_2})) and \(\mathcal{A}_i(u,v) \, i \in 
-\{1, 2\} \) is the state that the model would go to when the system is at state 
-\( (u,v) \) and a class \(i\) individual arrives.
+in equation (\ref{eq:accepting_states_type_2})) and \(\mathcal{A}_i(u,v)\) for
+\(i \in \{1, 2\} \) is the state that the system would go to when the system is
+at state \( (u,v) \) and an individual of type \(i\) arrives.
 

### 2022-03-09 sections/queueing_model/main.tex
Change some of the definitions

@@
 \section{A queueing model for the ED-EMS interface}\label{sec:queueing_model}
-% TODO: If this is to be one paper maybe the first two paragraphs do not need to
-% include so much details or even better omit some of the details in the game
-% overview section.
 In this section, a more in-depth explanation of the queueing model shown in 
@@
 The model consists of two types of individuals; type 1 and type 2.
-% TODO: Decide whether to define type 1, 2 only in queueing section, only in game section, or both
-Type 2 individuals are non-urgent patients arriving in ambulances (i.e. patients
-in ambulances that would not be at risk if they were blocked at the parking 
-space) and type 1 individuals are individuals arriving from other sources 
+Type 2 individuals are patients arriving in ambulances who can be blocked 
+(usually patients that are deemed not to be critical) 
+and type 1 individuals are individuals arriving from other sources 
 (e.g walk-in patients, urgent patients from either walk-ins or ambulances).
@@
     \item \(\mu\): The service rate for individuals receiving service
-    \item \(C\): The number of servers
+    \item \(C\): The number of servers (either healthcare professionals
+    or available beds in the ED)
     \item \(T\): The threshold at which type 2 individuals are blocked
@@
 whose waiting time falls within a predefined time target (for both types).
-% TODO: Explain why these performance measures are needed? (for the game)
 

### 2022-03-10 sections/introduction/main.tex
Clearly state the major contributions

@@
 \begin{itemize}
-    \item The emergence of gaming behaviour between EDs and the EMS.
     \item A queueing model with 2 consecutive waiting spaces where one would 
     serve as a parking space for the ambulances
+    \item Performance measure formulas for the queueing model
+    \item A 3-player game theoretic model between the EMS and two EDs
+    \item The emergence of gaming behaviour between EDs and the EMS.
 \end{itemize}
@@
 the three players.
-Whilst giving some consideration to equilibrium behaviour similarly to the 
-work of~\cite{FirmCompetition, FirmCompetition2, deo2011centralized, 
-veltman2005equilibrium}, emergent behaviour is more precisely addressed by 
-considering a number of learning algorithms.
 This study explores two new concepts: getting performance measures for a new
-queueing theoretic model with a tandem buffer and a single service centre and 
+queueing theoretic model with a parking space and a service centre and
 using a learning algorithm to model the emergence of behaviour.
-The developed theoretical model is then illustrated through the application to 
+The developed theoretical model is illustrated through the application to 
 a healthcare system of two EDs and the EMS, exploring the inefficiencies that 

### 2022-03-10 sections/literature_review/main.tex
Clearly state the major contributions

@@
 expected delay.
+In this paper, while giving some consideration to equilibrium behaviour,
+similar to the work of~\cite{FirmCompetition, FirmCompetition2}, emergent
+behaviour is more precisely addressed by considering learning algorithms like
+asymmetric replicator dynamics~\cite{fudenberg1998theory}.
 
@@
 profit and lower demand rate.
-
-% Major contributions
-% TODO: Write major contributions in relation to the literature review
+In this paper the concepts described in~\cite{d2015pure, burnetas2013customer,
+bacsar2002stackelberg} are extended by introducing a threshold parameter that 
+determines when individuals can progress from one queue to the other.

### 2022-03-14 sections/literature_review/main.tex
Apply reiview suggestions from Vince

@@
 was considered that also had capacity as a decision variable.
-In~\cite{knight2017measuring} a normal form game is built that is informed by a 
-two-dimensional Markov chain in order to model interactions between critical
-care units.
 An additional paper that focuses on competition is~\cite{fan2009short} where
@@
 individuals choosing to queue.
-In public healthcare type settings~\cite{knight2013selfish}, this is not 
+In public healthcare type settings, this is not 
 necessarily the case. 
-Players might not necessarily aim to maximise the so called `market share'.
+Rational usage of public services will not necessarily lead to a socially
+optimal outcome.
 Rather, the overall service needs to be considered as players aim to minimise
@@
 based on patients' perceived quality of life.
-How individual behaviour based on congestion impacts the efficiency of public 
-services is investigated in~\cite{knight2013selfish}.
-The authors place the individuals' choices between different public services 
+In~\cite{knight2013selfish} the authors place the individuals' choices between
+different public services 
 within the formulation of routing games and measure inefficiencies using a 
@@
 low for systems with insufficient capacities.
+In~\cite{knight2017measuring} a normal form game is built that is informed by a 
+two-dimensional Markov chain in order to model interactions between critical
+care units.
 In~\cite{deo2011centralized} the authors study the network effect of ambulance 
@@
 decide how to distribute its patients among the two EDs.
+The players of the game are both the hospitals and the customers of the
+hospitals, as opposed to the previous models which are one or the other.
+Thus, the novelty of this paper in a way is combining both these aspects.
 
@@
 centre.
+There are several examples from literature that touch upon queueing models
+with tandem queues.
 In~\cite{d2015pure} the authors explore threshold joining strategies in a 

### 2022-03-14 sections/model_overview/methodology/main.tex
Apply reiview suggestions from Vince

@@
 (\(D \rightarrow H_A, H_B\)). 
-This is done using backwards induction, by first solving the game from the
-ambulance's point of view and then from the hospital's point of view.
+This is done using backwards induction. 
+For each action choice of the hospitals, first solve the game from the
+ambulance's point of view.
+This in effect results in a 2-player normal form game representing the
+hospital's point of view.
 Thus, for every pair of strategies \(T_A, T_B\), the values of \(p_A\) and 

### 2022-03-16 sections/conclusion/main.tex
Change overall structure (#35)
* Change the overall structure

New structure:
1. Intro + Motvation + Major cotnributions
2. Lit review + Major contributions
3. Queueing model (with performance measures formulas)
4. Game model (with methodology and numerical results)
5. Conclusion

* Minor changes

- Minor changes to sections and subsections
- Move figure from game section to queueing section

* Fix failing proselint task

Clean the text before running proselint on it. Currently just removes
`\centering' command from .tex files

* Modify introduction section

* Restructure game theoretic model

@@
 \end{itemize}
+% TODO: Make sure this is consistent with `intro' and `lit review' sections
 The former relates to the results of asymmetric replicator dynamics that showed 

### 2022-03-16 sections/introduction/main.tex
Change overall structure (#35)
* Change the overall structure

New structure:
1. Intro + Motvation + Major cotnributions
2. Lit review + Major contributions
3. Queueing model (with performance measures formulas)
4. Game model (with methodology and numerical results)
5. Conclusion

* Minor changes

- Minor changes to sections and subsections
- Move figure from game section to queueing section

* Fix failing proselint task

Clean the text before running proselint on it. Currently just removes
`\centering' command from .tex files

* Modify introduction section

* Restructure game theoretic model

@@
 
-There are numerous news articles that focus on the problems that arise when 
+There are numerous news articles that focus on the complexity that arises when
 ambulances stay blocked outside of the hospital for a long amount of 
 time~\cite{dailyrecords, staffordshirelive}.
-Some news reports also comment on the long idle time of ambulances when 
+Some news reports comment on the long idle time of ambulances when
 they are not in use~\cite{herefordtimes} and there are several reports of 
@@
 % Major contributions
-The novelty of our research contribution in this paper is to consider:
+The major contributions of this paper are:
 \begin{itemize}
@@
     serve as a parking space for the ambulances
-    \item Performance measure formulas for the queueing model
+    \item Analytic performance measure formulas for the queueing model
     \item A 3-player game theoretic model between the EMS and two EDs
-    \item The emergence of gaming behaviour between EDs and the EMS.
+    \item Numerical experiments showing emergent behaviour of gaming between
+    EDs and the EMS.
 \end{itemize}
@@
 This paper consists of two main sections.
-The first section presents a novel queueing model for a hospital with two
-types of patients and two waiting zones.
+Section \ref{sec:queueing_model} presents a novel queueing model for a hospital
+with two types of patients and two waiting zones.
 A detailed description of how to acquire the performance measure formulas of 
 such queueing system is given.
-The next section gives an overview of the game theoretic model and several
+Section \ref{sec:model_overview} gives an overview of the game theoretic model
+and several
 theoretic results pertaining to the performance measures of this model which 

### 2022-03-17 known.py
Update known words

@@ -16,6 +16,7 @@ words = {
     "captionpos",
     "CDF",
     "CDFs",
+    "center",
     "ciw's",
     "Ciw's",
     "Ciw",

### 2022-03-18 sections/conclusion/main.tex
Add changes to conclusion
- Rewrite the major contributions of the paper
- Add closed-form of steady state as area for further work

--- 2022-03-04 sections/conclusion/main.tex
@@
 to satisfy these regulations.
+The main contributions of this paper are:
+\begin{itemize}
+    \item A queueing model with 2 consecutive waiting spaces where one would
+    serve as a parking space for the ambulances
+    \item Analytic performance measure formulas for the queueing model
+    \item A 3-player game theoretic model between the EMS and two EDs
+    \item Numerical experiments showing emergent behaviour of gaming between
+    EDs and the EMS.
+\end{itemize}
 
@@
 decision making process.
-Finally this work assumes that the EMS and EDs act in a selfish and rational
+Moreover this work assumes that the EMS and EDs act in a selfish and rational
 way by only aiming to satisfy their own objectives.
@@
 behavioural traits.
+Finally, future work can touch upon the derivation of a closed form formula for
+the steady state probability vector of the queueing model
+(section \ref{sec:queueing_model}) to allow for faster computations of \(\pi\).

### 2022-03-21 sections/queueing_model/waiting_time/main.tex
Change vocabulary in queueing section
Change vocabulary to be more focused on the application (#33)
* Change vocabulary in game section

* Minor typo

Fix proselint failure by removing the word very from a comment

* Change vocabulary in methodology section

* Additional changes in game section

- Replace waiting zone 1 with hospital
- Replace waiting zone 2 with parking space
- Use type 2 patients everywhere instead of ambulance patients

* Change vocabulary in queueing section
Add sentence to explain reason behind figures 4-6

@@
 
-Waiting time is the amount of time that individuals from either type wait in 
-waiting zone 1 so that they can receive their service. 
+Waiting time is the amount of time that patients wait in 
+the hospital's waiting space before they can receive their service. 
 For a given set of parameters there are three different performance measures 
@@
 appendix~\ref{sec:appendix_des}).
+The figure is used to demonstrate the accuracy of the waiting time formula of
+the constructed queueing model.
 The simulation was ran 100 times and the recorded mean waiting time at each 

### 2022-03-21 sections/conclusion/main.tex
Apply changes from Vince's review

@@
 The motivation behind this study has been that emergency departments are
-under a lot of pressure to satisfy some regulations.
+under a lot of pressure to treat patients.
+This is in practice often centrally controlled through a mechanism of some sort
+of performance measure target.
 This paper shows how this can negatively impact the pathway of both the
@@
     \item A queueing model with 2 consecutive waiting spaces where one would
-    serve as a parking space for the ambulances
-    \item Analytic performance measure formulas for the queueing model
-    \item A 3-player game theoretic model between the EMS and two EDs
+    serve as a parking space for the ambulances;
+    \item Analytic performance measure formulas for the queueing model;
+    \item A 3-player game theoretic model between the EMS and two EDs;
     \item Numerical experiments showing emergent behaviour of gaming between
@@
 
-The model presented here assumes the presence of two players that can receive
-individuals.
+The model presented here assumes the presence of just two players that can
+receive individuals.
 However, in a realistic healthcare scenario an ambulance may have to decide

### 2022-03-21 sections/model_overview/main.tex
Apply reiview suggestions from Vince
Add diagram of the game (#36)
* Create a tikz image of the game

* Add minor changes to the text

* Update known words

* Remove the word "very"

* Fix caption

* Apply suggestions from Vince's review

Co-authored-by: Vince Knight <vince@vknight.org>

Co-authored-by: Vince Knight <vince@vknight.org>

@@
 lost ambulances is minimised. 
-As defined in section \ref{sec:model_overview}, the interaction between the two
+This can be illustrated by figure \ref{fig:diagram_of_game_theoretic_model}.
+The interaction between the two
 EDs is a normal form game that is then used to inform the decision of the EMS.
@@
 This corresponds to reacting to experienced delays.
+
+\input{imgs/game_theoretic_model_diagram/main.tex}
 
@@
 The parking space has a capacity of \(M\) and no servers.
-
-This is shown diagrammatically in Figure ~\ref{fig:diagram_of_queueing_system}.
-
-% TODO: Add figure here of the game as described by issue #32
+This is shown diagrammatically in Figure~\ref{fig:diagram_of_queueing_system}.
 

### 2022-03-23 reviews/EJOR/01/main.tex
Write initial response to reviewers
- Not all comments are addressed

\documentclass{article}

\title{Response to reviewers}
\author{}

\begin{document}
    \maketitle

    I would like to thank all the reviewers for their help and comments and for
    the time they took to overhaul the manuscript.
    Their suggestions were very helpful and have been considered to improve the
    manuscript.
    The following changes were made:

    \line(1, 0){0.92\textwidth}
    \begin{itemize}
        \item Reviewer 1 - Comment 2: \textit{Combine Sections 2 and 5
        together to demonstrate the underlying queueing models and the
        EMS - ED interface counterpart.
        The current arrangement is not easy to follow for finding the right
        explanations for each part of the assumptions adopted in the
        article.}

        \item Reviewer 3 - Comment 1: \textit{Sections 1 and 2 are
        difficult to read.
        It would be better to focus on the main contribution and its
        motivation in Section 1, and to put the literature review in a
        separate Section.}
    \end{itemize}
    The paper has been completely restructured.
    Sections 2 and 5 have been combined and the game theoretic model is now
    presented along with the results in one section.
    In addition, section 1 contains only the introduction while the
    literature review has moved to section 2.
    Finally, the queueing model section now comes before the game theoretic
    section.
    The current structure is: Introduction; Literature Review; A queueing
    model for the ED-EMS interface; Strategic manipulation of the ED-EMS
    interface; Results.

    \line(1, 0){0.92\textwidth}
    \begin{itemize}
        \item Reviewer 3 - Comment 2: \textit{Since the application in mind
        is the EMS-ED interface, it would be better to write the paper
        immediately from this perspective, instead of first abstracting it
        and then applying it to that problem.}
        \item Reviewer 3 - Comment 8: \textit{Figs 7-11: Row player and
        Column Player are unclear: hospital 1 and hospital 2 would be a
        better choice I presume.}
    \end{itemize}
    The paper is now written more application focused.
    All sections are now presented from the perspective of the EMS-ED
    interface.
    In the game theoretic section instead of row/column player we now use
    hospital A and hospital B.

    \line(1, 0){0.92\textwidth}
    \begin{itemize}
        \item Reviewer 1 - Comment 4: \textit{To highlight the contributions
        of this work, it is necessary to compare the novelty of this work
        with previous results in the literature.}
    \end{itemize}
    In the new literature review section we now compare the results from
    previous work with the results from this work to highlight the
    contributions of this work.

    \line(1, 0){0.92\textwidth}
    \begin{itemize}
        \item Reviewer 3 - Comment 6: \textit{Figure 3: about solving the
        Markov chain: the Markov chain is truncated to solve it. Therefore,
        probably N and M are not too small. What about the numerical
        complexity? Because if you just solve it, you have to invert the
        matrix? Is there some structure in the Markov chain that can be
        exploited if N and M would be large?}
        \item Reviewer 3 - Comment 7: \textit{Figures 4-6: why do you
        compare your calculated values with simulation?
        Is it to evaluate the truncations?
        Or are you not sure about the formulas?}
    \end{itemize}
    This is a very good observation.
    As the values of \(N\) and \(M\) increase, the truncated Markov chain
    becomes more complex to solve.
    We have touched upon building a closed-form formula for the steady state
    probabilities but it's still work in progress.
    Figures 4-6 are there to demonstrate the accuracy of our constructed
    model against its discrete event simulation equivalent.
    An additional paragraph is added that talks about truncating the model
    and the old figures have been replaced with ones that compare the
    results from the truncated Markov model with the results from the
    untruncated simulation model.

    \line(1, 0){0.92\textwidth}
    \begin{itemize}
        \item Reviewer 3 - Comment 3: \textit{In section 2, a diagram
        of the full system (including the two queues and the EMS) would
        increase readability.}
    \end{itemize}
    A full system diagram is now added in the game theoretic model section.

    \line(1, 0){0.92\textwidth}
    \begin{itemize}
        \item Reviewer 3 - Comment 9: \textit{Page 22 scenario at bottom of
        the page: this scenario does not seem like a realistic scenario:
        the mean number of patients offered per time unit is larger than
        that can be treated, meaning that many patients would be rejected
        by the hospital. Please comment on the reality of the selected
        scenarios}
    \end{itemize}
    TBA % TODO: Reply to this comment once addressed.

    \line(1, 0){0.92\textwidth}
    \begin{itemize}
        \item Reviewer 3 - Comment 5: \textit{A key modelling assumption is
        that a fraction \(p_A\) of patients is distributed to hospital A.
        Some comments on how realistic this is should be added. Do
        distributers have a choice? Don't they just have to choose the
        nearest hospital? Do they really do it randomly, don' t they take
        into account queues at the hospitals (e.g. join the shortest
        ambulance queue)? what about urgency of patients? I would expect
        patients that come in are prioritized since they are probably more
        urgent.}
    \end{itemize}
    TBA % TODO: Reply to this comment once addressed.

    \line(1, 0){0.92\textwidth}
    \begin{itemize}
        \item Reviewer 3 - Comment 4: \textit{The authors claim their model
        has applications in a range of sectors and settings, but have given
        no examples.}
    \end{itemize}
    TBA % TODO: Reply to this comment once addressed.

    \line(1, 0){0.92\textwidth}
    \begin{itemize}
        \item Reviewer 1 - Comment 3: \textit{In the game-theoretic
        formulation and analysis part, it is better to present the
        essential components of a normal-form representation, including the
        players in the game, the strategies available to each player and the
        payoff received by each player for each combination of strategies
        that could be chosen by the players, etc.}
    \end{itemize}
    TBA % TODO: Reply to this comment once addressed

    \line(1, 0){0.92\textwidth}
    \begin{itemize}
        \item Reviewer 1 - Comment 1: \textit{Rewrite the Highlights (for
        review) of the paper, and really capture the sense of work.}
    \end{itemize}
    TBA % TODO: Reply to this comment once addressed

    \line(1, 0){0.92\textwidth}
    \begin{itemize}
        \item Reviewer 1 - Comment 5: \textit{There are some mistakes/typos
        with English grammar and writing in the article.}
    \end{itemize}
    TBA % TODO: Reply to this comment once addressed

\end{document}

### 2022-03-23 known.py
Update known words

@@ -24,6 +24,7 @@ words = {
     "codegreen",
     "commentstyle",
     "DES",
+    "distributers",
     "dt",
     "dx",
     "dy",
@@ -61,6 +62,7 @@ words = {
     "polytope",
     "polytopes",
     "pre",
+    "prioritized",
     "probs",
     "pystyle",
     "queueing",
@@ -74,6 +76,7 @@ words = {
     "stochasticity",
     "terminalstyle",
     "th",
+    "truncations",
     "unobservable",
     "untruncated",
     "Zx",

### 2022-03-23 reviews/EJOR/01/main.tex
Apply suggestions from proselint
Add minor change
Apply suggestions from Vince's review
Co-authored-by: Vince Knight <vince@vknight.org>

@@
     I would like to thank all the reviewers for their help and comments and for
-    the time they took to overhaul the manuscript.
-    Their suggestions were very helpful and have been considered to improve the
+    the time they took to review the manuscript.
+    Their suggestions were extremely helpful and we believe this has resulted in an improved
     manuscript.
-    The following changes were made:
+    Below is a point by point response and summary of changes made.
 
@@
     \end{itemize}
-    The paper is now written more application focused.
+    The paper is presented with the application of the model as the main focus.
     All sections are now presented from the perspective of the EMS-ED
@@
     \end{itemize}
-    In the new literature review section we now compare the results from
+    In the new literature review section we now directly compare the results from
     previous work with the results from this work to highlight the
@@
     \end{itemize}
-    This is a very good observation.
+    This observation was really helpful and lead to us conducting more numerical experiments to clarify the point of truncating the state space.
     As the values of \(N\) and \(M\) increase, the truncated Markov chain
@@
     We have touched upon building a closed-form formula for the steady state
-    probabilities but it's still work in progress.
+    probabilities but that is still a work in progress and not something we are able
+    to include in this manuscript.
     Figures 4-6 are there to demonstrate the accuracy of our constructed
-    model against its discrete event simulation equivalent.
+    model against its discrete event simulation equivalent and these have been expanded on.
     An additional paragraph is added that talks about truncating the model
@@
     results from the truncated Markov model with the results from the
-    untruncated simulation model.
+    untruncated simulation model. We feel that these extra numeric results 
+    do clarify the paper and are thankful for the reviewer comments.
 

### 2022-03-25 imgs/timings/data/parking_capacity_50_inc_trials/main.py
Modify truncation and timing scripts

@@ -1,0 +1,414 @@
+import time
+
+import numpy as np
+import ambulance_game as abg
+
+lambda_2 = 4
+
+lambda_1 = 2
+mu = 3
+num_of_servers = 3
+threshold = 8
+buffer_capacity = 15
+warm_up_time = 100
+runtime = 10000
+
+capacities = (10, 30, 50)
+
+
+def output_to_file(str_list, filename="demo.csv"):
+    with open(filename, "a") as f:
+        f.write(str_list + "\n")
+
+
+simulation_single_trial_unbounded = []
+for _ in range(2):
+    start_time = time.time()
+    abg.simulation.get_multiple_runs_results(
+        lambda_2=lambda_2,
+        lambda_1=lambda_1,
+        mu=mu,
+        num_of_servers=num_of_servers,
+        threshold=threshold,
+        system_capacity=float("inf"),
+        buffer_capacity=buffer_capacity,
+        seed_num=None,
+        warm_up_time=warm_up_time,
+        num_of_trials=1,
+        runtime=runtime,
+        class_type=None,
+    )
+    end_time = time.time()
+    simulation_single_trial_unbounded.append(end_time - start_time)
+output_to_file(
+    str(simulation_single_trial_unbounded), "simulation_single_trial_unbounded.csv"
+)
+print("simulation_single_trial_unbounded.csv created")
+
+simulation_single_trial_bounded_10 = []
+for _ in range(2):
+    start_time = time.time()
+    abg.simulation.get_multiple_runs_results(
+        lambda_2=lambda_2,
+        lambda_1=lambda_1,
+        mu=mu,
+        num_of_servers=num_of_servers,
+        threshold=threshold,
+        system_capacity=10,
+        buffer_capacity=buffer_capacity,
+        seed_num=None,
+        warm_up_time=warm_up_time,
+        num_of_trials=1,
+        runtime=runtime,
+        class_type=None,
+    )
+    end_time = time.time()
+    simulation_single_trial_bounded_10.append(end_time - start_time)
+output_to_file(
+    str(simulation_single_trial_bounded_10),
+    "simulation_single_trial_bounded_10.csv",
+)
+print("simulation_single_trial_bounded_10.csv created")
+
+simulation_single_trial_bounded_30 = []
+for _ in range(2):
+    start_time = time.time()
+    abg.simulation.get_multiple_runs_results(
+        lambda_2=lambda_2,
+        lambda_1=lambda_1,
+        mu=mu,
+        num_of_servers=num_of_servers,
[…]

### 2022-03-25 imgs/truncation_effect/blocking/main.py

@@ -4,6 +4,12 @@ import matplotlib.pyplot as plt
 import numpy as np
 import ambulance_game as abg
 
+
+def output_to_file(str_list, filename="demo.csv"):
+    with open(filename, "a") as f:
+        f.write(str_list + "\n")
+
+
 lambda_1 = 2
 mu = 3
 num_of_servers = 3
@@ -127,9 +133,9 @@ for index, (ax, all_markov_times, all_bounded_sim_times) in enumerate(
     )
 
     legend_elements = [
-        Line2D([0], [0], color="red", lw=2, label="Markov Chain"),
-        Patch(facecolor="tab:blue", label="Simulation (Unbounded)", alpha=0.6),
-        Patch(facecolor="tab:orange", label="Simulation (Bounded)", alpha=0.6),
+        Line2D([0], [0], color="red", lw=2, label="Finite state Markov chain"),
+        Patch(facecolor="tab:blue", label="Simulation", alpha=0.6),
+        Patch(facecolor="tab:orange", label="Truncated simulation", alpha=0.6),
     ]
     ax.legend(handles=legend_elements, loc="upper left")
     ax.set_title(f"$N$ = $M$ = {all_capacity_values[index]}")
@@ -138,3 +144,18 @@ for index, (ax, all_markov_times, all_bounded_sim_times) in enumerate(
 
 plt.suptitle("Truncation effect on blocking time")
 plt.savefig("demo.pdf", transparent=True)
+
+
+output_to_file(str(all_sim_unbound_blocking_times), "sim_unbound_blocking_times.csv")
+output_to_file(
+    str(all_sim_bound_blocking_times_low), "sim_bound_blocking_times_low.csv"
+)
+output_to_file(
+    str(all_sim_bound_blocking_times_mid), "sim_bound_blocking_times_mid.csv"
+)
+output_to_file(
+    str(all_sim_bound_blocking_times_high), "sim_bound_blocking_times_high.csv"
+)
+output_to_file(str(all_markov_blocking_times_low), "markov_blocking_times_low.csv")
+output_to_file(str(all_markov_blocking_times_mid), "markov_blocking_times_mid.csv")
+output_to_file(str(all_markov_blocking_times_high), "markov_blocking_times_high.csv")

### 2022-03-25 imgs/truncation_effect/proportion/main.py

@@ -4,6 +4,12 @@ import matplotlib.pyplot as plt
 import numpy as np
 import ambulance_game as abg
 
+
+def output_to_file(str_list, filename="demo.csv"):
+    with open(filename, "a") as f:
+        f.write(str_list + "\n")
+
+
 lambda_1 = 2
 mu = 3
 num_of_servers = 3
@@ -122,9 +128,9 @@ for index, (ax, all_markov_times, all_bounded_sim_times) in enumerate(
     )
 
     legend_elements = [
-        Line2D([0], [0], color="red", lw=2, label="Markov Chain"),
-        Patch(facecolor="tab:blue", label="Simulation (Unbounded)", alpha=0.6),
-        Patch(facecolor="tab:orange", label="Simulation (Bounded)", alpha=0.6),
+        Line2D([0], [0], color="red", lw=2, label="Finite state Markov chain"),
+        Patch(facecolor="tab:blue", label="Simulation", alpha=0.6),
+        Patch(facecolor="tab:orange", label="Truncated simulation", alpha=0.6),
     ]
     ax.legend(handles=legend_elements, loc="best")
     ax.set_title(f"$N$ = $M$ = {all_capacity_values[index]}")
@@ -133,3 +139,11 @@ for index, (ax, all_markov_times, all_bounded_sim_times) in enumerate(
 
 plt.suptitle("Truncation effect on proportion within target")
 plt.savefig("demo.pdf", transparent=True)
+
+output_to_file(str(all_sim_unbound_props), "sim_unbound_props.csv")
+output_to_file(str(all_sim_bound_props_low), "sim_bound_props_low.csv")
+output_to_file(str(all_sim_bound_props_mid), "sim_bound_props_mid.csv")
+output_to_file(str(all_sim_bound_props_high), "sim_bound_props_high.csv")
+output_to_file(str(all_markov_props_low), "markov_props_low.csv")
+output_to_file(str(all_markov_props_mid), "markov_props_mid.csv")
+output_to_file(str(all_markov_props_high), "markov_props_high.csv")

### 2022-03-25 imgs/truncation_effect/waiting/main.py

@@ -4,6 +4,12 @@ import matplotlib.pyplot as plt
 import numpy as np
 import ambulance_game as abg
 
+
+def output_to_file(str_list, filename="demo.csv"):
+    with open(filename, "a") as f:
+        f.write(str_list + "\n")
+
+
 lambda_1 = 2
 mu = 3
 num_of_servers = 3
@@ -128,9 +134,9 @@ for index, (ax, all_markov_times, all_bounded_sim_times) in enumerate(
     )
 
     legend_elements = [
-        Line2D([0], [0], color="red", lw=2, label="Markov Chain"),
-        Patch(facecolor="tab:blue", label="Simulation (Unbounded)", alpha=0.6),
-        Patch(facecolor="tab:orange", label="Simulation (Bounded)", alpha=0.6),
+        Line2D([0], [0], color="red", lw=2, label="Finite state Markov chain"),
+        Patch(facecolor="tab:blue", label="Simulation", alpha=0.6),
+        Patch(facecolor="tab:orange", label="Truncated simulation", alpha=0.6),
     ]
     ax.legend(handles=legend_elements, loc="upper left")
     ax.set_title(f"$N$ = $M$ = {all_capacity_values[index]}")
@@ -139,3 +145,13 @@ for index, (ax, all_markov_times, all_bounded_sim_times) in enumerate(
 
 plt.suptitle("Truncation effect on waiting time")
 plt.savefig("demo.pdf", transparent=True)
+
+output_to_file(str(all_sim_unbound_waiting_times), "sim_unbound_waiting_times.csv")
+output_to_file(str(all_sim_bound_waiting_times_low), "sim_bound_waiting_times_low.csv")
+output_to_file(str(all_sim_bound_waiting_times_mid), "sim_bound_waiting_times_mid.csv")
+output_to_file(
+    str(all_sim_bound_waiting_times_high), "sim_bound_waiting_times_high.csv"
+)
+output_to_file(str(all_markov_waiting_times_low), "markov_waiting_times_low.csv")
+output_to_file(str(all_markov_waiting_times_mid), "markov_waiting_times_mid.csv")
+output_to_file(str(all_markov_waiting_times_high), "markov_waiting_times_high.csv")

### 2022-03-25 sections/model_overview/main.tex
Add paragraph addressing reviewr's comment

@@
 individuals and smaller \(\alpha\) a higher weight on the time blocked. 
+Note here that the choice of \(p_A\) and \(p_B\) rely solely on equation
+\ref{eq:obj_distributor}.
+An extension that can be applied here is the use of unobservable queues.
+The ambulance service does not necessarily know at which state hospitals A and
+B are at, and thus may need to make decisions based on other
+information~\cite{unobservablequeue}.
+While this is not an unrealistic scenario it is outside of the scope of this
+paper.
+There are several other factors that can affect the routing of the patients 
+that are also outside the scope, for example the distance of each hospital or
+even the priority level of each patient.
 

### 2022-03-25 known.py
Update known words

@@ -73,5 +73,6 @@ words = {
     "stochasticity",
     "terminalstyle",
     "th",
+    "unobservable",
     "Zx",
 }

### 2022-03-25 sections/model_overview/main.tex
Define normal form game explicitly (#40)

--- 2022-03-21 sections/model_overview/main.tex
@@
 
-In order to define the normal form game the two payoff matrices of the hospitals 
-are required. From equation \ref{eq:obj_queueing_systems} the utilities of the
-hospitals can be formulated as:
-
+From equation \ref{eq:obj_queueing_systems} the utilities of the
+hospitals can be formulated.
+The 2-player normal form game between the two hospitals is defined by:
+\begin{itemize}
+    \item \textbf{Players}: Hospitals \(H_A\) and \(H_B\)
+    \item \textbf{Strategy spaces}: \(T_A = \{1, 2, \dots, N_A\}, 
+    T_B = \{1, 2, \dots, N_B\}\)
+    \item \textbf{Utilities}:    
     \begin{equation} \label{eq:payoff_entry}
-    U_{T_A, T_B}^i = 1 - \left( 
-        \hat{P} - P(W_i < t) 
-    \right)^2 \quad \textbf{where } i \in \{A, B\}
+        U_{T_A, T_B}^i = 1 - \left( \hat{P} - P(W_i < t) \right)^2 \quad
+        \textbf{where } i \in \{A, B\}
     \end{equation}
+\end{itemize}
 
@@
 \end{equation}
-% TODO: Define here the normal form game properly
 
 Based on the choice of strategy of these two hospitals, the ambulance service 
-will then 
-make their own choice of the proportion of individuals to send to each system.
+will then make their own choice of the proportion of individuals to send to
+each system.
 

### 2022-03-25 reviews/EJOR/01/main.tex
Minor changes
Apply proselint suggestion
Address two more comments

@@
     the time they took to review the manuscript.
-    Their suggestions were extremely helpful and we believe this has resulted in an improved
-    manuscript.
+    Their suggestions were extremely helpful and we believe this has resulted
+    in an improved manuscript.
     Below is a point by point response and summary of changes made.
@@
     \end{itemize}
-    The paper is presented with the application of the model as the main focus.
+    The paper is presented with the application of the model as the focus.
     All sections are now presented from the perspective of the EMS-ED
@@
     \end{itemize}
-    In the new literature review section we now directly compare the results from
-    previous work with the results from this work to highlight the
+    In the new literature review section we now directly compare the results
+    from previous work with the results from this work to highlight the
     contributions of this work.
@@
     \end{itemize}
-    This observation was really helpful and lead to us conducting more numerical experiments to clarify the point of truncating the state space.
+    This observation was really helpful and lead to us conducting more numerical
+    experiments to clarify the point of truncating the state space.
     As the values of \(N\) and \(M\) increase, the truncated Markov chain
@@
     We have touched upon building a closed-form formula for the steady state
-    probabilities but that is still a work in progress and not something we are able
-    to include in this manuscript.
+    probabilities but that is still a work in progress and not something we are
+    able to include in this manuscript.
     Figures 4-6 are there to demonstrate the accuracy of our constructed
-    model against its discrete event simulation equivalent and these have been expanded on.
+    model against its discrete event simulation equivalent and these have been
+    expanded on.
     An additional paragraph is added that talks about truncating the model
@@
     \end{itemize}
-    TBA % TODO: Reply to this comment once addressed.
+    An additional paragraph has been added that touches upon the possibility of
+    more complex queueing models where the hospital distance or patient's
+    priority type are considered.
 
@@
     \end{itemize}
-    TBA % TODO: Reply to this comment once addressed
+    In the new manuscript the normal form game is explicitly defined in the
+    game theoretic section. The players, strategies and payoffs are clearly
+    defined.
 

### 2022-03-25 sections/conclusion/main.tex
Fix failing alex check
Instead of `just` use `only`
Add a final TODO to be fixed

@@
 \end{itemize}
+Although our research is motivated by the particular EMS-ED example, our 
+developed modelling framework and behavioural insights has application to 
+similar systems across a range of sectors and settings.
+% TODO: Give example(s) of applications
+% For example, the queueing model can also be used to
 
@@
 
-The model presented here assumes the presence of just two players that can
+The model presented here assumes the presence of only two players that can
 receive individuals.

### 2022-03-26 sections/queueing_model/blocking_time/main.tex
Add sentence to explain reason behind figures 4-6
Address several todos
Update plots in paper to illustarte the truncation

@@
 \(\lambda_2\).
+The figure is used to demonstrate the accuracy of the blocking time formula of
+the constructed queueing model as well as the effect of truncating the model.
 The simulation was ran 100 times and the recorded mean blocking time at each 
 iteration is used to populate the violin plots.
-It can be seen that the blocking times generated by the simulation match the
-ones generated by the Markov chains model.
+Similar to figure \ref{fig:markov_vs_des_waiting_time_comparison_overall}, these
+plots shows a comparison between the calculated mean blocking time using Markov 
+chain, using a truncated simulation and using a simulation with infinite
+capacity (without the artificial parameters \(N\) and \(M\)).
+The blocking times generated by the truncated simulation match the ones
+generated by the Markov chains model.
+Note that this comparison includes just type 2 individuals since type 1 
+individuals cannot be blocked.
 
@@
     \centering
-    \includegraphics[width=.8\textwidth]{imgs/blocking_time_comparison/blocking.pdf}
+    \includegraphics[width=\textwidth]{imgs/truncation_effect/blocking/main.pdf}
     \caption{
-        Comparison of mean blocking time between values obtained from the 
-        Markov chain formulas and values obtained from simulation.
+        Comparison of mean blocking time between values obtained from the Markov 
+        chain formula, values obtained from the truncated simulation and values
+        obtained from the untruncated simulation.
     }

### 2022-03-26 sections/queueing_model/proportion_within_target/main.tex
Add sentence to explain reason behind figures 4-6
Update plots in paper to illustarte the truncation

@@
 and discrete event simulation (appendix~\ref{sec:appendix_des}).
+The figure is used to demonstrate the accuracy of the formula for the 
+proportion of individuals within time of the constructed queueing model
+as well as the effect that truncating the model has on the formula.
 The simulation was ran 100 times and the recorded proportions at each iteration 
 is used to populate the violin plots.
-The proportions generated by the simulation match the ones generated by the 
-Markov chains model.
+Similar to figures \ref{fig:markov_vs_des_waiting_time_comparison_overall} and
+\ref{fig:markov_vs_des_blocking_time_comparison}, these plots shows a comparison
+between the calculated mean proportion of individuals within time using Markov 
+chain, using a truncated simulation and using a simulation with infinite
+capacity (without the artificial parameters \(N\) and \(M\)).
+The proportions generated by the truncated simulation match the ones generated
+by the Markov chains model.
 Note that this comparison includes both type 1 and type 2 individuals.
@@
     \centering
-    \includegraphics[width=.8\textwidth]{imgs/proportion_within_target_comparison/proportion_overall.pdf}
+    \includegraphics[width=\textwidth]{imgs/truncation_effect/proportion/main.pdf}
     \caption{
-        Comparison of proportion within target time for both type of 
-        individuals between values obtained from the Markov chain formulas 
-        and values obtained from simulation. 
+        Comparison of mean proportion of individuals within target time between 
+        values obtained from the Markov chain formula, values obtained from the
+        truncated simulation and values obtained from the untruncated
+        simulation. 
     }

### 2022-03-26 sections/queueing_model/waiting_time/main.tex
Update plots in paper to illustarte the truncation

@@
 The figure is used to demonstrate the accuracy of the waiting time formula of
-the constructed queueing model.
+the constructed queueing model as well as the effect of truncating the model.
 The simulation was ran 100 times and the recorded mean waiting time at each 
 iteration is used to populate the violin plots.
-The waiting times generated by the simulation match the ones generated by the 
-Markov chains model.
+In detail, figure \ref{fig:markov_vs_des_waiting_time_comparison_overall} shows
+the calculated mean waiting time using Markov chain, using a truncated 
+simulation and using a simulation with infinite capacity (without the artificial
+parameters \(N\) and \(M\)).
+Each plot corresponds to different values of \(N\) and \(M\) and is ran over 
+different values of \(\lambda_2\).
+The untruncated simulation values (blue) are the same at all three graphs since
+the effect of truncation does not apply to it.
+The waiting times generated by the truncated simulation match the ones generated 
+by the Markov chains model.
 Note that this comparison includes both type 1 and type 2 individuals.
@@
     \centering
-    \includegraphics[width=.8\textwidth]{imgs/waiting_time_comparison/waiting_overall.pdf}
+    \includegraphics[width=\textwidth]{imgs/truncation_effect/waiting/main.pdf}
     \caption{
-        Comparison of mean waiting time for both types of individuals between 
-        values obtained from the Markov chain formulas and values obtained from 
-        simulation.
+        Comparison of mean waiting time between values obtained from the Markov 
+        chain formula, values obtained from the truncated simulation and values
+        obtained from the untruncated simulation.
     }

### 2022-03-27 imgs/timings/data/parking_capacity_50_inc_trials/main.py
Produce data for timing experiments

@@ -31,7 +31,7 @@ for _ in range(2):
         num_of_servers=num_of_servers,
         threshold=threshold,
         system_capacity=float("inf"),
-        buffer_capacity=buffer_capacity,
+        buffer_capacity=float("inf"),
         seed_num=None,
         warm_up_time=warm_up_time,
         num_of_trials=1,
@@ -55,7 +55,7 @@ for _ in range(2):
         num_of_servers=num_of_servers,
         threshold=threshold,
         system_capacity=10,
-        buffer_capacity=buffer_capacity,
+        buffer_capacity=10,
         seed_num=None,
         warm_up_time=warm_up_time,
         num_of_trials=1,
@@ -80,7 +80,7 @@ for _ in range(2):
         num_of_servers=num_of_servers,
         threshold=threshold,
         system_capacity=30,
-        buffer_capacity=buffer_capacity,
+        buffer_capacity=30,
         seed_num=None,
         warm_up_time=warm_up_time,
         num_of_trials=1,
@@ -106,7 +106,7 @@ for _ in range(2):
         num_of_servers=num_of_servers,
         threshold=threshold,
         system_capacity=50,
-        buffer_capacity=buffer_capacity,
+        buffer_capacity=50,
         seed_num=None,
         warm_up_time=warm_up_time,
         num_of_trials=1,
@@ -132,10 +132,10 @@ for _ in range(2):
         num_of_servers=num_of_servers,
         threshold=threshold,
         system_capacity=float("inf"),
-        buffer_capacity=buffer_capacity,
+        buffer_capacity=float("inf"),
         seed_num=None,
         warm_up_time=warm_up_time,
-        num_of_trials=20,
+        num_of_trials=100,
         runtime=runtime,
         class_type=None,
     )
@@ -158,10 +158,10 @@ for _ in range(2):
         num_of_servers=num_of_servers,
         threshold=threshold,
         system_capacity=10,
-        buffer_capacity=buffer_capacity,
+        buffer_capacity=10,
         seed_num=None,
         warm_up_time=warm_up_time,
-        num_of_trials=20,
+        num_of_trials=100,
         runtime=runtime,
         class_type=None,
     )
@@ -184,10 +184,10 @@ for _ in range(2):
         num_of_servers=num_of_servers,
         threshold=threshold,
         system_capacity=30,
-        buffer_capacity=buffer_capacity,
+        buffer_capacity=30,
         seed_num=None,
         warm_up_time=warm_up_time,
[…]

### 2022-03-28 sections/queueing_model/truncation_effect/main.tex
Minor changes to truncation paragraph

\subsection{Truncation effect timings} \label{sec:truncation_effect}

The choice of the artificial parameters \(N\) and \(M\) is an important 
decision of the model.
In the untruncated simulation these values are set to be infinite. 
This is more computationally expensive to run.
Table \ref{tab:truncation_effect_timings} shows the relative timings of the
different approaches used to get the performance measures.

\begin{table}[h]
    \centering
    \begin{tabular}{c|cc|ccc}
        & \multicolumn{2}{c}{\textbf{Simulation timings}} & 
        \multicolumn{3}{c}{\textbf{Markov chain timings}} \\
        \textbf{Value of} & \textbf{Single} & \textbf{A hundred} & 
        \textbf{Waiting time} & \textbf{Blocking time} & 
        \textbf{Proportion within} \\
        \textbf{N and M} & \textbf{trial} & \textbf{trials} & 
        \textbf{formula} & \textbf{formula} & \textbf{time formula} \\
        \hline
        \(10\) & 1 & 144.3 & 0.015 & 0.014 & 0.014 \\
        \hline
        \(30\) & 1 & 143.4 & 3.731 & 3.828 & 3.649 \\
        \hline
        \(50\) & 1 & 139.8 & 31.57 & 38.39 & 31.98 \\
        \hline
        \(\infty\) & 1 & 142.1 & N/A & N/A & N/A \\
    \end{tabular}
    \caption{Relative timings of the simulation and Markov chain model}
    \label{tab:truncation_effect_timings}
\end{table}

### 2022-03-28 known.py

@@ -74,5 +74,6 @@ words = {
     "terminalstyle",
     "th",
     "unobservable",
+    "untruncated",
     "Zx",
 }

### 2022-03-28 known.py
Update known words

@@ -14,6 +14,7 @@ words = {
     "breaklines",
     "calc",
     "captionpos",
+    "ccc",
     "CDF",
     "CDFs",
     "center",

### 2022-03-28 sections/conclusion/main.tex
Add example of another application of the model

@@
 similar systems across a range of sectors and settings.
-% TODO: Give example(s) of applications
-% For example, the queueing model can also be used to
+The queueing model can be applied to any setting where individuals may be
+blocked on a separate queue.
+An example of such setting can be any type of delivery service where customers
+can purchase goods either online or walk in the store.
+More specifically consider a food delivery service where customers can order
+food online or walk in the store.
+At busier times, the person delivering the food may be blocked outside the
+restaurant in an attempt to improve the waiting times for walk-in customers.
 

### 2022-03-29 sections/queueing_model/waiting_time/main.tex
Apply suggestions from Vince's review
Co-authored-by: Vince Knight <vince@vknight.org>

@@
 In detail, figure \ref{fig:markov_vs_des_waiting_time_comparison_overall} shows
-the calculated mean waiting time using Markov chain, using a truncated 
+the calculated mean waiting time using the Markov chain, using a truncated 
 simulation and using a simulation with infinite capacity (without the artificial
 parameters \(N\) and \(M\)).
-Each plot corresponds to different values of \(N\) and \(M\) and is ran over 
+Each plot corresponds to different values of \(N\) and \(M\) and is run over 
 different values of \(\lambda_2\).
-The untruncated simulation values (blue) are the same at all three graphs since
+The untruncated simulation values are the same at all three graphs since
 the effect of truncation does not apply to it.

### 2022-03-29 imgs/asymmetric_rd_and_PoA/main.py
Add script and notebook of previous plots

@@ -1,0 +1,829 @@
+import csv
+import itertools
+import os
+import pathlib
+
+import matplotlib.colors as mcolors
+import matplotlib.pyplot as plt
+import nashpy as nash
+import numpy as np
+import pandas as pd
+
+import ambulance_game as abg
+
+# from nashpy.algorithms.lemke_howson_lex import lemke_howson_lex
+
+
+def get_index_of_values(problem_parameters, data, atol=1e-08, rtol=1e-05):
+    """
+    Get the indices of the rows that match the given parameters' values
+    """
+    index = data.index
+    condition = (
+        np.isclose(
+            data["lambda_2"], problem_parameters["lambda_2"], atol=atol, rtol=rtol
+        )
+        & np.isclose(
+            data["lambda_1_1"], problem_parameters["lambda_1_1"], atol=atol, rtol=rtol
+        )
+        & np.isclose(
+            data["lambda_1_2"], problem_parameters["lambda_1_2"], atol=atol, rtol=rtol
+        )
+        & np.isclose(data["mu_1"], problem_parameters["mu_1"], atol=atol, rtol=rtol)
+        & np.isclose(data["mu_2"], problem_parameters["mu_2"], atol=atol, rtol=rtol)
+        & np.isclose(data["num_of_servers_1"], problem_parameters["num_of_servers_1"])
+        & np.isclose(data["num_of_servers_2"], problem_parameters["num_of_servers_2"])
+        & np.isclose(data["system_capacity_1"], problem_parameters["system_capacity_1"])
+        & np.isclose(data["system_capacity_2"], problem_parameters["system_capacity_2"])
+        & np.isclose(data["buffer_capacity_1"], problem_parameters["buffer_capacity_1"])
+        & np.isclose(data["buffer_capacity_2"], problem_parameters["buffer_capacity_2"])
+        & np.isclose(data["alpha"], problem_parameters["alpha"])
+        & np.isclose(data["target"], problem_parameters["target"], atol=atol, rtol=rtol)
+    )
+    indices = index[condition]
+    return indices
+
+
+def create_directory_with_notebook(data, index_value):
+    """
+    Create the directory with main.ipynb that contains a brief analysis for that scenario
+    """
+    hash_value = data[index_value : index_value + 1]["hash_value"]
+    dirname = hash_value.to_string(index=False)[1:]
+    new_dir = pathlib.Path() / dirname
+    new_dir.mkdir(exist_ok=True)
[…]

### 2022-03-29 sections/queueing_model/blocking_time/main.tex
Apply suggestion by alex
Investigate the truncation effect (#34)
* Get initial plots of truncation effects

Plots added on unbounded simulation VS Markov chain (while
increasing capacity):
- Waiting time
- Blocking time
- Proportion of individuals within time

* Add bounded simulation to same plot

* Write script to generate duration for each method

* Get timing data when M=50

Times for N = (10, 30, 50, inf) for markov (waiting, blocking and
proportion formula) and simulation (1 trial, 20 trials)

* Get timing data when M=5

Times for N = (10, 30, 50, inf) for markov (waiting, blocking and
p

@@
 plots shows a comparison between the calculated mean blocking time using Markov 
-chain, using a truncated simulation and using a simulation with infinite
-capacity (without the artificial parameters \(N\) and \(M\)).
+chain, using a truncated simulation and using a simulation without the
+artificial parameters \(N\) and \(M\).
 The blocking times generated by the truncated simulation match the ones
 generated by the Markov chains model.
-Note that this comparison includes just type 2 individuals since type 1 
+Note that this comparison includes only type 2 individuals since type 1 
 individuals cannot be blocked.

### 2022-03-29 sections/queueing_model/proportion_within_target/main.tex
Investigate the truncation effect (#34)
* Get initial plots of truncation effects

Plots added on unbounded simulation VS Markov chain (while
increasing capacity):
- Waiting time
- Blocking time
- Proportion of individuals within time

* Add bounded simulation to same plot

* Write script to generate duration for each method

* Get timing data when M=50

Times for N = (10, 30, 50, inf) for markov (waiting, blocking and
proportion formula) and simulation (1 trial, 20 trials)

* Get timing data when M=5

Times for N = (10, 30, 50, inf) for markov (waiting, blocking and
proportion formula) and si

@@
 between the calculated mean proportion of individuals within time using Markov 
-chain, using a truncated simulation and using a simulation with infinite
-capacity (without the artificial parameters \(N\) and \(M\)).
+chain, using a truncated simulation and using a simulation 
+without the artificial parameters \(N\) and \(M\).
 The proportions generated by the truncated simulation match the ones generated

### 2022-03-29 known.py

@@ -14,6 +14,7 @@ words = {
     "breaklines",
     "calc",
     "captionpos",
+    "ccc",
     "CDF",
     "CDFs",
     "center",
@@ -74,5 +75,6 @@ words = {
     "terminalstyle",
     "th",
     "unobservable",
+    "untruncated",
     "Zx",
 }

### 2022-03-29 imgs/asymmetric_rd_and_PoA/main.py
Change plots axis labels

@@ -581,7 +581,7 @@ def plot_asymmetric_replicator_dynamics_with_penalty(
     plt.plot(all_xs)
     plt.xlabel("Timepoints")
     plt.ylabel("Probability")
-    plt.title("Row player")
+    plt.title("Hospital A")
     plt.legend([f"$s_{i + 1}$" for i in range(len(all_xs[0]))])
     if penalty is not None:
         plt.plot(
@@ -597,7 +597,7 @@ def plot_asymmetric_replicator_dynamics_with_penalty(
     plt.plot(all_ys)
     plt.xlabel("Timepoints")
     plt.ylabel("Probability")
-    plt.title("Column player")
+    plt.title("Hospital B")
     plt.legend([f"$s_{i + 1}$" for i in range(len(all_ys[0]))])
     if penalty is not None:
         plt.plot(
@@ -610,12 +610,12 @@ def plot_asymmetric_replicator_dynamics_with_penalty(
         plt.annotate("Incentives", (len(all_ys) / 2, 1.1), ha="center")
 
     plt.subplot(2, 2, 3)
-    plt.title("Row player - PoA")
+    plt.title("Hospital A - PoA")
     plt.plot(poa_span, performance_value_poa_A, color="black", linewidth=6)
     plt.ylim(top=poa_plot_max, bottom=poa_plot_min)
 
     plt.subplot(2, 2, 4)
-    plt.title("Column player - PoA")
+    plt.title("Hospital B - PoA")
     plt.plot(poa_span, performance_value_poa_B, color="black", linewidth=6)
     plt.ylim(top=poa_plot_max, bottom=poa_plot_min)
 
@@ -791,7 +791,7 @@ def plot_asymmetric_replicator_dynamics_with_dual_parameters(
     plt.plot(all_xs)
     plt.xlabel("Timepoints")
     plt.ylabel("Probability")
-    plt.title("Row player")
+    plt.title("Hospital A")
     plt.legend([f"$s_{{{i + 1}}}$" for i in range(len(all_xs[0]))])
     plt.plot(
         [len(all_xs) / divide, len(all_xs) / divide],
@@ -806,7 +806,7 @@ def plot_asymmetric_replicator_dynamics_with_dual_parameters(
     plt.plot(all_ys)
     plt.xlabel("Timepoints")
     plt.ylabel("Probability")
-    plt.title("Column player")
+    plt.title("Hospital B")
[…]

### 2022-03-29 sections/model_overview/numerical_results/main.tex
Scale payoff matrices to be more presentable

@@
 \ref{fig:ard_penalty}).
-Note that the values of the payoff matrices only differ on the fourth digit
-which is the raw utility of the strategies played.
+Note that for the presentation of data, a scaling has been applied to obtain
+the values of the payoff matrices.
+The results are not affected by this scaling.
 
@@
     \begin{bmatrix}
-        0.9995052 & 0.9995052 & 0.9995052 & 0.9995052 & 0.9995052 
-        & 0.9995052 & 0.9995052 \\
-        0.99954989 & 0.99954978 & 0.99954961 & 0.99954924 & 0.99954845 
-        & 0.9995466 & 0.999539 \\
-        0.99968233 & 0.99968194 & 0.99968151 & 0.99968067 & 0.99967874 
-        & 0.9996734 & 0.999649  \\
-        0.99990299 & 0.99990245 & 0.99990189 & 0.99990081 & 0.99989832
-        & 0.9998909 & 0.9998517 \\
-        \color{blue}0.99999996 & \color{blue}0.99999994 & \color{blue}0.99999992 
-        & \color{blue}0.99999988 & \color{blue}0.99999973 & \color{blue}0.9999989 
-        & \color{blue}0.9999859 \\
-        0.9998773 & 0.99987995 & 0.99988236 & 0.99988643 & 0.99989417 
-        & 0.9999126 & 0.9999712
+        5.0518 & 5.0518 & 5.0518 & 5.0518 & 5.0518 &
+        5.0518 & 5.0518 \\
+        5.4989 & 5.4977 & 5.4960 & 5.4924 & 5.4844 &
+        5.4654 & 5.3875 \\
+        6.8232  & 6.8192 & 6.8150 & 6.8065 & 6.7871  &
+        6.7334 & 6.4906 \\
+        9.0298 & 9.0244 & 9.0187 & 9.0078 & 8.9827 &
+        8.9082 & 8.5145 \\
+        \color{blue}9.9996 & \color{blue}9.9994 & \color{blue}9.9992 & 
+        \color{blue}9.9987 & \color{blue}9.9972 & \color{blue}9.9893 & 
+        \color{blue}9.8571 \\
+        8.7740 & 8.8006 & 8.8249 & 8.8660 & 8.9438 &
+        9.1295 & 9.7157
     \end{bmatrix}
@@
     \begin{bmatrix}
-        0.99917127 & 0.99925823 & 0.99946188 & 0.99968499 & 0.9998942 
-        & \color{red}1.0 & 0.99982128 \\
-        0.99917127 & 0.99925479 & 0.99945638 & 0.99968051 & 0.99989153 
-        & \color{red}0.99999997 & 0.9998333  \\
-        0.99917127 & 0.99924532 & 0.99943793 & 0.99966451 & 0.99988286 
-        & \color{red}0.99999966 & 0.99985269 \\
-        0.99917127 & 0.99924146 & 0.99942878 & 0.99965484 & 0.99987667 
-        & \color{red}0.99999921 & 0.99986701 \\
-        0.99917127 & 0.9992342 &  0.99941013 & 0.99963286 & 0.99986077 
-        & \color{red}0.9999972 & 0.9998958  \\
-        0.99917127 & 0.99921279 & 0.99934961 & 0.99954933 & 0.99978407 
-        & \color{red}0.99997106 & 0.99997276 \\
+        1.7127 & 2.5822 & 4.6186 & 6.8497 & 8.9418 &
+        \color{red}9.9999 & 8.2148 \\
+        1.7127 & 2.5477 & 4.5634 & 6.8047 & 8.9150  &
+        \color{red}9.9996 & 8.3358 \\
+        1.7127 & 2.4528    & 4.3784 & 6.6441 & 8.8278 &
+        \color{red}9.9965 & 8.5306 \\
+        1.7127 & 2.4141 & 4.2867 & 6.5470 & 8.7656 &
+        \color{red}9.9919 & 8.6745 \\
+        1.7127 & 2.3415 & 4.0998 & 6.3265 & 8.6058 &
+        \color{red}9.9716 & 8.9634 \\
+        1.7127 & 2.1269 & 3.4930 & 5.4885 & 7.8353 &
+        \color{red}9.7075 & 9.7322 \\
     \end{bmatrix}
@@
     \begin{bmatrix}
-        0.99950518 & 0.99950518 & 0.99950518 & 0.99950518 & 0.99950518
-        & 0.99950518 & 0.99950518 \\
-        0.99954989 & 0.99954978 & 0.99954961 & 0.99954924 & 0.99954845
-        & 0.99954656 & 0.99953879 \\
-        0.99968233 & 0.99968194 & 0.99968151 & 0.99968067 & 0.99967874
-        & 0.99967339 & 0.9996492  \\
-        0.99990299 & 0.99990245 & 0.99990189 & 0.99990081 & 0.99989832
-        & 0.9998909 & 0.99985171 \\
-        \color{blue}0.99969996 & \color{blue}0.99969994 & \color{blue}0.99969992 
-        & \color{blue}0.99969988 & \color{blue}0.99969973 & \color{blue}0.99969895 
-        & \color{blue}0.99968586 \\
-        0.9998773 &  0.99987995 & 0.99988236 & 0.99988643 & 0.99989417
-        & 0.99991264 & 0.99997122 \\
+        5.0518 & 5.0518 & 5.0518 & 5.0518 & 5.0518 &
+        5.0518 & 5.0518  \\
+        5.4989 & 5.4977 & 5.4960 & 5.4924 & 5.4844 &
+        5.4654 & 5.3875 \\
+        6.8232 & 6.8192 & 6.8150 & 6.8065 & 6.7871 &
+        6.7334 & 6.4906 \\
+        9.0298 & 9.0244 & 9.0187 & 9.0078 & 8.9827 &
+        8.9082 & 8.5145 \\
+        \color{blue}6.9996 & \color{blue}6.9994 & \color{blue}6.9992 & \color{blue}6.9987  & \color{blue}6.9972 &
+        \color{blue}6.9893 & \color{blue}6.8571 \\
+        8.7740 & 8.8006 & 8.8249 & 8.8660 & 8.9438 &
+        9.1295 & 9.7157 \\
     \end{bmatrix}
@@
     \begin{bmatrix}
-        0.99917127 & 0.99925823 & 0.99946188 & 0.99968499 & 0.9998942
-        & \color{red}0.9997 & 0.99982128 \\
-        0.99917127 & 0.99925479 & 0.99945638 & 0.99968051 & 0.99989153
-        & \color{red}0.99969997 & 0.9998333 \\
-        0.99917127 & 0.99924532 & 0.99943793 & 0.99966451 & 0.99988286
-        & \color{red}0.99969966 & 0.99985269 \\
-        0.99917127 & 0.99924146 & 0.99942878 & 0.99965484 & 0.99987667
-        & \color{red}0.99969921 & 0.99986701 \\
-        0.99917127 & 0.9992342 &  0.99941013 & 0.99963286 & 0.99986077
-        & \color{red}0.9996972 & 0.9998958 \\
-        0.99917127 & 0.99921279 & 0.99934961 & 0.99954933 & 0.99978407
-        & \color{red}0.99967106 & 0.99997276 \\
+        1.7127 & 2.5822 & 4.6186 & 6.8497 & 8.9418 &
+        \color{red}6.9999 & 8.2148 \\
+        1.7127 & 2.5477 & 4.5634 & 6.8047 & 8.9150 &
+        \color{red}6.9996 & 8.3358 \\
+        1.7127 & 2.4528   & 4.3784 & 6.6441 & 8.8278 &
+        \color{red}6.9965 & 8.5306 \\
+        1.7127 & 2.4141 & 4.2867 & 6.5470 & 8.7656 &
+        \color{red}6.9919 & 8.6745 \\
+        1.7127 & 2.3415 & 4.0998 & 6.3265 & 8.6058 &
+        \color{red}6.9716 & 8.9634  \\
+        1.7127 & 2.1269 & 3.4930 & 5.4885 & 7.8353 &
+        \color{red}6.7076 & 9.7322 \\
     \end{bmatrix}

### 2022-03-29 sections/appendix/descrete_event_simulation/main.tex
Changes based on self review
I just read the whole thing and made some minor
changes here and there.
Minor additional changes

@@
-\section{Discrete Event Simulation}\label{sec:appendix_des}
+\section{Discrete event simulation}\label{sec:appendix_des}
 
@@
 \subsubsection{How to get the optimal distribution of class 2 individuals among 2 
-queuing models:}
+queueing models:}
 
@@
     \item \lstinline[style=pystyle]{build_model}: \textit{Builds a ciw object 
-    that represents a model of a queuing network with two waiting spaces.}
+    that represents a model of a queueing network with two waiting spaces.}
     \item \lstinline[style=pystyle]{build_custom_node}: \textit{Build a custom 

### 2022-03-29 sections/model_overview/main.tex
Address several todos
Address several TODOs (#41)
* Update highlights

* Address several todos

* Add a final TODO to be fixed

* Add example of another application of the model

* Fix a typo

* Add script and notebook of previous plots

* Rename jupyter notebook

* Change plots axis labels

* Scale payoff matrices to be more presentable

* Remove unnecessary equations

* Minor additional changes

* Address the high traffic intensity

@@
 \begin{itemize}
-    \item \( \lambda_2 \): The rate of non-emergency patients that the EMS 
-    receives and distributes to EDs
-    % TODO: Use consistent notation of non-urgent/non-emergency patients
+    \item \( \lambda_2 \): The rate of patients (who can be blocked) that the 
+    EMS receives and distributes to EDs
     \item \( \lambda_{1_i} \): The arrival rate of other patients to ED 
@@
     professionals) in the ED \(i\in\{A, B\}\)
-    % TODO: Make sure that servers are defined the same way throughout
     \item \( T_i \): The action that ED \(i\in\{A, B\} \) chooses to play which 
@@
 professionals able to see them.
-% TODO: Should this be healthcare professionals or available beds?
 The second waiting space (i.e. the parking space for ambulances) is where 
@@
 
-Following this queuing model, the two queueing systems' choice of strategy will 
-then rely solely on satisfying their own 
-objective, which is to satisfy:
+Following this queueing model, the two queueing systems' choice of strategy will 
+then rely solely on satisfying their own objective.
+The objective function is defined as:
 
-\begin{equation}
-    P(W < t) \geq \hat{P}
+\begin{equation}\label{eq:obj_queueing_systems}
+    \arg \max_{T_i} \quad -\left( \hat{P} - P(W_i < t) \right)^2 \qquad 
+    i \in {A, B}
 \end{equation}
@@
 target. 
-There are numerous objective functions that can be used to capture this 
-behaviour. 
-For example one approach is to use the threshold that maximises the probability 
-that 
-the mean waiting is more than the target time, and completely ignore the 
-percentage goal \(\hat{P}\).
-
-\begin{equation}
-    \arg \max_{T_i} \quad P(W_i < t)
-\end{equation}
-
-A more sophisticated objective function would be to get the proportion 
-of individuals as close to the percentage aim. 
-In other words, to find the threshold that minimises the difference between the 
-probability and the percentage goal (or maximise its negation).
-
-% TODO: Maybe only this equation is needed here. Remove the previous two?
-\begin{equation}\label{eq:obj_queueing_systems}
-    \arg \max_{T_i} \quad -\left( \hat{P} - P(W_i < t) \right)^2
-\end{equation}
+In other words, their aim is to find the threshold that minimises the 
+difference between the probability \(P(W_i < t)\) and the percentage goal 
+(or maximise its negation).
 

### 2022-03-29 reviews/EJOR/01/main.tex
Address another two comments
- More applications examples
- Rewritten highlights
Address the final comments

@@
     \end{itemize}
-    TBA % TODO: Reply to this comment once addressed.
+    The queueing systems in the particular example are meant to be very
+    busy systems. In the new manuscript it is more clearly stated.
 
@@
     \end{itemize}
-    TBA % TODO: Reply to this comment once addressed.
+    Examples of other applications have been added in the conclusion section
+    of the manuscript.
 
@@
     \end{itemize}
-    TBA % TODO: Reply to this comment once addressed
+    Highlights have been rewritten to be more explicit in terms of the work
+    that was done.
 
@@
     \end{itemize}
-    TBA % TODO: Reply to this comment once addressed
+    We have thoroughly checked the grammar and spelling of the manuscript.
 

### 2022-03-30 sections/model_overview/main.tex
Highlight choice of queue and potential extensions
Rewrite the whole paragraph so that the choice of unobservable queues
is highlighted and clearly state the potential new extensions

@@
 individuals and smaller \(\alpha\) a higher weight on the time blocked. 
-Note here that the choice of \(p_A\) and \(p_B\) rely solely on equation
+The choice of \(p_A\) and \(p_B\) rely solely on equation
 \ref{eq:obj_distributor}.
-An extension that can be applied here is the use of unobservable queues.
-The ambulance service does not necessarily know at which state hospitals A and
-B are at, and thus may need to make decisions based on other
-information~\cite{unobservablequeue}.
-While this is not an unrealistic scenario it is outside of the scope of this
-paper.
-There are several other factors that can affect the routing of the patients 
-that are also outside the scope, for example the distance of each hospital or
-even the priority level of each patient.
+Note that the current system is modelled using unobservable queues which is not
+necessarily an unrealistic approach~\cite{unobservablequeue}.
+However, there are several other factors that can affect the routing of the
+patients that are outside the scope of this paper.
+For example the distance from each hospital or even the priority level of each
+patient may be a significant factor that affects the ambulance service's
+decision.
 

### 2022-03-30 known.py
Update known words

@@ -3,6 +3,7 @@
 words = {
     "Abacws",
     "abg",
+    "affine",
     "alsoletter",
     "apalike",
     "automata",

### 2022-03-30 sections/model_overview/main.tex
Reword a sentence

@@
 necessarily an unrealistic approach~\cite{unobservablequeue}.
-However, there are several other factors that can affect the routing of the
+Another approach would be to allow the ambulance service to observe the state
+of each hospital before deciding which one to join for a given individual.
+There are several other factors that can affect the routing of the
 patients that are outside the scope of this paper.

### 2022-03-30 sections/conclusion/main.tex
Address several TODOs (#41)
* Update highlights

* Address several todos

* Add a final TODO to be fixed

* Add example of another application of the model

* Fix a typo

* Add script and notebook of previous plots

* Rename jupyter notebook

* Change plots axis labels

* Scale payoff matrices to be more presentable

* Remove unnecessary equations

* Minor additional changes

* Address the high traffic intensity
Changes after first supervisory review (#44)
* Apply minor changes

* Highlight choice of queue and potential extensions

Rewrite the whole paragraph so that the choice of unobservable

@@
 can purchase goods either online or walk in the store.
-More specifically consider a food delivery service where customers can order
-food online or walk in the store.
 At busier times, the person delivering the food may be blocked outside the
@@
 \ref{sec:proportion_within_target}).
-This novel queuing model is the first contribution of the paper.
+This novel queueing model is the first contribution of the paper.
 The game theoretic model is then applied to a healthcare scenario by looking at
@@
 agent-based model.
-This in turn can be used to model ED staff as agents each with their own
-behavioural traits.
+This in turn can be used to model emergent behaviour based on assumptions of
+individual behavioural traits of ED staff.
 Finally, future work can touch upon the derivation of a closed form formula for

### 2022-03-30 sections/model_overview/numerical_results/main.tex
Address several TODOs (#41)
* Update highlights

* Address several todos

* Add a final TODO to be fixed

* Add example of another application of the model

* Fix a typo

* Add script and notebook of previous plots

* Rename jupyter notebook

* Change plots axis labels

* Scale payoff matrices to be more presentable

* Remove unnecessary equations

* Minor additional changes

* Address the high traffic intensity
Changes after first supervisory review (#44)
* Apply minor changes

* Highlight choice of queue and potential extensions

Rewrite the whole paragraph so that the choice of unobservable

@@
 
-% TODO: Make clear that we are speaking about a flooded model here.
+For this particular scenario, two busy queueing systems will be
+used with a high traffic intensity (\(\rho > 1\)).
 Consider a game with two smaller (lower \( N_i, M_i \)) and busier (higher 
@@
 \ref{fig:ard_penalty}).
-Note that for the presentation of data, a scaling has been applied to obtain
-the values of the payoff matrices.
+Note that for the presentation of data, an affine transformation has been
+applied to obtain the values of the payoff matrices
+(\(A_ij = 10000(a_{ij} - 0.999) \text{ and } B_{ij} = 10000(b_{ij} - 0.999)\)
+where \(a_{ij}\) and \(b_{ij}\) are the raw utilities).
 The results are not affected by this scaling.
@@
         8.9082 & 8.5145 \\
-        \color{blue}6.9996 & \color{blue}6.9994 & \color{blue}6.9992 & \color{blue}6.9987  & \color{blue}6.9972 &
-        \color{blue}6.9893 & \color{blue}6.8571 \\
+        \color{blue}6.9996 & \color{blue}6.9994 & \color{blue}6.9992 &
+        \color{blue}6.9987 & \color{blue}6.9972 & \color{blue}6.9893 &
+        \color{blue}6.8571 \\
         8.7740 & 8.8006 & 8.8249 & 8.8660 & 8.9438 &

### 2022-04-05 sections/literature_review/main.tex
Apply changes to intro and lit review

@@
 expected delay.
-In this paper, while giving some consideration to equilibrium behaviour,
+In our work, while giving some consideration to equilibrium behaviour,
 similar to the work of~\cite{FirmCompetition, FirmCompetition2}, emergent
@@
 hospitals, as opposed to the previous models which are one or the other.
-Thus, the novelty of this paper in a way is combining both these aspects.
+Thus, the novelty of our work is combining both these aspects.
 
@@
 profit and lower demand rate.
-In this paper the concepts described in~\cite{d2015pure, burnetas2013customer,
+In our work, the concepts described in~\cite{d2015pure, burnetas2013customer,
 bacsar2002stackelberg} are extended by introducing a threshold parameter that 

### 2022-04-05 sections/conclusion/main.tex
Apply changes to conclusion

@@
 under a lot of pressure to treat patients.
-This is in practice often centrally controlled through a mechanism of some sort
-of performance measure target.
+This is, in practice, often centrally controlled through a mechanism of some
+sort of performance measure target.
 This paper shows how this can negatively impact the pathway of both the
@@
 An example of such setting can be any type of delivery service where customers
-can purchase goods either online or walk in the store.
-At busier times, the person delivering the food may be blocked outside the
-restaurant in an attempt to improve the waiting times for walk-in customers.
+can purchase goods either online or in-person.
+At busier times, the person delivering the product may be blocked outside the
+store in an attempt to improve the waiting times for walk-in customers.
 
@@
 \begin{itemize}
-    \item Inefficiencies can be learned and emerge naturally
-    \item Targeted incentivisation of behaviours can help escape inefficiencies
+    \item Inefficiencies can be learned and emerge naturally;
+    \item Targeted incentivisation of behaviours can help escape inefficiencies.
 \end{itemize}
 The former relates to the results of asymmetric replicator dynamics that showed
-that inefficient scenarios can arise by playing the game while the latter
+that inefficient scenarios can arise by playing the game, while the latter
 implies that the learned inefficiencies can be escaped by carefully applying
@@
 the best way to describe the model.
-In reality ED managers could have far more complex parameters for their
+In reality ED managers might adopt far more complex parameters for their
 decision making process.
@@
 way by only aiming to satisfy their own objectives.
-In fact, modelling behaviour in a healthcare setting is a much more complex
-task where some cooperation may often be observed.
+In some settings, cooperation may be observed and would therefore require an
+adapted modelling approach.
 Another extension would be to explore the behaviour of the ED staff via an
-agent-based model.
+agent-based simulation model.
 This in turn can be used to model emergent behaviour based on assumptions of
 individual behavioural traits of ED staff.
-Finally, future work can touch upon the derivation of a closed form formula for
+Finally, future work could touch upon the derivation of a closed form formula for
 the steady state probability vector of the queueing model

### 2022-04-05 sections/appendix/proportion_within_target_formula/main.tex
Minor changes to appendix

@@
 Consider the case when an arrival occurs when the model is at a specific state.
-
-\paragraph{Time distribution at specific state (1 server):}
 
@@
 
+\underline{\textit{Time distribution at specific state (1 server):}}
 Consider the Markov model of Figure 
@@
 
-\paragraph{Time distribution at a state (multiple servers):}
+\underline{\textit{Time distribution at a state (multiple servers):}}
 
@@
 
-\paragraph{Specific CDF of hypoexponential distribution}
+\underline{\textit{Specific CDF of hypoexponential distribution:}}
 Equations (\ref{eq:general_cdf_hypoexponential}) and 
@@
 
-\paragraph{Proof of equation (\ref{eq:hypoexponential_expression_to_proof})}
-
+\underline{
+    \textit{Proof of equation (\ref{eq:hypoexponential_expression_to_proof}):}
+}
 This section aims to show that there exists a simplified version of equation 
@@
 
-\paragraph{Proportion within target for both types of individuals}
-
+\underline{\textit{Proportion within target for both types of individuals:}}
 Given the two CDFs of the Erlang and Hypoexponential distributions a new 
@@
 
-\paragraph{Overall proportion within target}
-
+\underline{\textit{Overall proportion within target:}}
 The overall proportion of individuals for both types of individuals is given by 

### 2022-04-05 sections/introduction/main.tex
Add a final TODO to be fixed
Changes after second supervisory review (#45)
* Add changes to response to reviewers

* Fix square in general markov model image

* Add another keyword

* Apply changes to intro and lit review

* Apply changes to queueing mode section

* Apply changes to game theoretic mode section

* Apply changes to conclusion

* Minor changes to appendix

* Compile PDF

@@
 they are not in use~\cite{herefordtimes} and there are several reports of 
-examples where this became an issue for new patients~\cite{southwalesargus}.
-A particular article looked into this problem from the point of view of an 
-ambulance paramedic:
-
-\begin{quotation}
-    % <!--alex ignore he-she her-him-->
-    ``He knows if a patient arrives more urgently in need of help, his will be 
-    pushed back''~\cite{bbcwales}
-
-    ``We used to bring poorly patients in, and we were out on the road again in
-    15 minutes.''~\cite{bbcwales}
-\end{quotation}
+examples where this became an issue for new patients~\cite{southwalesargus}
+and paramedics~\cite{bbcwales}.
 
@@
 the threshold that the given ED chooses to play.
-High threshold indicates that the ED accepts ambulance patients even if it is 
-relatively full, while low threshold means that the ED blocks ambulances more 
+A high threshold indicates that the ED accepts ambulance patients even if it is 
+relatively full, while a low threshold means that the ED blocks ambulances more 
 frequently.
-In the United Kingdom the National Heath Services (NHS) sets some regulations 
+
+In the United Kingdom, the National Heath Services (NHS) sets some regulations 
 on ED performance.
@@
 \begin{itemize}
-    \item A queueing model with 2 consecutive waiting spaces where one would 
-    serve as a parking space for the ambulances
-    \item Analytic performance measure formulas for the queueing model
-    \item A 3-player game theoretic model between the EMS and two EDs
+    \item A queueing model with two consecutive waiting spaces where one would 
+    serve as a parking space for the ambulances.
+    \item Analytic performance measure formulas for the queueing model.
+    \item A 3-player game theoretic model between the EMS and two EDs.
     \item Numerical experiments showing emergent behaviour of gaming between
@@
 This study explores two new concepts: getting performance measures for a new
-queueing theoretic model with a parking space and a service centre and
+queueing theoretic model with a parking space and a service centre, and
 using a learning algorithm to model the emergence of behaviour.
@@
 To the authors knowledge, no such model of a tandem queueing model with a pair 
-of parameters for the buffer has been considered.
-Although our research is motivated by the particular EMS-ED example, our 
-developed modelling framework and behavioural insights has application to 
-similar systems across a range of sectors and settings.
+of parameters for the buffer has been previously considered.
 

### 2022-04-05 sections/model_overview/methodology/main.tex
Changes after second supervisory review (#45)
* Add changes to response to reviewers

* Fix square in general markov model image

* Add another keyword

* Apply changes to intro and lit review

* Apply changes to queueing mode section

* Apply changes to game theoretic mode section

* Apply changes to conclusion

* Minor changes to appendix

* Compile PDF

@@
 
-The utilities to each player can be represented by 3 matrices; the two payoff 
+The utilities to each player can be represented by 3 matrices: the two payoff 
 matrices of the normal form game and the routing matrix.
@@
 Thus, using equation (\ref{eq:obj_distributor}) for all possible sets of 
-thresholds we can get the full routing matrix that consists of the proportions
+thresholds, we can get the full routing matrix \(R\) (equation
+\ref{eq:routing_matrix})
+that consists of the proportions
 to send to hospital A (\(p_A\)) and to hospital B (\(p_B\)).
@@
 
-Consider Figure \ref{fig:imperfect_info_game} and the flow of the game that was
-described (i.e. \(H_A, H_B \rightarrow D\)).
+Now consider Figure \ref{fig:imperfect_info_game} and the flow of the game that
+was described (i.e. \(H_A, H_B \rightarrow D\)).
 Due to the fact that the payoff matrices \(A\) and \(B\) depend on the routing 

### 2022-04-05 sections/model_overview/numerical_results/main.tex
Changes after second supervisory review (#45)
* Add changes to response to reviewers

* Fix square in general markov model image

* Add another keyword

* Apply changes to intro and lit review

* Apply changes to queueing mode section

* Apply changes to game theoretic mode section

* Apply changes to conclusion

* Minor changes to appendix

* Compile PDF

@@
 the concept of the price of anarchy is used.
-Price of anarchy is a measure that is used to quantify the efficiency of a
-behaviour \cite{roughgarden2005selfish}.
+Price of anarchy (PoA) is a measure that is used to quantify the efficiency of
+a behaviour \cite{roughgarden2005selfish}.
 In other words the price of anarchy is the worst-case equilibria measure and it 
@@
 The learning algorithm reaches a stable pair of 
-strategies where \(T_A = 5\) and \(T_B = 6\). After a number of iterations the
-price of anarchy for both players stabilises and barely increases until the 
-final iteration.
+strategies where \(T_A = 5\) and \(T_B = 6\). 
+Thereafter, the
+price of anarchy for both players stabilises and barely increases.
 
@@
 Figure \ref{fig:ard_lambda_2} shows a similar run of the
-algorithm but when the strategies begin to stabilise an increase in the
-arrival rate of ambulances occurs (i.e \( \lambda_2 = 24 \)).
+algorithm but when the strategies begin to stabilise, an increase in the
+arrival rate of ambulances occurs (i.e. \( \lambda_2 = 24 \)).
 
@@
 due to rational individual behaviour decreases. 
-This is non-sensical though.
+This is non-sensical however.
 What it really shows is that the steep increase in \( \lambda_2 \) leaves 
@@
 \textbf{Incentivising players:}
-From Figures \ref{fig:ard_lambda_2} and \ref{fig:ard_num_of_servers} it can be
-seen that we can change some parameters of the model to make it more efficient.
+From Figures \ref{fig:ard_lambda_2} and \ref{fig:ard_num_of_servers} it is
+observed that we can change some parameters of the model to make it more
+efficient.
 The approach used on Figure \ref{fig:ard_penalty} is slightly different than 
@@
 Once the played strategies in asymmetric replicator dynamics strategies 
-converge the payoff matrices of the two are scaled in such a way so that the 
+converge, the payoff matrices of the two are scaled in such a way so that the 
 utilities of the selected strategy are penalised. This corresponds to a precise

### 2022-04-25 reviews/EJOR/01/Response to Reviewers.tex
Rename some file names

\documentclass{article}

\title{Response to reviewers}
\author{A game theoretic model of the behavioural gaming that takes \\
place at the ED-EMS interface}

\begin{document}
    \maketitle

    The authors would like to thank all the reviewers for their
    constructive feedback and for
    the time they took to review the manuscript.
    Their suggestions were extremely helpful and we believe this has resulted
    in a much improved manuscript.
    Below is a point by point response and summary of changes made, which have
    been grouped together if reviewers provided similar
    suggestions/improvements.

    \line(1, 0){0.92\textwidth}
    \begin{itemize}
        \item Reviewer 1 - Comment 2: \textit{Combine Sections 2 and 5
        together to demonstrate the underlying queueing models and the
        EMS - ED interface counterpart.
        The current arrangement is not easy to follow for finding the right
        explanations for each part of the assumptions adopted in the
        article.}

        \item Reviewer 3 - Comment 1: \textit{Sections 1 and 2 are
        difficult to read.
        It would be better to focus on the main contribution and its
        motivation in Section 1, and to put the literature review in a
        separate Section.}
    \end{itemize}
    The paper has been completely restructured.
    Sections 2 and 5 have been combined and the game theoretic model is now
    presented along with the results in one section.
    In addition, section 1 contains only the introduction while the
    literature review has moved to section 2.
    Finally, the queueing model section now comes before the game theoretic
    section.
    The current structure is: Introduction; Literature Review; A queueing
    model for the ED-EMS interface; Strategic manipulation of the ED-EMS
    interface; Results.
    We thank the reviewers for their suggestions and hope that the major
    restructuring now ensures that the manuscript flows in a much more coherent
    way.

    \line(1, 0){0.92\textwidth}
    \begin{itemize}
        \item Reviewer 3 - Comment 2: \textit{Since the application in mind
        is the EMS-ED interface, it would be better to write the paper
        immediately from this perspective, instead of first abstracting it
        and then applying it to that problem.}
        \item Reviewer 3 - Comment 8: \textit{Figs 7-11: Row player and
        Column Player are unclear: hospital 1 and hospital 2 would be a
        better choice I presume.}
    \end{itemize}
    The paper is presented with the application of the model as the focus.
    All sections are now presented from the perspective of the EMS-ED
    interface.
    In the game theoretic section instead of row/column player we now use
    hospital A and hospital B.

    \line(1, 0){0.92\textwidth}
    \begin{itemize}
        \item Reviewer 1 - Comment 4: \textit{To highlight the contributions
        of this work, it is necessary to compare the novelty of this work
        with previous results in the literature.}
    \end{itemize}
    In the new literature review section we now directly compare the results
    from previous work with the results from this work to highlight the
    contributions of this work.

    \line(1, 0){0.92\textwidth}
    \begin{itemize}
        \item Reviewer 3 - Comment 6: \textit{Figure 3: about solving the
        Markov chain: the Markov chain is truncated to solve it. Therefore,
        probably N and M are not too small. What about the numerical
        complexity? Because if you just solve it, you have to invert the
        matrix? Is there some structure in the Markov chain that can be
        exploited if N and M would be large?}
        \item Reviewer 3 - Comment 7: \textit{Figures 4-6: why do you
        compare your calculated values with simulation?
        Is it to evaluate the truncations?
        Or are you not sure about the formulas?}
    \end{itemize}
    This observation was really helpful and lead to us conducting more numerical
    experiments to clarify the point of truncating the state space.
    As the values of \(N\) and \(M\) increase, the truncated Markov chain
    becomes more complex to solve.
    We have touched upon building a closed-form formula for the steady state
    probabilities but that is still a work in progress and not something we are
    able to include in this manuscript.
    Figures 4-6 are there to demonstrate the accuracy of our constructed
    model against its discrete event simulation equivalent and these have been
    expanded on.
    An additional paragraph is now included that discusses the truncation of
    the model
    and the previous figures have been replaced with ones that compare the
    results from the truncated Markov model with the results from the
    untruncated simulation model.
    We feel that these extra numeric results
    help clarify the paper and are thankful for the reviewer comments.

    \line(1, 0){0.92\textwidth}
    \begin{itemize}
        \item Reviewer 3 - Comment 3: \textit{In section 2, a diagram
        of the full system (including the two queues and the EMS) would
        increase readability.}
    \end{itemize}
    A full system diagram is now added in the game theoretic model section.

    \line(1, 0){0.92\textwidth}
    \begin{itemize}
        \item Reviewer 3 - Comment 9: \textit{Page 22 scenario at bottom of
        the page: this scenario does not seem like a realistic scenario:
        the mean number of patients offered per time unit is larger than
        that can be treated, meaning that many patients would be rejected
        by the hospital. Please comment on the reality of the selected
        scenarios}
    \end{itemize}
    The queueing systems in the particular example are meant to be extremely
    busy systems.
    In the new manuscript this is more clearly stated.

    \line(1, 0){0.92\textwidth}
    \begin{itemize}
        \item Reviewer 3 - Comment 5: \textit{A key modelling assumption is
        that a fraction \(p_A\) of patients is distributed to hospital A.
        Some comments on how realistic this is should be added. Do
        distributers have a choice? Don't they just have to choose the
        nearest hospital? Do they really do it randomly, don' t they take
        into account queues at the hospitals (e.g. join the shortest
        ambulance queue)? what about urgency of patients? I would expect
        patients that come in are prioritized since they are probably more
        urgent.}
    \end{itemize}
    An additional paragraph has been added that touches upon the possibility of
    more complex queueing models where the hospital distance or patient's
    priority type are considered.

    \line(1, 0){0.92\textwidth}
    \begin{itemize}
        \item Reviewer 3 - Comment 4: \textit{The authors claim their model
        has applications in a range of sectors and settings, but have given
        no examples.}
    \end{itemize}
    Examples of other applications have been added in the conclusion section
    of the manuscript.

    \line(1, 0){0.92\textwidth}
    \begin{itemize}
        \item Reviewer 1 - Comment 3: \textit{In the game-theoretic
        formulation and analysis part, it is better to present the
        essential components of a normal-form representation, including the
        players in the game, the strategies available to each player and the
        payoff received by each player for each combination of strategies
        that could be chosen by the players, etc.}
    \end{itemize}
    In the new manuscript the normal form game is explicitly defined in the
    game theoretic section. The players, strategies and payoffs are clearly
    defined.

    \line(1, 0){0.92\textwidth}
    \begin{itemize}
        \item Reviewer 1 - Comment 1: \textit{Rewrite the Highlights (for
        review) of the paper, and really capture the sense of work.}
    \end{itemize}
    Highlights have been rewritten to be more explicit in terms of the work
    that was done.

    \line(1, 0){0.92\textwidth}
    \begin{itemize}
        \item Reviewer 1 - Comment 5: \textit{There are some mistakes/typos
        with English grammar and writing in the article.}
    \end{itemize}
    We have thoroughly checked the grammar and spelling of the manuscript.

\end{document}

### 2022-04-25 sections/model_overview/main.tex
Address all reviewers comments (#31)
* Prepare for addressing reviewers comments (#18)

* Add comments of reviewers

`main.md` consists of the comments of all three reviewers and the editor

* Include editor's comments

* Change vocabulary to be more focused on the application (#33)

* Change vocabulary in game section

* Minor typo

Fix proselint failure by removing the word very from a comment

* Change vocabulary in methodology section

* Additional changes in game section

- Replace waiting zone 1 with hospital
- Replace waiting zone 2 with parking space
- Use type 2 patients everywhere in

@@
 The strategies of the two EDs are the range of thresholds that they can choose
-from and their utilities is the proportion of individuals whose time in the 
+from and their utilities are the proportions of individuals whose time in the 
 system is within a predetermined target time.
@@
 ambulances, that are sent from the
-ambulance service, stay until their patients are allowed to enter the hospital.
+EMS distributor, stay until their patients are allowed to enter the hospital.
 The parking space has a capacity of \(M\) and no servers.
@@
 Here, \(\alpha\) represents the ``importance'' of each objective,
-where high \(\alpha\) indicates a higher weight on the proportion of lost 
-individuals and smaller \(\alpha\) a higher weight on the time blocked. 
+where a high \(\alpha\) indicates a higher weight on the proportion of lost 
+individuals and a smaller \(\alpha\) a higher weight on the time blocked. 
 The choice of \(p_A\) and \(p_B\) rely solely on equation
@@
 players~\cite{Berwanger2008}. In this study the state of the problem that is
-hidden is the threshold that each of the hospitals chooses to play.
+hidden is the threshold that each hospital ED chooses to play.
 In other words, each hospital chooses to play a strategy without 

### 2022-04-25 sections/queueing_model/blocking_time/main.tex
Address several TODOs (#41)
* Update highlights

* Address several todos

* Add a final TODO to be fixed

* Add example of another application of the model

* Fix a typo

* Add script and notebook of previous plots

* Rename jupyter notebook

* Change plots axis labels

* Scale payoff matrices to be more presentable

* Remove unnecessary equations

* Minor additional changes

* Address the high traffic intensity
Address all reviewers comments (#31)
* Prepare for addressing reviewers comments (#18)

* Add comments of reviewers

`main.md` consists of the comments of all three reviewers and the e

@@
 
-% TODO: Possibly replace the contents of this section with the ones for the 
-% closed form formula of the blocking time
-% Currently the direct approach one is shown
-
 Blocking time is the amount of time that type 2 patients wait in the parking 
-space before they are allowed to proceed to the hospital.
+space before they are allowed to proceed into the hospital.
 Unlike the waiting time, the blocking time is only calculated for type 2 
@@
 the constructed queueing model as well as the effect of truncating the model.
-The simulation was ran 100 times and the recorded mean blocking time at each 
+The simulation was run 100 times and the recorded mean blocking time at each 
 iteration is used to populate the violin plots.

### 2022-04-25 sections/queueing_model/main.tex
Investigate the truncation effect (#34)
* Get initial plots of truncation effects

Plots added on unbounded simulation VS Markov chain (while
increasing capacity):
- Waiting time
- Blocking time
- Proportion of individuals within time

* Add bounded simulation to same plot

* Write script to generate duration for each method

* Get timing data when M=50

Times for N = (10, 30, 50, inf) for markov (waiting, blocking and
proportion formula) and simulation (1 trial, 20 trials)

* Get timing data when M=5

Times for N = (10, 30, 50, inf) for markov (waiting, blocking and
proportion formula) and si

@@
 figure \ref{fig:diagram_of_queueing_system} will be given.
-This is a queueing model that consists of two waiting zones; the parking space
+This is a queueing model that consists of two waiting zones: the parking space
 and the hospital waiting space.
@@
 Type 2 individuals arrive at the parking space and wait there until they are 
-allowed to move to the hospital.
+allowed to move into the hospital.
 They are allowed to proceed only when the number of 
@@
 \input{sections/queueing_model/proportion_within_target/main.tex}
+
+\input{sections/queueing_model/truncation_effect/main.tex}

### 2022-04-25 imgs/asymmetric_rd/main.py

@@ -45,14 +45,14 @@ plt.subplot(1, 2, 1)
 plt.plot(xs)
 plt.xlabel("Timepoints")
 plt.ylabel("Probability")
-plt.title("Row player")
+plt.title("Hospital A")
 plt.legend([f"$s_{{{i + 1}}}$" for i in range(len(xs[0]))])
 
 plt.subplot(1, 2, 2)
 plt.plot(ys)
 plt.xlabel("Timepoints")
 plt.ylabel("Probability")
-plt.title("Column player")
+plt.title("Hospital B")
 plt.legend([f"$s_{{{i + 1}}}$" for i in range(len(ys[0]))])
 
-plt.savefig("asymmetric_rd.png", transparent=True)
+plt.savefig("asymmetric_rd_2.png", transparent=True)

### 2022-04-25 imgs/asymmetric_rd_and_PoA/main.py

@@ -1,0 +1,829 @@
+import csv
+import itertools
+import os
+import pathlib
+
+import matplotlib.colors as mcolors
+import matplotlib.pyplot as plt
+import nashpy as nash
+import numpy as np
+import pandas as pd
+
+import ambulance_game as abg
+
+# from nashpy.algorithms.lemke_howson_lex import lemke_howson_lex
+
+
+def get_index_of_values(problem_parameters, data, atol=1e-08, rtol=1e-05):
+    """
+    Get the indices of the rows that match the given parameters' values
+    """
+    index = data.index
+    condition = (
+        np.isclose(
+            data["lambda_2"], problem_parameters["lambda_2"], atol=atol, rtol=rtol
+        )
+        & np.isclose(
+            data["lambda_1_1"], problem_parameters["lambda_1_1"], atol=atol, rtol=rtol
+        )
+        & np.isclose(
+            data["lambda_1_2"], problem_parameters["lambda_1_2"], atol=atol, rtol=rtol
+        )
+        & np.isclose(data["mu_1"], problem_parameters["mu_1"], atol=atol, rtol=rtol)
+        & np.isclose(data["mu_2"], problem_parameters["mu_2"], atol=atol, rtol=rtol)
+        & np.isclose(data["num_of_servers_1"], problem_parameters["num_of_servers_1"])
+        & np.isclose(data["num_of_servers_2"], problem_parameters["num_of_servers_2"])
+        & np.isclose(data["system_capacity_1"], problem_parameters["system_capacity_1"])
+        & np.isclose(data["system_capacity_2"], problem_parameters["system_capacity_2"])
+        & np.isclose(data["buffer_capacity_1"], problem_parameters["buffer_capacity_1"])
+        & np.isclose(data["buffer_capacity_2"], problem_parameters["buffer_capacity_2"])
+        & np.isclose(data["alpha"], problem_parameters["alpha"])
+        & np.isclose(data["target"], problem_parameters["target"], atol=atol, rtol=rtol)
+    )
+    indices = index[condition]
+    return indices
+
+
+def create_directory_with_notebook(data, index_value):
+    """
+    Create the directory with main.ipynb that contains a brief analysis for that scenario
+    """
+    hash_value = data[index_value : index_value + 1]["hash_value"]
+    dirname = hash_value.to_string(index=False)[1:]
+    new_dir = pathlib.Path() / dirname
+    new_dir.mkdir(exist_ok=True)
[…]

### 2022-04-25 known.py

@@ -3,6 +3,7 @@
 words = {
     "Abacws",
     "abg",
+    "affine",
     "alsoletter",
     "apalike",
     "automata",
@@ -14,14 +15,17 @@ words = {
     "breaklines",
     "calc",
     "captionpos",
+    "ccc",
     "CDF",
     "CDFs",
+    "center",
     "ciw's",
     "Ciw's",
     "Ciw",
     "codegreen",
     "commentstyle",
     "DES",
+    "distributers",
     "dt",
     "dx",
     "dy",
@@ -59,6 +63,7 @@ words = {
     "polytope",
     "polytopes",
     "pre",
+    "prioritized",
     "probs",
     "pystyle",
     "queueing",
@@ -72,5 +77,8 @@ words = {
     "stochasticity",
     "terminalstyle",
     "th",
+    "truncations",
+    "unobservable",
+    "untruncated",
     "Zx",
 }

### 2022-04-25 tasks.py

@@ -70,12 +70,20 @@ def proselint(c):
                 updated_errors.append(error)
         return updated_errors
 
+    def clean_text(text):
+        """
+        Remove latex commands from text
+        """
+        cleaned_text = text.replace("\centering", "")
+        return cleaned_text
+
     all_tex_files = list(pathlib.Path().glob("**/*.tex"))
     exit_codes = [0]
     for path in all_tex_files:
         with open(path, "r") as f:
             text = f.read()
-            errors = plnt.tools.lint(text)
+            cleaned_text = clean_text(text)
+            errors = plnt.tools.lint(cleaned_text)
         errors = remove_expected_errors(errors)
         if errors:
             print(f"In {path} the following errors were found: ")

### 2022-06-23 sections/literature_review/main.tex
Add suggested references in lit review

@@
 low for systems with insufficient capacities.
+In~\cite{TwoTierHealthcareSystem} a two-tier healthcare system with a capacity
+constrained is studied where patients can choose between two systems to receive
+their service.
+The first system is labelled as the free system (public government-funded
+hospital) which offers service without seeking any profit and the second one is
+the toll system (private hospital) that aims to maximise its own profit.
+The authors, also compare the two-tier system with its one-tier equivalent,
+where only the free system exists.
 In~\cite{knight2017measuring} a normal form game is built that is informed by a 
@@
 care units.
+In~\cite{EfficiencyQualityTradeOff} a queueing-game-theoretical model is
+introduced where there are two types of service providers; a high quality
+highly-congested hospital and a low quality low-congested hospital.
+The authors study a two-stage Stackelberg game where the government is the
+\textit{leader} and the arriving patients are the \textit{followers}.
 In~\cite{deo2011centralized} the authors study the network effect of ambulance 

### 2022-06-23 known.py
Update known words

@@ -74,6 +74,7 @@ words = {
     "Senghennydd",
     "sensical",
     "societally",
+    "Stackelberg",
     "stochasticity",
     "terminalstyle",
     "th",

### 2022-06-28 reviews/EJOR/02/ResponsetoReviewers.tex
Add response to reviewers

\documentclass{article}

\title{Response to reviewers}
\author{A game theoretic model of the behavioural gaming that takes \\
place at the ED-EMS interface}

\begin{document}
    \maketitle

    The authors would like to thank once again all the reviewers for their
    constructive feedback and for
    the time they took to review the manuscript.
    Please find the summary of the changes made:

    \line(1, 0){0.92\textwidth}
    \begin{itemize}
        \item Reviewer 1: \textit{The following two papers are related to the
        current work and I suggest the authors add them in the references with
        citations in the literature review: \\
        1. Chen, W., Z. G. Zhang, and X. Chen. 2020. "On Two-tier Healthcare
        System Under Capacity Constraint." International Journal of Production
        Research 58 (12): 3744-3764. \\
        2. Wang, J., Z. Wang, Z. G. Zhang and F. Wang. 2021.
        ``Efficiency-quality trade-off in allocating resource to public
        healthcare systems.'' International Journal of Production Research, \\
        DOI:10.1080/00207543.2021.1992529}
    \end{itemize}

    These two papers are now cited in the manuscript at the literature review
    section.

    \line(1, 0){0.92\textwidth}
    \begin{itemize}
        \item Reviewer 2: I gave a look into the new version and the comments
        made by the authors following the reviews they received.
        My criticism towards the paper as stated in the first round stays.
        It is basically the question of what are the standards of EJOR.
        If a paper which states a interesting model and gives details on
        numerical procedures for solving it but without any theorems and
        insights is good enough, then it should be accepted as the paper is
        doing a good job of what it promises.
        Otherwise, they should look for a more applied journal where what they
        do is sufficient.
    \end{itemize}

    Here's a list of reasons of why I think this paper should be considered for
    publication in EJOR.
    Firstly, reviewer 2 states that the paper does not provide any insights.
    We would like to point out that this paper does provide theoretical results
    and insights.
    Section 3 provides detailed theoretical expressions of the queueing model's
    performance measures.
    Expressions of the waiting time, blocking time and proportion of
    individuals within target have been derived and are presented in the paper.
    Also, section 4.2 contains a list of applied scenarios where insights 
    are presented.
    A busy model is examined and insights on ways to increase the relative
    efficiency of the model are presented.

    Secondly here is a list of papers already published in EJOR that introduce
    a new model and give details on numerical procedures for solving it but
    without any new theorems:
    \begin{itemize}
        \item A queueing model for general group screening policies and dynamic
        item arrivals \\
        https://doi.org/10.1016/j.ejor.2010.05.042
        \item Selfish routing in public services: \\
        https://doi.org/10.1016/j.ejor.2013.04.003
        \item The effect of ambulance relocations on the performance of
        ambulance service providers \\
        https://doi.org/10.1016/j.ejor.2015.12.022
        \item Robust and stochastic formulations for ambulance deployment and
        dispatch \\
        https://doi.org/10.1016/j.ejor.2019.05.011
        \item A Markovian queueing model for ambulance offload delays \\
        https://doi.org/10.1016/j.ejor.2012.11.030
        \item Models and algorithms for an integrated vessel scheduling and tug
        assignment problem within a canal harbor \\
        https://doi.org/10.1016/j.ejor.2021.10.037
        \item The application of operational research to European air traffic
        flow management - understanding the context \\
        https://doi.org/10.1016/S0377-2217(99)00084-3
    \end{itemize}

    Finally, note that the aims and scope of EJOR do not emphasise that a paper
    should present a new theorem in order to be published.
    Here's the aim and scope of EJOR as listed in their website: \\[0.5cm]
    \textit{
        The European Journal of Operational Research (EJOR) publishes high
        quality, original papers that contribute to the methodology of operational
        research (OR) and to the practice of decision making. EJOR contains the
        following types of papers:
        \begin{itemize}
            \item Invited Reviews, explaining to the general OR audience the developments in an OR topic over the recent years
            \item Innovative Applications of OR, describing novel ways to solve real problems
            \item Theory and Methodology Papers, presenting original research results contributing to the methodology of OR and to its theoretical foundations,
            \item Short Communications, if they correct important errors found in papers previously published in EJOR
        \end{itemize}
    }

\end{document}

### 2022-06-28 reviews/EJOR/02/ResponsetoReviewers.tex
Apply suggestions from code review
Co-authored-by: Vince Knight <vince@vknight.org>

@@
     the time they took to review the manuscript.
-    Please find the summary of the changes made:
+    We are also pleased to see that the reviewers feel that the revision has addressed their comments and that the manuscript presents scientifically correct and useful results.
+    We have made the remaining requested minor changes and also provide a response to one of the 
+    reviewers whose remaining concern is about the fit of this paper for EJOR.
 
@@
 
-    Here's a list of reasons of why I think this paper should be considered for
-    publication in EJOR.
-    Firstly, reviewer 2 states that the paper does not provide any insights.
-    We would like to point out that this paper does provide theoretical results
+    We are grateful for the opportunity to respond to this as it seems that the 
+    remaining concern is the fit of this work in EJOR and not the work itself.
+    Firstly, this paper does provide theoretical results
     and insights.
@@
 
-    Secondly here is a list of papers already published in EJOR that introduce
-    a new model and give details on numerical procedures for solving it but
-    without any new theorems:
+    We do understand the main point being raised by the reviewer in that this paper is not a purely theoretic one.
+    For the benefits of the handling editor who we believe is left with the decision of whether or not the paper is in the scope of EJOR, here is a list of a number of papers published in EJOR that have a similar applied emphasis:
     \begin{itemize}

### 2022-06-28 reviews/EJOR/02/ResponsetoReviewers.tex
Further minor changes
- Add main arguments for publishing our paper to editor
- Include authors, date published and Volume/issue on previous papers
- Add response to reviewer 3
- Minor rewords

@@
 \documentclass{article}
+
+\usepackage{amssymb}
 
@@
     the time they took to review the manuscript.
-    We are also pleased to see that the reviewers feel that the revision has addressed their comments and that the manuscript presents scientifically correct and useful results.
-    We have made the remaining requested minor changes and also provide a response to one of the 
-    reviewers whose remaining concern is about the fit of this paper for EJOR.
+    We are also pleased to see that the reviewers feel that the revision has
+    addressed their comments and that the manuscript presents scientifically
+    correct and useful results.
+    We have made the remaining requested minor changes and also provide a
+    response to one of the reviewers whose remaining concern is about the fit
+    of this paper for EJOR.
+    Our main arguments are:
+    \begin{itemize}
+        \item Our paper provides theoretical results and insights
+        \item There is a number of pages in EJOR that are similar to ours
+        \item The EJOR scope does not emphasise that a paper should present a
+        new theorem in order to be published
+    \end{itemize}
 
@@
 
-    These two papers are now cited in the manuscript at the literature review
+    These two papers are now discussed and included in the literature review
     section.
@@
 
-    We do understand the main point being raised by the reviewer in that this paper is not a purely theoretic one.
-    For the benefits of the handling editor who we believe is left with the decision of whether or not the paper is in the scope of EJOR, here is a list of a number of papers published in EJOR that have a similar applied emphasis:
+    We do understand the main point being raised by the reviewer in that this
+    paper is not a purely theoretic one.
+    For the benefits of the handling editor who we believe is left with the
+    decision of whether or not the paper is in the scope of EJOR, here is a
+    list of examples of papers published in EJOR that have a similar applied
+    emphasis:
     \begin{itemize}
-        \item A queueing model for general group screening policies and dynamic
-        item arrivals \\
+        \item[$\rhd$] \textbf{A queueing model for general group screening
+        policies and dynamic item arrivals} published in 2010, Volume 207,
+        Issue 2, by Dieter Claeys, Joris Walraevens, Koenraad Laevens and
+        Herwig Bruneel \\
         https://doi.org/10.1016/j.ejor.2010.05.042
-        \item Selfish routing in public services: \\
+        \item[$\rhd$] \textbf{Selfish routing in public services} published in
+        2013, Volume 230, Issue 1, by Vincent A.Knight and Paul R. Harper \\
         https://doi.org/10.1016/j.ejor.2013.04.003
-        \item The effect of ambulance relocations on the performance of
-        ambulance service providers \\
+        \item[$\rhd$] \textbf{The effect of ambulance relocations on the
+        performance of ambulance service providers} published in 2016, Volume
+        252, Issue 1, by T. C. van Barneveld, S. Bhulai and R.D.van der Mei \\
         https://doi.org/10.1016/j.ejor.2015.12.022
-        \item Robust and stochastic formulations for ambulance deployment and
-        dispatch \\
+        \item[$\rhd$] \textbf{Robust and stochastic formulations for ambulance
+        deployment and dispatch} published in 2019, Volume 279, Issue 2, by
+        Dimitris Bertsimas and Yeesian Ng \\
         https://doi.org/10.1016/j.ejor.2019.05.011
-        \item A Markovian queueing model for ambulance offload delays \\
+        \item[$\rhd$] \textbf{A Markovian queueing model for ambulance offload
+        delays} published in 2013, Volume 226, Issue 3, by Eman Almehdawe, Beth
+        Jewkes and Qi-Ming He \\
         https://doi.org/10.1016/j.ejor.2012.11.030
-        \item Models and algorithms for an integrated vessel scheduling and tug
-        assignment problem within a canal harbor \\
+        \item[$\rhd$] \textbf{Models and algorithms for an integrated vessel
+        scheduling and tug assignment problem within a canal harbor} published
+        in 2022, Volume 300, Issue 3, by Matteo Petris, Paola Pellegrini and
+        Raffaele Pesenti \\
         https://doi.org/10.1016/j.ejor.2021.10.037
-        \item The application of operational research to European air traffic
-        flow management - understanding the context \\
+        \item[$\rhd$] \textbf{The application of operational research to
+        European air traffic flow management - understanding the context}
+        published in 2000, Volume 123, Issue 1, by Paula Leal de Matos and
+        Richard Ormerod \\
         https://doi.org/10.1016/S0377-2217(99)00084-3
@@
 
-    Finally, note that the aims and scope of EJOR do not emphasise that a paper
+    Finally, we note that the aims and scope of EJOR do not emphasise that a paper
     should present a new theorem in order to be published.
@@
         \begin{itemize}
-            \item Invited Reviews, explaining to the general OR audience the developments in an OR topic over the recent years
-            \item Innovative Applications of OR, describing novel ways to solve real problems
-            \item Theory and Methodology Papers, presenting original research results contributing to the methodology of OR and to its theoretical foundations,
-            \item Short Communications, if they correct important errors found in papers previously published in EJOR
+            \item[$\square$] Invited Reviews, explaining to the general OR audience the developments in an OR topic over the recent years
+            \item[$\square$] Innovative Applications of OR, describing novel ways to solve real problems
+            \item[$\square$] Theory and Methodology Papers, presenting original research results contributing to the methodology of OR and to its theoretical foundations,
+            \item[$\square$] Short Communications, if they correct important errors found in papers previously published in EJOR
         \end{itemize}
@@
 
+    \line(1, 0){0.92\textwidth}
+    \begin{itemize}
+        \item Reviewer 3: \textit{The authors handled my remarks well.}
+    \end{itemize}
+    Thank you.
+
 \end{document}

### 2022-06-28 known.py
Update known words

@@ -4,6 +4,7 @@ words = {
     "Abacws",
     "abg",
     "affine",
+    "Almehdawe",
     "alsoletter",
     "apalike",
     "automata",
@@ -12,7 +13,9 @@ words = {
     "backcolor",
     "backgroundcolor",
     "basicstyle",
+    "Bhulai",
     "breaklines",
+    "Bruneel",
     "calc",
     "captionpos",
     "ccc",
@@ -22,6 +25,7 @@ words = {
     "ciw's",
     "Ciw's",
     "Ciw",
+    "Claeys",
     "codegreen",
     "commentstyle",
     "DES",
@@ -31,8 +35,11 @@ words = {
     "dy",
     "ED's",
     "EDs",
+    "EJOR",
+    "Eman",
     "equilibria",
     "erlang",
+    "harbor",
     "HB",
     "Howson",
     "hypoexponential",
@@ -41,9 +48,12 @@ words = {
     "incentivisation",
     "incentivised",
     "incentivising",
+    "Jewkes",
     "keepspaces",
     "keywordcolor",
     "keywordstyle",
+    "Koenraad",
+    "Laevens",
     "Lemke",
     "LHS",
     "Markovian",
@@ -59,6 +69,8 @@ words = {
     "num",
     "numpy",
     "Panayides",
+    "Pesenti",
+    "Petris",
     "PoA",
     "polytope",
     "polytopes",
@@ -67,6 +79,7 @@ words = {
     "probs",
     "pystyle",
     "queueing",
+    "relocations",
     "rgb",
     "RGB",
     "RHS",
@@ -81,5 +94,8 @@ words = {
     "truncations",
     "unobservable",
     "untruncated",
+    "Walraevens",
+    "Yeesian",
+    "Zhang",
     "Zx",
 }

### 2022-06-28 known.py
Update known words again

@@ -12,7 +12,9 @@ words = {
     "Ay",
     "backcolor",
     "backgroundcolor",
+    "Barneveld",
     "basicstyle",
+    "Bertsimas",
     "Bhulai",
     "breaklines",
     "Bruneel",
@@ -28,7 +30,10 @@ words = {
     "Claeys",
     "codegreen",
     "commentstyle",
+    "de",
+    "der",
     "DES",
+    "Dimitris",
     "distributers",
     "dt",
     "dx",
@@ -41,6 +46,7 @@ words = {
     "erlang",
     "harbor",
     "HB",
+    "Herwig",
     "Howson",
     "hypoexponential",
     "ieeetr",
@@ -49,26 +55,35 @@ words = {
     "incentivised",
     "incentivising",
     "Jewkes",
+    "Joris",
     "keepspaces",
     "keywordcolor",
     "keywordstyle",
     "Koenraad",
     "Laevens",
+    "Leal",
     "Lemke",
     "LHS",
     "Markovian",
     "math",
+    "Matos",
+    "Matteo",
+    "Mei",
     "memoryless",
     "Michalis",
     "mult",
     "nan",
     "nansum",
     "nashpy",
+    "Ng",
     "NHS",
     "np",
     "num",
     "numpy",
+    "Ormerod",
     "Panayides",
+    "Paola",
+    "Pellegrini",
     "Pesenti",
     "Petris",
     "PoA",
@@ -78,7 +93,9 @@ words = {
     "prioritized",
     "probs",
     "pystyle",
+    "Qi",
     "queueing",
+    "Raffaele",
     "relocations",
     "rgb",
     "RGB",

### 2022-07-01 sections/literature_review/main.tex
Address all reviewers comments from second revision (#46)
* Add editor and reviewers comments

* Add suggested references in lit review

* Update known words

* Apply suggestion by proselint

* Add response to reviewers

* Apply suggestions from code review

Co-authored-by: Vince Knight <vince@vknight.org>

* Further minor changes

- Add main arguments for publishing our paper to editor
- Include authors, date published and Volume/issue on previous papers
- Add response to reviewer 3
- Minor rewords

* Update known words

* Update known words again

* Fix minor typo

Co-authored-by: Vince Knig

@@
 introduced where there are two types of service providers; a high quality
-highly-congested hospital and a low quality low-congested hospital.
+high-congested hospital and a low quality low-congested hospital.
 The authors study a two-stage Stackelberg game where the government is the

### 2022-07-01 known.py

@@ -4,6 +4,7 @@ words = {
     "Abacws",
     "abg",
     "affine",
+    "Almehdawe",
     "alsoletter",
     "apalike",
     "automata",
@@ -11,8 +12,12 @@ words = {
     "Ay",
     "backcolor",
     "backgroundcolor",
+    "Barneveld",
     "basicstyle",
+    "Bertsimas",
+    "Bhulai",
     "breaklines",
+    "Bruneel",
     "calc",
     "captionpos",
     "ccc",
@@ -22,18 +27,26 @@ words = {
     "ciw's",
     "Ciw's",
     "Ciw",
+    "Claeys",
     "codegreen",
     "commentstyle",
+    "de",
+    "der",
     "DES",
+    "Dimitris",
     "distributers",
     "dt",
     "dx",
     "dy",
     "ED's",
     "EDs",
+    "EJOR",
+    "Eman",
     "equilibria",
     "erlang",
+    "harbor",
     "HB",
+    "Herwig",
     "Howson",
     "hypoexponential",
     "ieeetr",
@@ -41,24 +54,38 @@ words = {
     "incentivisation",
     "incentivised",
     "incentivising",
+    "Jewkes",
+    "Joris",
     "keepspaces",
     "keywordcolor",
     "keywordstyle",
+    "Koenraad",
+    "Laevens",
+    "Leal",
     "Lemke",
     "LHS",
     "Markovian",
     "math",
+    "Matos",
+    "Matteo",
+    "Mei",
     "memoryless",
     "Michalis",
     "mult",
     "nan",
     "nansum",
     "nashpy",
+    "Ng",
     "NHS",
     "np",
     "num",
     "numpy",
+    "Ormerod",
     "Panayides",
+    "Paola",
+    "Pellegrini",
+    "Pesenti",
+    "Petris",
     "PoA",
     "polytope",
     "polytopes",
@@ -66,7 +93,10 @@ words = {
     "prioritized",
     "probs",
     "pystyle",
+    "Qi",
     "queueing",
+    "Raffaele",
+    "relocations",
     "rgb",
     "RGB",
     "RHS",
@@ -74,11 +104,15 @@ words = {
     "Senghennydd",
     "sensical",
     "societally",
+    "Stackelberg",
     "stochasticity",
     "terminalstyle",
     "th",
     "truncations",
     "unobservable",
     "untruncated",
+    "Walraevens",
+    "Yeesian",
+    "Zhang",
     "Zx",
 }
